---
title: "Bias Correction USJ"
author: "Gustavo Facincani Dourado"
date: "9/17/2020"
output: html_document
---

The Big Creek system is composed of subbasins 31-38, which discharge into Mammoth Pool Reservoir (subbasin 21), together with subbasins 22 and 23 (both gauged). Subbasins 32-35 have a very poor record of USGS gauge data. There are many mismatches on the time that the gauges in the region present historical records. So, here we're collecting data as of an uncontrolled system, according to the data available for each subbasin, to bias correct the Livneh data for these regions per subbasin individually, as the VIC runoff is not well represented in this part of the Upper San Joaquin river system.


```{r}
library(readr)
library(tidyverse)
library(hyfo)
library(lubridate)
```

```{r}
#Reading Livneh data, that is going to be used for bias correction and filtering them to have objects with the same length of the observed data, to be used as the simulated vs observed
path <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/hydrology/historical/Livneh/runoff/"

Sub20_Livneh <- read_csv(paste(path,"tot_runoff_sb20_mcm.csv",sep="")) %>% #below Mammoth Pool
   filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31")))

Sub21_Livneh <- read_csv(paste(path,"tot_runoff_sb21_mcm.csv",sep="")) %>%
  rename(Inflow = tot_runoff_sb21)

Sub21_PreBC <- Sub21_Livneh%>% #Mammoth Pool
   filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31")))


Sub22_Livneh <- read_csv(paste(path,"tot_runoff_sb22_mcm.csv",sep="")) %>%
  rename(Inflow = tot_runoff_sb22)
Sub22_PreBC <- Sub22_Livneh %>% #Granite Creek
   filter(between(Date, as.Date("1965-10-01"), as.Date("1986-09-29")))

Sub23_Livneh <- read_csv(paste(path,"tot_runoff_sb23_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb23)
Sub23_PreBC <- Sub23_Livneh%>% #San Joaquin River
    filter(between(Date, as.Date("1951-10-01"), as.Date("1991-09-29")))


Sub31_Livneh <- read_csv(paste(path,"tot_runoff_sb31_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb31) 
Sub31_PreBC <-  Sub31_Livneh %>% #Thomas Edison Lake
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31")))


Sub36_Livneh <- read_csv(paste(path,"tot_runoff_sb36_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb36)
Sub36_PreBC <- Sub36_Livneh %>% #Bear Creek
   filter(between(Date, as.Date("1975-10-01"), as.Date("1986-09-29")))

Sub37_Livneh <- read_csv(paste(path,"tot_runoff_sb37_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb37)
Sub37_PreBC <-  Sub37_Livneh %>% #SF San Joaquin River
  filter(between(Date, as.Date("2009-10-01"), as.Date("2013-12-31")))


Sub38_Livneh <- read_csv(paste(path,"tot_runoff_sb38_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb38)
Sub38_PreBC <- Sub38_Livneh %>% #Florence Lake
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29")))


```

```{r}
#Read the gauge data for the same period of the data we have for Livneh
USJpath <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/"

#Subbasins 21, 31 and 38 have Florence Lake, Thomas A. Edison Lake and Mammoth Pool Reservoir respectively
Reservoir_stor <- read_csv(paste0(USJpath, "gauges/storage_mcm.csv", sep = ""), col_types = cols(Date = col_date(), .default = col_double()))#%>% #reading data column as data, others as numeric
#filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31"))) #selecting period of available gauged data
Reservoir_stor[2:10] <- (Reservoir_stor[2:10])*810.7131821 #transform mcm/day to ACF/day
Reservoir_stor
#The other subbasins only streamflow
Reservoir_flow <- read_csv(paste0(USJpath, "gauges/streamflow_cfs.csv", sep = ""), col_types = cols(Date = col_date(), .default = col_double()))#%>% #reading data column as data, others as numeric
#filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31"))) #selecting period of available gauged data

Reservoir_flow[2:50] <- (Reservoir_flow[2:50]*86400)/43560 #transform cfs to ACF/day
                         #/35.314666)*86400/1000000 #as reservoir data is in million cubic meters (mcm), let's convert cfs to mcm
Reservoir_flow
```

```{r}
#Water balance of reservoirs to determine inflows
#Subbasin 38 - Florence
Florence_outflow <- Reservoir_flow[c(1,3,4)] %>% #gauges 11229500 and USGS 11230000, outflow of Florence
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29")))

Sub38 <- Reservoir_stor[c(1,8)] %>% #selecting gauge with storage data
filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29"))) %>%
   mutate(ChangeStorage = `USGS 11229600 FLORENCE LK NR BIG C CA` - lag(`USGS 11229600 FLORENCE LK NR BIG C CA`, default = first(`USGS 11229600 FLORENCE LK NR BIG C CA`)), #getting daily change in storage
          Outflow = rowSums(Florence_outflow[2:3], na.rm=T), #sum of USGS 11229500 and USGS 11230000, which correspond to flow below the reservoir and Ward Tunnel intake, respectively 
          flow = ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) %>% #getting inflow, in which inflow = change in storage (storage of the day minus the storage of the previous day + outflow of the day
           select(Date, flow)#remove the already used column 
Sub38

#Subbasins 31 - Thomas Edison
Thomas_outflow <- Reservoir_flow[c(1,14)] %>%
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31")))

Sub31 <- Reservoir_stor[c(1,6)] %>% #selecting gauge with storage data
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31"))) %>%
   mutate(ChangeStorage = `USGS 11231000 LK THOMAS A. EDISON NR BIG C CA` - lag(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`, default = first(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`)), #getting daily change in storage
          Outflow = Thomas_outflow$`USGS 11231500 MONO C BL LK THOMAS A EDISON CA`, #getting outflow
          flow = ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) %>% 
           select(Date, flow)#remove the already used column 
Sub31

#Subbasin 21 - Mammoth Pool Reservoir
#Mammoth_outflow <- Reservoir_flow[c(1,17,18)] %>%
#   filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31")))

#Sub21 <- Reservoir_stor[c(1,10)] %>% #selecting gauge below Thomas Edison
#    filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31"))) %>%
#  replace(is.na(Reservoir_flow$`USGS 11234760 SAN JOAQUIN R AB SHAKEFLAT C NR BIG CREEK CA`), 0) %>%
#   mutate(ChangeStorage = `USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA` - lag(`USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA`, default = first(`USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA`)), #getting change in storage
#          PH_Flow = Mammoth_outflow$`USGS 11235100 MAMMOTH POOL PP NR BIG CREEK CA`, 
#          Below_Reservoir = Mammoth_outflow$`USGS 11234760 SAN JOAQUIN R AB SHAKEFLAT C NR BIG CREEK CA`,
#          Sub20 = Sub20_Livneh$tot_runoff_sb20) %>% #getting outflow, summing up the flow below the reservoir, flow to the PH and I'm subtracting the contribution from Subbasin 20, as it is below the reservoir, before the gauge
#          mutate(Inflow = rowSums(na.omit(.[3:5])) - Sub20) %>% #here I'm subtracting the contribution of Sub20, which is a small area below the dam, above the USGS gauge, and omitting NAs as we have 2 years of missing data in the record
#           select(Date, Inflow) #remove the already used column  
#Sub21
```


```{r}
#Subbasin 22
Sub22 <- Reservoir_flow[c(1,3)] %>% #Granite Creek
   filter(between(Date, as.Date("1965-10-01"), as.Date("1986-09-29"))) %>%
  rename(flow = 2)
Sub22

#Subbasin 23
Sub23 <- Reservoir_flow[c(1,2)]%>% #San Joaquin River
    filter(between(Date, as.Date("1951-10-01"), as.Date("1991-09-29")))%>%
  rename(flow = 2)
Sub23

#Subbasin 36
Sub36 <- Reservoir_flow[c(1,8)]%>% #Bear Creek
   filter(between(Date, as.Date("1975-10-01"), as.Date("1986-09-29")))%>%
  rename(flow = 2)
Sub36

#Subbasin 37 
#If we consider these gauges, around 24% of the days will have negative values

#Sub37 <- Reservoir_flow[c(1,5,7)] %>% #SF San Joaquin, with inflow from Florence Lake
#   filter(between(Date, as.Date("1975-10-01"), as.Date("1980-09-29"))) %>%
#  mutate(Inflow = (`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230000 SF SAN JOAQUIN R NR FLORENCE LK CA`)) 
#Sub37

#Considering this slightly shorter record, we only have 4 days with negative flow
Sub37 <- Reservoir_flow[c(1,6,7)] %>% #SF San Joaquin, with inflow from Florence Lake
   filter(between(Date, as.Date("2009-10-01"), as.Date("2013-12-31"))) %>%
  mutate(flow = ifelse((`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230070 SF SAN JOAQUIN R AB HOOPER C NR FLORENCE LAKE CA`) < 0,0, (`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230070 SF SAN JOAQUIN R AB HOOPER C NR FLORENCE LAKE CA`)))%>%
           select(Date, flow)#remove the already used column 
Sub37

#PortalPH <- Reservoir_flow[17] #Portal is ignored by now, as "The water delivered to Huntington Lake may also pass through Portal Powerhouse at the exit of the Ward Tunnel depending upon the amount of water being transported. Page 71 https://www.sce.com/sites/default/files/inline-files/p120bc3_initialstatement_and_exhibitsad_and_h.pdf
#PortalPH
```


```{r}

path <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/USJR/SubCatchment_RO_BC"

Make_Figures <- function(Observed, Simulated, Subbasin, StartDate, EndDate, Area){
Area <- "Florence Lake" 
Observed <- Sub38 
Simulated<-  Sub38_PreBC
Subbasin <- "sb38"
StartDate <- "1950-01-01"
EndDate <- "1980-09-29"

Pre_BC <- Simulated %>% #getting the data pre-bias correction
  mutate(Data = "Pre-Bias Correction (Livneh)") %>% #getting the numbers back into cfs to plot
  rename(`Inflow (ft^3/s)` = 2) %>%
  mutate(`Inflow (ft^3/s)` = (`Inflow (ft^3/s)`*810.7131821/86400))
Pre_BC

Pre_BC2 <- Pre_BC %>%
  group_by(yr = year(Date), mon = month(Date), Data) %>% #summarise by month-year
  summarise(`Inflow (ft^3/s)` = sum(`Inflow (ft^3/s)`)) %>% #getting ACF back to cfs for plotting
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep="")))) %>%
  select(Date, `Inflow (ft^3/s)`, Data) 
Pre_BC2

BC_daily <- read_csv(paste(path,"/tot_runoff_",Subbasin,"_mcm.csv", sep="")) %>% #Getting the Bias Corrected data we generated
  mutate(Data = "Post-Bias Correction (Livneh)") %>%
  rename(`Inflow (ft^3/s)` = 2) %>%
  mutate(`Inflow (ft^3/s)` = (`Inflow (ft^3/s)`*810.7131821/86400)) %>%
   filter(between(Date, as.Date(StartDate), as.Date(EndDate)))

BC_daily

BC_daily2 <- BC_daily %>%
  group_by(yr = year(Date), mon = month(Date), Data) %>% 
  summarise(`Inflow (ft^3/s)` = sum(`Inflow (ft^3/s)`)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep="")))) %>%
  select(Date, `Inflow (ft^3/s)`, Data) 
BC_daily2

Reference <- Observed %>% #getting the observed data from USGS
    mutate(Data = "USGS Reference (Observed)") %>%
  rename(`Inflow (ft^3/s)` = 2)%>%
  mutate(`Inflow (ft^3/s)` = `Inflow (ft^3/s)`/(86400/43560))
Reference

Reference2 <- Reference %>%
  group_by(yr = year(Date), mon = month(Date), Data) %>% 
  summarise(`Inflow (ft^3/s)` = sum(`Inflow (ft^3/s)`)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep="")))) %>%
  select(Date, `Inflow (ft^3/s)`, Data)
Reference2

Final <- rbind(Pre_BC, BC_daily, Reference)
Final
Final$Data <- factor(Final$Data, levels = c("USGS Reference (Observed)", "Pre-Bias Correction (Livneh)","Post-Bias Correction (Livneh)"))

Final2 <- rbind(Pre_BC2, BC_daily2, Reference2)
Final2
Final2$Data <- factor(Final2$Data, levels = c("USGS Reference (Observed)", "Pre-Bias Correction (Livneh)","Post-Bias Correction (Livneh)"))

##Line Curve
#Final2 <- Final %>%
#  mutate(Yearmon = zoo::as.yearmon(Date)) %>%
#  group_by(Yearmon, Data) %>%
#  summarise(Inflow = sum(Inflow)) %>%
#  ungroup() %>%
#  mutate(Date = as.Date(Yearmon))

ggplot(Final,aes(x=Date, y=`Inflow (ft^3/s)`, color=Data ))+ geom_line(size = 0.3, alpha = 0.9)+ xlab("Date")+ ylab(expression("Inflow ("*ft^3/s*")"))+ scale_x_date(date_labels = "%Y-%m", breaks = "years")+ scale_y_continuous(breaks = scales::pretty_breaks())+
  ggtitle(paste0(Area)) +theme(plot.title = element_text(hjust = 0.5))+
ggsave(filename=paste(path,"/",Subbasin,"_line_daily.png",sep=""), units="in",width=6.5,height=3)#,res=360)

ggplot(Final2,aes(x=Date, y=`Inflow (ft^3/s)`, color=Data ))+ ylab(expression("Inflow ("*ft^3/month*")"))+ geom_line()+ scale_x_date(date_labels = "%Y-%m", breaks = "years") +ggtitle(paste0(Area)) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_continuous(breaks = scales::pretty_breaks())+
  ggsave(filename=paste(path,"/",Subbasin,"_line_monthly.png",sep=""), units="in",width=6.5,height=3)

ggplot(Final,aes(x=Date, y=`Inflow (ft^3/s)`+0.00001, color=Data ))+ geom_line(size = 0.3, alpha = 0.9)+ xlab("Date")+ ylab(expression("Inflow ("*ft^3/s*")"))+ scale_x_date(date_labels = "%Y-%m", breaks = "years")+ scale_y_log10(breaks = scales::pretty_breaks())+
  ggtitle(paste0(Area)) +theme(plot.title = element_text(hjust = 0.5))+
ggsave(filename=paste(path,"/",Subbasin,"_line_daily_logscale.png",sep=""), units="in",width=6.5,height=3)#,res=360)

ggplot(Final2,aes(x=Date, y=`Inflow (ft^3/s)`+0.00001, color=Data ))+ ylab(expression("Inflow ("*ft^3/month*")"))+ geom_line()+ scale_x_date(date_labels = "%Y-%m", breaks = "years") +ggtitle(paste0(Area)) + theme(plot.title = element_text(hjust = 0.5)) + scale_y_log10(breaks = scales::pretty_breaks())+
  ggsave(filename=paste(path,"/",Subbasin,"_line_monthly_logscale.png",sep=""), units="in",width=6.5,height=3)

##FDC Curve
data.nm <- unique(Final$Data)
Final$FDC <- NA
for (i in (1:length(data.nm))){
  vls <- Final$`Inflow (ft^3/s)`[Final$Data==data.nm[i]]+0.00001
  Fn <- ecdf(vls)
  Final$FDC[Final$Data==data.nm[i]] <- 1-Fn(vls) # exceedance probabilities
}

ggplot(Final, aes(x=FDC, y=`Inflow (ft^3/s)`, color=Data)) + geom_line(size = 0.6, alpha = 0.5) + #geom_point(shape=21, size=0.05, alpha=0.25) + #scale_y_log10(limits = c(min(Final$`Inflow (ft^3/s)`+0.00001),NA))+
        ylab(expression("Inflow ("*ft^3/s*")")) + xlab("Exceedance probability") + ggtitle(paste0(Area)) + theme(plot.title = element_text(hjust = 0.5))+
  ggsave(filename=paste(path,"/",Subbasin,"_fdc.png",sep=""), units="in",width=6.5,height=3.5)#,res=360)

## Box&whisker
ggplot(Final, aes(x=Data, y=`Inflow (ft^3/s)`)) + geom_boxplot() +
 #       scale_y_log10(limits=c(3e-1,3e3)) +
        ylab(expression("Inflow ("*ft^3/s*")")) + xlab("Data")  +ggtitle(paste0(Area)) +theme(plot.title = element_text(hjust = 0.5))+
  ggsave(filename=paste(path,"/",Subbasin,"_box.png",sep=""), units="in",width=6.5,height=4)#,res=360)


## Q-Q plot
ggplot(Final, aes(sample=`Inflow (ft^3/s)`, color=Data)) + stat_qq(shape=21, size=0.75)+ylab(expression("Sample Quantiles ("*ft^3/s*")"))+ xlab("Theorical Quantiles (Normal Distribution)")+ggtitle(paste0(Area)) + theme(plot.title = element_text(hjust = 0.5))+
  png(filename=paste(path,"/",Subbasin,"_qq.png",sep=""), units="in",width=6.5,height=3,res=360)
#}


```

```{r}
#Make_Figures(Sub21, Sub21_PreBC, "sb21", "1980-10-01", "2013-12-31")
Make_Figures(Sub22, Sub22_PreBC, "sb22", "1965-10-01" ,"1986-09-29", "Granite Creek") 
```

```{r}
Make_Figures(Sub23, Sub23_PreBC, "sb23", "1951-10-01", "1991-09-29", "San Joaquin River")
```

```{r}
Make_Figures(Sub31, Sub31_PreBC, "sb31", "1954-10-12", "2013-12-31", "Thomas A. Edison Lake")
```

```{r}
Make_Figures(Sub36, Sub36_PreBC, "sb36", "1975-10-01", "1986-09-29", "Bear Creek")
```

```{r}
Make_Figures(Sub37, Sub37_PreBC, "sb37", "2009-10-01", "2013-12-31", "Hooper Creek")
```

```{r}
Make_Figures(Sub38, Sub38_PreBC, "sb38", "1950-01-01", "1980-09-29", "Florence Lake")
```


```{r}
#Extra figure using CDEC data
#Florence Lake CDEC FNF

Obs_Fl <- cdec_query("SFR", 65, "M",  "1950-01-01", "1980-09-30") %>%
  mutate(Value = Value/810.71318210885,
         Date = as.Date(DateTime, format = "%Y/%m/%d"),
         month = month(DateTime), year = year(DateTime),
         Data = "CDEC - DWR",
         flw = Value) 
Obs_Fl

Sim_Fl <- read_csv(paste(path,"/tot_runoff_sb38_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "Bias Corrected Livneh") %>%
  select(Date, Data, flw) %>%
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-30")))
  
Sim_Fl

Florence_USGS<- Sub38 %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(flow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "USGS") %>%
  select(Date, Data, flw) %>%
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-30")))

Florence <- rbind(Obs_Fl[c(10,13,14)], Sim_Fl, Florence_USGS)
Florence
```

```{r}
ggplot(Florence, aes(x = Date, y = flw, color = Data)) + geom_line(size = 0.3, alpha = 0.9) +
   ylab("Flow (mcm/month)")+ggtitle("Florence Lake")+
  png(filename=paste(path,"/sb38_line_monthly_CDEC_line.png",sep=""), units="in",width=6.5,height=3,res=360)

```


```{r}
#Extra figure using CDEC data
library(cder)
#SJF = FNF of USJ basin
Obs_USJ <- cdec_query("SJF", 65, "M",  "1950-01-01", "2013-12-31") %>%
  mutate(Value = Value/810.71318210885,
         Date = as.Date(DateTime, format = "%Y/%m/%d"),
         month = month(DateTime), year = year(DateTime),
         Data = "Upper San Joaquin Basin",
         flw = Value)
Obs_USJ

Florence <- Sim_Fl %>%
  mutate(Data = "Florence Lake")

Granite <- read_csv(paste(path,"/tot_runoff_sb22_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "Granite Creek") %>%
  select(Date, Data, flw)
  
SJR <- read_csv(paste(path,"/tot_runoff_sb23_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "San Joaquin River") %>%
  select(Date, Data, flw)

Thomas <- read_csv(paste(path,"/tot_runoff_sb31_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "Thomas A. Edison Lake") %>%
  select(Date, Data, flw)

Bear <- read_csv(paste(path,"/tot_runoff_sb36_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "Bear Creek") %>%
  select(Date, Data, flw)

Hooper <- read_csv(paste(path,"/tot_runoff_sb37_mcm.csv", sep="")) %>%
  group_by(yr = year(Date), mon = month(Date)) %>% 
  summarise(flw = sum(Inflow)) %>% 
  ungroup() %>%
  mutate(Date = as.Date(ymd(paste(yr,'-', mon,'-01', sep=""))),
         Data = "Hooper Creek") %>%
  select(Date, Data, flw)

```

```{r}
USJBasin <- rbind(Obs_USJ[c(10,13,14)], Florence, Hooper, Bear, Granite, SJR, Thomas)
#Cherry$Data <- factor(Cherry$Data, levels = c("CDEC - DWR", "Bias Corrected Livneh"))
USJBasin 
```

```{r}
ggplot(USJBasin, aes(x = Date, y = flw, color = Data)) + geom_line(size = 0.3, alpha = 0.9) +
   ylab("Flow (mcm/month)")+ggtitle("Upper San Joaquin Basin")+ scale_x_date(limits = as.Date(c("1980-01-01","2010-12-31")))+ scale_y_log10() +
  png(filename=paste(path,"/line_monthly_CDEC_Basin.png",sep=""), units="in",width=6.5,height=3,res=360)
```

```{r}
ggplot(USJBasin, aes(x = Date, y = flw, color = Data)) + geom_line(size = 0.3, alpha = 0.9) +
   ylab("Flow (mcm/month)")+ggtitle("Upper San Joaquin Basin")+ scale_x_date(limits = as.Date(c("1980-01-01","2010-12-31")))+ #scale_y_log10() +
  png(filename=paste(path,"/line_monthly_CDEC_Basin2.png",sep=""), units="in",width=6.5,height=3,res=360)
```
