---
title: "Untitled"
author: "Gustavo Facincani Dourado"
date: "8/17/2020"
output: html_document
---

```{r}
library(ncdf4)
library(lubridate)
library(reshape2)
library(dplyr)
library(hyfo)
library(ggplot2)
```

```{r}
#start with empty workspace
#rm(list=ls(all=TRUE))

#Set working directory
setwd("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/")
wd <- setwd("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/")
#Read NC file with monthly bias-corrected flows
ncfname <- paste(wd, "/", "TUOR/BC_Data_Berkeley/CCSM4.rcp85.DPR_I.1950-2100.monthly.BC.nc", sep = "")
mdlname <- "CCSM4_rcp85"
modelname <- "CCSM4"
ncin <- nc_open(ncfname)
ncin
```

```{r}
t <- ncvar_get(ncin, "time")
flw.array <- ncvar_get(ncin,'flow')
t <- as.Date.numeric(t,origin = "1900-01-01")
BCFlow_Berk <- data.frame(t,flw.array/35.314666)#converting cfs to cms #*86400/1000000) #or using this forZ mcm^3/day
colnames(BCFlow_Berk) <- c('Date','Flw')
BCFlow_Berk$Date <- as.Date(ymd(BCFlow_Berk$Date))
BCFlow_Berk <- extractPeriod(BCFlow_Berk,startDate = '2006-01-15', endDate = '2099-12-15')
BCFlow_Berk
```

```{r}
#Get daily VIC flows at the Reservoir
data <- list()
for (f in (1:19)){
   if (f < 10) {
      f <- paste("0", as.character(f), sep="")
    } else {
      f <- as.character(f)
    }
    
  d <- read.csv(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_woBC/CCSM4_rcp85/tot_runoff_sb",f,".csv", sep=""))
  data[[f]] <- d
}
```

```{r}
df <- Reduce(function(x,y) full_join(x,y, by=c('Date')), data)

colnames(df) <-  c('Date',1:19)
#df$Date <- as.Date(df$Date, format = "%d/%m/%Y")

df$TotFlw <- df$'1'+df$'2'+df$'3'+df$'4'+df$'5'+df$'6'+df$'7'+df$'8'+df$'9'+df$'10'+df$'11'+df$'12'+df$'13'+df$'14'+df$'15'+df$'16'+df$'17'+df$'18'+df$'19'#+df$'20'+df$'21'+df$'22'+df$'23'+df$'24'+df$'25'+df$'26'+df$'27'+df$'28'+df$'29'+df$'30'+df$'31'+df$'32'+df$'33'+df$'34'+df$'35'+df$'36'+df$'37'+df$'38'

daily_flw_vic <- data.frame(df$Date,df$TotFlw)
colnames(daily_flw_vic) <- c('Date','Flw')
daily_flw_vic$Date <- as.Date(ymd(daily_flw_vic$Date))
daily_flw_vic$Flw <- daily_flw_vic$Flw #I'm using mcm/day, so turn it back into m^3/s
print((daily_flw_vic))
```

```{r}
#Aggregate to monthly value
monthly_flw_vic <- aggregate(daily_flw_vic[,2],by=list(year(daily_flw_vic$Date),month(daily_flw_vic$Date)),FUN=mean,na.rm=TRUE)
colnames(monthly_flw_vic) <- c('Year','Month','Flw')
monthly_flw_vic <- monthly_flw_vic[with(monthly_flw_vic,order(monthly_flw_vic$'Year')),]
monthly_flw_vic$Date <- paste(monthly_flw_vic$Year,'-', monthly_flw_vic$Month,'-15', sep="")
monthly_flw_vic <- monthly_flw_vic[,c(4,3)]
monthly_flw_vic$Date <- as.Date(ymd(monthly_flw_vic$Date))
monthly_flw_vic_orig <- monthly_flw_vic
monthly_flw_vic_orig$Type <- as.factor('Pre-Bias Correction')

print(monthly_flw_vic_orig)
print(BCFlow_Berk)
```

```{r}
#Bias Correction
new_df <- list()
bc_df <- list()
fin_df <- list()

for (i in (1:12)){
  print(i)
  obs <- filter(BCFlow_Berk,month(BCFlow_Berk$Date)== i)
  hind <- filter(monthly_flw_vic,month(monthly_flw_vic$Date)== i)

  bF <- getBiasFactor(hind,obs,method = "scaling", scaleType = "multi",preci = FALSE, prThreshold = 0, extrapolate = "no")
  for (f in (1:19)){
    new_df[[f]] <- filter(data[[f]],month(as.Date(data[[f]]$Date, format = "%Y-%m-%d")) ==i)
    bc_df[[f]] <- applyBiasFactor(new_df[[f]],bF)
    if (i==1){
      fin_df[[f]] <- bc_df[[f]]
    }
    else {
      fin_df[[f]] <- bind_rows(fin_df[[f]],bc_df[[f]])
     
    }
  }
}

```

```{r}
#Sort and write
  for (f in (1:19)){
   if (f < 10) {
      f <- paste("0", as.character(f), sep="")
    } else {
      f <- as.character(f)
    }
  fin_df[[as.numeric(f)]] <- arrange(fin_df[[as.numeric(f)]], Date)
  write.csv(fin_df[[as.numeric(f)]],file=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/CCSM4_rcp85/tot_runoff_sb",f,".csv", sep=""),row.names=F)
}

df_new <- Reduce(function(x,y) full_join(x,y, by=c('Date')), fin_df)
colnames(df_new) <-  c('Date',1:19)


```

```{r}
df_new$TotFlw <- df_new$'1'+df_new$'2'+df_new$'3'+df_new$'4'+df_new$'5'+df_new$'6'+df_new$'7'+df_new$'8'+df_new$'9'+df_new$'10'+df_new$'11'+df_new$'12'+df_new$'13'+df_new$'14'+df_new$'15'+df_new$'16'+df_new$'17'+df_new$'18'+df_new$'19'#+df_new$'20'+df_new$'21'+df_new$'22'+df_new$'23'+df_new$'24'+df_new$'25'+df_new$'26'+df_new$'27'+df_new$'28'+df_new$'29'+df_new$'30'+df_new$'31'+df_new$'32'+df_new$'33'+df_new$'34'+df_new$'35'+df_new$'36'+df_new$'37'+df_new$'38'
daily_flw_vic <- data.frame(df_new$Date,df_new$TotFlw)
colnames(daily_flw_vic) <- c('Date','Flw')
daily_flw_vic$Date <- as.Date(ymd(daily_flw_vic$Date))
daily_flw_vic$Flw <- daily_flw_vic$Flw

#Aggregate to monthly value
monthly_flw_vic <- aggregate(daily_flw_vic[,2],by=list(year(daily_flw_vic$Date),month(daily_flw_vic$Date)),FUN=mean,na.rm=TRUE)
colnames(monthly_flw_vic) <- c('Year','Month','Flw')
monthly_flw_vic <- monthly_flw_vic[with(monthly_flw_vic,order(monthly_flw_vic$'Year')),]
monthly_flw_vic$Date <- paste(monthly_flw_vic$Year,'-', monthly_flw_vic$Month,'-15', sep="")
monthly_flw_vic_mod <- monthly_flw_vic[,c(4,3)]
monthly_flw_vic_mod$Date <- as.Date(ymd(monthly_flw_vic_mod$Date))
monthly_flw_vic_mod$Type <- as.factor('Post-Bias Correction')

#Plot
BCFlow_Berk$Type <- as.factor('Bias-Corrected Reference')
monthly_flw_vic_orig <- extractPeriod(monthly_flw_vic_orig,startDate = '2006-01-15', endDate = '2099-12-15')
monthly_flw_vic_mod <- extractPeriod(monthly_flw_vic_mod,startDate = '2006-01-15', endDate = '2099-12-15')
BCFlow_Berk <- extractPeriod(BCFlow_Berk,startDate = '2006-01-15', endDate = '2099-12-15')
data_to_plot <- bind_rows(monthly_flw_vic_orig,monthly_flw_vic_mod,BCFlow_Berk)
data_to_plot <- melt(data_to_plot,id.vars=c('Date','Type'))
data_to_plot <- data_to_plot[,c(1,2,4)]
colnames(data_to_plot) <- c('Date','Data','Flow')
data_to_plot$Data <- as.factor(data_to_plot$Data)

data_to_plot$Data <- factor(data_to_plot$Data, levels=c("Pre-Bias Correction", "Post-Bias Correction", "Bias-Corrected Reference"))

print(head(data_to_plot))
```


data_to_plot$Month <- format(data_to_plot$Date,"%m")

print(tail(data_to_plot))

data2 <- data_to_plot %>%
  filter(!Data == "Post-Bias Correction")

ggplot(data2) +
  geom_point(aes(x = Flow[data2$Data == "Bias-Corrected Reference"], 
                 y = Flow[data2$Data == "Pre-Bias Correction"])) +
  facet_wrap(~as.factor(Month))




```{r}
##Line Curve
line <- ggplot(data_to_plot,aes(x=Date, y=Flow, color=Data))+ geom_line()+  scale_x_date(limits = as.Date(c('2006-01-01','2099-12-31')))
line + png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/", mdlname,"/",mdlname,"_line.png",sep=""), units="in",width=6.5,height=3,res=360)
```

```{r}
##CFD Curve
data.nm <- unique(data_to_plot$Data)
data_to_plot$FDC <- NA
for (i in (1:length(data.nm))){
  vls <- data_to_plot$Flow[data_to_plot$Data==data.nm[i]]
  Fn <- ecdf(vls)
  data_to_plot$FDC[data_to_plot$Data==data.nm[i]] <- 1-Fn(vls) # exceedance probabilities
}

ggplot(data_to_plot, aes(x=FDC, y=Flow, color=Data)) + geom_line() + geom_point(shape=21, size=0.05, alpha=0.25) + #[rvic.hist.all.m$Model=="CCSM4_rcp85",]
        scale_y_log10(limits=c(3e-1,3e3)) +
#        facet_wrap(~Data, ncol=2) +
        ylab(expression("Q ("*m^3/s*")")) + xlab("Exceedance probability") +
  png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_fdc.png",sep=""), type="cairo", units="in",width=6.5,height=3.5,res=360)
```

```{r}
## Box&whisker
ggplot(data_to_plot, aes(x=Data, y=Flow)) + geom_boxplot() +
 #       scale_y_log10(limits=c(3e-1,3e3)) +
        ylab(expression("Q ("*m^3/s*")")) + xlab("Data")  +
png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_box.png",sep=""), type="cairo", units="in",width=6.5,height=4,res=360)


```

```{r}
## Q-Q plot
ggplot(data_to_plot, aes(sample=Flow, color=Data)) + stat_qq(shape=21, size=0.75) +
        #+ facet_wrap(~Data, ncol=2)
png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_qq.png",sep=""), type="cairo", units="in",width=6.5,height=3,res=360)

```

```{r}
BiasCorrection <- as.data.frame(data_to_plot$Flow[data_to_plot$Data == "Post-Bias Correction"])
BiasCorrection2 <-as.data.frame(data_to_plot$Flow[data_to_plot$Data == "Bias-Corrected Reference"])
BiasCorrection$Date <- data_to_plot$Date[data_to_plot$Data == "Bias-Corrected Reference"]
head(BiasCorrection2)

bias <- cbind(BiasCorrection, BiasCorrection2) %>%
  rename(`Post-Bias Correction` = `data_to_plot$Flow[data_to_plot$Data == "Post-Bias Correction"]`,
         Reference = `data_to_plot$Flow[data_to_plot$Data == "Bias-Corrected Reference"]`) %>%
  mutate(month = format(Date,"%B"))
bias

bias$month <- factor(bias$month, levels = c("January", "February", "March","April", "May", "June", "July", "August", "September", "October", "November", "December"))
```


```{r}


myformula <- y ~ x
ggplot(bias, aes(y = `Post-Bias Correction`, x = Reference)) +
  geom_point() +
  xlim(0,370) + ylim(0,370)+
  geom_smooth(method = "lm", se=FALSE, color="black", formula = myformula) +
  ggpmisc::stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")), formula = myformula, parse = TRUE, size = 3) +
            
  facet_wrap(~month, scales = "fixed") 

``````

```{r}
BiasCorrection <- as.data.frame(Final$tot_runoff_sb21[Final$Data == "Post-Bias Correction"])
BiasCorrection1 <- as.data.frame(Final$tot_runoff_sb21[Final$Data == "Pre-Bias Correction (Livneh)"])
BiasCorrection2 <-as.data.frame(Final$tot_runoff_sb21[Final$Data == "USGS Reference (Observed)"])
BiasCorrection$Date <- Final$Date[Final$Data == "Post-Bias Correction"]
head(BiasCorrection2)
head(BiasCorrection)

bias <- cbind(BiasCorrection,BiasCorrection1, BiasCorrection2) %>%
  rename(`Post-Bias Correction` = `Final$tot_runoff_sb21[Final$Data == "Post-Bias Correction"]`,
         Reference = `Final$tot_runoff_sb21[Final$Data == "USGS Reference (Observed)"]`,
         `Pre-Bias Correction` = `Final$tot_runoff_sb21[Final$Data == "Pre-Bias Correction (Livneh)"]`) %>%
  mutate(month = format(Date,"%B"))
bias

bias$month <- factor(bias$month, levels = c("January", "February", "March","April", "May", "June", "July", "August", "September", "October", "November", "December"))
```


```{r}


myformula <- y ~ x
ggplot(bias, aes(y = `Post-Bias Correction`, x = Reference)) +
  geom_point() +
  xlim(0,370) + ylim(0,370)+
  geom_smooth(method = "lm", se=FALSE, color="black", formula = myformula) +
  ggpmisc::stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")), formula = myformula, parse = TRUE, size = 3) +
            
  facet_wrap(~month, scales = "fixed") 

ggplot(bias, aes(y = `Pre-Bias Correction`, x = Reference)) +
  geom_point() +
  xlim(0,370) + ylim(0,370)+
  geom_smooth(method = "lm", se=FALSE, color="black", formula = myformula) +
  ggpmisc::stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~")), formula = myformula, parse = TRUE, size = 3) +
            
  facet_wrap(~month, scales = "fixed") 

``````
