```{r}

library(bibliometrix)
library(readr)
#library(bootnet)
#library(networktools)
#library(NetworkComparisonTest)
#library(ggraph)
library(dplyr)
```


```{r}
#wos <- readFiles("C:/Users/gusta/Desktop/PhD/Classes/ES207/savedrecs.txt")
#wos
file <- ("C:/Users/gusta/Downloads/savedrecs (5).bib")

M <- convert2df(file, dbsource = "wos", format = "bibtex")
M
```

```{r}
bibliometrix::biblioshiny()


results <- biblioAnalysis(wosdf, sep = ";")
results

S <- summary(object = results, k = 10, pause = FALSE)
S

plot(x = results, k = 10, pause = FALSE)
```

```{r}
countries <- read_csv("C:/Users/gusta/University of California Merced/VICE Lab - UCM - Review paper/World_Collaboration_Map.csv")
countries
```


```{r}

combined <- plyr::rbind.fill(world, countries)
combined
```


```{r}
library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")

world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

## [1] "sf"  
## [1] "data.frame"
ggplot(data = world) +
    geom_sf() +
  
```


ERL <- readxl::read_excel("C:/Users/gusta/University of California Merced/VICE Lab - UCM - Review paper/Paper_ERL2.xlsx", sheet = "Sheet4")[,-1]
#ERL2 <-  as.data.frame(ifelse(ERL[c(-1, -23)] == "Yes", as.numeric(1), as.numeric(0))) %>%
#  cbind(., ERL[c(1,23)])
#ERL2

#po <- reshape2::melt(ERL2, id =c("Paper", "Country")) %>%
#  reshape2::dcast(., Paper~variable+value) #%>%
 # mutate(`0` = NULL) %>%
  #filter(!is.na(`1`))
ERL


ERL2 <- data.table::rbindlist(combn(ERL, 2, simplify=F)) %>%
   group_by(A, B) %>%
  summarise(weight = dplyr::n()) %>% 
  ungroup()
ERL2 




ggraph(ERL2, layout = "graphopt") + 
    geom_node_point() +
    geom_edge_link(aes(width = weight), alpha = 0.8) + 
    scale_edge_width(range = c(0.2, 2)) +
    #geom_node_text(aes(label = label), repel = TRUE) +
    #labs(edge_width = "Letters") +
    theme_graph()



mynetwork <- estimateNetwork(ERL2, default = "EBICglasso", corMethod = "cor", corArgs = list(method = "spearman", use = "pairwise.complete.obs"))

plot(mynetwork, layout = "spring", vsize = 6, border.color = "black", color = "lightblue")


```{r}
library(readxl)
library(igraph)
library(cooccur)
finches = read_xlsx("C:/Users/gusta/University of California Merced/VICE Lab - UCM - Review paper/Paper_ERL3.xlsx", sheet = "Sheet5")
finches
net2 = graph_from_incidence_matrix(finches)
#net2.bp <- bipartite.projection(net2)
net2.bp = as_incidence_matrix(net2)  %*% t(as_incidence_matrix(net2)) 

diag(net2.bp) <- 1

net2.bp <- sweep(net2.bp,        # Apply sweep function
      2,
      1,
      FUN = "-")
net2.bp

net2.bp <- sweep(net2.bp,       # Apply sweep function
      2,
      2,
      FUN = "/")
#net2.bp
#colnames(net2.bp) <- finches$Paper
#rownames(net2.bp) <-finches$Paper
#net2.np <- t(as_incidence_matrix(net2)) %*%   as_incidence_matrix(net2)
# diag(net2) <- 0
# Find significant pairwise co-occurrences.
#co <- print(cooccur(finches[,-1], thresh=F, spp_names = T, true_rand_classifier = 0))
#co[, 'sp1_name'] == rownames(finches)[co$sp1]
#co[, 'sp2_name'] == rownames(finches)[co$sp2]
```

```{r}
#library(statnet)

#colnames(finches$Paper) = rownames(finches$Paper) = LETTERS[finches$Paper]
colnames(net2.bp) <- finches$Paper
rownames(net2.bp) <- finches$Paper
network <- graph_from_adjacency_matrix(net2.bp, mode = "undirected", weighted = TRUE, diag = F)
#node.size= c(14,14,14)

png(file="C:/Users/gusta/University of California Merced/VICE Lab - UCM - Review paper/saving_plot51.png", width=1800, height=1200, res = 350)
par(mar=c(0.1,0.1,0.1,0.1))
V(network)$size=igraph::degree(network)%>%log()*4
E(network)$width=E(network)$weight%>%log()/2
E(network)$color = "gray85"
plot(network,#vertex.size=node.size, 
edge.width = E(network)$weight/3, edge.arrow.size=.5, vertex.color="gray74", vertex.size=3, 
     vertex.frame.color="gray55", vertex.label.color="black", 
     vertex.label.cex=.5, vertex.label.dist=1, edge.curved=0.5,layout=layout_with_lgl, pt.cex=1, cex=.8, bty="n", ncol=1, pch=21, pointsize=70)

#tkplot(network)

#dev.off()
```


```{r}
library(flipPlots)
SankeyDiagram(net2.bp,
              link.color = "Source", 
              weights = my.data$freq) 

```

# Create a data frame of the nodes in the network. 
nodes <- data.frame(id = 1:nrow(finches),
                    label = finches$Paper,
                    color = "#606482",
                    shadow = TRUE) 
nodes

edges <- data.frame(from = co$sp1, to = co$sp2, value = co$obs_cooccur, total = co$sp1_inc)
edges


library(visNetwork)
#png(file="C:/Users/gusta/University of California Merced/VICE Lab - UCM - Review paper/saving_plot2.png", width=3000, height=7000)
visNetwork(nodes = nodes, edges = edges, height = "500px", width = "100%") %>% 
 # visNodes(size = edges$total) %>%
  visOptions(highlightNearest = TRUE)%>%
    visLayout(randomSeed = 123) %>%
  visPhysics(stabilization = FALSE)#%>%
# visConfigure(enabled = TRUE)#visIgraphLayout(layout = "layout_with_kk")

#dev.off()# diag(net2) <- 0


```{r}
vcol <- rep("gray40", vcount(net))

vcol[diam] <- "gold"

ecol <- rep("gray80", ecount(net))

ecol[E(net, path=diam)] <- "orange" 

# E(net, path=diam) finds edges along a path, here 'diam'

plot(net, vertex.color=vcol, edge.color=ecol, edge.arrow.mode=0)
```


```{r}

library(network)
```

```{r}
#To obtain the most frequent cited manuscripts:

CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:10])


#To obtain the most frequent cited first authors:

CR <- citations(M, field = "author", sep = ";")
cbind(CR$Cited[1:10])
CR$Papers[1:10,]


#author's dominance
DF <- dominance(results, k = 10)
DF

#Authors’ h-index

indices <- Hindex(M, field = "author", elements="BORNMANN L", sep = ";", years = 10)

# Bornmann's impact indices:
indices$H


#To calculate the h-index of the first 10 most productive authors (in this collection):

authors=gsub(","," ",names(results$Authors)[1:10])

indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)

indices$H
```


```{r}
#Top-Authors’ Productivity over the Time

topAU <- authorProdOverTime(M, k = 10, graph = TRUE)


#Bipartite networks
#cocMatrix is a general function to compute a bipartite network selecting one of the metadata attributes
#For example, to create a network Manuscript x Publication Source you have to use the field tag “SO”:
A <- cocMatrix(M, Field = "SO", sep = ";")
A
#Sorting, in decreasing order, the column sums of A, you can see the most relevant publication sources:

sort(Matrix::colSums(A), decreasing = TRUE)[1:5]
```


```{r}

#Citation network
B <- cocMatrix(M, Field = "CR", sep = ".  ")
B
#Author network
C <- cocMatrix(M, Field = "AU", sep = ";")
C

#Country network
#Authors’ Countries is not a standard attribute of the bibliographic data frame. You need to extract this information from affiliation attribute using the function metaTagExtraction.

D <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
D
```


```{r}

#Author keyword network
E <- cocMatrix(M, Field = "DE", sep = ";")
E
#Keyword Plus network
F <- cocMatrix(M, Field = "ID", sep = ";")
F
```


```{r}
#The following code calculates a classical article coupling network:

NetMatrix1 <- biblioNetwork(M, analysis = "coupling", network = "references", sep = ".  ")
NetMatrix1

NetMatrix2 <- biblioNetwork(M, analysis = "coupling", network = "authors", sep = ";")

#Co-citation
NetMatrix3 <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ".  ")

#Using the function biblioNetwork, you can calculate an authors’ collaboration network:
NetMatrix4 <- biblioNetwork(M, analysis = "collaboration", network = "authors", sep = ";")
```


```{r}

# An example of a classical keyword co-occurrences network

NetMatrix5 <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")
netstat <- networkStat(NetMatrix5)
names(netstat$network)
summary(netstat, k=10)
```


```{r}
# Create a country collaboration network

M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M, analysis = "collaboration", network = "countries", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = dim(NetMatrix)[1], Title = "Country Collaboration", type = "circle", size=TRUE, remove.multiple=FALSE,labelsize=0.7,cluster="none")
```


```{r}
# Create a co-citation network

NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)

```

```{r}
# Create keyword co-occurrences network

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

# Conceptual Structure using keywords (method="CA")

CS <- conceptualStructure(M,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)

```


```{r}
# Create a historical citation network
options(width=130)
histResults <- histNetwork(M, min.citations = 1, sep = ";")

# Plot a historical co-citation network
net <- histPlot(histResults, n=15, size = 10, labelsize=5)
```

