```{r}
library(dplyr)
library(readr)
library(extrafont)
#font_import()
#loadfonts(device = "win")
library(ggplot2)
library(cowplot)
```


```{r}
Livneh_Gen_USJ_NOPT <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/baseline - 2021-10-13 - no planning/upper_san_joaquin/historical/Livneh/Hydropower_Energy_MWh.csv")[, #c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)
                                                                                                                                                                                                                                                                                                      ] %>%
    filter(Date > "2004-09-30")%>%
  filter(Date < "2005-10-01")%>%
  mutate(Total_NOpt  = rowSums(.[c(2:17)]))
Livneh_Gen_USJ_NOPT


Livneh_Gen_USJ_OPT <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/historical/Livneh/Hydropower_Energy_MWh.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] %>%
  filter(node > "2004-09-30")%>%
  filter(node < "2005-10-01")%>%
  mutate(Total_Opt  = rowSums(.[c(2:17)]))
Livneh_Gen_USJ_OPT

hydrology <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/hydrology/historical/Livneh/preprocessed/full_natural_flow_daily_mcm.csv")%>%
  filter(date > "2004-09-30")%>%
  filter(date < "2005-10-01")
hydrology

elec_prices <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/Electricity_prices_daily_2009.csv")
elec_prices


elec_prices2 <- read_csv("C:/Users/gusta/Desktop/PhD/historical-2009.csv")
elec_prices2


all <- cbind(Livneh_Gen_USJ_OPT[-c(2:17)], Livneh_Gen_USJ_NOPT[-c(1:17)], elec_prices[-c(1)], hydrology[-c(1)]) %>%
  mutate(Month = as.numeric(format(node, "%m"))) #%>%
  #group_by(Month) %>%
#  summarize(Total_Opt = mean(Total_Opt),
 #           Total_NOpt = mean(Total_NOpt))
all <- all[1:365,]
all
```

```{r}
all2 <- all[,-4] %>%
  rename("Generation w/ planning"= Total_Opt,
         "Generation w/o planning" = Total_NOpt,
         "Full natural flow" = flow) %>%
  mutate(`Generation w/ planning` = `Generation w/ planning`/1000,
         `Generation w/o planning` = `Generation w/o planning`/1000) %>%
  reshape2::melt(., id = c("node", "Month"))
all2
```


```{r}

elec_prices2 <- read_csv("C:/Users/gusta/Desktop/PhD/historical-2009.csv")%>%
  mutate(Date2 = as.Date(Date2, '%m/%d/%Y'))
elec_prices2


#lubridate::year(elec_prices2$Date)
elec_prices2

```


g1 <-ggplot(elec_prices2) +  theme_bw(base_size=12, base_family='Times New Roman')+
  geom_line(aes(x=Hour, y = `Electricity Price [$/MWh]`), color = "black", size= 1.1)+
  # geom_area(aes(x = node,y = Prices, ymin= 60, ymax = Prices), color = "green", fill = "green", alpha=0.5) +
  scale_y_continuous(limits = c(40,NA), breaks=c(40,6080,100, 120), expand= c(0,0))+ ylab ("Mean Daily\nElectricity Prices (US$/MWh)" )+
  scale_x_continuous(expand = c(0, 0), breaks = scales::breaks_pretty(13))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        text = element_text(size=12),
        axis.text.y = element_text(size = 12))



```{r}
g1 <-ggplot(all) +  theme_bw(base_size=10, base_family='sans')+
  geom_line(aes(x=node, y = Prices), color = "black", size= 1.1)+
 # geom_line(elec_prices2, mapping = aes(x=Date2, y = `Electricity Price [$/MWh]`), color = "light gray", size= 1.1)+
  # geom_area(aes(x = node,y = Prices, ymin= 60, ymax = Prices), color = "green", fill = "green", alpha=0.5) +
  scale_y_continuous(limits = c(60,NA), breaks=c(60,80,100, 120), expand= c(0,0))+ ylab ("Mean Daily\n Electricity Prices \n(US$/MWh)" )+
  scale_x_date(expand = c(0, 0), breaks = scales::breaks_pretty(13))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        text = element_text(size=10),
        axis.text.y = element_text(size = 10))

g2 <- ggplot(all2) +
  theme_bw(base_size=10, base_family='sans')+
geom_line(aes(x=node, y= value, color = variable), size= 1.1) +#+ geom_area(aes(Livneh_Gen_USJ_OPT, x= node, y= Total_Opt))
  #geom_line(aes(x=node, y= Total_NOpt, color = "Non-optimized generation"), size= 1.1)+ 
  scale_x_date(expand = c(0, 0), breaks = scales::breaks_pretty(13))+# breaks = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+ 
  ylab("Electricity\nGeneration (GWh/day)")+
  scale_y_continuous(limits = c(0,NA), expand = c(0, 0), sec.axis = sec_axis(trans=~.*1, name = "Full natural flow (mcm/day)"))+
  #geom_line(aes(x=node, y= flow, color = "Full natural flow"), size= 1.1)+
  
   scale_color_manual(values = c("#009E73","#D55E00", "#56B4E9")) +
  theme(axis.title.x=element_blank(),
        #axis.text.x=element_blank(),
       # axis.ticks.x=element_blank(),
        #plot.title = element_text(hjust = 0.5),
        #plot.subtitle = element_text(hjust = 0.5),
        #strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.position = "bottom",#c(0.15, 0.80),
        legend.title = element_blank(),
       legend.direction = "horizontal",
       legend.background=element_rect(fill = alpha("white", 0)),
       text = element_text(size=10),
       legend.text=element_text(size=10),
       axis.text.y = element_text(size = 10),
       axis.text.x = element_text(size = 10))


plot_grid(g1,g2,align = "v", nrow = 2, rel_heights = c(1.2/5, 3.8/5)) 

g <- plot_grid(g1,g2,align = "v", nrow = 2, rel_heights = c(1.2/5, 3.8/5)) 

#g1 + png(file="Generation_USJ_daily_2005_b.png", units = "in", width = 8, height = 5, res=300)

#g2+ png(file="Generation_USJ_daily_2005_a.png", units = "in", width = 8, height = 5, res=300)


```

```{r}
save_plot("Figure14.png", g, units = "in", base_width = 8, base_height = 8, dpi=300) 
```

ggplot(all) + # theme_bw(base_size=12)+# base_family='Times New Roman')+
  geom_line(aes(x=node, y = Prices), color = "black", size= 1.1)+
  # geom_area(aes(x = node,y = Prices, ymin= 60, ymax = Prices), color = "green", fill = "green", alpha=0.5) +
  scale_y_continuous(limits = c(60,NA), breaks=c(60,80,100, 120), expand= c(0,0))+ ylab ("Mean Daily Electricity\nPrices (US$/day)" )+
  scale_x_date(expand = c(0, 0), breaks = scales::breaks_pretty(13))+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        text = element_text(size=12),
        axis.text.y = element_text(size = 12))
