---
title: "HW9_FacincaniDourado"
author: "Gustavo Facincani Dourado"
date: "4/15/2020"
output: html_document
---

Chapter 9. 

Exercise 2. Use simulation to evaluate the revised Poisson model in problem 9 in Chapter 8. A potential problem of such data is the excess number of zeroes, a phenomenon known as zero-inﬂation [Lambert, 1992].


```{r}
library(tidyverse)
library(msme)
urlfile <- "https://raw.githubusercontent.com/songsqian/eesR/master/R/Data/sturgeon.csv"
stur <- read_csv(url(urlfile))
```

```{r}
stur
```

```{r}
ggplot(stur, aes(x = CATCH)) + geom_histogram(binwidth = 1) + 
  labs(title = "Histogram of Sturgeon Catch Data",
       y = "Density",
       x = "Catch")
```

```{r}
#Simple Poisson Model
stur.m1 <- glm(CATCH ~ YEAR, data = stur, offset = log(Effort), family = "poisson")
summary(stur.m1)
```

```{r}
library(broom)
tidy(stur.m1, exponentiate = TRUE)
```

```{r}
library(jtools)
summ(stur.m1)

```

```{r}
stur %>% 
  gather(YEAR, TEMP, SALINITY, COND, DTSF, DO, key = "var", value = "value") %>%
  ggplot(aes(x = value, y = CATCH)) +
  geom_point(alpha = 0.5, na.rm = T) +
  facet_wrap(~var, scales = "free")
```

```{r}
#Poisson with more variables
stur.m2 <- glm(CATCH ~ YEAR + TEMP + SALINITY + DTSF, data = stur, offset = log(Effort), family = "poisson")
summary(stur.m2)
```

```{r}
#Quasipoisson
stur.m3 <- glm(CATCH ~ YEAR + TEMP + SALINITY + DTSF, data = stur, offset = log(Effort), family = "quasipoisson")
summary(stur.m3)
```


So, let's compare the models using simulation.

```{r}
y <- stur$CATCH
n <-dim(stur)[1]
n.sims <- 5000
zeros <- mean(stur$CATCH==0)
zeros
```
There are 43.87% of zeros in the data.


```{r}
#Simple Poisson Regression
y.rep.mean1 <- numeric()
for (i in 1:n.sims){
  y.rep1 <- rpois(n, predict(stur.m1, type = "response"))
  y.rep.mean1 [i] <- mean(y.rep1 ==0)}

zeros1 <- mean(y.rep1==0)
zeros1

print(paste("The simulation shows that the Poisson Regression gives", zeros1*100,"% of zeros"))
```

```{r}
#Poisson Regression with added variables
y.rep.mean2 <- numeric()
for (i in 1:n.sims){
  y.rep2 <- rpois(n, predict(stur.m2, type = "response"))
  y.rep.mean2 [i] <- mean(y.rep2 ==0)}

zeros2 <- mean(y.rep2==0)
zeros2

print(paste("The simulation shows that the Poisson Regression with added variables gives", zeros2*100,"% of zeros"))
```

```{r}
#QuasiPoisson Regression
y.rep.mean3 <- numeric()
for (i in 1:n.sims){
  y.rep3 <- rpois(n, predict(stur.m3, type = "response"))
  y.rep.mean3 [i] <- mean(y.rep3 ==0)}

zeros3 <- mean(y.rep3==0)
zeros3

print(paste("The simulation shows that the QuasiPoisson Regression gives", zeros3*100,"% of zeros"))
```

```{r}
library(pscl)
library(broom)

#Zero-inflated Poisson Regression

stur.m4 <- zeroinfl(CATCH ~ YEAR + TEMP + SALINITY + DTSF, offset = log(Effort), dist = 'poisson', data = stur)
summary(stur.m4)
```

```{r}
P__disp(stur.m4)
```
Checking for over-dispersion we can see that the Zero-inflated model has a better fit, because of the dispersion < 2.

```{r}
#Zero-inflated Poisson Regression
y.rep.mean4 <- numeric()
for (i in 1:n.sims){
  y.rep4 <- rpois(n, predict(stur.m4, type = "response"))
  y.rep.mean4 [i] <- mean(y.rep4 ==0)}

zeros4 <- mean(y.rep4==0)
zeros4

print(paste("The simulation shows that the Zero-inflated Poisson Regression gives", zeros4*100,"% of zeros"))
```

```{r}
#Zero-inflated Negative Binomial Poisson Regression

stur.m5 <- zeroinfl(CATCH ~ YEAR + TEMP + SALINITY + DTSF, offset = log(Effort), dist = 'negbin', data = stur)
summary(stur.m5)
```

```{r}
P__disp(stur.m5)
```
Checking for over-dispersion we can see that the Zero-inflated negative binomial model has the best fit of all, because of the dispersion close to 1.

```{r}
#Zero-inflated Negative Binomial Poisson Regression
y.rep.mean5 <- numeric()
for (i in 1:n.sims){
  y.rep5 <- rpois(n, predict(stur.m5, type = "response"))
  y.rep.mean5 [i] <- mean(y.rep5 ==0)}

zeros5 <- mean(y.rep5==0)
zeros5

print(paste("The simulation shows that the Zero-inflated Negative Binomial Poisson Regression gives", zeros5*100,"% of zeros"))
```

```{r}

require(ggplot2)
#Plotting the simulated percent of zeros among model


#Plot the data for simple Poisson
ggplot(data.frame(y.rep.mean1), aes(y.rep.mean1)) + 
  geom_histogram(aes(y=..density..))

#Plot the data for Poisson with added variables
ggplot(data.frame(y.rep.mean2), aes(y.rep.mean2)) + 
  geom_histogram(aes(y=..density..))

#Plot the data for QuasiPoisson
ggplot(data.frame(y.rep.mean3), aes(y.rep.mean3)) + 
  geom_histogram(aes(y=..density..))

#plot the data for Zero-inflated Poisson
ggplot(data.frame(y.rep.mean4), aes(y.rep.mean4)) + 
  geom_histogram(aes(y=..density..))

#plot the data for Zero-inflated Negative Binomial Poisson
ggplot(data.frame(y.rep.mean5), aes(y.rep.mean5)) + 
  geom_histogram(aes(y=..density..))
```

However, by only using simulation, I repeatedly got results around 20% (usually 17-22%) for all models, which is still not satisfactory. The representation can be seen in the histograms above.
