---
title: "ES207_FinalExam_FacincaniDourado"
author: "Gustavo Facincani Dourado"
date: "5/11/2020"
output: html_document
---

```{r}
#For this part of the exam, I'll keep the "simulated" and "observed" data I created/altered for the Part A.
library(lubridate)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(reshape2)
library(base)
library(gridExtra)
library(extrafont)
loadfonts()
fonts()
```
Functional Programming

Functions Part 1: Select a function you have written for this class that you think will be most useful to your research.

I decided for this function from my homework 10, found here:
https://github.com/GustavoFacincani/es207_hw4/blob/master/FacincaniDourado_HW4.html

```{r}
daily.mean <- function(df) { #function to get the daily O3 mean concentration
  df %>% 
  group_by(site = as.factor(site), date) %>% #creating groups by site
  summarize(o3 = mean(obs, na.rm = TRUE)) %>% #creating a column for the daily mean o3 concentrations
  drop_na()  #to drop row with missing values
  }
```

Question 1) Describe why you chose this function and what you plan to do with it in the future (200 words or less). Reference Part A as necessary.

I chose this function as it can be adapted to produce different results for other data, so that we can produce not only daily means, but also montly means or montlhy sums, for example, and group it by other parameters of interest, such as day, month or year. For instance, in the case of daily means, I can use this function to get the daily means of my historic and simulated flows under different climate change scenarios, to compare their responses.

Question 2) Improve the function to be more useful and more generic moving forward. Remember, a good function is short, performs a single operation, and uses intuitive names. You must include:
1. comments on what it does, what all of the inputs are (in order), what it requires of the inputs and the state of the system (a vector, a ts object, etc.), what side-effects it may have (e.g., plots histogram of residuals), and what all of its outputs are (in order).
2. a sanity checking argument using stopifnot() with a meaningful error message.
3. Demonstrate that this function works across at least three different use case scenarios. At least one should be realistic (something similar to your data), and at least one should be severe (something that might fail if you didn’t have appropriate error checks and messages in place).

In this case, I will adapt and transform the "daily.mean" function, to get the monthly mean of flows I'm interested in, instead of O3 concentration.

```{r}
#First I'll select the data
HydroFlow <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm.csv")[-c(1,2),] #reading in the observed data, skipping the 2 rows after the headings that are blank
Hydro_flow <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm2.csv")[-c(1,2),] #reading in the simulated data, skipping the 2 rows after the headings that are blank


head(HydroFlow)
head(Hydro_flow)

```

```{r}
#Now let's rearrange it to facilitate reading
HFO <- HydroFlow %>% #selecting the observed data
  gather(PH, Flow, `Moccasin PH`:`Dion R Holm PH`) #making the columns names (power houses) become rows of the column named PH, and the hydropower flows, rows of the column Flow

head(HFO)

HFS <- Hydro_flow %>% #selecting the simulated data
  gather(PH, Flow, `Moccasin PH`:`Dion R Holm PH`) #making the columns names (power houses) become rows of the column named PH, and the hydropower flows, rows of the column Flow

head(HFS)

comparison <- data.frame(HFO, HFS) #create a dataframe with all the data
head(comparison)
```

```{r}
#Rearranging the function 

daily.mean <- function(ModvsObs) { #function to get the daily mean concentration of two datasets at the same time
  
HydroPowerObs <- HFO %>% #Selecting the observed data by creating an object
   mutate(MonthDay = format(as.Date(HFO$node, format = "%m/%d/%Y"), "%m/%d")) %>% #creating a column for day and month only
  group_by(PH = as.factor(PH), MonthDay) %>% #grouping by day-month and power house
  summarize(MeanDailyFlow = mean(Flow, na.rm=TRUE)) #summarize the data by mean hydropower flow
  if(!is.numeric(HFO$Flow)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }

HydroPowerSim <- HFS %>% #Selecting the simulated data
  mutate(MonthDay = format(as.Date(HFS$node, format = "%m/%d/%Y"), "%m/%d")) %>% #creating a column for day and month only
  group_by(PH = as.factor(PH), MonthDay) %>% #grouping by day-month and power house
  summarize(MeanDailyFlow = mean(Flow, na.rm=TRUE)) #summarize the data by mean hydropower flow
if(!is.numeric(HFS$Flow)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
}
compare <- data.frame(HydroPowerObs, HydroPowerSim) #create a dataframe with all the data
return(compare) #the output is a data frame with all observed, followed by the simulated data
}
HP1 <- map(comparison, daily.mean) #apply the function to each element of the object "comparison"
head(HP1)

```
The function worked well to produce the daily mean for all power houses.

```{r}
#Another scenario where we can use this same function's structure is for monthly means
#So, with minor adjustments, we have that:

monthly.mean <- function(ModvsObs) { #function to get the daily mean concentration of two datasets at the same time
  
HydroPowerObs <- HFO %>% #Selecting the observed data by creating an object
   mutate(MonthYear = format(as.Date(HFO$node, format = "%m/%d/%Y"), "%Y/%m")) %>% #creating a column for month and year only
  group_by(PH = as.factor(PH), MonthYear) %>% #grouping by month-year and power house
  summarize(MonthlyFlow = sum(Flow, na.rm=TRUE)) #summarize the data by sum of monthly hydropower flow
  if(!is.numeric(HFO$Flow)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }

HydroPowerSim <- HFS %>% #Selecting the observed data by creating an object
   mutate(MonthYear = format(as.Date(HFS$node, format = "%m/%d/%Y"), "%Y/%m")) %>% #creating a column for month and year only
  group_by(PH = as.factor(PH), MonthYear) %>% #grouping by month-year and power house
  summarize(MonthlyFlow = sum(Flow, na.rm=TRUE)) #summarize the data by sum of monthly hydropower flow
if(!is.numeric(HFS$Flow)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
}
compare <- data.frame(HydroPowerObs, HydroPowerSim) #create a dataframe with all the data
return(compare) #the output is a data frame with the observed, followed by the simulated data
}
HP <- map(comparison, monthly.mean) #apply the function to each element of the object "comparison"
head(HP)

```
The function again worked just fine for monthly means!


```{r}
#Read data with characters instead of numeric data
df3 <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm3.csv")[-c(1,2),] #reading in the observed data, skipping the 2 rows after the headings that are blank

#Now let's rearrange it to facilitate reading
HFO <- df3 %>% #selecting the observed data
  gather(PH, Flow, `Moccasin PH`:`Dion R Holm PH`) #making the columns names (power houses) become rows of the column named PH, and the hydropower flows, rows of the column Flow

head(HFO)

HFS <- Hydro_flow %>% #selecting the simulated data
  gather(PH, Flow, `Moccasin PH`:`Dion R Holm PH`) #making the columns names (power houses) become rows of the column named PH, and the hydropower flows, rows of the column Flow

head(HFS)

comparison3 <- data.frame(HFO, HFS) #create a dataframe with all the data
comparison3


head(comparison3)
```

```{r}
#Applying the function
#HP3 <- map(comparison3, daily.mean) #creating vector

#HP3
```
The function worked well to produce an error, due to the presence of characters instead of numeric data in the file. Note: I can't run the command, otherwise I can't knit the file, but it gives to following message: "Error in .f(.x[[i]], ...) : This function only works for numeric input! You have provided an object of class: numeric".


Functions Part 2: Select a function one of your classmates has written for this class from their GitHub repository that you think will be most useful to your research.
Describe why you chose this function and what you plan to do with it in the future (200 words or less). Cite who you got this function from. Reference Part A as necessary.
Improve the function to be more useful and more generic moving forward. Remember, a good function is short, performs a single operation, and uses intuitive names. You must include:
1. comments on what it does, what all of the inputs are (in order), what it requires of the inputs and the state of the system (a vector, a ts object, etc.), what side-effects it may have (e.g., plots histogram of residuals), and what all of its outputs are (in order).
2. a sanity checking argument using stopifnot() with a meaningful error message.
3. Demonstrate that this function works across at least three different use case scenarios. At least one should be realistic (something similar to your data), and at least one should be severe (something that might fail if you didn’t have appropriate error checks and messages in place).

I decided for this function from homework 4 from Edwin's repository, found here: https://github.com/erivasmeraz/ES207_hw6/blob/master/model_assessment.R. 

```{r}
model.assess <- function(sim, obs) {require(hydroGOF)
  a.mae <- mae(sim = sim, obs = obs)
  b.rmse <- rmse(sim = sim, obs = obs)
  c.pbias <- pbias(sim = sim, obs = obs)
  Values <- c(a.mae, b.rmse, c.pbias)
  Names <- c('mae', 'rmse', 'pbias')
  stats <- tibble(Names, Values)
  return(stats)
}
```

This function will be very useful to me as I will also need to compare modeled data to historic observed data of hydropower flow and streamflow of regulated river systems (environmental flows).This function requires numeric values from simulated data (sim) and observed data to produce a tibble (subclass of a dataframe) with two columns, one composed of the name of statistical tests (characters) to evaluate the goodness-of-fit of the modeled data, and the other composed of the result of each test (numeric). The tests are vectors in the formula, and they are produced in this order: Mean Absolute Error (mae), Root Mean Square Error (rmse), Percent Bias (pbias). The results can be added to tables or graphical techniques for model evaluation. 
But in my case, I already decided for other statistical tests, so I'll change the statistical tests to those that are of my interest (replacing RMSE by the Ratio of RMSE to the standard deviation of the observations (RSR), and MAE by the Nash-Sutcliffe Efficiency (SNE)). I decided for these test as they are recommended by Moriasi et al. (2017), as mentioned in Part A. And in order to make the function more useful and replicable without requiring the installation of a package, I would prefer to use the formulas of the statistical tests that are of my interest:


To start, let's take the formulas of the statistical tests

Nash-Sutcliffe Efficiency (NSE) -  indicates how well the plot of observed versus simulated data fits the 1:1 line, in which 1 = perfect match, 0 = predictions are as accurate as the mean, <0 = mean is better. 

NSE <- 1 - sum((Obs - Sim)^2)/sum((Obs - mean(Obs))^2, na.rm =TRUE)
NSE

Percent bias (PBIAS) - measures the average tendency of the simulated values to be larger or smaller than their observed ones, in which 0 = optimal, low-magnitude values = accurate, positive/negative = over/underestimation.

PBIAS <- 100 *sum((Sim - Obs)/sum(Obs), na.rm =TRUE)
PBIAS

RSR - Ratio of RMSE (Root mean square error) to the standard deviation of the observations, in which the closer to zero, the better.

rmse = sqrt( mean( (Sim - Obs)^2, na.rm = TRUE) )

RSR <- rmse / sd(Obs)
RSR

So now, I'll change the function's commands to produce my statistical tests by their own formulas, with more proper naming and comments for clarity and easy reuse and replicability, so we have that:
```{r}
#Function to test goodness-of-fit using RSR, PBIAS and NSE tests
model.assess <- function(Sim, Obs) { #the inputs are numeric simulated and observed data
  if(!is.numeric(Sim)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }
  if(!is.numeric(Obs)) { #verifies if the observed data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of classes: ', class(Obs)[1])
  }    
  rmse = sqrt( mean( (Sim - Obs)^2, na.rm = TRUE) ) #Formula to calculate RMSE
  RSR <- rmse / sd(Obs) #object producing RSR test from the RMSE formula
  PBIAS <- 100 *(sum((Sim - Obs)/sum(Obs), na.rm =TRUE)) #object producing PBIAS test
  NSE <- 1 - sum((Obs - Sim)^2)/sum((Obs - mean(Obs))^2, na.rm =TRUE) #object producing NSE test
    Values <- c(RSR, PBIAS, NSE) #Creates a column for the results of the tests
  Test <- c('RSR', 'PBIAS', 'NSE') #Creates a column for the name of the tests
  stats <- tibble(Test, Values) #Creates a tibble of the final products of the tests, giving numeric values for each test in this order: RSR, PBIAS, NSE
  return(stats) #returns a tibble as a result, which can be used in graphs or tables
}
```

```{r}
#Wrangling the observed data
df <- HydroFlow %>%
  ungroup %>% #removes grouping
select(node, `Moccasin PH`, `Kirkwood PH`, `Don Pedro PH`, `Dion R Holm PH`) %>% #separates out the variables of interests (in this case I'll select all power houses)
  mutate(MonthYear = format(as.Date(HydroFlow$node, format = "%m/%d/%Y"), "%Y-%m")) %>% #creates a MonthYear column
  group_by(MonthYear) %>% #groups the data by MonthYear
  summarize(Moccasin = sum( `Moccasin PH`),
            Kirkwood = sum(`Kirkwood PH`), 
            DonPedro = sum(`Don Pedro PH`), 
            DiorRH = sum(`Dion R Holm PH`)) #applies the sum of hydropower flows per group of MonthYear

#Wrangling the simulated data
df2 <- Hydro_flow %>%
  ungroup %>% #removes grouping
select(node, `Moccasin PH`, `Kirkwood PH`, `Don Pedro PH`, `Dion R Holm PH`) %>% #separates out the variables of interests (in this case I'll select all power houses)
  mutate(MonthYear = format(as.Date(Hydro_flow$node, format = "%m/%d/%Y"), "%Y-%m")) %>% #creates a MonthYear column
  group_by(MonthYear) %>% #groups the data by MonthYear
  summarize(Moccasin2 = sum( `Moccasin PH`),
            Kirkwood2 = sum(`Kirkwood PH`), 
            DonPedro2 = sum(`Don Pedro PH`), 
            DiorRH2 = sum(`Dion R Holm PH`)) #applies the sum of hydropower flows per group of MonthYear
```

```{r}
#Let's try the function out with the data from Moccasin Power House read down below

Sim <- c(df$Moccasin) #selecting my simulated data
Obs <- c(df2$Moccasin2) #selecting my observed data

monthly.ma <- model.assess(Sim, Obs) #testing if the function works
head(monthly.ma)

```
The function works if we want to have a monthly-step assessment.

```{r}
#Let's try the function out with the daily data from Moccasin Power House read down below

Sim <- c(HydroFlow$`Moccasin PH`) #selecting my simulated data
Obs <- c(Hydro_flow$`Moccasin PH`) #selecting my observed data

daily.ma <- model.assess(Sim, Obs) #testing if the function works
head(daily.ma)
```
The function also works if we want to have a daily-step assessment.

```{r}
#Using data with written NAs

HydroFlow3 <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm3.csv")[-c(1,2),] #reading in the observed data, skipping the 2 rows after the headings that are blank

head(HydroFlow3)
head(HydroFlow)

Obs <- c(HydroFlow3$`Dion R Holm PH`) #selecting my simulated data
Sim <- c(HydroFlow$`Dion R Holm PH`) #selecting my observed data

#NAs.ma <- model.assess(Sim, Obs) #testing if the function works
#NAs.ma

```
The function also works if we have problems with the data, as in this case, in which we have characters in the column "Dion R Holm PH" of the simulated data. Note: I can't run the command, otherwise I can't knit the file, but it gives to following message: "Error in model.assess(Sim, Obs) : This function only works for numeric input! You have provided an object of classes: character".


Good Workflow

Create either a small subset of data from one thesis chapter (a tibble with no more than 50 rows). If you do not have data yet, create a dummy-dataset that you anticipate will be similar to your expected data from your research. If you need help coming up with some dummy data, please see me ASAP.
Write an R notebook with good documentation demonstrating your analysis workflow. You must include:
Reading in the data

```{r}
HydroFlow <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm.csv")[-c(1,2),] #reading in the observed data, skipping the 2 rows after the headings that are blank
Hydro_flow <- read_csv("C:/Users/gusta/Desktop/PhD/DataAnalysis/Hydropower_Flow_mcm2.csv")[-c(1,2),] #reading in the modeled data, skipping the 2 rows after the headings that are blank


head(HydroFlow) #check it
head(Hydro_flow) #check it 
```

Wrangling the data

```{r}
#Wrangling the observed data
df <- HydroFlow %>%
  ungroup %>% #removes grouping
select(node, `Moccasin PH`, `Kirkwood PH`, `Don Pedro PH`, `Dion R Holm PH`) %>% #separates out the variables of interests (in this case I'll select all power houses)
  mutate(MonthYear = format(as.Date(HydroFlow$node, format = "%m/%d/%Y"), "%Y-%m")) %>% #creates a MonthYear column
  group_by(MonthYear) %>% #groups the data by MonthYear
  summarize(Moccasin = sum( `Moccasin PH`),
            Kirkwood = sum(`Kirkwood PH`), 
            DonPedro = sum(`Don Pedro PH`), 
            DiorRH = sum(`Dion R Holm PH`)) #applies the sum of hydropower flows per group of MonthYear

#Wrangling the simulated data
df2 <- Hydro_flow %>%
  ungroup %>% #removes grouping
select(node, `Moccasin PH`, `Kirkwood PH`, `Don Pedro PH`, `Dion R Holm PH`) %>% #separates out the variables of interests (in this case I'll select all power houses)
  mutate(MonthYear = format(as.Date(Hydro_flow$node, format = "%m/%d/%Y"), "%Y-%m")) %>% #creates a MonthYear column
  group_by(MonthYear) %>% #groups the data by MonthYear
  summarize(Moccasin2 = sum( `Moccasin PH`),
            Kirkwood2 = sum(`Kirkwood PH`), 
            DonPedro2 = sum(`Don Pedro PH`), 
            DiorRH2 = sum(`Dion R Holm PH`)) #applies the sum of hydropower flows per group of MonthYear

head(df) #checking if everything is ok
head(df2) #checking if everything is ok

```

Applying one of the functions from above to your data. This must include a vectorized approach (meaning using lapply() ldply() or map() and mutate()).

```{r}
#Here I can use the Function to test goodness-of-fit using RSR, PBIAS and NSE tests

model.assess <- function(Sim, Obs) { #the inputs are numeric simulated and observed data
  if(!is.numeric(Sim)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }
  if(!is.numeric(Obs)) { #verifies if the observed data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of classes: ', class(Obs)[1])
  }    
  rmse = sqrt( mean( (Sim - Obs)^2, na.rm = TRUE) ) #Formula to calculate RMSE
  RSR <- rmse / sd(Obs) #Vector producing RSR test from the RMSE formula
  PBIAS <- 100 *(sum((Sim - Obs)/sum(Obs), na.rm =TRUE)) #Vector producing PBIAS test
  NSE <- 1 - sum((Obs - Sim)^2)/sum((Obs - mean(Obs))^2, na.rm =TRUE) #Vector producing NSE test
    Values <- c(RSR, PBIAS, NSE) #Creates a column for the results of the tests
  Test <- c('RSR', 'PBIAS', 'NSE') #Creates a column for the name of the tests
  stats <- tibble(Test, Values) #Creates a tibble of the final products of the tests, giving numeric values for each test in this order: RSR, PBIAS, NSE
  return(stats) #returns a tibble as a result, which can be used in graphs or tables
  }

#Let's try it out with the Moccasin PH

Sim <- c(df$Moccasin) #selecting my simulated data
Obs <- c(df2$Moccasin2) #selecting my observed data

ma <- model.assess(Sim, Obs) #testing if the function works
ma

```


Visualizing the result in a publication quality plot and a publication quality table.


```{r}
#Let's pick Moccasin PH for that

Hydro_flow$node <- as.Date(Hydro_flow$node, format = "%m/%d/%Y") #make node read as date
HydroFlow$node <- as.Date(HydroFlow$node, format = "%m/%d/%Y") #make node read as date

Hydro_flow$Month <- as.Date(cut(Hydro_flow$node, breaks = "month")) #create month column to facilitate plotting
HydroFlow$Month <- as.Date(cut(HydroFlow$node, breaks = "month")) #create month column to facilitate plotting
head(Hydro_flow) #check it
head(HydroFlow) #check it

```

```{r}
#Plotting a publication quality figure
                           
s <- ggplot(data =Hydro_flow) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  stat_summary(aes( x = Month, y = `Moccasin PH`, color = "#00AFBB"), #plot monthly observed data in greenish blue
               fun.y = sum, geom = "line") + #showing monthly sum in a line
 stat_summary(data = HydroFlow, aes(x = Month, y = `Moccasin PH`, color="#FC4E07"), #plot monthly observed data in orange
              fun.y = sum, geom = "line") + #showing monthly sum in a line
     scale_x_date(date_breaks = "6 years", date_labels = "%b/%Y") + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = "Moccasin PH", #identify the colors in a legend
                          breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed", "Simulated"), #select the variables
                          guide = "legend")+
  labs(title = "Observed vs. Simulated", #title
       x = "Date", #name of x axis
       y = "Hydropower Flow (mcm)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) #center the title
s

```

```{r} 
#Creating a publication quality table

#To have more data for the table, let's use the function for other power houses

#Kirkwood Power House
Sim2 <- df$Kirkwood #selecting my simulated data
Obs2 <- df2$Kirkwood2 #selecting my observed data
ma2 <- model.assess(Sim2, Obs2)

#Don Pedro Power House
Sim3 <- df$DonPedro #selecting my simulated data
Obs3 <- df2$DonPedro2 #selecting my observed data
ma3 <- model.assess(Sim3, Obs3)
#Dior R Holm Power House
Sim4 <- df$DiorRH #selecting my simulated data
Obs4 <- df2$DiorRH2 #selecting my observed data
ma4 <- model.assess(Sim4, Obs4)

statis <- cbind(ma, ma2[,2], ma3[,2],ma4[,2])

colnames(statis) <- c("Performance Statistics", "Moccasin PH","Kirkwood PH", "Don Pedro PH", "Dion R Holm PH")

library(sjPlot)
stat_table <- tab_df(statis, 
                     title = "Comparison of the Simulated with Observed data")


stat_table
```
