---
title: "GCMs_download"
author: "Gustavo Facincani Dourado"
date: "8/2/2020"
output: html_document
---

```{r}
init_year <- 2030
end_year <- 2060

climate_scenario <- 'CanESM2'
  variables <- c('ET','Tair','baseflow','precip','rainfall','runoff','snow_melt','snowfall','tot_runoff')
 study_path <- 'http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/'

  for (i in variables) {
	folder = toString(study_path, climate_scenario, rcp, sep="/")
	save_path = toString(study_path, climate_scenario, rcp, i, sep="/")
	for (year in range(init_year,end_year+1)){
		data_file = toString(variable, ".", toString(year),".v0.CA_NV.nc",sep="/")
		path = toString(folder, data_file, sep="/")
		print('now downloading: ', path, sep="/")
		testfile = urllib.URLopener()
		testfile.retrieve(path, save_path,data_file, sep="/")
  }
```



```{r}
#download_nc <- function(model, rcp, variable){

year <- c(2006:2100)

model <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
#YearStart <- "2006" #earliest year for GCM data
#YearStop<- "2100" #latest year for GCM data
rcp <- c("rcp45", "rcp85") #emission scenarios
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest


for (year in years) {
#  for(model in models){
 #   for(rcp in rcps){
  #    for(variable in variables){
ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",model,"/",rcp,"/",variable,".",year,".v0.CA_NV.nc")

#newdir <- paste0("C:/Users/gusta/Desktop/PhD/CERCWET/")
#dir.create(newdir)      # should test for error
#    cwd <- getwd()          # CURRENT dir
 #   setwd(newdir) 
download.file(url=ncdfURL,destfile=paste0(newdir,"/", model,"_",rcp,"_",variable,"_",year,"_","CA_NV.nc"), mode = "wb")
setwd(cwd)
}#}}}


#}
```
download.file(url=fullurl, destfile=paste0("somedata/CALADAPT/projected_data_monthly/", ccmods[[c]], "/", ccscenario[[s]], "/", varofinterest[[v]], "/", varofinterest[[v]], "_month_", ccmods[[c]], "_", ccscenario[[s]], "_", time[[t]], "-", month[[m]], ".v0.CA_NV.tif"), method="curl")


```{r}
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest

modelMat <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs

rcp <- c("rcp45", "rcp85") #emission scenarios

lapply(modelMat, download_nc, rcp=rcp, variable=variable)

```



```{r}
download_nc <- function(model, rcp, variable){

year <- c(2006:2100)

model <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
#YearStart <- "2006" #earliest year for GCM data
#YearStop<- "2100" #latest year for GCM data
rcp <- c("rcp45", "rcp85") #emission scenarios
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest


for (i in seq_along(year)) {
ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",model,"/",rcp,"/",variable,".",i,".v0.CA_NV.nc")

for(a in seq_along(model)){
  for(b in seq_along(rcp)){
newdir <- setwd("C:/Users/gusta/Desktop/PhD/CERCWET/")
newdir2 <- dir.create(newdir,a,b)}}

#dir.create(newdir)      # should test for error
#    cwd <- getwd()          # CURRENT dir
#    setwd(newdir) 
    for(a in seq_along(model)){
  for(b in seq_along(rcp)){
files <- paste0(a,"_",b,"_",variable,"_",i,"_","CA_NV.nc")}}
#for(a in model){
 # for(b in rcp){
  #  for(c in variable){
for (file in seq_along(files)) {
download.file(url=ncdfURL,destfile= paste(file),mode = "wb")
#setwd(cwd)
}
}
}
```

```{r}
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest

modelMat <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs

rcp <- c("rcp45", "rcp85") #emission scenarios

lapply(modelMat, download_nc, rcp=rcp, variable=variable)

```

```{r}
#download_nc <- function(model, rcp, variable){

year <- c(2006:2100)

model <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
#YearStart <- "2006" #earliest year for GCM data
#YearStop<- "2100" #latest year for GCM data
rcp <- c("rcp45", "rcp85") #emission scenarios
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest


for (i in year) {
ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",model,"/",rcp,"/",variable,".",i,".v0.CA_NV.nc")

for(a in model){
  for(b in rcp){
#newdir <- paste0("C:/Users/gusta/Desktop/PhD/CERCWET/",a,"_",b,"_",variable,"_",i,"_","CA_NV.nc")
#newdir2 <- dir.create(newdir,a,b)}}
      # should test for error
#    cwd <- getwd()          # CURRENT dir
#    setwd(newdir) 
    for(a in model){
  for(b in rcp){
#files <- paste0(a,"_",b,"_",variable,"_",i,"_","CA_NV.nc")}}
newdir <- paste0("C:/Users/gusta/Desktop/PhD/CERCWET/",a,"_",b,"_",variable,"_",i,"_","CA_NV.nc")
dir.create(newdir)
cwd <- getwd()          # CURRENT dir
setwd(newdir) 
#for(a in model){
 # for(b in rcp){
  #  for(c in variable){
for (file in files) {
#download.file(url=ncdfURL,destfile= paste0(newdir, "/",file),mode = "wb")

  }
}}

func.download_files <- function(link) {

  download.file(url=link,destfile= paste0(newdir2),mode = "wb")
   
}
}}}
mapply(FUN = func.download_files,link=ncdfURL)
setwd(cwd)
#}
```
```{r}
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest

modelMat <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs

rcp <- c("rcp45", "rcp85") #emission scenarios

lapply(modelMat, download_nc, rcp=rcp, variable=variable)

```


```{r}
download_nc <- function(model, rcp, variable){
  year <- c(2006:2100)
  
  ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",rep(model, length(model)),"/",rep(rcp, length(rcp)),"/",rep(variable, length(variable)), ".",rep(year, length(year)),".v0.CA_NV.nc")
  
  dest <-  paste0("C:/Users/gusta/Desktop/PhD/CERCWET/",rep(model, length(model)),"/",rep(rcp, length(rcp)),sep="")
                 #,"/",rep(variable, length(variable)),"_",rep(year, length(year)),"_","CA_NV.nc", sep="")
  dir.create(dest)
 
 #  download.file(url=ncdfURL,destfile=dest, mode = "wb")
  Map(function(u, d) download.file(u, d, mode="wb"), ncdfURL, dest)

}
```

```{r}
modelMat <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
YearStart <- "2006"
YearStop<- "2100"
rcp <- c("rcp45", "rcp85")
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "snow_melt", "snowfall", "tot_runoff")

lapply(modelMat, download_nc, rcp=rcp, variable=variable)
```


```{r}
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "runoff", "SWE", "snow_melt", "snowfall", "tot_runoff") #variables of interest

modelMat <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs

rcp <- c("rcp45", "rcp85") #emission scenarios

lapply(modelMat, download_nc, rcp=rcp, variable=variable)

```


```{r}
#working on this
download_nc <- function(model, rcp, variable){
  year <- c(2006:2100)
  

  ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",rep(model, length(model)),"/",rep(rcp, length(rcp)),"/",rep(variable, length(variable)), ".",rep(year, length(year)),".v0.CA_NV.nc")
  
  neway<-paste0("C:/Users/gusta/Desktop/PhD/CERCWET/",rep(model, length(model)),"/",rep(rcp, length(rcp)),"/",rep(variable, length(variable)), ".",rep(year, length(year)),".v0.CA_NV.nc") 

  dest <-  paste0(rep(model, length(model)),"/",rep(rcp, length(rcp)),"/",rep(variable, length(variable)), ".",rep(year, length(year)),".v0.CA_NV.nc")
#  dir.create(dest)
 
   download.file(url=ncdfURL,destfile=dest, mode = "wb")
 # Map(function(u, d) download.file(u, d, method = "libcurl", quiet = TRUE), ncdfURL, dest)

}
```

```{r}
models <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
YearStart <- "2006"
  year <- c(2006:2100)
YearStop<- "2100"
rcp <- c("rcp45", "rcp85")
variable <- c("ET", "Tair", "baseflow", "precip", "rainfall", "SWE", "runoff", "snow_melt", "snowfall", "tot_runoff")

lapply(models, download_nc, rcp=rcp, variable=variable)
```


```{r}
#working on this
#download_nc <- function(models, rcps, variables){
  years <- c(2006:2100)
GCMs_loca <- "http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/"
GCM_dir <- paste(GCMs_loca,model,"/",rcp,"/",variable, ".",year, sep = "")
setwd("C:/Users/gusta/Desktop/PhD/CERCWET/") 

models <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
rcps <- c("rcp45", "rcp85")
variables <- c("ET", "Tair", "baseflow", "precip", "rainfall", "SWE", "runoff", "snow_melt", "snowfall", "tot_runoff")
  
for(year in years) {
  for(variable in variables) {
    for(rcp in rcps){
      for(model in models) {
#  ncdfURL <- paste0("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/",model,"/",rcp,"/",variable, ".",year,".v0.CA_NV.nc", sep = "")



#  dest <-  paste0(~model,"/",rcp,"/",variable, ".",year,".v0.CA_NV.nc", sep = "")
#  dir.create(dest)
filenames <- paste(variable, ".",year, ".v0.CA_NV.nc", sep="" )
	#determine the GCM and RCP directory
for(i in filenames) {
		pth <- paste( "./", model,"/", rcp,"/", sep = "")
		#if the directory doesn't exist, make it!
#		if (!file.exists(pth)){
#			dir.create(pth)
		}

 #  download.file(url=ncdfURL,destfile=dest, mode = "wb")
 # Map(function(u, d) download.file(u, d, mode = "wb"), ncdfURL, dest)
	download.file( paste( GCM_dir , i , sep="" ) , paste( "./", model,"/", rcp,"/" , i, sep="" ) , mode="wb" )

      }}}}
#}
```

```{r}
library(rvest)
library(stringr)
page <- xml2::read_html("http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/")

page %>%
  html_nodes("a") %>%       # find all links
  html_attr("href") %>%     # get the url
  str_subset("\\.nc")   # look at the first one
```

```{r}
 url <- "http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/ACCESS1-3/rcp45/"
doc <- read_html(url)
href <- html_attr(html_nodes(doc, "a"), "href")[[2]]

href
```


```{r}
setwd("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs")

#main NHIS FTP directory with documentation
nhis_doc_ftp <- "ftp://ftp.cdc.gov/pub/Health_Statistics/NCHS/Dataset_Documentation/NHIS/"

#loop through 1963 - 2010
for ( year in 1963:1964 ){

	#create the full string to the FTP folder of the current year
	year_ftp_dir <- paste( nhis_doc_ftp , year , "/" , sep="" )
	
	#figure out what all of the files within that folder are named
	filenames <- getURL( year_ftp_dir , dirlistonly=T )
	filenames1 <- tolower( strsplit(filenames, "\r*\n")[[1]] )
	
	#as written, the program downloads EVERY file in each year's directory
	#however, if you only want to download files with "person" or "core" in their filename
	#uncomment this line..
	#save only the files with the word "person" or "core" in them
	filenames2 <- filenames1[ grepl("person" , filenames1) | grepl("core" , filenames1) ]
	print(filenames)}
```
	#loop through all of those files and save them to your working directory
	for ( i in filenames ){ 
	
		#determine the year directory
		pth <- paste( "./" , year , "/" , sep="" )
		#if the directory doesn't exist, make it!
		if (!file.exists(pth)){
			dir.create(pth)
		}

		download.file( paste( year_ftp_dir , i , sep="" ) , paste( "./" , year , "/" , i , sep = "" ) , mode="wb" )
	}	
}


```{r}
library(RCurl)    

#set your output folder
#setwd("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs")

GCMs_loca <- "http://albers.cnr.berkeley.edu/data/scripps/loca_vic-output/"

rcps <- c("rcp45", "rcp85")
variables <- c("ET", "Tair")#, "baseflow", "precip", "rainfall", "SWE", "runoff", "snow_melt", "snowfall", "tot_runoff")
GCMs <- c(#"CanESM2", "CNRM-CM5", "HadGEM2-ES","MIROC5"  these we already have
              "ACCESS1‐0","CCSM4", "CESM1-BGC","CMCC-CMS","GFDL-CM3","HadGEM2-CC")#all 10 GCMs
#loop through 2006-2099

for (GCM in GCMs){
  for(rcp in rcps) {
    for(variable in variables) {
      for ( year in 2006:2007){
      GCM_dir <- paste(GCMs_loca,GCM,"/",rcp,"/", sep = "")

doc <- read_html(GCM_dir)
filenames <- html_attr(html_nodes(doc, "a"), "href")
filenames2 <- filenames[ grepl("ET.2" , filenames) | grepl("Tair" , filenames)| grepl("baseflow" , filenames) | grepl("precip" , filenames) | grepl("rainfall" , filenames) | grepl("SWE" , filenames) | grepl("runoff" , filenames) | grepl("snow_melt" , filenames) | grepl("snowfall" , filenames) | grepl("tot_runoff" , filenames)]

#print(filenames)
#print(filenames2)


        
	#loop through all of those files and save them to your working directory
	for ( i in filenames2 ){ 
	
		#determine the GCM and RCP directory
		pth <- paste( "C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/", GCM,"/", rcp,"/" , sep="" )
		#if the directory doesn't exist, make it!
		if (!dir.exists(pth)){
			dir.create(file.path(pth), recursive = TRUE)
		}

		download.file( paste( GCM_dir , i , sep="" ) , paste("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/", GCM,"/", rcp,"/" , i, sep="" ) , mode="wb" )
	}	

    }}}}
  
  
```