---
title: "Gridplots"
author: "Gustavo Facincani Dourado"
date: "5/15/2020"
output: html_document
---

```{r}
library(hydroGOF)

stat_poly_eq(formula = "y~x", #adding equation
             aes(label = paste0(..eq.label..)), 
             parse = TRUE, label.x.npc = "center", label.y.npc = 0.97, size = 3.45, family= "Times New Roman")+
     stat_poly_eq(formula = "y~x", #adding R squared
             aes(label = paste0(..rr.label..)), 
             parse = TRUE, label.x.npc = 0.95, label.y.npc = 0.05, size = 3.45, family= "Times New Roman")+
```

```{r}
#Merced full dataset
MRC.full <- dataset %>%
  filter(StationID == "MRC") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
  scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "15 years",
                  date_labels = "%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

MRC.full + facet_wrap(~ Month, ncol=4, scales = "free") +
  
  png("mer_montlhy_timeseries.png", units ="in", width=8, height=5, res = 300)



```

```{r}
#Stanislaus full dataset
SNS.full <- dataset %>%
  filter(StationID == "SNS") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "15 years",
                  date_labels = "%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Stanislaus River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SNS.full + facet_wrap(~ Month, ncol=4, scales = "free") +
  
  png("stn_montlhy_timeseries.png", units ="in", width=8, height=5, res = 300)

```

```{r}
#Tuolumne full data set
TLG.full <- dataset %>%
  filter(StationID == "TLG") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "15 years",
                  date_labels = "%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title= "Tuolumne River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

TLG.full + facet_wrap(~ Month, ncol=4, scales = "free") +
  
  png("tuo_montlhy_timeseries.png", units ="in", width=8, height=5, res = 300)

```

```{r}
#Upper San Joaquin full data set
SJF.full <- dataset %>%
  filter(StationID == "SJF") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "15 years", 
                  date_labels = "%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
   scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title= "Upper San Joaquin River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SJF.full + facet_wrap(~ Month, ncol=4, scales = "free") +
  
  png("usj_montlhy_timeseries.png", units ="in", width=8, height=5, res = 300)
```

```{r}
note <- data.frame(x = c(as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01")),
                   y = c(1.15, 1.15, 1.15, 1.15), #adding where to add text 
                   label = c(paste(MRC.ma), paste(SJF.ma), paste(SNS.ma), paste(TLG.ma)),
                   StationID = c("MRC", "SJF", "SNS", "TLG"))

note2 <- data.frame(x = c(as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01")),
                   y = c(1.15, 1.15, 1.15, 1.15), #adding where to add text 
                   label = c(paste(MRC.ma2), paste(SJF.ma2), paste(SNS.ma2), paste(TLG.ma2)),
                   StationID = c("MRC", "SJF", "SNS", "TLG"))

```

```{r}
#adding manually results of statistical tests
#all basins

ggplot(dataset) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#56B4E9"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#E69F00")) +
       scale_y_continuous(limits = c(0, 1.28),
         expand = c(0, 0)) +
     scale_x_date(date_labels = "%b/%Y",
                  breaks = c(as.Date("1950-10-01"), as.Date("1960-10-01"), as.Date("1970-10-01"), as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
                 #limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
   scale_color_identity(name = element_blank(),
                         breaks = c("#56B4E9", "#E69F00"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(x = element_blank(), 
       y = "Monthly full natural flow (MAF)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) + #center the title
  
  geom_text(note, #adding where to add text 
              mapping = aes(x=x, y=y, label = label), size=3, family= "Times New Roman") + #adding manually results of statistical tests
  
  facet_wrap(~ StationID, ncol=1, scales= "free_y",  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
  
png("allbasins_timeseries3.png", units ="in", width=8, height=5, res = 300)
```


note <- data.frame(x = c(as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01")),
                   y = c(1.15, 1.15, 1.15, 1.15), #adding where to add text 
                   label = c(paste(MRC.ma), paste(SJF.ma), paste(SNS.ma), paste(TLG.ma)),
                   StationID = c("MRC", "SJF", "SNS", "TLG"))

#adding manually results of statistical tests

```{r}

#Scatterplot

ggplot(dataset, aes(x=Obs_flow, y=Sim_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(alpha = 0.5) +
  geom_point(aes(x=Sim_flow, y=Obs_flow), alpha=0)+
  stat_smooth(method = "lm", se = TRUE) +
  scale_y_continuous(expand = c(0, 0)) +
     scale_x_continuous(expand = c(0, 0)) + 
  labs(x = "Obserced (CDEC)", 
       y = "Simulated(Livneh)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) + #center the title
  facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))  +
   stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               label.x.npc = 0.95, label.y.npc = 0.1,
               formula = formula, parse = TRUE, size = 4.5, family= "Times New Roman")
```
  
```{r}
#Annual Scatterplot

ggplot(dataset, aes(x=Obs_flow, y=Sim_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(alpha = 0.5) +
  geom_point(aes(x=Sim_flow, y=Obs_flow), alpha=0)+
  stat_smooth(method = "lm", se = TRUE) +
  scale_y_continuous(expand = c(0, 0)) +
     scale_x_continuous(expand = c(0, 0)) + 
  labs(x = "Obserced (CDEC)", 
       y = "Simulated(Livneh)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) + #center the title
  facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))  +
   stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               label.x.npc = 0.95, label.y.npc = 0.1,
               formula = formula, parse = TRUE, size = 4.5, family= "Times New Roman")
```

png("allbasins_scatterplot.png", units ="in", width=5, height=5, res = 300)


```{r}
#Annual scatter plot USJ
dataset %>%
  filter(StationID == "SJF") %>%
ggplot(aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=13.5, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
   geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  geom_point(aes(Obs_flow, Sim_flow), alpha = 0.3)+
  scale_x_continuous(limits = c(0,1.4),
                     n.breaks = 4) +
  scale_y_continuous(limits = c(0,1.4),
                     n.breaks = 4) +
 labs(title = "Upper San Joaquin River",
   x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis
  
      stat_smooth(aes(x = Obs_flow, y = Sim_flow), 
                method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) + 
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..eq.label..)), 
             parse = TRUE, label.x.npc = "center", label.y.npc = 0.97, size = 4, family= "Times New Roman")+
     stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..rr.label..)), 
             parse = TRUE, label.x.npc = 0.95, label.y.npc = 0.05, size = 4, family= "Times New Roman")+
  
#  annotate("text", x = 0, y = 1.3, label = paste0(model.assess(dataset$Sim_flow, dataset$Obs_flow)),  collapse = "\n", hjust = 0, size=2.4, family= "Times New Roman") +
  
   facet_wrap(~ Month, ncol=4,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +

  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) + 
  png("usj_monthly_scatterplot.png", units ="in", width=8, height=7, res = 300)
```

```{r}
#Annual scatter plot STN
dataset %>%
  filter(StationID == "SNS") %>%
ggplot(aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=13.5, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(aes(Obs_flow, Sim_flow), alpha = 0.3)+
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_continuous(limits = c(0, 0.7),
                     n.breaks = 4) +
  scale_y_continuous(limits = c(0, 0.7),
                     n.breaks = 4) +
 labs(title = "Stanislaus River",
   x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
    stat_smooth(aes(x = Obs_flow, y = Sim_flow), 
                method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) + 
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..eq.label..)), 
             parse = TRUE, label.x.npc = "center", label.y.npc = 0.97, size = 4, family= "Times New Roman")+
     stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..rr.label..)), 
             parse = TRUE, label.x.npc = 0.95, label.y.npc = 0.05, size = 4, family= "Times New Roman")+
   facet_wrap(~ Month, ncol=4,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +
  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
      
png("stn_monthly_scatterplot.png", units ="in", width=8, height=7, res = 300)
```

```{r}

```

```{r}
#Annual scatter plot TUO
dataset %>%
  filter(StationID == "TLG") %>%
ggplot(aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=13.5, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(aes(Obs_flow, Sim_flow), alpha = 0.3)+
    geom_point(aes(Sim_flow, Obs_flow), alpha = 0)+
   geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  scale_x_continuous(limits = c(0, 1.5),
                     n.breaks = 4) +
  scale_y_continuous(limits = c(0, 1.5),
                     n.breaks = 4) +
 labs(title = "Tuolumne River",
   x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis
  
    stat_smooth(aes(x = Obs_flow, y = Sim_flow), 
                method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) + 
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..eq.label..)), 
             parse = TRUE, label.x.npc = "center", label.y.npc = 0.97, size = 4, family= "Times New Roman")+
     stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..rr.label..)), 
             parse = TRUE, label.x.npc = 0.95, label.y.npc = 0.05, size = 4, family= "Times New Roman")+
   facet_wrap(~ Month, ncol=4,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +
  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +

  png("tuo_monthly_scatterplot.png", units ="in", width=8, height=7, res = 300)
```

```{r}
#Annual scatter plot MER

dataset %>%
  filter(StationID == "MRC") %>%
ggplot(aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=13.5, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(aes(Obs_flow, Sim_flow), alpha = 0.3)+
   geom_abline(intercept = 0, slope = 1, linetype = "dashed") +

  scale_x_continuous(limits = c(0, 0.7),
                     n.breaks = 4) +
  scale_y_continuous(limits = c(0, 0.7),
                     n.breaks = 4) +
 labs(title = "Merced River",
   x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
    stat_smooth(aes(x = Obs_flow, y = Sim_flow), 
                method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) + 
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..eq.label..)), 
             parse = TRUE, label.x.npc = "center", label.y.npc = 0.97, size = 4, family= "Times New Roman")+
     stat_poly_eq(formula = "y~x", 
             aes(label = paste0(..rr.label..)), 
             parse = TRUE, label.x.npc = 0.95, label.y.npc = 0.05, size = 4, family= "Times New Roman")+
   facet_wrap(~ Month, ncol=4,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +
  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))

png("mer_monthly_scatterplot.png", units ="in", width=8, height=7, res = 300)
```

```{r}
#Annual scatter all basins
ggplot(dataset, aes(x = Obs_annual_flow, y = Sim_annual_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(aes(x = Obs_annual_flow, y = Sim_annual_flow), alpha = 0.1)+ 
    geom_point(aes(x = Sim_annual_flow, y = Obs_annual_flow), alpha = 0)+ 
 labs(x = "Observed - CDEC (MAF)", 
       y = "Simulated - Livneh (MAF)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
    stat_smooth(aes(x = Obs_annual_flow, y = Sim_annual_flow), method = "lm", se = TRUE, colour="#FC4E07") +
    scale_y_continuous(expand = c(0.005, 0.005)) +
     scale_x_continuous(expand = c(0.005, 0.005)) +
  theme(aspect.ratio = 1,
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
     stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~~")), 
               label.x.npc = 0.95, label.y.npc = 0.1,
               formula = formula, parse = TRUE, size = 4.5, family= "Times New Roman") +
     facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "free") +
png("allbasins_annual_scatterplot.png", units ="in", width=5, height=5, res = 300)
```

```{r}
formula <- dataset$Sim_annual_flow ~ dataset$Obs_annual_flow
library(ggpmisc)
#Annual scatter plot for all basins
ggplot(dataset, aes(x = Obs_annual_flow, y = Sim_annual_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(aes(x = Obs_annual_flow, y = Sim_annual_flow), alpha = 0.1)+ 
    geom_point(aes(x = Sim_annual_flow, y = Obs_annual_flow), alpha = 0)+ 
 labs(x = "Observed - CDEC (MAF)", 
       y = "Simulated - Livneh (MAF)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
    geom_smooth(aes(x = Obs_annual_flow, y = Sim_annual_flow), method = "lm", se = TRUE, colour="#FC4E07", fullrange=TRUE) +
    scale_y_continuous(expand = c(0,0)) +
     scale_x_continuous(expand = c(0,0)) +
  theme(aspect.ratio = 1,
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
     facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "free") +
#  stat_smooth_func(geom="text", 
#                   method = "lm", 
#                   hjust=0,parse=TRUE,
#                   label.x.npc = 0.95, label.y.npc = 0.1,
#                   size = 3, family= "Times New Roman")+
   stat_poly_eq(formula = formula, parse = TRUE, 
               mapping = aes(label = stat(rr.label)))  +
#               label.x.npc = "right", label.y.npc = 0.15,
               
  xlim(NA, 5) +
  ylim(NA, 5) +
 png("allbasins_annual_scatterplot.png", units ="in", width=5, height=5, res = 300)
```

```{r}
SNS.sim2 <- SNS.sim %>% mutate(StationID = "SNS")
  
TLG.sim2 <-  TLG.sim %>% mutate(StationID = "TLG")

SJF.sim2 <- SJF.sim  %>% mutate(StationID = "SJF")

MRC.sim2 <- MRC.sim  %>% mutate(StationID = "MRC")

Obs2 <- rbind(SNS.obs, TLG.obs, SJF.obs, MRC.obs) %>%
  mutate(Class = "Observed") %>%
  select(StationID, DateTime, Value, Class) %>%
  dplyr::rename(Date = DateTime, Flow = Value)
Obs2

Sim2 <- rbind(SNS.sim2, TLG.sim2, SJF.sim2, MRC.sim2)%>%
  mutate(Class = "Simulated") %>%
    dplyr::rename(Date = date, Flow = flow)
Sim2

dataset2 <- rbind(Sim2, Obs2)  %>% 
  mutate(Date = as.Date(Date, format = "%Y/%m/%d"),
         Month = as.factor(format(as.Date(Date, format = "%Y/%m/%d"), "%B")),
         Year = as.Date(cut(Date, breaks = "year")), #create year column to facilitate plotting
         Class = as.factor(dataset2$Class))
dataset2
```

```{r}
head(dataset)
```


```{r}
melteddataset <- melt(dataset,id.vars= c('StationID', 'Date', 'Month', 'Year'), measure.vars=c('Obs_flow','Sim_flow'), value.name = "Flow")
melteddataset

meltedannual <- melt(dataset,id.vars= c('StationID', 'Date', 'Month', 'Year'), measure.vars=c('Obs_annual_flow','Sim_annual_flow'), value.name = "Flow")
meltedannual
```


#Selecting only the data that is interesting
dataset2 <- as.data.frame(fulldataset[c("StationID", "DateTime", "Value", "flow")] %>%
  ungroup %>%
  rename(Sim_flow = flow, Obs_flow = Value, Date = DateTime) %>%
  mutate(Date = as.Date(Date, format = "%Y/%m/%d")) %>%
  mutate(Month = format(as.Date(Date, format = "%Y/%m/%d"), "%B")) %>%
  mutate(Year = as.Date(cut(dataset$Date, breaks = "year"))) %>% #create year column to facilitate plotting
  group_by(Year, StationID) %>%
    mutate(Obs_annual_flow = sum(Obs_flow)) %>%
    mutate(Sim_annual_flow = sum(Sim_flow)))


```{r}
wtr_yr <- function(dates, start_month=10) {
  # Convert dates into POSIXlt
  dates.posix = as.POSIXlt(dates)
  # Year offset
  offset = ifelse(dates.posix$mon >= start_month - 1, 1, 0)
  # Water year
  adj.year = dates.posix$year + 1900 + offset
  # Return the water year
  adj.year
}

datasetWY <- dataset2 %>%
  mutate(wtr_yrVAR=factor(wtr_yr(Date))) %>%
  mutate(CDdate= as.Date(as.numeric(Date - as.Date(paste0(wtr_yrVAR,"-10-01"))), origin = "1950-10-01"))

datasetWY %>%  ggplot(aes(x =CDdate, y=Flow, group = Year, color = Class)) +
  geom_boxplot() + theme_bw()+scale_x_date(date_breaks = "1 year", date_labels = "%Y")+theme_bw()
```


```{r}
ggplot(dataset2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes(x = Date, y = Flow, group = Class, fill = Class), outlier.size = 0.7)+ #plot monthly observed data in greenish blue
  scale_fill_manual(labels = c("Observed full natural flow (CDEC)", "Simulated full natural flow (Livneh)"), values=c("#56B4E9", "#E69F00")) +
scale_y_continuous(limits = c(0, 1.28),
         expand = c(0, 0)) +
     scale_x_date(date_labels = "%Y",
                  breaks = c(as.Date("1950-10-01"), as.Date("1960-10-01"), as.Date("1970-10-01"), as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
                  expand = c(0, 0)) + #removes blank space
  labs(x = element_blank(), 
       y = "Monthly full natural flow (MAF)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19))+
  
  geom_text(note, #adding where to add text 
              mapping = aes(x=x, y=y, label = label), size=3, family= "Times New Roman") + #adding manually results of statistical tests
  
  facet_wrap(~ StationID, ncol=1, scales= "free_y",  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
  
png("allbasins_total_boxplot.png", units ="in", width=8, height=5, res = 300)

```

```{r}
dataset %>%
  group_by(StationID) %>%
  summarise(pbiastotal = mean(pbias_monthly))

model.assess(TLG.sim$flow, TLG.obs$Value)

p <- dataset %>%
  filter(StationID == "TLG") %>%
 mutate(p = 100 *sum(dataset$Sim_flow - dataset$Obs_flow)/sum(dataset$Obs_flow))
p
```

```{r}
test_table <- dataset %>%
  group_by(StationID, Month) %>%
  dplyr::summarize(pbias = mean(pbias_monthly),
            nse = mean(nse_monthly),
            rsr = mean(rsr_monthly)) 

#write_csv(test_table, "tests_allbasins.csv", append=FALSE, col_names=TRUE)
```

```{r}
ggplot(dataset2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes(x = Date, y = Flow, group = interaction(Year, Class), fill = Class), outlier.size = 0.7)+ #plot monthly observed data in greenish blue
  scale_fill_manual(labels = c("Observed full natural flow (CDEC)", "Simulated full natural flow (Livneh)"), values=c("#56B4E9", "#E69F00")) +
scale_y_continuous(limits = c(0, 1.28),
         expand = c(0, 0)) +
     scale_x_date(date_labels = "%Y",
                  breaks = c(as.Date("1950-10-01"), as.Date("1960-10-01"), as.Date("1970-10-01"), as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
                  expand = c(0, 0)) + #removes blank space
  labs(x = element_blank(), 
       y = "Monthly full natural flow (MAF)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19))+
  
  geom_text(note, #adding where to add text 
              mapping = aes(x=x, y=y, label = label), size=3, family= "Times New Roman") + #adding manually results of statistical tests
  
  facet_wrap(~ StationID, ncol=1, scales= "free_y",  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
  
png("allbasins_boxplot.png", units ="in", width=8, height=5, res = 300)
```


```{r}
#not used
ggplot(dataset, aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes(x = Obs_flow, y = Sim_flow, group = Year), alpha = 0.1)+ 
 labs(x = "Observed - CDEC (MAF)", 
       y = "Simulated - Livneh (MAF)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
    stat_smooth(aes(x = Obs_annual_flow, y = Sim_annual_flow), method = "lm", se = TRUE, colour="#FC4E07") +
    scale_y_continuous(expand = c(0.005, 0.005)) +
     scale_x_continuous(expand = c(0.005, 0.005)) +
  theme(strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
     stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~~")), 
               label.x.npc = 0.95, label.y.npc = 0.1,
               formula = formula, parse = TRUE, size = 4.5, family= "Times New Roman") +
     facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"))) 
#png("allbasins_annual_boxplot.png", units ="in", width=5, height=5, res = 300)
```


ggplot(datos, aes(x = corriente, y = dosis, colour = cristal)) +    
geom_point() + 
geom_smooth(method="lm", se=F, formula=my.formula) +
stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), formula = my.formula, parse = TRUE) +
facet_wrap(~datos$cristal)

ggplot(datos, aes(x = corriente, y = dosis, colour = cristal)) +
geom_point() +
geom_smooth(method="lm", se=F, formula=my.formula) +
stat_poly_eq(aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), formula = my.formula, parse = TRUE, label.y = 0.9) +
ylim(0, 1) +
facet_wrap(~datos$cristal)


```{r}
#Flow Duration Curve
FDC <- dataset %>%
    group_by(StationID) %>%
  mutate(Obs_flow = sort(Obs_flow),
         Obs_annual_flow = sort(Obs_flow),
         Sim_flow = sort(Sim_flow),
         Sim_annual_flow = sort(Sim_flow),
         Rank = sequence(rle(as.character(StationID))$lengths),
         Perc_Exc = (1-Rank/(sum(nrow(dataset))/4))*100)
FDC
```

```{r}
FDC_annual <- FDC %>%
  group_by(StationID, Year) %>%
  summarize(Obs_annual_flow = mean(Obs_annual_flow),
            Sim_annual_flow = mean(Sim_annual_flow)) %>%
  mutate(Rank = sequence(rle(as.character(StationID))$lengths),
                 Perc_Exc = (1-Rank/(sum(nrow(FDC_annual))/4))*100)
         
FDC_annual
```

```{r}
#Monthly flow duration curve
ggplot(FDC) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Perc_Exc, y = Obs_flow, colour = "#00AFBB"))+
  geom_line(aes(x = Perc_Exc, y = Sim_flow, colour = "#FC4E07")) +
    scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed full natural flow (CDEC)","Simulated full natural flow (Livneh)"), #select the variables
                          guide = "legend")+
 labs(x = "Exceedance Probability", 
       y = "Discharge(MAF/Year)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
     scale_x_continuous(expand = c(0.005, 0.005),
                        breaks = c(0, 20,40, 60, 80),
                     labels = c('0%', '20%', '40%', '60%', '80%')) +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) + #center the title
       facet_wrap(~StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"), scales = "free")) 
    
  png("allbasins_montlhy_FDC.png", units ="in", width=5, height=5, res = 300)
```


```{r}
#Annual flow duration curve
ggplot(FDC_annual) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Perc_Exc, y = Obs_annual_flow, colour = "#00AFBB"))+
  geom_line(aes(x = Perc_Exc, y = Sim_annual_flow, colour = "#FC4E07")) +
    scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed full natural flow (CDEC)","Simulated full natural flow (Livneh)"), #select the variables
                          guide = "legend")+
 labs(x = "Exceedance Probability", 
       y = "Discharge(MAF/Year)") + #name of x axis
  theme(plot.title = element_text(hjust = 0.5)) +
     scale_x_continuous(expand = c(0.005, 0.005),
                        breaks = c(0, 20,40, 60, 80, 100),
                     labels = c('0%', '20%', '40%', '60%', '80%', '100%')) +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) + #center the title
       facet_wrap(~StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River"), scales = "free")) +
    
  png("allbasins_annual_FDC.png", units ="in", width=5, height=5, res = 300)
```

```{r}

```