---
title: "Howerwork_3"
author: "Gustavo Facincani Dourado"
date: "2/12/2020"
output: html_document
---

Exercise 4.

```{r}
#Getting the data 

library(tidyverse)
LakeErie <- read_csv("C:/Users/gusta/Desktop/PhD/Classes/ES207/LakeErie1.csv")

head(LakeErie)
```

```{r}
#Comands for testing the TP distribution:

ggplot(data=as.data.frame(qqnorm(LakeErie$TP , plot=F)), mapping=aes(x=x, y=y)) + geom_point() + geom_smooth(method="lm", se=FALSE)

```
TP does not match the normal distribution, requiring non-parametric tests.
```{r}

#Comands for testing the chla distribution:

qqnorm(log(LakeErie$chla))
qqline(log(LakeErie$chla), col = 'red')

```
The chlorophil A distribution is close to normal, but not normal even in log scale, being a little bit skewed.

```{r}
#Comands to plot TP data using lattice


library(lattice)
qqmath(~TP | factor(Year), data = LakeErie, distribution = qnorm, panel = function(x, ...){
    panel.qqmath(x, ...)
    panel.qqmathline(x, ...)
}) 
       f.value = ppoints(100)
qqmath(~TP | TP, LakeErie, groups = Year, aspect = "xy",
       f.value = ppoints(100), auto.key = list(space = "right"))
xlab = "QNorm",
ylab = "TP")
```
The only year that can be plotted is 2013, as the others have no data and the data is still skewed.

```{r}
#Comands to plot chla data using lattice

library(lattice)
qqmath(~chla | factor(Year), data = LakeErie, distribution = qnorm, panel = function(x, ...){
    panel.qqmath(x, ...)
    panel.qqmathline(x, ...)
}) 
       f.value = ppoints(100))
qqmath(~chla | TP, LakeErie, groups = Year, aspect = "xy",
       f.value = ppoints(100), auto.key = list(space = "right")),
xlab = "QNorm",
ylab = "chla")
```
<span style="color: green"> All years have data that are still skewed.</span>

Exercise 3.1. Helsel & Hirsch

```{r}
#Getting granodiorite data

x <- c(6.0, 0.5, 0.4, 0.7, 0.8, 6.0, 5.0, 0.6, 1.2, 0.3, 0.2, 0.5, 0.5, 10, 0.2, 0.2, 1.7, 3.0 )
x

```

Non-parametric 95% interval

<span style="color: green"> The granodiorite is a small set of data (18 samples), using the equations R l =  x' + 1 and Ru =  n − x' = x . </span>

