---
title: "Livneh vs Observed"
author: "Gustavo Facincani Dourado"
date: "5/14/2020"
output: html_document
---

```{r}
library(tidyverse, quietly = TRUE)
library(readr, quietly = TRUE)
library(extrafont)
library(ggplot2, quietly = TRUE)
library(ggthemes, quietly = TRUE)
library(stringr, quietly = TRUE)
library(grid)
library(ggpubr)
library(scales)
library(ggpmisc)
library(gridExtra)
library(cder)
library(lubridate)
library(dplyr)
library(eia)

#Color blind 
#cbbPalette <- c("#000000" #black, #999999 #grey, "#E69F00" #orange, "#56B4E9" blue, "#009E73" #green, "#F0E442" #yellow, "#0072B2" #darkblue, "#D55E00" #red, "#CC79A7" #pink)

#Code for generating .png images:
#png("name_image.png", units ="in", width=8, height=5, res = 300)
```
#Function to extract and deal with data from CDDEC 
#Codes for each basin: MRC = Merced, SNS = Stanislaus, TLG = Tuolumne, SJF = Upper San Joaquin
CDEC <- function(code) { 
basin <- cder::cdec_query(code, 65, "M", "1980-10-01", "2010-09-30") #Code, ID, time (monthly data), start and end dates
basin$DateTime <- base::as.Date(basin$DateTime, format = "%Y/%m/%d") #change to date format

basin$Value <- basin$Value/810.71318210885 #divide by 810.71318210885 instead, to get million

basin <- basin %>%
  dplyr::select(DateTime, Value) %>% #select only the columns we'll use
  dplyr::rename(date1 = DateTime, #rename columns to match those of the GCMs
                "Observed (CDEC)" = Value)
  

basin
}
MRC.CDEC <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/MRC_natural_flow_monthly_mcm.csv")

TLG.CDEC <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/TLG_natural_flow_monthly_mcm.csv")

SNS.CDEC <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/SNS_natural_flow_monthly_mcm.csv")

SJF.CDEC <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/SJF_natural_flow_monthly_mcm.csv")

names(SNS.CDEC)[2] <- "SNS_flow"
names(TLG.CDEC)[2] <- "TLG_flow"
names(SJF.CDEC)[2] <- "SJF_flow"
names(MRC.CDEC)[2] <- "MRC_flow"

head(SNS.CDEC)
#rbind(MRC.CDEC, TLG.CDEC, SNS.CDEC, SJF.CDEC)


```{r}
#Getting observed data from CDEC for each basin, selecting only water years between 1950 and 2013
SNS.obs <- cdec_query("SNS", 65, "M", "1950-10-01", "2013-09-30")
SNS.obs$DateTime <- as.Date(SNS.obs$DateTime, format = "%Y/%m/%d")

MRC.obs <- cdec_query("MRC", 65, "M", "1950-10-01", "2013-09-30")
MRC.obs$DateTime <- as.Date(MRC.obs$DateTime, format = "%Y/%m/%d")

TLG.obs <- cdec_query("TLG", 65, "M", "1950-10-01", "2013-09-30")
TLG.obs$DateTime <- as.Date(TLG.obs$DateTime, format = "%Y/%m/%d")

SJF.obs <- data.frame(cdec_query("SJF", 65, "M", "1950-10-01", "2013-09-30"))
SJF.obs$DateTime <- as.Date(SJF.obs$DateTime, format = "%Y/%m/%d")

#Converting the flows in Acre-feet to million acre-feet
SJF.obs$Value <- SJF.obs$Value/1000000        #or divide by 810.71318210885 instead, to get million cubic meters
SNS.obs$Value <- SNS.obs$Value/1000000        #or divide by 810.71318210885 instead, to get million cubic meters
MRC.obs$Value <- MRC.obs$Value/1000000        #or divide by 810.71318210885 instead, to get million cubic meters
TLG.obs$Value <- TLG.obs$Value/1000000        #or divide by 810.71318210885 instead, to get million cubic meters

#Binding the stations together
Obs <- rbind(SNS.obs, TLG.obs, SJF.obs, MRC.obs)
Obs
```

```{r}
#Reading in Livneh data of each basin filtering only water years between 1950 and 2013
SNS.sim <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/SNS_natural_flow_monthly_mcm.csv") %>%
 filter(date >= as.Date("1950-10-01") & date <= as.Date("2013-09-30"))
MRC.sim <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/MRC_natural_flow_monthly_mcm.csv") %>%
 filter(date >= as.Date("1950-10-01") & date <= as.Date("2013-09-30"))
TLG.sim <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/TLG_natural_flow_monthly_mcm.csv") %>%
 filter(date >= as.Date("1950-10-01") & date <= as.Date("2013-09-30"))
SJF.sim <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Livneh/sJF_natural_flow_monthly_mcm.csv") %>%
 filter(date >= as.Date("1950-10-01") & date <= as.Date("2013-09-30"))

#Transform from million cubic meters to million acre feet
SJF.sim$flow <- SJF.sim$flow*0.00081071318210885             
SNS.sim$flow <- SNS.sim$flow*0.00081071318210885                
MRC.sim$flow <- MRC.sim$flow*0.00081071318210885                
TLG.sim$flow <- TLG.sim$flow*0.00081071318210885                


Sim <- rbind(SNS.sim, TLG.sim, SJF.sim, MRC.sim)
Sim
```

```{r}
#Creating one tibble
fulldataset <- cbind(Sim, Obs)
head(fulldataset)
```

```{r}
#Selecting only the data that is interesting
dataset <- fulldataset[c("StationID", "DateTime", "Value", "flow")] %>%
  ungroup %>%
  dplyr::rename(Sim_flow = flow, Obs_flow = Value, Date = DateTime) %>%
  mutate(Date = as.Date(Date, format = "%Y/%m/%d"),
  Month = factor(format(as.Date(Date, format = "%Y/%m/%d"), "%B")), 
  Year = as.Date(cut(Date, breaks = "year")))%>% #create year column to facilitate plotting
  group_by(Year, StationID) %>%
    mutate(Obs_annual_flow = sum(Obs_flow)) %>%
    mutate(Sim_annual_flow = sum(Sim_flow))
   
    


dataset

dataset$Month <- factor(dataset$Month,
                        level= c("January","February","March","April","May","June","July","August","September","October","November","December"))
```

```{r}
calc_pbias <- function(df) {
  100*(sum(df[["Sim_flow"]] - df[["Obs_flow"]])/sum((df[["Obs_flow"]]), na.rm =TRUE))
}

calc_rsr <- function(df) {
  sqrt( mean( (df[["Sim_flow"]] - df[["Obs_flow"]])^2, na.rm = TRUE))/sd(df[["Obs_flow"]])
}

calc_nse <- function(df) {
  1 - sum((df[["Obs_flow"]] - df[["Sim_flow"]])^2)/sum((df[["Obs_flow"]] - mean(df[["Obs_flow"]]))^2)
}
```

```{r}
dataset <- dataset %>%
  group_by(StationID, Month) %>%
  nest() %>%
  mutate(pbias_monthly = map(data, calc_pbias),
         rsr_monthly = map(data, calc_rsr),
         nse_monthly = map(data, calc_nse)) %>%
  unnest(cols = c(data, pbias_monthly, rsr_monthly, nse_monthly))
dataset
```

```{r}
# We are using mean here to reduce {statistic}_monthly into a single value
# this is acceptable because the {statistic}_monthly columns have the same
# value for each site-month pair

dataset_labels <- dataset %>%
  group_by(StationID, Month) %>%
  summarize(pbias = mean(pbias_monthly),
            rsr = mean(rsr_monthly),
            nse = mean(nse_monthly)) %>%
  mutate(label = paste0("RSR= ", sprintf("%.3f", round(rsr, digits=3)), "\nPBIAS = ", sprintf("%.3f",round(pbias, digits=3)),"\nNSE = ", sprintf("%.3f",round(nse, digits=3))))
  
dataset_labels
```

```{r}
model.assess <- function(Sim, Obs) { #the inputs are numeric simulated and observed data
  if(!is.numeric(Sim)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }
  if(!is.numeric(Obs)) { #verifies if the observed data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Obs)[1])
  }    
  rmse = sqrt( mean( (Sim - Obs)^2, na.rm = TRUE) ) #Formula to calculate RMSE
  RSR <- rmse / sd(Obs) #object producing RSR test from the RMSE formula
  PBIAS <- 100 *(sum((Sim - Obs)/sum(Obs), na.rm =TRUE)) #object producing PBIAS test
  NSE <- 1 - sum((Obs - Sim)^2)/sum((Obs - mean(Obs))^2, na.rm =TRUE) #object producing NSE test
  stats <- print(paste0("RSR = ", sprintf("%.3f", round(RSR, digits=3)), "    PBIAS = ", sprintf("%.3f",round(PBIAS, digits=3)),"    NSE = ", sprintf("%.3f",round(NSE, digits=3))))  
  return(stats) #returns the results of the tests
}

```

```{r}
model.assess2 <- function(Sim, Obs) { #the inputs are numeric simulated and observed data
  if(!is.numeric(Sim)) { #verifies if the simulated data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Sim)[1])
  }
  if(!is.numeric(Obs)) { #verifies if the observed data is really numeric
    stop('This function only works for numeric input!\n', #throws an error if it is not
         'You have provided an object of class: ', class(Obs)[1])
  }    
  rss <- sum((Sim - Obs) ^ 2)  ## residual sum of squares
  tss <- sum((Obs - mean(Obs)) ^ 2)  ## total sum of squares
  rsq <- 1 - rss/tss
  PBIAS <- 100 *(sum((Sim - Obs)/sum(Obs), na.rm =TRUE)) #object producing PBIAS test
  NSE <- 1 - sum((Obs - Sim)^2)/sum((Obs - mean(Obs))^2, na.rm =TRUE) #object producing NSE test
  stats <- print(paste0("R\u00B2= ", sprintf("%.3f", round(rsq, digits=3)), "    PBIAS = ", sprintf("%.3f",round(PBIAS, digits=3)),"    NSE = ", sprintf("%.3f",round(NSE, digits=3))))  
  return(stats) #returns the results of the tests
}

```

```{r}
ll <- data.frame(Month=c(),label=c())
nM <- length(Month)
lapply(1:nM, function(i){
  a <- Sim_flow*i*i*0.5
  b <- Obs_flow*i
  m <- model.assess(a,b)
  ll <<- rbind(ll,data.frame(Month=Month[i],label=m))
})
labels <- ll
```

```{r}

#Model assessment of each basin
#Merced
MRC.ma <- data.frame(model.assess(MRC.sim$flow, MRC.obs$Value))
MRC.ma
#Tuolumne
TLG.ma <- data.frame(model.assess(TLG.sim$flow, TLG.obs$Value))
TLG.ma
#Stanislaus
SNS.ma <- data.frame(model.assess(SNS.sim$flow, SNS.obs$Value))
SNS.ma 
#Upper San Joaquin
SJF.ma <- data.frame(model.assess(SJF.sim$flow, SJF.obs$Value))
SJF.ma
```

```{r}
MRC.ma <- model.assess(MRC.sim$flow, MRC.obs$Value)
MRC.ma
a <- 100 *sum(MRC.sim$flow - MRC.obs$Value)/sum(MRC.obs$Value)
a

MRCp <- dataset %>%
  filter(StationID == "MRC")
b <- 100 *sum(dataset$Obs_flow - dataset$Sim_flow)/sum(dataset$Sim_flow)
b

MRCp
MRC.sim
MRC.obs

```


```{r}
#Merced
MRC <-  dataset %>%
  filter(StationID == "MRC") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07")) +
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "2 years", 
                  date_labels = "%b/%Y",
                  limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                      labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River", #title
       x = element_blank(), 
       y = "Monthly full natural Flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title
MRC
#MRC + annotate("text", as.Date("1987-07-01"), y = 600, label = "RSR = 0.32\nPBIAS = 0.03\nNSE = 0.90",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman")
```

```{r}
#Creating a function

Merced <- function(X, Y) {dataset %>%
  filter(StationID == X) %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07")) +
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "2 years", 
                  date_labels = "%b/%Y",
                  limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                      labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = Y, #title
       x = element_blank(), 
       y = "Monthly full natural Flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5))
}


Merced(Y = "shut the fuck up", X = "MRC")

```

```{r}
#Stanislaus
SNS <- dataset %>%
  filter(StationID == "SNS") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "2 years", 
                  date_labels = "%b/%Y",
                  limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Stanislaus River", #title
       x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SNS + annotate("text", as.Date("1987-07-01"), y = 600, label = "RSR = 0.29\nPBIAS = -0.01\nNSE = 0.91",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman") 

```



```{r}
#Upper San Joaquin
SJF <- dataset %>%
  filter(StationID == "SJF") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "2 years",
                  date_labels = "%b/%Y",
                  limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Upper San Joaquin River", #title
       x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SJF + annotate("text", as.Date("1987-07-01"), y = 900, label = "RSR = 0.45\nPBIAS = 0.01\nNSE = 0.80",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman") 

```

```{r}
#Tuolumne

TLG <- dataset %>%
  filter(StationID == "TLG") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "2 years",
                  date_labels = "%b/%Y",
                  limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Tuolumne River", #title
       x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

TLG + annotate("text", as.Date("1987-07-01"), y = 1000, label = "RSR = 0.42\nPBIAS = 0.00\nNSE = 0.83",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman")
```

```{r}
#Merced full dataset
MRC.full <- dataset %>%
  filter(StationID == "MRC") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "10 years",
                  date_labels = "%b/%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

MRC.full + annotate("text", as.Date("1960-07-01"), y = 700, label = "RSR = 0.32\nPBIAS = 0.3\nNSE = 0.90",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman") +

```

```{r}
#Stanislaus full dataset
SNS.full <- dataset %>%
  filter(StationID == "SNS") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "10 years",
                  date_labels = "%b/%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Stanislaus River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SNS.full + annotate("text", as.Date("1960-07-01"), y = 700, label = "RSR = 0.29\nPBIAS = -0.01\nNSE = 0.91",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman")

```

```{r}
#Tuolumne full data set
TLG.full <- dataset %>%
  filter(StationID == "TLG") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "10 years", 
                  date_labels = "%b/%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title= "Tuolumne River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

TLG.full + annotate("text", as.Date("1960-07-01"), y = 1500, label = "RSR = 0.42\nPBIAS = 0.00\nNSE = 0.83",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman")

```

```{r}
#Upper San Joaquin full data set
SJF.full <- dataset %>%
  filter(StationID == "SJF") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "10 years", 
                  date_labels = "%b/%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title= "Upper San Joaquin River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SJF.full + annotate("text", as.Date("1959-07-01"), y = 1350, label = "RSR = 0.45\nPBIAS = 0.01\nNSE = 0.80",  collapse = "\n", hjust = 0, size=4, family= "Times New Roman")
```

```{r}
#Upper San Joaquin full data set
SJF.full <- dataset %>%
  filter(StationID == "SJF") %>%
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = Obs_flow, colour = "#00AFBB"))+ #plot monthly observed data in greenish blue
 geom_line(aes(x = Date, y = Sim_flow, colour = "#FC4E07"))+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "10 years", 
                  date_labels = "%b/%Y",
                 # limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                         breaks = c("#00AFBB", "#FC4E07"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title= "Upper San Joaquin River",
    x = element_blank(), 
       y = "Monthly full natural flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title

SJF.full + facet_wrap(~ Month, ncol=3, scales = "free")
```


grid.arrange(MRC.full, SNS.full, TLG.full, SJF.full, ncol=2)

grid.arrange(MRC, SNS, TLG, SJF, ncol=2)


```{r}
#Creating observed vs. simulated
#Scatterplot
note <- data.frame(x = c(as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01"), as.Date("1961-02-01")),
                   y = c(1.15, 1.15, 1.15, 1.15), #adding where to add text 
                   label = c(paste(MRC.ma), paste(SJF.ma), paste(SNS.ma), paste(TLG.ma)),
                   StationID = c("MRC", "SJF", "SNS", "TLG"))

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

coefs <- coef(datas) # linear model coefficients
b0 <- round(coefs[1], 2) # round for printing
b1 <- round(coefs[2], 2) # round for printing
r2 <- round(summary(mod1)$r.squared, 2) # r squared
eqn <- bquote(italic(y) == .(b0) + .(b1)*italic(x) * "," ~~ r^2 == .(r2)) # formula and rsuared for printing
```

```{r}
#all basins scatter plot with annual data

note2 <-  data.frame(x = c(0.05, 0.05, 0.05, 0.05),
                   y = c(1.15, 1.15, 1.15, 1.15), #adding where to add text 
                   label = c(paste(MRC.ma), paste(SJF.ma), paste(SNS.ma), paste(TLG.ma)),
                   StationID = c("MRC", "SJF", "SNS", "TLG"))


ggplot(dataset, aes(x = Obs_annual_flow, y = Sim_annual_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(alpha = 0.2)+ 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
 labs(x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis
  theme() +
    stat_smooth(aes(x = Obs_annual_flow, y = Sim_annual_flow), 
                method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) +
    scale_y_continuous(limits = c(0, 7),
                       expand = c(0.005, 0.005)) +
     scale_x_continuous(limits = c(0, 7),
                        expand = c(0.005, 0.005)) +
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0("atop(", ..eq.label.., ",", ..rr.label.., ")")), 
             parse = TRUE, label.x.npc = 0.05, label.y.npc = 0.97, size = 3.5, family= "Times New Roman")+
   facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +
  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
#geom_text(note2, #adding where to add text 
#              mapping = aes(x=, y=y, label = label), size=3, family= "Times New Roman") +
png("allbasins_annualdata_scatterplot.png", units ="in", width=5, height=5, res = 300)
```


```{r}
#all basins scatter plot with monthly data



formula <- dataset$Sim_flow ~ dataset$Obs_flow

ggplot(dataset, aes(x = Obs_flow, y = Sim_flow)) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_point(alpha = 0.3)+ 
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
 labs(x = "Observed full natural flow - CDEC (MAF)", 
       y = "Simulated full natural flow - Livneh (MAF)") + #name of x axis

    stat_smooth(aes(x = Obs_flow, y = Sim_flow), method = "lm", se = TRUE, colour="#FC4E07", fullrange = TRUE) +
    scale_y_continuous(limits = c(0, 1.65),
                       expand = c(0.005, 0.005)) +
     scale_x_continuous(limits = c(0, 1.65),
                        expand = c(0.005, 0.005)) +
   stat_poly_eq(formula = "y~x", 
             aes(label = paste0("atop(", ..eq.label.., ",", ..rr.label.., ")")), 
             parse = TRUE, label.x.npc = 0.05, label.y.npc = 0.98, size = 3.5, family= "Times New Roman")+
   facet_wrap(~ StationID, ncol=2,  labeller = labeller(StationID = c("MRC" = "Merced River", "SJF"= "Upper San Joaquin River", "SNS" = "Stanislaus River", "TLG" = "Tuolumne River")), scales = "fixed") +
  theme(aspect.ratio = 1,
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
png("allbasins_monthlydata_scatterplot.png", units ="in", width=5, height=5, res = 300)
```


```{r}

```

```{r}

MRC.obs$Year <- as.Date(cut(MRC.obs$DateTime, breaks = "year")) #create month column to facilitate plotting
MRC.sim$Year <- as.Date(cut(MRC.sim$date, breaks = "year")) 


MRC.com <- ggplot(x = MRC.obs$DateTime, y = MRC.sim$flow) + 
   geom_point(aes(alpha=0.3, colorblind_pal())) +
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
      scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "4 years", 
                  date_labels = "%Y",
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  labs(x = "Observed data (CDEC)", #name of x axis
       y = "Modeled data (Livneh)") #name of x axis
  
MRC.com 
```