---
title: "Generation"
author: "Gustavo Facincani Dourado"
date: "6/12/2020"
output: html_document
---

```{r}
library(lfstat)
library(extrafont)
library(reshape2)
library(dplyr)
library(ggplot2)
library(readr)
```
```{r}
#Merced
#Baseline 2045 -      1,2,6,10
#No IFR 2045 -   1,3,7,11
#Baseline 2045 - 1,4,8,12
#No IFR 2045 -   1,5,9,13

#Tuolumne
#Baseline 2045 -      1,2,6,10,14
#No IFR 2045 -   1,3,7,11,15
#Baseline 2045 - 1,4,8,12,16
#No IFR 2045 -   1,5,9,13,17

#Stanislaus
#Baseline -      1,2,6,10,14,18,22,26,30,34,38,42
#No IFR 2045 -   1,3,7,11,15,19,23,27,31,35,39,43
#Baseline 2045 - 1,4,8,12,16,20,24,28,32,36,40,44
#No IFR 2045 -   1,5,9,13,17,21,25,29,33,37,41,45

#USJ
#Baseline 2045 -      1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62
#No IFR 2045 -                      1,3,7,11,15,19,23,27,31,35,39,43,47,51,55,59,63
#Baseline 2045 - 1,4,8,12,16,20,24,28,32,36,40,44,48,52,56,60,64
#No IFR 2045 -                      1,5,9,13,17,21,25,29,33,37,41,45,49,53,57,61,65
```

```{r}
scenario <- c(1,2,6,10)
Livneh_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/historical/Livneh/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2010-09-30")))

Livneh_HPFlow_Mer <- Livneh_HPFlow_Mer %>%
  mutate(`Livneh (Historical)` = rowSums(Livneh_HPFlow_Mer[c(2:4)]))
Livneh_HPFlow_Mer

CanES_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/CanESM2_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)]

CanES_HPFlow_Mer<- CanES_HPFlow_Mer %>%
  mutate("CanESM2\u2020" = rowSums(CanES_HPFlow_Mer[c(2:4)]))
CanES_HPFlow_Mer

CNRM_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/CNRM-CM5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)]

CNRM_HPFlow_Mer<- CNRM_HPFlow_Mer  %>%
  mutate("CNRM-CM5\u2020" = rowSums(CNRM_HPFlow_Mer[c(2:4)]))
CNRM_HPFlow_Mer


HadGEM_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/HadGEM2-ES_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)]

HadGEM_HPFlow_Mer<- HadGEM_HPFlow_Mer %>%
  mutate("HadGEM2-ES\u2020" = rowSums(HadGEM_HPFlow_Mer[c(2:4)]))
HadGEM_HPFlow_Mer


MIROC_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/MIROC5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
MIROC_HPFlow_Mer<- MIROC_HPFlow_Mer  %>%
  mutate("MIROC5\u2020" = rowSums(MIROC_HPFlow_Mer[c(2:4)]))
MIROC_HPFlow_Mer

HadGEMCC_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/HadGEM2-CC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
HadGEMCC_HPFlow_Mer<- HadGEMCC_HPFlow_Mer  %>%
  mutate(`HadGEM2-CC` = rowSums(HadGEMCC_HPFlow_Mer[c(2:4)]))
HadGEMCC_HPFlow_Mer

CCSM4_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/CCSM4_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
CCSM4_HPFlow_Mer<- CCSM4_HPFlow_Mer  %>%
  mutate(CCSM4 = rowSums(CCSM4_HPFlow_Mer[c(2:4)]))
CCSM4_HPFlow_Mer

CMCC_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/CMCC-CMS_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
CMCC_HPFlow_Mer<- CMCC_HPFlow_Mer  %>%
  mutate(`CMCC-CMS` = rowSums(CMCC_HPFlow_Mer[c(2:4)]))
CMCC_HPFlow_Mer

CESM_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/CESM1-BGC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
CESM_HPFlow_Mer<- CESM_HPFlow_Mer  %>%
  mutate(`CESM1-BGC` = rowSums(CESM_HPFlow_Mer[c(2:4)]))
CESM_HPFlow_Mer

ACCESS1_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/ACCESS1-0_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
ACCESS1_HPFlow_Mer<- ACCESS1_HPFlow_Mer  %>%
  mutate(`ACCESS1-0` = rowSums(ACCESS1_HPFlow_Mer[c(2:4)]))
ACCESS1_HPFlow_Mer

GFDL_HPFlow_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/merced/gcms/GFDL-CM3_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(scenario)] 
GFDL_HPFlow_Mer<- GFDL_HPFlow_Mer  %>%
  mutate(`GFDL-CM3` = rowSums(GFDL_HPFlow_Mer[c(2:4)]))
GFDL_HPFlow_Mer

```

```{r}
library(reshape2)
library(lfstat)
#Can't cbind livneh as it has one day less (Feb 29) in its count
#Deal with Livneh separately

Livneh_Mer <- Livneh_HPFlow_Mer[-c(2,3,4)] 
Livneh_Mer <- melt(Livneh_Mer, id = "node")
Livneh_Mer


HPFlow_Mer <- cbind(CanES_HPFlow_Mer[-c(2,3,4)], CNRM_HPFlow_Mer[-c(1,2,3,4)], 
                HadGEM_HPFlow_Mer[-c(1,2,3,4)], MIROC_HPFlow_Mer[-c(1,2,3,4)], 
                CMCC_HPFlow_Mer[-c(1,2,3,4)], ACCESS1_HPFlow_Mer[-c(1,2,3,4)],
                HadGEMCC_HPFlow_Mer[-c(1,2,3,4)], CESM_HPFlow_Mer[-c(1,2,3,4)],
                CCSM4_HPFlow_Mer[-c(1,2,3,4)], GFDL_HPFlow_Mer[-c(1,2,3,4)])

#HPFlow_Mer <- HPFlow_Mer %>%
#       mutate(Ensemble = rowMeans(as.matrix((.[-1])))) %>%
#  filter(between(node, as.Date("2029-10-01"), as.Date("2060-09-30")))
#HPFlow_Mer
#HPFlow_Mer

HPFlow_Mer1 <- melt(HPFlow_Mer, id = "node") #, "Basin", "Year", "Month")) #"Annual_Can",                                   "Annual_CNRM", "Annual_Had", "Annual_MIR")
  #           Month = as.Date(cut(node, breaks = "month")),

#             mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
 #          Year = as.Date(cut(node, breaks = "year")))
HPFlow_Mer1



HPFlow_Mer2 <- rbind(HPFlow_Mer1, Livneh_Mer) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         #Year = as.Date(cut(node, breaks = "year")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 4.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))
HPFlow_Mer2

HPFlow_Mer2$variable <- factor(HPFlow_Mer2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

HPFlow_Mer3 <- HPFlow_Mer2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

HPFlow_Mer3


HPFlow_Mer4 <- HPFlow_Mer3 
#df[3:ncol(df)] <- df[3:ncol(df)]-df[,2]

```


#Merced annual generation
HPFlow_Mer2 %>%
  filter(variable == "MIROC5") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Merced River",
    subtitle = "MIROC5",
    x = element_blank(),
       y = "Total Electricity Generation (MWh)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Mer_HPFlow_MIROC5_March.png", units ="in", width=8, height=5, res = 300)


library(readxl)

NoIFRs_perc <- read_xlsx("C:/Users/gusta/Desktop/PhD/Classes/ES207/Merced_TotalAnnual_HPFlow_RCP4.5_Baseline.xlsx", sheet = 2)
NoIFRs_perc$Month <- factor(NoIFRs_perc$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
Baseline2 <- melt(NoIFRs_perc, id = c("Year", "Month"))
Baseline2



ggplot(Baseline2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value*100, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(-100, NA),
                      expand = c(0, NA),
                      labels=comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       title = "Baseline",
       subtitle = "Merced River",
    x = element_blank(), 
       y = "Δ Total Electricity Generation (%)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Mer_HPFlow_10GCMs_NoIFRs_percdiff_March.png", units ="in", width=10, height=5, res = 300)



Generation <- merge(HPFlow_Mer3, WYT_SJVI, by = c("variable", "Year")) %>%
  filter(!RCP == "rcp45")
Generation




```{r}
library(scales)
#Merced annual generation
#HPFlow_Mer2 %>%
#  filter(variable == "CanESM2") %>%

ggplot(HPFlow_Mer2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       title = "No Instream2045 prices)",
       subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Mer_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
#HPFlow_Mer3 %>%
#  filter(variable == "Livneh (Historical)" | variable == "ACCESS1-0" | variable == "CNRM-CM5") %>%
ggplot(HPFlow_Mer3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma,
                      breaks= c(0,200,400, 600, 800)) +
 #   scale_x_discrete(limits=c(c("Livneh (Historical)", "ACCESS1-0",# "CMCC-CMS", "MIROC5", "GFDL-CM3", "CCSM4", "HadGEM2-ES", "HadGEM2-CC", "CanESM2", "CESM1-BGC", 
  #                              "CNRM-CM5")))+ 
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5", title = "Merced River",
       subtitle = "No Instreamflow Requirement (2045 prices)",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Mer_annual_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


ggplot(HPFlow_Mer1) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(width = 0.4, aes( x = variable, y = value, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
   # scale_x_discrete(limits=c("Livneh", "HadGEM2-ES", "CanESM2/u2020", "MIROC5", "CNRM-CM5"))+
 # scale_fill_manual(values = c("#5A5A5A", "#E69F00", "#F0E442", "#009E73", "#56B4E9")) +

  labs(fill = "RCP 4.5",
       title = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (MWh)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))
  #png("Mer_HPFlow_GCMs3_March.png", units ="in", width=10, height=4, res = 300)




ggplot(HPFlow_Mer2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = WaterYear, y = value, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
    scale_x_discrete(breaks = c("1981", "1991", "2001", "2010", "2031", "2041", "2051", "2060"))+
#  scale_fill_manual(values = c("#5A5A5A", "#E69F00", "#F0E442", "#009E73", "#56B4E9")) +

  labs(fill = "RCP 4.5",
       title = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (MWh)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  
  facet_wrap(~variable, ncol=1, scales= "free")
 # png("Mer_HPFlow_GCMs4_March.png", units ="in", width=8, height=5, res = 300)



```{r}
Livneh_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/historical/Livneh/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)]
Livneh_HPFlow_Tuo

Livneh_HPFlow_Tuo <- Livneh_HPFlow_Tuo %>%
 mutate(`Livneh (Historical)` = rowSums(Livneh_HPFlow_Tuo[c(2:5)])) %>%
      filter(between(node, as.Date("1950-10-01"), as.Date("2010-09-30")))
Livneh_HPFlow_Tuo

CanES_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/CanESM2_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)]

CanES_HPFlow_Tuo <- CanES_HPFlow_Tuo %>%
 mutate("CanESM2\u2020" = rowSums(CanES_HPFlow_Tuo[c(2:5)]))
CanES_HPFlow_Tuo

CNRM_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/CNRM-CM5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 

CNRM_HPFlow_Tuo <- CNRM_HPFlow_Tuo %>%
 mutate("CNRM-CM5\u2020" = rowSums(CNRM_HPFlow_Tuo[c(2:5)]))
CNRM_HPFlow_Tuo

HadGEM_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/HadGEM2-ES_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)]

HadGEM_HPFlow_Tuo <- HadGEM_HPFlow_Tuo %>%
 mutate("HadGEM2-ES\u2020" = rowSums(HadGEM_HPFlow_Tuo[c(2:5)]))
HadGEM_HPFlow_Tuo

MIROC_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/MIROC5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)]

MIROC_HPFlow_Tuo <- MIROC_HPFlow_Tuo %>%
 mutate("MIROC5\u2020" = rowSums(MIROC_HPFlow_Tuo[c(2:5)]))
MIROC_HPFlow_Tuo


HadGEMCC_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/HadGEM2-CC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
HadGEMCC_HPFlow_Tuo<- HadGEMCC_HPFlow_Tuo  %>%
  mutate(`HadGEM2-CC` = rowSums(HadGEMCC_HPFlow_Tuo[c(2:5)]))
HadGEMCC_HPFlow_Tuo

CCSM4_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/CCSM4_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
CCSM4_HPFlow_Tuo<- CCSM4_HPFlow_Tuo  %>%
  mutate(CCSM4 = rowSums(CCSM4_HPFlow_Tuo[c(2:5)]))
CCSM4_HPFlow_Tuo

CMCC_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/CMCC-CMS_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
CMCC_HPFlow_Tuo<- CMCC_HPFlow_Tuo  %>%
  mutate(`CMCC-CMS` = rowSums(CMCC_HPFlow_Tuo[c(2:5)]))
CMCC_HPFlow_Tuo

CESM_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/CESM1-BGC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
CESM_HPFlow_Tuo<- CESM_HPFlow_Tuo  %>%
  mutate(`CESM1-BGC` = rowSums(CESM_HPFlow_Tuo[c(2:5)]))
CESM_HPFlow_Tuo

ACCESS1_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/ACCESS1-0_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
ACCESS1_HPFlow_Tuo<- ACCESS1_HPFlow_Tuo  %>%
  mutate(`ACCESS1-0` = rowSums(ACCESS1_HPFlow_Tuo[c(2:5)]))
ACCESS1_HPFlow_Tuo

GFDL_HPFlow_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results//Binary IFRs x Prices - 2021-04-08/tuolumne/gcms/GFDL-CM3_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14)] 
GFDL_HPFlow_Tuo<- GFDL_HPFlow_Tuo  %>%
  mutate(`GFDL-CM3` = rowSums(GFDL_HPFlow_Tuo[c(2:5)]))
GFDL_HPFlow_Tuo

```

```{r}

Livneh_Tuo <- Livneh_HPFlow_Tuo[-c(2:5)] 
Livneh_Tuo <- melt(Livneh_Tuo, id = "node")
Livneh_Tuo


HPFlow_Tuo <- cbind(CanES_HPFlow_Tuo[-c(2:5)], CNRM_HPFlow_Tuo[-c(1:5)], 
                HadGEM_HPFlow_Tuo[-c(1:5)], MIROC_HPFlow_Tuo[-c(1:5)],
                CMCC_HPFlow_Tuo[-c(1:5)], ACCESS1_HPFlow_Tuo[-c(1:5)],
                HadGEMCC_HPFlow_Tuo[-c(1:5)], CESM_HPFlow_Tuo[-c(1:5)],
                CCSM4_HPFlow_Tuo[-c(1:5)], GFDL_HPFlow_Tuo[-c(1:5)])
 

#HPFlow_Mer

#HPFlow_Tuo <- HPFlow_Tuo %>%
#       mutate(Ensemble = rowMeans(as.matrix((.[-1])))) %>%
#  filter(between(node, as.Date("2029-10-01"), as.Date("2060-09-30")))
#HPFlow_Tuo

HPFlow_Tuo1 <- melt(HPFlow_Tuo, id = "node")
HPFlow_Tuo1


HPFlow_Tuo2 <- rbind(HPFlow_Tuo1, Livneh_Tuo) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = as.factor(format(as.Date(node, format = "%Y"), "%Y")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 4.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))

HPFlow_Tuo2

HPFlow_Tuo2$variable <- factor(HPFlow_Tuo2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

HPFlow_Tuo3 <- HPFlow_Tuo2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 
HPFlow_Tuo3

```


#Merced annual generation
HPFlow_Tuo2 %>%
  filter(variable == "CanESM2") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Stanislaus River",
    subtitle = "CanESM2",
    x = element_blank(),
       y = "Total Electricity Generation (MWh)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))

#Merced annual generation
#HPFlow_Mer2 %>%
#  filter(variable == "CanESM2") %>%

```{r}
ggplot(HPFlow_Tuo2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       title = "No Instreamflow Requirement (2045 prices)",
       subtitle = "Tuolumne River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Tuo_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=10, height=5, res = 300)
```

```{r}
#annual aggreagate
#annual aggreagate
ggplot(HPFlow_Tuo3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma,
                      breaks= c(0,1000,2000, 3000)) +
 #   scale_x_discrete(limits=c(c("Livneh (Historical)", "ACCESS1-0",# "CMCC-CMS", "MIROC5", "GFDL-CM3", "CCSM4", "HadGEM2-ES", "HadGEM2-CC", "CanESM2", "CESM1-BGC", 
  #                              "CNRM-CM5")))+ 
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5", title = "Tuolumne River",
       subtitle = "Baseline - RCP 4.5 (2045 prices)",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Tuo_annual_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/historical/Livneh/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2010-09-30")))

Livneh_HPFlow_Stn <- Livneh_HPFlow_Stn %>%
  mutate(`Livneh (Historical)` = rowSums(Livneh_HPFlow_Stn[c(2:12)]))
Livneh_HPFlow_Stn

CanES_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/CanESM2_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)]

CanES_HPFlow_Stn<- CanES_HPFlow_Stn %>%
  mutate("CanESM2\u2020" = rowSums(CanES_HPFlow_Stn[c(2:12)]))
CanES_HPFlow_Stn

CNRM_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/CNRM-CM5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)]

CNRM_HPFlow_Stn<- CNRM_HPFlow_Stn  %>%
  mutate("CNRM-CM5\u2020" = rowSums(CNRM_HPFlow_Stn[c(2:12)]))
CNRM_HPFlow_Stn


HadGEM_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/HadGEM2-ES_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)]

HadGEM_HPFlow_Stn<- HadGEM_HPFlow_Stn %>%
  mutate("HadGEM2-ES\u2020" = rowSums(HadGEM_HPFlow_Stn[c(2:12)]))
HadGEM_HPFlow_Stn


MIROC_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/MIROC5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] 
MIROC_HPFlow_Stn<- MIROC_HPFlow_Stn  %>%
  mutate("MIROC5\u2020" = rowSums(MIROC_HPFlow_Stn[c(2:12)]))
MIROC_HPFlow_Stn

HadGEMCC_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/HadGEM2-CC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)]  
HadGEMCC_HPFlow_Stn<- HadGEMCC_HPFlow_Stn  %>%
  mutate(`HadGEM2-CC` = rowSums(HadGEMCC_HPFlow_Stn[c(2:12)]))
HadGEMCC_HPFlow_Stn

CCSM4_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/CCSM4_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] 
CCSM4_HPFlow_Stn<- CCSM4_HPFlow_Stn  %>%
  mutate(CCSM4 = rowSums(CCSM4_HPFlow_Stn[c(2:12)]))
CCSM4_HPFlow_Stn

CMCC_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/CMCC-CMS_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] 
CMCC_HPFlow_Stn<- CMCC_HPFlow_Stn  %>%
  mutate(`CMCC-CMS` = rowSums(CMCC_HPFlow_Stn[c(2:12)]))
CMCC_HPFlow_Stn

CESM_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/CESM1-BGC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] 
CESM_HPFlow_Stn<- CESM_HPFlow_Stn  %>%
  mutate(`CESM1-BGC` = rowSums(CESM_HPFlow_Stn[c(2:12)]))
CESM_HPFlow_Stn

ACCESS1_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/ACCESS1-0_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)]  
ACCESS1_HPFlow_Stn<- ACCESS1_HPFlow_Stn  %>%
  mutate(`ACCESS1-0` = rowSums(ACCESS1_HPFlow_Stn[c(2:12)]))
ACCESS1_HPFlow_Stn

GFDL_HPFlow_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/stanislaus/gcms/GFDL-CM3_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(  1,2,6,10,14,18,22,26,30,34,38,42)] 
GFDL_HPFlow_Stn<- GFDL_HPFlow_Stn  %>%
  mutate(`GFDL-CM3` = rowSums(GFDL_HPFlow_Stn[c(2:12)]))
GFDL_HPFlow_Stn

```

```{r}
Livneh_Stn_Gen <- Livneh_HPFlow_Stn[-c(2:12)] 
Livneh_Stn_Gen <- melt(Livneh_Stn_Gen, id = "node")
Livneh_Stn_Gen

```

```{r}
HPFlow_Stn <- cbind(CanES_HPFlow_Stn[-c(2:12)], CNRM_HPFlow_Stn[-c(1:12)], 
                HadGEM_HPFlow_Stn[-c(1:12)], MIROC_HPFlow_Stn[-c(1:12)],
                CMCC_HPFlow_Stn[-c(1:12)], ACCESS1_HPFlow_Stn[-c(1:12)],
                HadGEMCC_HPFlow_Stn[-c(1:12)], CESM_HPFlow_Stn[-c(1:12)],
                CCSM4_HPFlow_Stn[-c(1:12)], GFDL_HPFlow_Stn[-c(1:12)])
HPFlow_Stn
 

#HPFlow_Stn <- HPFlow_Stn %>%
#       mutate(Ensemble = rowMeans(as.matrix((.[-1])))) %>%
#  filter(between(node, as.Date("2029-10-01"), as.Date("2060-09-30")))
#HPFlow_Stn

HPFlow_Stn2 <- melt(HPFlow_Stn, id = "node")
HPFlow_Stn2

HPFlow_Stn2 <- rbind(HPFlow_Stn2, Livneh_Stn_Gen) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 4.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))
  

HPFlow_Stn2$variable <- factor(HPFlow_Stn2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

HPFlow_Stn3 <- HPFlow_Stn2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

HPFlow_Stn2
```

HPFlow_Stn2 %>%
  filter(variable == "CanESM2") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Stanislaus River",
    subtitle = "CanESM2",
    x = element_blank(),
       y = "Total Electricity Generation (MWh)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))


```{r}
ggplot(HPFlow_Stn2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       title = "No Instreamflow Requirement (2045 prices)",
       subtitle = "Stanislaus River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Stn_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=10, height=5, res = 300)
```

```{r}
#annual aggreagate
#annual aggreagate
ggplot(HPFlow_Stn3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA))+
     #                 labels = comma,
      #                breaks= c(0,200,400, 600, 800)) +
 #   scale_x_discrete(limits=c(c("Livneh (Historical)", "ACCESS1-0",# "CMCC-CMS", "MIROC5", "GFDL-CM3", "CCSM4", "HadGEM2-ES", "HadGEM2-CC", "CanESM2", "CESM1-BGC", 
  #                              "CNRM-CM5")))+ 
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5", title = "Stanislaus River",
       subtitle = "No Instreamflow Requirement (2045 prices)",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Stn_annual_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/historical/Livneh/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] 
Livneh_HPFlow_USJ

Livneh_HPFlow_USJ <-Livneh_HPFlow_USJ %>%
 mutate(`Livneh (Historical)` = rowSums(Livneh_HPFlow_USJ[c(2:17)])) %>%
      filter(between(node, as.Date("1950-10-01"), as.Date("2010-09-30")))
Livneh_HPFlow_USJ


CanES_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/CanESM2_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]
CanES_HPFlow_USJ

CanES_HPFlow_USJ <- CanES_HPFlow_USJ %>%
   mutate("CanESM2\u2020" = rowSums(CanES_HPFlow_USJ[c(2:17)]))
CanES_HPFlow_USJ
  

CNRM_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/CNRM-CM5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]
CNRM_HPFlow_USJ

CNRM_HPFlow_USJ <- CNRM_HPFlow_USJ %>%
   mutate("CNRM-CM5\u2020" = rowSums(CNRM_HPFlow_USJ[c(2:17)]))

CNRM_HPFlow_USJ


HadGEM_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/HadGEM2-ES_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]
HadGEM_HPFlow_USJ

HadGEM_HPFlow_USJ <- HadGEM_HPFlow_USJ %>%
   mutate("HadGEM2-ES\u2020" = rowSums(HadGEM_HPFlow_USJ[c(2:17)]))
HadGEM_HPFlow_USJ


MIROC_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/MIROC5_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]
MIROC_HPFlow_USJ
MIROC_HPFlow_USJ <- MIROC_HPFlow_USJ %>%
   mutate("MIROC5\u2020"= rowSums(MIROC_HPFlow_USJ[c(2:17)]))

MIROC_HPFlow_USJ

HadGEMCC_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/HadGEM2-CC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]  
HadGEMCC_HPFlow_USJ<- HadGEMCC_HPFlow_USJ  %>%
  mutate(`HadGEM2-CC` = rowSums(HadGEMCC_HPFlow_USJ[c(2:17)]))
HadGEMCC_HPFlow_USJ

CCSM4_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/CCSM4_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] 
CCSM4_HPFlow_USJ<- CCSM4_HPFlow_USJ  %>%
  mutate(CCSM4 = rowSums(CCSM4_HPFlow_USJ[c(2:17)]))
CCSM4_HPFlow_USJ

CMCC_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/CMCC-CMS_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] 
CMCC_HPFlow_USJ<- CMCC_HPFlow_USJ  %>%
  mutate(`CMCC-CMS` = rowSums(CMCC_HPFlow_USJ[c(2:17)]))
CMCC_HPFlow_USJ

CESM_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/CESM1-BGC_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] 
CESM_HPFlow_USJ<- CESM_HPFlow_USJ  %>%
  mutate(`CESM1-BGC` = rowSums(CESM_HPFlow_USJ[c(2:17)]))
CESM_HPFlow_USJ

ACCESS1_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/ACCESS1-0_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)]  
ACCESS1_HPFlow_USJ<- ACCESS1_HPFlow_USJ  %>%
  mutate(`ACCESS1-0` = rowSums(ACCESS1_HPFlow_USJ[c(2:17)]))
ACCESS1_HPFlow_USJ

GFDL_HPFlow_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-04-08/upper_san_joaquin/gcms/GFDL-CM3_rcp85/Hydropower_Flow_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c( 1,2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,62)] 
GFDL_HPFlow_USJ<- GFDL_HPFlow_USJ  %>%
  mutate(`GFDL-CM3` = rowSums(GFDL_HPFlow_USJ[c(2:17)]))
GFDL_HPFlow_USJ
```

```{r}
Livneh_USJ_Gen <- Livneh_HPFlow_USJ[-c(2:17)] 
Livneh_USJ_Gen <- melt(Livneh_USJ_Gen, id = "node")
Livneh_USJ_Gen

```

```{r}

HPFlow_USJ <- cbind(CanES_HPFlow_USJ[-c(2:17)], CNRM_HPFlow_USJ[-c(1:17)], 
                 HadGEM_HPFlow_USJ[-c(1:17)], MIROC_HPFlow_USJ[-c(1:17)],
                 CMCC_HPFlow_USJ[-c(1:17)], ACCESS1_HPFlow_USJ[-c(1:17)],
                 HadGEMCC_HPFlow_USJ[-c(1:17)], CESM_HPFlow_USJ[-c(1:17)],
                 CCSM4_HPFlow_USJ[-c(1:17)], GFDL_HPFlow_USJ[-c(1:17)])
HPFlow_USJ


#HPFlow_USJ <- HPFlow_USJ %>%
#  mutate(Ensemble = rowMeans(as.matrix((.[-1])))) %>%
#  filter(between(node, as.Date("2029-10-01"), as.Date("2060-09-30")))
#HPFlow_USJ

HPFlow_USJ2 <- melt(HPFlow_USJ, id = "node")
HPFlow_USJ2

HPFlow_USJ2 <- rbind(HPFlow_USJ2, Livneh_USJ_Gen) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 4.5")) %>%
  group_by(Year, Month, variable) %>%
  dplyr::summarize(MonthlyTotal = sum(value))


HPFlow_USJ2$variable <- factor(HPFlow_USJ2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

HPFlow_USJ3 <- HPFlow_USJ2 %>%
  group_by(Year, variable) %>%
  dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

HPFlow_USJ2
```


```{r}
ggplot(HPFlow_USJ2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       title = "No Instreamflow Requirement (2045 prices)",
       subtitle = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("USJ_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=10, height=5, res = 300)
```

```{r}
#annual aggreagate
#annual aggreagate
ggplot(HPFlow_USJ3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA))+
     #                 labels = comma,
      #                breaks= c(0,200,400, 600, 800)) +
 #   scale_x_discrete(limits=c(c("Livneh (Historical)", "ACCESS1-0",# "CMCC-CMS", "MIROC5", "GFDL-CM3", "CCSM4", "HadGEM2-ES", "HadGEM2-CC", "CanESM2", "CESM1-BGC", 
  #                              "CNRM-CM5")))+ 
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5", title = "Upper San Joaquin River",
       subtitle = "No Instreamflow Requirement (2045 prices)",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("USJ_annual_HPFlow_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```



```{r}
#Facet wraps of all basins

HPFlow_Mer2$Basin <- factor("Merced River")
HPFlow_Mer3$Basin <- factor("Merced River")
HPFlow_Tuo2$Basin <- factor("Tuolumne River")
HPFlow_Tuo3$Basin <- factor("Tuolumne River")
HPFlow_Stn2$Basin <- factor("Stanislaus River")
HPFlow_Stn3$Basin <- factor("Stanislaus River")
HPFlow_USJ2$Basin <- factor("Upper San Joaquin River")
HPFlow_USJ3$Basin <- factor("Upper San Joaquin River")

all_HPFlow_monthly <- rbind(HPFlow_Mer2, HPFlow_Tuo2, HPFlow_Stn2 ,HPFlow_USJ2)
all_HPFlow_monthly$Basin <- factor(all_HPFlow_monthly$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
#all_storage_year
all_HPFlow_monthly

all_HPFlow_yearly <- rbind(HPFlow_Mer3, HPFlow_Tuo3, HPFlow_Stn3, HPFlow_USJ3)
all_HPFlow_yearly$Basin <- factor(all_HPFlow_yearly$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
#all_storage_year
all_HPFlow_yearly
```

```{r}
all_HPFlow_monthly$Month <- factor(all_HPFlow_monthly$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
all_HPFlow_monthly

All_Montlhy_Stats_Gen <- aggregate(MonthlyTotal ~ Month+variable+Basin, all_HPFlow_monthly, summary)
write.csv(All_Montlhy_Stats_Gen, "All_Monthly_Stats_HPFlow_NoIFRs_2045prices_rcp85_Report_March.csv")

All_Annual_Stats_Gen <- aggregate(AnnualTotal ~ variable+Basin, all_HPFlow_yearly, summary)
write.csv(All_Annual_Stats_Gen, "All_Annual_Stats_HPFlow_NoIFRs_2045prices_rcp85_Report_March.csv")
```

```{r}
HPFlow_Annual <- merge(all_HPFlow_yearly, WYT_SJVI, by = c("variable", "Year")) %>%
  filter(!RCP == "rcp45")
HPFlow_Annual

HPFlow_Annual_FNF <- merge(HPFlow_Annual, RCP85annual, by = c("variable", "Year", "Basin"))# %>%
 # filter(!RCP == "rcp45")
HPFlow_Annual_FNF

HPflow <- merge(all_HPFlow_monthly, WYT_SJVI, by = c("variable", "Year")) %>%
  filter(!RCP == "rcp45") %>%
  mutate(MonthYear = as.Date(as.yearmon(paste(Month,"/",2000,sep=""),format = "%b/%Y"))) %>%
  group_by(Basin, variable, MonthYear) %>%
  summarize(Mean = mean(MonthlyTotal),
            Median = median(MonthlyTotal),
            Min = min(MonthlyTotal),
            Max = max(MonthlyTotal)) %>%
  mutate(Months = format(MonthYear, "%m"))
HPflow

#Generation$Months <- factor(Generation$Months, levels = c("2000-10-01", "2000-11-01", "2000-12-01", "2000-01-01", "2000-02-01", "2000-03-01", "2000-04-01", "2000-05-01", "2000-06-01", "2000-07-01", "2000-08-01", "2000-09-01"))

HPflow2 <- merge(all_HPFlow_monthly, WYT_SJVI, by = c("variable", "Year")) %>%
  filter(!RCP == "rcp45") %>%
  mutate(MonthYear = as.Date(as.yearmon(paste(Month,"/",2000,sep=""),format = "%b/%Y"))) %>%
  group_by(Basin, MonthYear) %>%
  summarize(Mean = mean(MonthlyTotal),
            Stdev = sd(MonthlyTotal),
            n = 12,
            error = qnorm(0.975)*Stdev/sqrt(n),
            lower_bound = Mean - error,
            upper_bound = Mean + error) %>%
  mutate(Months = format(MonthYear, "%m"))
HPflow2
```

```{r}
HPFlow_stats <- merge(all_HPFlow_monthly, WYT_SJVI, by = c("variable", "Year")) %>%
  filter(!RCP == "rcp45") %>%
  mutate(#MonthYear = as.Date(as.yearmon(paste(Month,"/",2000,sep=""),format = "%b/%Y")),
         MonthlyTotal = MonthlyTotal/1000) %>%
  group_by(Basin, variable,Year, WYT) %>%
  summarize(Min = min(MonthlyTotal),
            #`1st Quintile Generation` = quantile(MonthlyTotal, 0.2, na.rm = TRUE),
            `1st Quartile Generation` = quantile(MonthlyTotal, 0.25, na.rm=TRUE),
            #`2nd Quintile Generation` = quantile(MonthlyTotal, 0.4, na.rm = TRUE),
            #`Mean Generation` = mean(MonthlyTotal, na.rm=TRUE),
            `Median Generation` = median(MonthlyTotal, na.rm=TRUE),
            #`4th Quintile Generation` = quantile(MonthlyTotal, 0.6, na.rm = TRUE),
            `3rd Quartile Generation` = quantile(MonthlyTotal, 0.75, na.rm=TRUE),
            #`5th Quintile Generation` = quantile(MonthlyTotal, 0.8, na.rm = TRUE),
            Max = max(MonthlyTotal)) %>%
  melt(., id = c("Basin", "variable", "Year", "WYT"))
  #          Annual_total = sum(MonthlyTotal)) #%>%
 #mutate(Months = format(MonthYear, "%m"))
HPFlow_stats
```

```{r}
ggplot(HPFlow_Annual)+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_rect(aes(fill = WYT, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf))+
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=scales::comma) +
   
      geom_line(aes( x = as.numeric(Year), y = AnnualTotal/1000, linetype = Basin)) + #plot monthly observed data in greenish blue
   scale_x_discrete(breaks = c("1981", "1991", "2001", "2010","2031", "2041", "2051", "2060"),
      expand = c(0, NA))+
   #geom_line(aes(x = node, y = value)) +
#scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +
  scale_fill_manual(values = c("tomato2", "orange", "#FEDC56", "cyan3", "dodgerblue2"))+
  
 scale_linetype_manual(values = c("dotted", "longdash", "dotdash", "solid"), name = "Basin")+ #c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"), name = "Basin")+
  
  labs(fill = "Water Year Type",
       title = "Baseline (2009 prices)",
       subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "vertical")+
   guides(linetype = guide_legend(nrow = 4, byrow = T))+
     guides(fill = guide_legend(nrow = 5, byrow = T))+
  facet_wrap(~variable, ncol = 1, scales ="free_x", strip.position= "left")+
png("Allbasins_HPFlow_rcp85_timeseries_PostReport.png", units ="in", width=9, height=13, res = 300)
```

```{r}
ggplot(HPFlow_Annual_FNF)+# %>% filter(Basin == "Merced River"))+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') +
   geom_point(aes( x = (AnnualTotal.y), y =AnnualTotal.x/1000, color = variable, group = variable))+
  scale_x_log10(expand = c(0,0)) +#, breaks = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
  scale_y_log10(expand = c(0,0)) +
 # scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ), guide = "none") +
  scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ))+
  labs(color = "RCP 8.5",
       title = "Baseline (2009 prices)",
      # subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
         aspect.ratio = 1,
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "horizontal")+
   guides(fill = FALSE)+
     guides(color = guide_legend(nrow = 2, byrow = F))+
  facet_wrap(Basin~WYT, scales ="fixed",ncol = 5, strip.position= "top")+
png("Allbasins_HPFlow_spread_rcp85_scatterplot_GCM_PostReport.png", units ="in", width=9, height=9, res = 300) #width=6, height=13
  
  
```

```{r}
ggplot(HPFlow_Annual_FNF)+# %>% filter(Basin == "Merced River"))+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') +
   geom_point(aes( x = (AnnualTotal.y), y =AnnualTotal.x/1000, color = WYT, group = variable))+
  scale_x_log10(expand = c(0,0)) +#, breaks = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
  scale_y_log10(expand = c(0,0)) +
 # scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ), guide = "none") +
  scale_color_manual(values = c("tomato2", "orange", "#FEDC56", "cyan3", "dodgerblue2"))+
                       #c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ))+
  labs(color = "RCP 8.5",
       title = "Baseline (2009 prices)",
      # subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
         aspect.ratio = 1,
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "horizontal")+
   guides(fill = FALSE)+
     guides(color = guide_legend(nrow = 1, byrow = F))+
  facet_wrap(Basin~variable, scales ="fixed", ncol = 11, strip.position= "top")+
png("Allbasins_HPFlow_spread_rcp85_scatterplot_PostReport.png", units ="in", width=20, height=10, res = 300) #width=6, height=13
  
  
```

```{r}
ggplot(Generation)+# %>% filter(Basin == "Merced River"))+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') +
  geom_ribbon(aes(x=MonthYear,ymin=Min/1000,ymax=Max/1000,group=variable, fill = variable), alpha = 0.1)+
  geom_line(aes( x = (MonthYear), y =Median/1000, color = variable, group = variable))+
  scale_x_date(date_labels = "%b", expand = c(0,0)) +#, breaks = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ), guide = "none") +
  scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ))+
  labs(fill = "RCP 8.5",
       title = "Baseline (2009 prices)",
      # subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "horizontal")+
   guides(fill = FALSE)+
     guides(color = guide_legend(nrow = 2, byrow = F))+
  facet_wrap(~Basin, ncol = 1, scales ="free_y", strip.position= "left")+
png("Allbasins_HPFlow_spread_rcp85_timeseries_PostReport.png", units ="in", width=9, height=13, res = 300) #width=6, height=13
  
  
```

```{r}
ggplot()+# %>% filter(Basin == "Merced River"))+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') +
  geom_ribbon(Generation2,mapping = aes(x=MonthYear,ymin=lower_bound/1000,ymax=upper_bound/1000), alpha = 0.1)+
  geom_line(Generation, mapping =aes( x = (MonthYear), y =Mean/1000, color = variable, group = variable))+
  scale_x_date(date_labels = "%b", expand = c(0,0)) +#, breaks = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ), guide = "none") +
  scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" ))+
  labs(fill = "RCP 8.5",
       title = "Baseline (2009 prices)",
      # subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "horizontal")+
   guides(fill = FALSE)+
     guides(color = guide_legend(nrow = 2, byrow = F))+
  facet_wrap(~Basin, ncol = 1, scales ="free_y", strip.position= "left")+
png("Allbasins_HPFlow__MeanCI_rcp85_timeseries_PostReport.png", units ="in", width=9, height=13, res = 300) #width=6, height=13
  
  
```

```{r}

ggplot(HPFlow_Annual)+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_rect(aes(fill = WYT, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf))+
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=scales::comma) +
   
      geom_line(aes( x = as.numeric(Year), y = AnnualTotal/1000, linetype = Basin)) + #plot monthly observed data in greenish blue
   scale_x_discrete(breaks = c("1981", "1991", "2001", "2010","2031", "2041", "2051", "2060"),
      expand = c(0, NA))+
   #geom_line(aes(x = node, y = value)) +
#scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +
  scale_fill_manual(values = c("tomato2", "orange", "#FEDC56", "cyan3", "dodgerblue2"))+
  
 scale_linetype_manual(values = c("dotted", "longdash", "dotdash", "solid"), name = "Basin")+ #c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"), name = "Basin")+
  
  labs(fill = "Water Year Type",
       title = "Baseline (2009 prices)",
       subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "vertical")+
   guides(linetype = guide_legend(nrow = 4, byrow = T))+
     guides(fill = guide_legend(nrow = 5, byrow = T))+
  facet_wrap(~variable, ncol = 1, scales ="free_x", strip.position= "left")+
png("Allbasins_HPFlow_rcp85_timeseries_PostReport.png", units ="in", width=9, height=13, res = 300) #width=6, height=13
```


```{r}

ggplot(HPFlow_Annual)+# %>% filter(variable == "ACCESS1-0" | variable == "GFDL-CM3")) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_rect(aes(fill = WYT, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf))+
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels=scales::comma) +
   
      geom_line(aes( x = as.numeric(Year), y = AnnualTotal/1000, linetype = Basin)) + #plot monthly observed data in greenish blue
   scale_x_discrete(breaks = c("1981", "1991", "2001", "2010","2031", "2041", "2051", "2060"),
      expand = c(0, NA))+
   #geom_line(aes(x = node, y = value)) +
#scale_color_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +
  scale_fill_manual(values = c("tomato2", "orange", "#FEDC56", "cyan3", "dodgerblue2"))+
  
 scale_linetype_manual(values = c("dotted", "longdash", "dotdash", "solid"), name = "Basin")+ #c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"), name = "Basin")+
  
  labs(fill = "Water Year Type",
       title = "Baseline (2009 prices)",
       subtitle = "Merced River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "right",
        legend.direction = "vertical",
        legend.box.margin = margin(t = -10),
        plot.title = element_text(hjust = 0.5),
           plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"),
        legend.box = "vertical")+
   guides(linetype = guide_legend(nrow = 4, byrow = T))+
     guides(fill = guide_legend(nrow = 5, byrow = T))+
  facet_wrap(~variable, ncol = 1, scales ="free_x", strip.position= "left")+
png("Allbasins_HPFlow_rcp85_timeseries_PostReport3.png", units ="in", width=9, height=15, res = 300) #width=6, height=13
```

```{r}
Figure_Annual_WYT <-function(basin){ 
  ggplot(HPFlow_Annual %>% filter(Basin == basin))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(#limits = c(0, NA),
                      expand = c(0, 0))+
     #                 labels = comma,
      #                breaks= c(0,200,400, 600, 800)) +
 #   scale_x_discrete(limits=c(c("Livneh (Historical)", "ACCESS1-0",# "CMCC-CMS", "MIROC5", "GFDL-CM3", "CCSM4", "HadGEM2-ES", "HadGEM2-CC", "CanESM2", "CESM1-BGC", 
  #                              "CNRM-CM5")))+ 
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 8.5", title = basin,
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~WYT, scales = "fixed", ncol = 1, strip.position = "left")+
png(paste(basin,"_annual_HPFlow_per_WYT_rcp85_baseline_PostReport_2031_2090.png",sep=""), units ="in", width=11.5, height=15, res = 300)
}
```

```{r}
Figure_Annual_WYT("Stanislaus River")
```

```{r}
Figure_Annual_WYT("Tuolumne River")
```

```{r}
Figure_Annual_WYT("Merced River")
```

```{r}
Figure_Annual_WYT("Upper San Joaquin River")
```

```{r}
Figure_per_WYT <- function(basin){
ggplot(Generation %>% filter(Basin == basin)) + 
  theme_bw(base_size=18, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 8.5",
       title = basin,
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~WYT, scales = "fixed", ncol = 1, strip.position = "left")+
png(paste(basin, "_HPFlow_10GCMs_rcp85_baseline_PostReport.png",sep=""), units ="in", width=10, height=15, res = 300)}
```

```{r}
#annual aggreagate
ggplot(all_HPFlow_yearly) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal/1000, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
#    scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 4.5",
       #title = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Electricity Generation (GWh/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
         axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        legend.text = element_text(size = 9),
       legend.key.size = unit(0.75,"line"),
        panel.spacing.y = unit(0, "lines"))+
    facet_wrap(~Basin, scales = "free_y")+
png("AllBasins_annual_HPFlow_10GCMs_rcp85_NoIFRs_2045prices_Report_March.png", units ="in", width=8, height=5, res = 300)
```



```{r}
Figure_per_WYT("Merced River")
```

```{r}
Figure_per_WYT("Tuolumne River")
```

```{r}
Figure_per_WYT("Stanislaus River")
```

```{r}
Figure_per_WYT("Upper San Joaquin River")

````

```{r}
Merced_Montlhy_Stats_Gen <- aggregate(MonthlyTotal ~ Month+variable, HPFlow_Mer2, mean)
Merced_Montlhy_Stats_Gen$Month <- factor(Merced_Montlhy_Stats_Gen$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
Merced_Montlhy_Stats_Gen <- reshape::cast(Merced_Montlhy_Stats_Gen, Month~variable)
write.csv(Merced_Montlhy_Stats_Gen, "Merced_Monthly_Stats_HPFlow_NoIFRs_2045prices_Report_March.csv")


Merced_Annual_Stats_Gen <- aggregate(AnnualTotal ~ variable, HPFlow_Mer3, mean)
write.csv(Merced_Annual_Stats_Gen, "Merced_Annual_Stats_HPFlow_NoIFRs_2045prices_Report_March.csv")
```

```{r}
HPFlow_Mer2$Month <- factor(HPFlow_Mer2$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) 
write.csv(HPFlow_Mer2, "Merced_Monthly_Stats_HPFlow_RCP4.5_SWRCB2.csv")
```

```{r}

Baseline <- reshape::cast(HPFlow_Mer2[-c(1:744),], Year+Month~variable)
Baseline
write.csv(Baseline, "Merced_TotalAnnual_HPFlow_RCP4.5_Baseline.csv")
```

```{r}
ggplot(all_HPFlow_monthly) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#E69F00", "#F0E442", "#009E73", "#56B4E9")) +

  labs(fill = "RCP 4.5",
       #title = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Electricity Generation (MWh/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~Basin, scales = "free_y")+
png("AllBasins_HPFlow_GCMs_March.png", units ="in", width=8, height=5, res = 300)
```

```{r}
#annual aggreagate
ggplot(all_HPFlow_yearly) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A", "#E69F00", "#F0E442", "#009E73", "#56B4E9")) +

  labs(fill = "RCP 4.5",
       #title = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Electricity Generation (MWh/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
         axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        legend.text = element_text(size = 9),
       legend.key.size = unit(0.75,"line"),
        panel.spacing.y = unit(0, "lines"))+
    facet_wrap(~Basin, scales = "free_y")+
png("AllBasins_HPFlow_GCMs2_March.png", units ="in", width=8, height=5, res = 300)
```

