---
title: "Storage_GCMs"
author: "gustavo Facincani Dourado"
date: "6/14/2020"
output: html_document
---

```{r}
#Baselien 20009
#Mer 1,6
#Tuo 1,2,6,10,14
#Stn 1,2,6,10,14,18,22,26,30,34,38
#USJ 1,2,6,10,14,18,22,26,30,34

#No IFR 20009
#Mer 1,7
#Tuo 1,3,7,11,15
#Stn 1,3,7,11,15,19,23,27,31,35,39
#USJ 1,3,7,11,15,19,23,27,31,35

#Baselien 20045
#Mer 1,8
#Tuo 1,4,8,12,16
#Stn 1,4,8,12,16,20,24,28,32,36,40
#USJ 1,4,8,12,16,20,24,28,32,36

#No IFR 20045
#Mer 1,9
#Tuo 1,5,9,13,17
#Stn 1,5,9,13,17,21,25,29,33,37,41
#USJ 1,5,9,13,17,21,25,29,33,37
library(ggplot2)
```

```{r}
Livneh_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `Livneh (Historical)` = as.numeric(`Lake McClure`)) %>%
    filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Mer

CanES_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           "CanESM2\u2020" = as.numeric(`Lake McClure`))
CanES_Stor_Mer

CNRM_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
        mutate(node = as.Date(node, format = "%Y-%m-%d"),
           "CNRM-CM5\u2020" = as.numeric(`Lake McClure`))
CNRM_Stor_Mer


HadGEM_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           "HadGEM2-ES\u2020" = as.numeric(`Lake McClure`))
HadGEM_Stor_Mer


MIROC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           "MIROC5\u2020" = as.numeric(`Lake McClure`))
MIROC_Stor_Mer


HadGEMCC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `HadGEM2-CC` = as.numeric(`Lake McClure`))
HadGEMCC_Stor_Mer


CESM1_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `CESM1-BGC` = as.numeric(`Lake McClure`))
CESM1_Stor_Mer


CCSM4_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           CCSM4 = as.numeric(`Lake McClure`))
CCSM4_Stor_Mer


GFDL_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `GFDL-CM3` = as.numeric(`Lake McClure`))
GFDL_Stor_Mer


ACCESS_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `ACCESS1-0` = as.numeric(`Lake McClure`))
ACCESS_Stor_Mer


CMCC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,6)] %>%
 mutate(node = as.Date(node, format = "%Y-%m-%d"),
           `CMCC-CMS` = as.numeric(`Lake McClure`))
CMCC_Stor_Mer

```




```{r}
Livneh_Mer_Stor1 <- Livneh_Stor_Mer[(-2)] 
Livneh_Mer_Stor1 <- melt(Livneh_Mer_Stor1, id = "node")
Livneh_Mer_Stor1


Stor_Mer <- cbind(CanES_Stor_Mer[(-2)], CNRM_Stor_Mer[(-2)], 
                HadGEM_Stor_Mer[(-2)], MIROC_Stor_Mer[(-2)], ACCESS_Stor_Mer[(-2)], CMCC_Stor_Mer[(-2)], HadGEMCC_Stor_Mer[(-2)],
                GFDL_Stor_Mer[(-2)], CESM1_Stor_Mer[(-2)], CCSM4_Stor_Mer[(-2)])
 

Stor_Mer1 <- melt(Stor_Mer, id = "node") %>%
  filter(between(node, as.Date("2030-10-01"), as.Date("2060-09-30")))
Stor_Mer1
```

```{r}
#Total capacity is 1238.6 mcm, 142 mcm is dead pool, so 1/3 of it is 365.533 

OperCap_McClure <- rbind(Stor_Mer1, Livneh_Mer_Stor1) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(142),
         OperatingCapacity = (value - DeadPool),
         Count = ifelse(OperatingCapacity > 365.533, 0,1))

OperCap_McClure$GCM <- OperCap_McClure$variable
OperCap_McClure$variable <- as.factor("Lake McClure")
OperCap_McClure

OperCap_McClure$GCM <- factor(OperCap_McClure$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))


Spill_Mer <- OperCap_McClure %>%
         #Scenario = as.factor("RCP 8.5"),
         #DeadPool = as.numeric(142),
         #OperatingCapacity = (Reservoir - DeadPool),
         mutate(Count = ifelse(value == 1238.6, 1,0),
         variable = as.factor("Lake McClure"),
         Basin = "Merced River")
Spill_Mer



```


```{r}
Stor_Mer2 <- rbind(Stor_Mer1, Livneh_Mer_Stor1) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))

  

Stor_Mer2$variable <- factor(Stor_Mer2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
 

Stor_Mer3 <- Stor_Mer2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Mer3
```



Stor_Mer2 %>%
  filter(variable == "MIROC5") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Merced River",
    subtitle = "MIROC5",
    x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
png("Mer_storage_MIROC5_March.png", units ="in", width=8, height=5, res = 300)


```{r}
ggplot(Stor_Mer2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Merced River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Mer_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Mer3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
   # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Merced River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Mer_annual_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
       `Livneh (Historical)` = rowSums(.[c(2,3,4,5)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Tuo

CanES_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2,3,4,5)]))
CanES_Stor_Tuo

CNRM_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2,3,4,5)]))
CNRM_Stor_Tuo


HadGEM_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2,3,4,5)]))
HadGEM_Stor_Tuo


MIROC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2,3,4,5)]))
MIROC_Stor_Tuo


HadGEMCC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2,3,4,5)]))
HadGEMCC_Stor_Tuo


CESM1_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2,3,4,5)]))
CESM1_Stor_Tuo


CCSM4_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2,3,4,5)]))
CCSM4_Stor_Tuo


GFDL_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2,3,4,5)]))
GFDL_Stor_Tuo


ACCESS_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2,3,4,5)]))
ACCESS_Stor_Tuo


CMCC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2,3,4,5)]))
CMCC_Stor_Tuo

```

```{r}
Livneh_Tuo_Stor <- Livneh_Stor_Tuo[-c(2,3,4,5)] 
Livneh_Tuo_Stor <- melt(Livneh_Tuo_Stor, id = "node")
Livneh_Tuo_Stor


Stor_Tuo <- cbind(CanES_Stor_Tuo[-c(2,3,4,5)], CNRM_Stor_Tuo[-c(1,2,3,4,5)], 
                HadGEM_Stor_Tuo[-c(1,2,3,4,5)], MIROC_Stor_Tuo[-c(1,2,3,4,5)],
                CMCC_Stor_Tuo[-c(1,2,3,4,5)], ACCESS_Stor_Tuo[-c(1,2,3,4,5)],
                GFDL_Stor_Tuo[-c(1,2,3,4,5)], CCSM4_Stor_Tuo[-c(1,2,3,4,5)],
                CESM1_Stor_Tuo[-c(1,2,3,4,5)], HadGEMCC_Stor_Tuo[-c(1,2,3,4,5)])
Stor_Tuo
 

Stor_Tuo1 <- melt(Stor_Tuo, id = "node")
Stor_Tuo1
```


```{r}
Stor_Tuo2 <- rbind(Stor_Tuo1, Livneh_Tuo_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))
Stor_Tuo2
  

Stor_Tuo2$variable <- factor(Stor_Tuo2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Stor_Tuo3 <- Stor_Tuo2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Tuo3

```

```{r}

Stor_DonPedro <- rbind(CanES_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "CanESM2\u2020"), 
                       CNRM_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "CNRM-CM5\u2020"), 
                       HadGEM_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "HadGEM2-ES\u2020"),
                       MIROC_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "MIROC5\u2020"),
                       CMCC_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "CMCC-CMS"),
                       ACCESS_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "ACCESS1-0"),
                       GFDL_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "GFDL-CM3"), 
                       CCSM4_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "CCSM4"),
                       CESM1_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "CESM1-BGC"), 
                       HadGEMCC_Stor_Tuo[-c(2,3,5,6)]%>%mutate(GCM = "HadGEM2-CC")) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"))
Stor_DonPedro

Stor_DonPedro <- rbind(Stor_DonPedro, Livneh_Tuo_Stor %>% rename(GCM = variable,`Don Pedro Reservoir` = value)%>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")))

Stor_DonPedro1 <- melt(Stor_DonPedro, id = c("node", "GCM"))
#Stor_DonPedro1[3] <- NULL
Stor_DonPedro1
#colnames(Livneh_Stor_Tuo)[6] <- "GCM"

#Stor_DonPedro <- rbind(Stor_Tuo1, Livneh_Tuo_Stor)# %>%
#  mutate(#Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
        #                   Year = water_year(node, origin = "usgs"),
        # Scenario = as.factor("RCP 8.5"))
#Stor_DonPedro
 

#Stor_DonPedro1 <- melt(Stor_DonPedro, id = c("node", "value"))
#colnames(Stor_DonPedro1)[4] <- "variable"
#Stor_DonPedro1[3] <- NULL
#Stor_DonPedro1
```

```{r}
#Total capacity of Don Pedro is 2504 mcm, 381.0965 mcm is dead pool, so 1/3 of it is 707.6345 



OperCap_DonPedro <- Stor_DonPedro1  %>%
#  rename(GCM=variable)%>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(381.0965),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 707.6345, 0,1),
         variable = as.factor("Don Pedro Reservoir"))

OperCap_DonPedro$GCM <- factor(OperCap_DonPedro$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_DonPedro

Spill_Tuo <- OperCap_DonPedro %>%
         mutate(Count = ifelse(value == 2504, 1,0),
         variable = as.factor("Don Pedro Reservoir"),
         Basin = "Tuolumne River")
Spill_Tuo
Spill_Mer

```



Stor_Tuo2 %>%
  filter(variable == "CanESM2") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Tuolumne River",
    subtitle = "CanESM2",
    x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))



```{r}
ggplot(Stor_Tuo2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Tuolumne River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Tuo_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Tuo3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
   # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Tuolumne River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Tuo_annual_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
       `Livneh (Historical)` = rowSums(.[c(2:11)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Stn

CanES_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2:11)]))
CanES_Stor_Stn

CNRM_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2:11)]))
CNRM_Stor_Stn


HadGEM_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2:11)]))
HadGEM_Stor_Stn


MIROC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2:11)]))
MIROC_Stor_Stn


HadGEMCC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2:11)]))
HadGEMCC_Stor_Stn


CESM1_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2:11)]))
CESM1_Stor_Stn


CCSM4_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2:11)]))
CCSM4_Stor_Stn


GFDL_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2:11)]))
GFDL_Stor_Stn


ACCESS_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2:11)]))
ACCESS_Stor_Stn


CMCC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2:11)]))
CMCC_Stor_Stn

```

```{r}
#Livneh_Stor_Stn$GCM <- "Livneh (Historical)" 
#CanES_Stor_Stn$GCM <- "CanESM2\u2020"
#CNRM_Stor_Stn$GCM <- "CNRM-CM5\u2020"
#MIROC_Stor_Stn$GCM <- "MIROC5\u2020"
#HadGEM_Stor_Stn$GCM <- "HadGEM2-ES\u2020"
#HadGEMCC_Stor_Stn$GCM <- "HadGEM2-CC"
#CESM1_Stor_Stn$GCM <- "CESM1-BGC"
#CCSM4_Stor_Stn$GCM <- "CCSM4"
#GFDL_Stor_Stn$GCM <- "GFDL-CM3"
#CMCC_Stor_Stn$GCM <- "CMCC-CMS"
#ACCESS_Stor_Stn$GCM <- "ACCESS1-0"

Livneh_Stn_Stor <- Livneh_Stor_Stn[-c(2:11)] 
Livneh_Stn_Stor <- melt(Livneh_Stn_Stor, id = "node")
Livneh_Stn_Stor

Stor_Stn <- cbind(CanES_Stor_Stn[-c(2:11)], CNRM_Stor_Stn[-c(2:11)], 
                HadGEM_Stor_Stn[-c(2:11)], MIROC_Stor_Stn[-c(2:11)],
                HadGEMCC_Stor_Stn[-c(2:11)], CESM1_Stor_Stn[-c(2:11)], 
                CCSM4_Stor_Stn[-c(2:11)], GFDL_Stor_Stn[-c(2:11)], 
                CMCC_Stor_Stn[-c(2:11)], ACCESS_Stor_Stn[-c(2:11)])
Stor_Stn
 

Stor_Stn1 <- melt(Stor_Stn, id = "node")
Stor_Stn1
```

```{r}
Stor_Stn2 <- rbind(Stor_Stn1, Livneh_Stn_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         value = as.numeric(value)) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(value))
 
  

Stor_Stn2$variable <- factor(Stor_Stn2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))


Stor_Stn3 <- Stor_Stn2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Stn3
```

```{r}
Stor_NewMelones <-  rbind(CanES_Stor_Stn[c(1,7)]%>%mutate(GCM = "CanESM2\u2020"), 
                       CNRM_Stor_Stn[c(1,7)]%>%mutate(GCM = "CNRM-CM5\u2020"), 
                       HadGEM_Stor_Stn[c(1,7)]%>%mutate(GCM = "HadGEM2-ES\u2020"),
                       MIROC_Stor_Stn[c(1,7)]%>%mutate(GCM = "MIROC5\u2020"),
                       CMCC_Stor_Stn[c(1,7)]%>%mutate(GCM = "CMCC-CMS"),
                       ACCESS_Stor_Stn[c(1,7)]%>%mutate(GCM = "ACCESS1-0"),
                       GFDL_Stor_Stn[c(1,7)]%>%mutate(GCM = "GFDL-CM3"), 
                       CCSM4_Stor_Stn[c(1,7)]%>%mutate(GCM = "CCSM4"),
                       CESM1_Stor_Stn[c(1,7)]%>%mutate(GCM = "CESM1-BGC"), 
                       HadGEMCC_Stor_Stn[c(1,7)]%>%mutate(GCM = "HadGEM2-CC")) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"))
Stor_NewMelones

Stor_NewMelones <- rbind(Stor_NewMelones, Livneh_Stn_Stor %>% rename(GCM = variable,`New Melones Lake` = value)%>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")))

Stor_NewMelones1 <- melt(Stor_NewMelones, id = c("node", "GCM"))
#Stor_NewMelones1[3] <- NULL
Stor_NewMelones1

```

```{r}
#Total capacity of New Melones is 2985 mcm, 98.6785 mcm is dead pool, so 1/3 of it is 962.1071667 



OperCap_NewMelones <- Stor_NewMelones1 %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(98.6785),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 962.1072, 0,1))


OperCap_NewMelones$GCM <- factor(OperCap_NewMelones$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_NewMelones

OperCap_NewMelones <- OperCap_NewMelones %>%
 # rename(GCM = variable) %>%
  mutate(variable = as.factor("New Melones Lake"))
OperCap_NewMelones


Spill_Stn <- OperCap_NewMelones %>%
         mutate(Count = ifelse(value == 2985, 1,0),
         variable = as.factor("New Melones Lake"),
         Basin = "Stanislaus River")
Spill_Stn  
```



#Total capacity is 2985 mcm, 98.6785 mcm is dead pool, so 1/3 of it is 962.1072 mcm 
OperCap_Stn <- rbind(Stor_Stn1, Livneh_Stn_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(98.6785),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 962.1072, 0,1))
OperCap_Stn




Stor_Stn2 %>%
  filter(variable == "CanESM2") %>%

ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Stanislaus River",
    subtitle = "CanESM2",
    x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))


```{r}
ggplot(Stor_Stn2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Stanislaus River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Stn_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Stn3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
   # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Stanislaus River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("Stn_annual_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
       `Livneh (Historical)` = rowSums(.[c(2:10)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_USJ

CanES_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2:10)]))
CanES_Stor_USJ

CNRM_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2:10)]))
CNRM_Stor_USJ


HadGEM_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2:10)]))
HadGEM_Stor_USJ


MIROC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2:10)]))
MIROC_Stor_USJ


HadGEMCC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2:10)]))
HadGEMCC_Stor_USJ


CESM1_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2:10)]))
CESM1_Stor_USJ


CCSM4_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2:10)]))
CCSM4_Stor_USJ


GFDL_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2:10)]))
GFDL_Stor_USJ


ACCESS_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2:10)]))
ACCESS_Stor_USJ


CMCC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2:10)]))
CMCC_Stor_USJ

```


```{r}
Livneh_USJ_Stor <- Livneh_Stor_USJ[-c(2:10)] 
Livneh_USJ_Stor <- melt(Livneh_USJ_Stor, id = "node")
Livneh_USJ_Stor

Stor_USJ <- cbind(CanES_Stor_USJ[-c(2:10)], CNRM_Stor_USJ[-c(2:10)], 
                HadGEM_Stor_USJ[-c(2:10)], MIROC_Stor_USJ[-c(2:10)],
                HadGEMCC_Stor_USJ[-c(2:10)], CCSM4_Stor_USJ[-c(2:10)],
                CESM1_Stor_USJ[-c(2:10)], ACCESS_Stor_USJ[-c(2:10)], 
                CMCC_Stor_USJ[-c(2:10)], GFDL_Stor_USJ[-c(2:10)])
Stor_USJ
 

Stor_USJ2 <- melt(Stor_USJ, id = "node")
Stor_USJ2
```

```{r}
Stor_USJ2 <- rbind(Stor_USJ2, Livneh_USJ_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
group_by(Year, Month, variable) %>%
   dplyr::summarize(MonthlyTotal = sum(as.numeric(value)))
 
  

Stor_USJ2$variable <- factor(Stor_USJ2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Stor_USJ3 <- Stor_USJ2 %>%
  group_by(Year, variable) %>%
   dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_USJ3
```

```{r}
#Storage capacity of Millerton
Livneh_Stor_USJ$GCM <- "Livneh (Historical)" 
CanES_Stor_USJ$GCM <- "CanESM2\u2020"
CNRM_Stor_USJ$GCM <- "CNRM-CM5\u2020"
MIROC_Stor_USJ$GCM <- "MIROC5\u2020"
HadGEM_Stor_USJ$GCM <- "HadGEM2-ES\u2020"
HadGEMCC_Stor_USJ$GCM <- "HadGEM2-CC"
CESM1_Stor_USJ$GCM <- "CESM1-BGC"
CCSM4_Stor_USJ$GCM <- "CCSM4"
GFDL_Stor_USJ$GCM <- "GFDL-CM3"
CMCC_Stor_USJ$GCM <- "CMCC-CMS"
ACCESS_Stor_USJ$GCM <- "ACCESS1-0"

Stor_Millerton <- rbind(Livneh_Stor_USJ[c(1,4,12)], CanES_Stor_USJ[c(1,4,12)],
                       CNRM_Stor_USJ[c(1,4,12)], HadGEM_Stor_USJ[c(1,4,12)],
                       MIROC_Stor_USJ[c(1,4,12)], HadGEMCC_Stor_USJ[c(1,4,12)],
                       CESM1_Stor_USJ[c(1,4,12)], CCSM4_Stor_USJ[c(1,4,12)],
                       GFDL_Stor_USJ[c(1,4,12)], CMCC_Stor_USJ[c(1,4,12)],
                       ACCESS_Stor_USJ[c(1,4,12)]) #Select only New Melones
Stor_Millerton
 

Stor_Millerton1 <- melt(Stor_Millerton, id = c("node", "GCM"))
Stor_Millerton1$variable <- as.factor("Millerton Lake")
Stor_Millerton1

```

```{r}
#Total capacity of Millerton is 641.42 mcm, 165.3532 mcm is dead pool, so 1/3 of it is 158.6889 



OperCap_Millerton <- Stor_Millerton1 %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
                           Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(165.3532),
         OperatingCapacity = (value - DeadPool),
         Count = ifelse(OperatingCapacity > 158.6889, 0,1))


OperCap_Millerton$GCM <- factor(OperCap_Millerton$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_Millerton

Spill_USJ <- OperCap_Millerton %>%
         mutate(Count = ifelse(value == 641.42, 1,0),
         variable = as.factor("Millerton Lake"),
         Basin = "Upper San Joaquin River")
Spill_USJ  

```

```{r}
Spill <- rbind(Spill_Stn, Spill_Mer, Spill_Tuo, Spill_USJ)

Spill$variable <- factor(Spill$variable, levels = c("Don Pedro Reservoir","New Melones Lake", "Lake McClure", "Millerton Lake"))
Spill <- Spill %>%
  filter(between(node, as.Date("1980-10-01"), as.Date("2060-09-30"))) %>%
  filter(!between(node, as.Date("2010-10-01"), as.Date("2013-09-30")))
Spill
```

```{r}
#Storage Capacity for STN

Storage <- function (Data, Reservoir, Title, Subtitle) {
Data %>%
    #  filter() #GCM == "Livneh (Historical)") %>%# | GCM == "ACCESS1-0" | GCM == "CNRM-CM5") %>%
  filter(variable == Reservoir) %>%
ggplot() +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1980", "1985", "1990", "1995", "2000", "2005", "2010", 
                              "2030", "2035", "2040", "2009", "2050", "2055", "2060"),
                    expand = c(0, NA))+

  facet_wrap(~GCM, scales = "free_x", ncol = 1, strip.position = "left") +
  
  
  labs(title = Title,
       subtitle = Subtitle,
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Days") +
 theme(#legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())
#        panel.spacing.y = unit(0, "lines")) +
  
}
```


```{r}
windowsFonts(Times=windowsFont("Times New Roman"))

Storage(Basins_Capacity, "New Melones Lake", "Stanislaus River\nNew Melones Lake", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
png("Stn_BelowOneThird_Operating_Capacity_rcp85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r} 
Storage(Basins_Capacity, "Millerton Lake", "Upper San Joaquin River\nMillerton Lake", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
png("USJ_BelowOneThird_Operating_Capacity_rcp85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
Storage(Basins_Capacity, "Lake McClure", "Merced River\nLake McClure", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
png("Mer_BelowOneThird_Operating_Capacity_rcp85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
Storage(Basins_Capacity, "Don Pedro Reservoir", "Tuolumne River\nDon Pedro Reservoir", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
png("Tuo_BelowOneThird_Operating_Capacity_rcp85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
Storage_csv <- Basins_Capacity %>%
  group_by(variable, GCM, Year) %>%
  summarize(Count = sum(Count, na.rm = T))
Storage_csv

write_csv(Storage_csv, "Allbasins_BelowOneThird_Storage_redflag.csv")
```


```{r}
ggplot(Basins_Capacity) +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                    expand = c(0, NA))+

  facet_wrap(GCM~variable, scales = "free_x", ncol = 4)+#,  strip.position = "left") +
  
  
  labs(title = "Storage Below One Third of Reservoir Operating Capacity",
       subtitle = "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)",
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Days") +
 theme(#strip.text.x = element_blank(),
       #legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
       # panel.spacing.y = unit(0, "lines")) +
png("AllBasins_BelowOneThird_Operating_Capacity_rcp85_Baseline_2009prices_Report_March.png", units ="in", width=8, height=16, res = 300)

```


```{r}
ggplot(Basins_Capacity) +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1991", "2001", 
                              "2031", "2041", "2051"),
                    expand = c(0, NA))+

  facet_grid(variable~GCM, scales = "free_x") +
  
  
  labs(title = "Storage Below One Third of Reservoir Operating Capacity",
       subtitle = "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)",
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Days") +
 theme(strip.text.y.left = element_text(angle = 0),#strip.text.x = element_blank(),
       #legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
       # panel.spacing.y = unit(0, "lines")) +
png("AllBasins_BelowOneThird_Operating_Capacity_FacetGrid_rcp85_Baseline_2009prices_Report_March.png", units ="in", width=18, height=6, res = 300)
```



Basins_Capacity %>%
  filter(GCM == "CanESM2") %>%
ggplot() +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                    expand = c(0, NA))+

  facet_wrap(~GCM, scales = "free_x", ncol = 1, strip.position = "left") +
  
  
  labs(title = "New Melones Lake",
       subtitle = "RCP 8.5 Scenario",
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Days") +
 theme(#legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())



```{r}
ggplot(Stor_USJ2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Upper San Joaquin River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("USJ_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_USJ3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
   # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +

  labs(fill = "RCP 8.5", title = "Upper San Joaquin River",
       subtitle = "Baseline (2009 prices)",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
png("USJ_annual_storage_10GCMs_Baseline_2009prices_rcp85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```

```{r}
#Facet wraps of all basins

Stor_Mer2$Basin <- "Merced River"
Stor_Mer3$Basin <- "Merced River"
Stor_Tuo2$Basin <- "Tuolumne River"
Stor_Tuo3$Basin <- "Tuolumne River"
Stor_Stn2$Basin <- "Stanislaus River"
Stor_Stn3$Basin <- "Stanislaus River"
Stor_USJ2$Basin <- "Upper San Joaquin River"
Stor_USJ3$Basin <- "Upper San Joaquin River"



all_storage_monthly <- rbind(Stor_Mer2, Stor_Tuo2, Stor_Stn2 ,Stor_USJ2)

all_storage_monthly$Basin <- factor(all_storage_monthly$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_monthly

all_storage_year <- rbind(Stor_Mer3, Stor_Tuo3, Stor_Stn3 ,Stor_USJ3)

all_storage_year$Basin <- factor(all_storage_year$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_year

```

```{r}
all_storage_monthly$Month <- factor(all_storage_monthly$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
all_storage_monthly

All_Montlhy_Stats_Stor <- aggregate(MonthlyTotal ~ Month+variable+Basin, all_storage_monthly, summary)
write.csv(All_Montlhy_Stats_Stor, "All_Monthly_Stats_Storage_Baseline_2009prices_RCP85_Report.csv")

All_Annual_Stats_Stor <- aggregate(AnnualTotal ~ variable+Basin, all_storage_year, summary)
write.csv(All_Annual_Stats_Stor, "All_Annual_Stats_Storage_Baseline_2009prices_RCP85_Report.csv")
```

```{r}
ggplot(all_storage_monthly) + 
  theme_bw(base_size=18, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
    scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 8.5",
       #title = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~Basin, scales = "free_y")+
png("AllBasins_storage_10GCMs_rcp85_Baseline_2009prices_Report_March.png", units ="in", width=15, height=10, res = 300)

```

```{r}
#annual aggreagate
ggplot(all_storage_year) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
    geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(limits = c(0, NA),
                      expand = c(0, NA),
                      labels = comma) +
#    scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +

  labs(fill = "RCP 8.5",
       #title = "Upper San Joaquin River",
    x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
         axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        legend.text = element_text(size = 9),
       legend.key.size = unit(0.75,"line"),
        panel.spacing.y = unit(0, "lines"))+
    facet_wrap(~Basin, scales = "free_y")+
png("AllBasins_annual_storage_10GCMs_rcp85_Baseline_2009prices_Report_March.png", units ="in", width=8, height=5, res = 300)
```

```{r}
#Facet wraps of all basins

Stor_Mer2$Basin <- "Merced River"
Stor_Mer3$Basin <- "Merced River"
Stor_Tuo2$Basin <- "Tuolumne River"
Stor_Tuo3$Basin <- "Tuolumne River"
Stor_Stn2$Basin <- "Stanislaus River"
Stor_Stn3$Basin <- "Stanislaus River"
Stor_USJ2$Basin <- "Upper San Joaquin River"
Stor_USJ3$Basin <- "Upper San Joaquin River"



all_storage_monthly <- rbind(Stor_Mer2, Stor_Tuo2, Stor_Stn2 ,Stor_USJ2)

all_storage_monthly$Basin <- factor(all_storage_monthly$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_monthly

all_storage_year <- rbind(Stor_Mer3, Stor_Tuo3, Stor_Stn3 ,Stor_USJ3)

all_storage_year$Basin <- factor(all_storage_year$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_year

```

```{r}
all_storage_monthly$Month <- factor(all_storage_monthly$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
all_storage_monthly


All_Annual_Stats_Stor <- aggregate(AnnualTotal ~ variable+Basin, all_storage_year, summary)
write.csv(All_Annual_Stats_Stor, "All_Annual_Stats_Storage_Baseline_2009prices_RCP8.5_Report.csv")
```


```{r}
Total_Spill1 <- Total_Spill %>%
 # mutate(Year = as.numeric(Year)) %>%
  filter(between(node, as.Date("1980-10-01"), as.Date("2060-09-30"))) %>%
  filter(!between(node, as.Date("2010-09-01"), as.Date("2030-09-30")))

Total_Spill1

```

```{r}


#Total_Spill$GCM <- factor(Total_Spill$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Spill_Mer$GCM <- factor(Spill_Mer$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Spill_Stn$GCM <- factor(Spill_Stn$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Spill_Tuo$GCM <- factor(Spill_Tuo$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Spill_USJ$GCM <- factor(Spill_USJ$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
Total_Spill <- rbind(Spill_Mer, Spill_Stn, Spill_Tuo, Spill_USJ)

Total_Spill
```

```{r}
spill_csv <- Total_Spill %>%
  group_by(Basin, variable,GCM,Year) %>%
  summarize(Count = sum(Count))

spill_csv


write_csv(spill_csv, "All_basins_Spill_count.csv")

```


```{r}
ggplot(Total_Spill) +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,160), breaks = c(0, 40, 80, 120, 160)) +
  scale_x_discrete(breaks = c("1980", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                    expand = c(0, NA))+

  facet_wrap(GCM~Basin, scales = "free_x", ncol = 4) +
  
  labs(#title = "Storage Below One Third of Reservoir Operating Capacity",
      subtitle = "RCP 8.5 Scenario",
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Spill occurrence (Days)") +
 theme(#strip.text.x = element_blank(),
       #legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
       # panel.spacing.y = unit(0, "lines")) +
png("AllBasins_Spill_FacetWrap_RCP85_2009prices_Baseline_Report_March.png", units ="in", width=8, height=8, res = 300)
```


```{r}
ggplot(Total_Spill) +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,160), breaks = c(0, 40, 80, 120, 160)) +
  scale_x_discrete(breaks = c("1981", "1991", "2001", 
                              "2031", "2041","2051"),
                    expand = c(0, NA))+

  facet_grid(Basin~GCM, scales = "free_x") +
  
  labs(#title = "Storage Below One Third of Reservoir Operating Capacity",
       subtitle = "RCP 8.5 Scenario",
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Spill occurrence (Days)") +
 theme(#strip.text.x = element_blank(),
       #legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
       # panel.spacing.y = unit(0, "lines")) +
png("AllBasins_Spill_FacetGrid.png", units ="in", width=12, height=8, res = 300)
```


```{r}
#Spill for each basin

Spill <- function (Data, Basins, Title, Subtitle) {
Data%>%
  #filter(Basin == Basins) %>%
  #  filter(GCM == "Livneh (Historical)" | GCM == "ACCESS1-0" | GCM == "CNRM-CM5") %>%
ggplot() +
     theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
ggthemes::scale_color_colorblind() +
   scale_y_continuous(expand = c(0, NA),
                      limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                    expand = c(0, NA))+

  facet_wrap(~GCM, scales = "free_x", ncol = 1, strip.position = "left") +
  
  
  labs(title = Title,
       subtitle = Subtitle,
       
  #  subtitle = "CanESM2",
    x = element_blank(),
       y = "Spill Occurrence (Days)") +
 theme(#legend.title = element_blank(),
    #legend.position = "bottom",
     #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())
#        panel.spacing.y = unit(0, "lines")) +
}
```

```{r}
  Spill(Total_Spill1 %>% filter(Basin == "Merced River"), "Merced River", "Merced River", "Baseline - 2009 prices (RCP 8.5 Scenario)") +
png("Mer_Spill_Baseline_2009prices_RCP85_10GCMs_Report_2.png", units ="in", width=5, height=16, res = 300)
```

```{r}
  Spill(Total_Spill1 %>% filter(Basin == "Upper San Joaquin River"),"Upper San Joaquin River", "Upper San Joaquin River", "Baseline - 2009 prices (RCP 8.5 Scenario)") +
png("USJ_Spill_Baseline_2009prices_RCP85_10GCMs_Report.png", units ="in", width=5, height=16, res = 300)
```

```{r}
  Spill(Total_Spill1 %>% filter(Basin == "Tuolumne River"), "Tuolumne River", "Tuolumne River", "Baseline - 2009 prices (RCP 8.5 Scenario)") +
png("Tuo_Spill_Baseline_2009prices_RCP85_10GCMs_Report.png", units ="in", width=5, height=16, res = 300)
```

```{r}
  Spill(Total_Spill1 %>% filter(Basin == "Stanislaus River"), "Stanislaus River", "Stanislaus River", "Baseline - 2009 prices (RCP 8.5 Scenario)") +
png("Stn_Spill_Baseline_2009prices_RCP85_10GCMs_Report.png", units ="in",width=5, height=16, res = 300)
```
---
  title: "Storage_GCMs"
author: "gustavo Facincani Dourado"
date: "6/14/2020"
output: html_document
---
  
  ```{r}
#NoIFRs 2009
#Mer 1,6
#Tuo 1,2,6,10,14
#Stn 1,2,6,10,14,18,22,26,30,34,38
#USJ 1,2,6,10,14,18,22,26,30,34

#No IFR 2009
#Mer 1,7
#Tuo 1,3,7,11,15
#Stn 1,3,7,11,15,19,23,27,31,35,39
#USJ 1,3,7,11,15,19,23,27,31,35

#NoIFRs 2009
#Mer 1,8
#Tuo 1,4,8,12,16
#Stn 1,4,8,12,16,20,24,28,32,36,40
#USJ 1,4,8,12,16,20,24,28,32,36

#No IFR 2009
#Mer 1,9
#Tuo 1,5,9,13,17
#Stn 1,5,9,13,17,21,25,29,33,37,41
#USJ 1,5,9,13,17,21,25,29,33,37
library(ggplot2)
```

```{r}
Livneh_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `Livneh (Historical)` = as.numeric(`Lake McClure`)) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Mer

CanES_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = as.numeric(`Lake McClure`))
CanES_Stor_Mer

CNRM_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = as.numeric(`Lake McClure`))
CNRM_Stor_Mer


HadGEM_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = as.numeric(`Lake McClure`))
HadGEM_Stor_Mer


MIROC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = as.numeric(`Lake McClure`))
MIROC_Stor_Mer


HadGEMCC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = as.numeric(`Lake McClure`))
HadGEMCC_Stor_Mer


CESM1_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = as.numeric(`Lake McClure`))
CESM1_Stor_Mer


CCSM4_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = as.numeric(`Lake McClure`))
CCSM4_Stor_Mer


GFDL_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = as.numeric(`Lake McClure`))
GFDL_Stor_Mer


ACCESS_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = as.numeric(`Lake McClure`))
ACCESS_Stor_Mer


CMCC_Stor_Mer <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/merced/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,7)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = as.numeric(`Lake McClure`))
CMCC_Stor_Mer

```




```{r}
Livneh_Mer_Stor1 <- Livneh_Stor_Mer[(-2)] 
Livneh_Mer_Stor1 <- melt(Livneh_Mer_Stor1, id = "node")
Livneh_Mer_Stor1


Stor_Mer <- cbind(CanES_Stor_Mer[(-2)], CNRM_Stor_Mer[(-2)], 
                  HadGEM_Stor_Mer[(-2)], MIROC_Stor_Mer[(-2)], ACCESS_Stor_Mer[(-2)], CMCC_Stor_Mer[(-2)], HadGEMCC_Stor_Mer[(-2)],
                  GFDL_Stor_Mer[(-2)], CESM1_Stor_Mer[(-2)], CCSM4_Stor_Mer[(-2)])


Stor_Mer1 <- melt(Stor_Mer, id = "node") %>%
  filter(between(node, as.Date("2030-10-01"), as.Date("2060-09-30")))
Stor_Mer1
```

```{r}
#Total capacity is 1238.6 mcm, 142 mcm is dead pool, so 1/3 of it is 365.533 

OperCap_McClure <- rbind(Stor_Mer1, Livneh_Mer_Stor1) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(142),
         OperatingCapacity = (value - DeadPool),
         Count = ifelse(OperatingCapacity > 365.533, 0,1))

OperCap_McClure$GCM <- OperCap_McClure$variable
OperCap_McClure$variable <- as.factor("Lake McClure")
OperCap_McClure

OperCap_McClure$GCM <- factor(OperCap_McClure$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

```


```{r}
Stor_Mer2 <- rbind(Stor_Mer1, Livneh_Mer_Stor1) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
  group_by(Year, Month, variable) %>%
  dplyr::summarize(MonthlyTotal = sum(value))



Stor_Mer2$variable <- factor(Stor_Mer2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))


Stor_Mer3 <- Stor_Mer2 %>%
  group_by(Year, variable) %>%
  dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Mer3
```



Stor_Mer2 %>%
  filter(variable == "MIROC5") %>%
  
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Merced River",
       subtitle = "MIROC5",
       x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines")) +
  png("Mer_storage_MIROC5_March.png", units ="in", width=8, height=5, res = 300)


```{r}
ggplot(Stor_Mer2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Merced River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Mer_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Mer3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Merced River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Mer_annual_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `Livneh (Historical)` = rowSums(.[c(2,3,4,5)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Tuo

CanES_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2,3,4,5)]))
CanES_Stor_Tuo

CNRM_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2,3,4,5)]))
CNRM_Stor_Tuo


HadGEM_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2,3,4,5)]))
HadGEM_Stor_Tuo


MIROC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2,3,4,5)]))
MIROC_Stor_Tuo


HadGEMCC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2,3,4,5)]))
HadGEMCC_Stor_Tuo


CESM1_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2,3,4,5)]))
CESM1_Stor_Tuo


CCSM4_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2,3,4,5)]))
CCSM4_Stor_Tuo


GFDL_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2,3,4,5)]))
GFDL_Stor_Tuo


ACCESS_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2,3,4,5)]))
ACCESS_Stor_Tuo


CMCC_Stor_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-16/tuolumne/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2,3,4,5)]))
CMCC_Stor_Tuo

```

```{r}
Livneh_Tuo_Stor <- Livneh_Stor_Tuo[-c(2,3,4,5)] 
Livneh_Tuo_Stor <- melt(Livneh_Tuo_Stor, id = "node")
Livneh_Tuo_Stor


Stor_Tuo <- cbind(CanES_Stor_Tuo[-c(2,3,4,5)], CNRM_Stor_Tuo[-c(1,2,3,4,5)], 
                  HadGEM_Stor_Tuo[-c(1,2,3,4,5)], MIROC_Stor_Tuo[-c(1,2,3,4,5)],
                  CMCC_Stor_Tuo[-c(1,2,3,4,5)], ACCESS_Stor_Tuo[-c(1,2,3,4,5)],
                  GFDL_Stor_Tuo[-c(1,2,3,4,5)], CCSM4_Stor_Tuo[-c(1,2,3,4,5)],
                  CESM1_Stor_Tuo[-c(1,2,3,4,5)], HadGEMCC_Stor_Tuo[-c(1,2,3,4,5)])
Stor_Tuo


Stor_Tuo1 <- melt(Stor_Tuo, id = "node")
Stor_Tuo1
```


```{r}
Stor_Tuo2 <- rbind(Stor_Tuo1, Livneh_Tuo_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
  group_by(Year, Month, variable) %>%
  dplyr::summarize(MonthlyTotal = sum(value))
Stor_Tuo2


Stor_Tuo2$variable <- factor(Stor_Tuo2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Stor_Tuo3 <- Stor_Tuo2 %>%
  group_by(Year, variable) %>%
  dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Tuo3

```

```{r}
Stor_DonPedro <- rbind(Stor_Tuo1, Livneh_Tuo_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"))
Stor_DonPedro

Stor_DonPedro1 <- melt(Stor_DonPedro, id = c("node", "variable"))
Stor_DonPedro1[3] <- NULL
Stor_DonPedro1
#colnames(Livneh_Stor_Tuo)[6] <- "GCM"

#Stor_DonPedro <- rbind(Stor_Tuo1, Livneh_Tuo_Stor)# %>%
#  mutate(#Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
#                   Year = water_year(node, origin = "usgs"),
# Scenario = as.factor("RCP 8.5"))
#Stor_DonPedro


#Stor_DonPedro1 <- melt(Stor_DonPedro, id = c("node", "value"))
#colnames(Stor_DonPedro1)[4] <- "variable"
#Stor_DonPedro1[3] <- NULL
#Stor_DonPedro1
```

```{r}
#Total capacity of Don Pedro is 2504 mcm, 381.0965 mcm is dead pool, so 1/3 of it is 707.6345 



OperCap_DonPedro <- Stor_DonPedro1  %>%
  rename(GCM=variable)%>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(381.0965),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 707.6345, 0,1),
         variable = as.factor("Don Pedro Reservoir"))


OperCap_DonPedro$GCM <- factor(OperCap_DonPedro$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_DonPedro

```



Stor_Tuo2 %>%
  filter(variable == "CanESM2") %>%
  
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Tuolumne River",
       subtitle = "CanESM2",
       x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))



```{r}
ggplot(Stor_Tuo2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Tuolumne River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Tuo_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Tuo3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Tuolumne River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Tuo_annual_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `Livneh (Historical)` = rowSums(.[c(2:11)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_Stn

CanES_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2:11)]))
CanES_Stor_Stn

CNRM_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2:11)]))
CNRM_Stor_Stn


HadGEM_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2:11)]))
HadGEM_Stor_Stn


MIROC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2:11)]))
MIROC_Stor_Stn


HadGEMCC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2:11)]))
HadGEMCC_Stor_Stn


CESM1_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2:11)]))
CESM1_Stor_Stn


CCSM4_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2:11)]))
CCSM4_Stor_Stn


GFDL_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2:11)]))
GFDL_Stor_Stn


ACCESS_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2:11)]))
ACCESS_Stor_Stn


CMCC_Stor_Stn <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/stanislaus/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,2,6,10,14,18,22,26,30,34,38)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2:11)]))
CMCC_Stor_Stn

```

```{r}
#Livneh_Stor_Stn$GCM <- "Livneh (Historical)" 
#CanES_Stor_Stn$GCM <- "CanESM2\u2020"
#CNRM_Stor_Stn$GCM <- "CNRM-CM5\u2020"
#MIROC_Stor_Stn$GCM <- "MIROC5\u2020"
#HadGEM_Stor_Stn$GCM <- "HadGEM2-ES\u2020"
#HadGEMCC_Stor_Stn$GCM <- "HadGEM2-CC"
#CESM1_Stor_Stn$GCM <- "CESM1-BGC"
#CCSM4_Stor_Stn$GCM <- "CCSM4"
#GFDL_Stor_Stn$GCM <- "GFDL-CM3"
#CMCC_Stor_Stn$GCM <- "CMCC-CMS"
#ACCESS_Stor_Stn$GCM <- "ACCESS1-0"

Livneh_Stn_Stor <- Livneh_Stor_Stn[-c(2:11)] 
Livneh_Stn_Stor <- melt(Livneh_Stn_Stor, id = "node")
Livneh_Stn_Stor

Stor_Stn <- cbind(CanES_Stor_Stn[-c(2:11)], CNRM_Stor_Stn[-c(2:11)], 
                  HadGEM_Stor_Stn[-c(2:11)], MIROC_Stor_Stn[-c(2:11)],
                  HadGEMCC_Stor_Stn[-c(2:11)], CESM1_Stor_Stn[-c(2:11)], 
                  CCSM4_Stor_Stn[-c(2:11)], GFDL_Stor_Stn[-c(2:11)], 
                  CMCC_Stor_Stn[-c(2:11)], ACCESS_Stor_Stn[-c(2:11)])
Stor_Stn


Stor_Stn1 <- melt(Stor_Stn, id = "node")
Stor_Stn1
```

```{r}
Stor_Stn2 <- rbind(Stor_Stn1, Livneh_Stn_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         value = as.numeric(value)) %>%
  group_by(Year, Month, variable) %>%
  dplyr::summarize(MonthlyTotal = sum(value))



Stor_Stn2$variable <- factor(Stor_Stn2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))


Stor_Stn3 <- Stor_Stn2 %>%
  group_by(Year, variable) %>%
  dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_Stn3
```

```{r}
Stor_NewMelones <- rbind(Stor_Stn1, Livneh_Stn_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"))
Stor_NewMelones

Stor_NewMelones1 <- melt(Stor_NewMelones, id = c("node", "variable"))
Stor_NewMelones1[3] <- NULL
Stor_NewMelones1

```

```{r}
#Total capacity of New Melones is 2985 mcm, 98.6785 mcm is dead pool, so 1/3 of it is 962.1071667 



OperCap_NewMelones <- Stor_NewMelones1 %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(98.6785),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 962.1072, 0,1))


OperCap_NewMelones$variable <- factor(OperCap_NewMelones$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_NewMelones

OperCap_NewMelones <- OperCap_NewMelones %>%
  rename(GCM = variable) %>%
  mutate(variable = as.factor("New Melones Lake"))
OperCap_NewMelones


Spill_Stn <- OperCap_NewMelones %>%
         mutate(Count = ifelse(value >= 3486, 1,0),
         variable = as.factor("New Melones Lake"))
Spill_Stn  


```

{r}
#Total capacity is 2985 mcm, 98.6785 mcm is dead pool, so 1/3 of it is 962.1072 mcm 
OperCap_Stn <- rbind(Stor_Stn1, Livneh_Stn_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(98.6785),
         OperatingCapacity = (as.numeric(value) - DeadPool),
         Count = ifelse(OperatingCapacity > 962.1072, 0,1))
OperCap_Stn



Stor_Stn2 %>%
  filter(variable == "CanESM2") %>%
  
  ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = value), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
  labs(title = "Stanislaus River",
       subtitle = "CanESM2",
       x = element_blank(),
       y = "Total Storage (mcm)") + #name of x axis
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))


```{r}
ggplot(Stor_Stn2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Stanislaus River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Stn_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
#annual aggreagate
ggplot(Stor_Stn3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Stanislaus River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("Stn_annual_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```


```{r}
Livneh_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/historical/Livneh/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `Livneh (Historical)` = rowSums(.[c(2:10)])) %>%
  filter(between(node, as.Date("1950-10-01"), as.Date("2011-09-30")))
Livneh_Stor_USJ

CanES_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CanESM2_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CanESM2\u2020" = rowSums(.[c(2:10)]))
CanES_Stor_USJ

CNRM_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CNRM-CM5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "CNRM-CM5\u2020" = rowSums(.[c(2:10)]))
CNRM_Stor_USJ


HadGEM_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/HadGEM2-ES_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "HadGEM2-ES\u2020" = rowSums(.[c(2:10)]))
HadGEM_Stor_USJ


MIROC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/MIROC5_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         "MIROC5\u2020" = rowSums(.[c(2:10)]))
MIROC_Stor_USJ


HadGEMCC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/HadGEM2-CC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `HadGEM2-CC` = rowSums(.[c(2:10)]))
HadGEMCC_Stor_USJ


CESM1_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CESM1-BGC_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CESM1-BGC` = rowSums(.[c(2:10)]))
CESM1_Stor_USJ


CCSM4_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CCSM4_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         CCSM4 = rowSums(.[c(2:10)]))
CCSM4_Stor_USJ


GFDL_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/GFDL-CM3_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `GFDL-CM3` = rowSums(.[c(2:10)]))
GFDL_Stor_USJ


ACCESS_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/ACCESS1-0_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `ACCESS1-0` = rowSums(.[c(2:10)]))
ACCESS_Stor_USJ


CMCC_Stor_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Binary IFRs x Prices - 2021-03-29/upper_san_joaquin/gcms/CMCC-CMS_rcp85/Reservoir_Storage_mcm.csv", col_types = cols(node = col_date(), .default = col_double()))[-c(1:3), c(1,3,7,11,15,19,23,27,31,35)] %>%
  mutate(node = as.Date(node, format = "%Y-%m-%d"),
         `CMCC-CMS` = rowSums(.[c(2:10)]))
CMCC_Stor_USJ

```


```{r}
Livneh_USJ_Stor <- Livneh_Stor_USJ[-c(2:10)] 
Livneh_USJ_Stor <- melt(Livneh_USJ_Stor, id = "node")
Livneh_USJ_Stor

Stor_USJ <- cbind(CanES_Stor_USJ[-c(2:10)], CNRM_Stor_USJ[-c(2:10)], 
                  HadGEM_Stor_USJ[-c(2:10)], MIROC_Stor_USJ[-c(2:10)],
                  HadGEMCC_Stor_USJ[-c(2:10)], CCSM4_Stor_USJ[-c(2:10)],
                  CESM1_Stor_USJ[-c(2:10)], ACCESS_Stor_USJ[-c(2:10)], 
                  CMCC_Stor_USJ[-c(2:10)], GFDL_Stor_USJ[-c(2:10)])
Stor_USJ


Stor_USJ2 <- melt(Stor_USJ, id = "node")
Stor_USJ2
```

```{r}
Stor_USJ2 <- rbind(Stor_USJ2, Livneh_USJ_Stor) %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5")) %>%
  group_by(Year, Month, variable) %>%
  dplyr::summarize(MonthlyTotal = sum(as.numeric(value)))



Stor_USJ2$variable <- factor(Stor_USJ2$variable, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))

Stor_USJ3 <- Stor_USJ2 %>%
  group_by(Year, variable) %>%
  dplyr::summarize(AnnualTotal = sum(MonthlyTotal)) 

Stor_USJ3
```

```{r}
#Storage capacity of Millerton
Livneh_Stor_USJ$GCM <- "Livneh (Historical)" 
CanES_Stor_USJ$GCM <- "CanESM2\u2020"
CNRM_Stor_USJ$GCM <- "CNRM-CM5\u2020"
MIROC_Stor_USJ$GCM <- "MIROC5\u2020"
HadGEM_Stor_USJ$GCM <- "HadGEM2-ES\u2020"
HadGEMCC_Stor_USJ$GCM <- "HadGEM2-CC"
CESM1_Stor_USJ$GCM <- "CESM1-BGC"
CCSM4_Stor_USJ$GCM <- "CCSM4"
GFDL_Stor_USJ$GCM <- "GFDL-CM3"
CMCC_Stor_USJ$GCM <- "CMCC-CMS"
ACCESS_Stor_USJ$GCM <- "ACCESS1-0"

Stor_Millerton <- rbind(Livneh_Stor_USJ[c(1,4,12)], CanES_Stor_USJ[c(1,4,12)],
                        CNRM_Stor_USJ[c(1,4,12)], HadGEM_Stor_USJ[c(1,4,12)],
                        MIROC_Stor_USJ[c(1,4,12)], HadGEMCC_Stor_USJ[c(1,4,12)],
                        CESM1_Stor_USJ[c(1,4,12)], CCSM4_Stor_USJ[c(1,4,12)],
                        GFDL_Stor_USJ[c(1,4,12)], CMCC_Stor_USJ[c(1,4,12)],
                        ACCESS_Stor_USJ[c(1,4,12)]) #Select only New Melones
Stor_Millerton


Stor_Millerton1 <- melt(Stor_Millerton, id = c("node", "GCM"))
Stor_Millerton1$variable <- as.factor("Millerton Lake")
Stor_Millerton1

```

```{r}
#Total capacity of Millerton is 641.42 mcm, 165.3532 mcm is dead pool, so 1/3 of it is 158.6889 



OperCap_Millerton <- Stor_Millerton1 %>%
  mutate(Month = as.factor(format(as.Date(node, format = "%B"), "%b")),
         Year = water_year(node, origin = "usgs"),
         Scenario = as.factor("RCP 8.5"),
         DeadPool = as.numeric(165.3532),
         OperatingCapacity = (value - DeadPool),
         Count = ifelse(OperatingCapacity > 158.6889, 0,1))

Spill_USJ <- OperCap_Millerton %>%
         mutate(Count = ifelse(value >= 641.42, 1,0),
         variable = as.factor("Millerton Lake"),
         Basin = "Upper San Joaquin River")
Spill_USJ  


OperCap_Millerton$GCM <- factor(OperCap_Millerton$GCM, levels = c("Livneh (Historical)", "ACCESS1-0", "CMCC-CMS", "MIROC5\u2020", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "HadGEM2-ES\u2020","CESM1-BGC", "CanESM2\u2020", "CNRM-CM5\u2020"))
OperCap_Millerton

```

```{r}
Basins_Capacity <- rbind(OperCap_McClure, OperCap_Millerton, OperCap_DonPedro, OperCap_NewMelones)

Basins_Capacity$variable <- factor(Basins_Capacity$variable, levels = c("New Melones Lake","Don Pedro Reservoir", "Lake McClure", "Millerton Lake"))
#Basins_Capacity <- Basins_Capacity %>%
 # filter(between(node, as.Date("1980-10-01"), as.Date("2060-09-30"))) %>%
#  filter(!between(node, as.Date("2010-10-01"), as.Date("2013-09-30")))
Basins_Capacity
```

```{r}
#Storage Capacity for STN

Storage <- function (Data, Reservoir, Title, Subtitle) {
  Data %>%
    #  filter() #GCM == "Livneh (Historical)") %>%# | GCM == "ACCESS1-0" | GCM == "CNRM-CM5") %>%
    filter(variable == Reservoir) %>%
    ggplot() +
    theme_bw(base_size=12, base_family='Times New Roman') +
    geom_bar(aes(x= Year, y=Count), stat = "identity") +
    ggthemes::scale_color_colorblind() +
    scale_y_continuous(expand = c(0, NA),
                       limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
    scale_x_discrete(breaks = c("1980", "1985", "1990", "1995", "2000", "2005", "2010", 
                                "2030", "2035", "2040", "2009", "2050", "2055", "2060"),
                     expand = c(0, NA))+
    
    facet_wrap(~GCM, scales = "free_x", ncol = 1, strip.position = "left") +
    
    
    labs(title = Title,
         subtitle = Subtitle,
         
         #  subtitle = "CanESM2",
         x = element_blank(),
         y = "Days") +
    theme(#legend.title = element_blank(),
      #legend.position = "bottom",
      #   legend.direction = "horizontal",
      #  legend.box.margin = margin(t = -17),
      plot.title = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5),
      strip.placement = "outside",
      strip.background = element_blank())
  #        panel.spacing.y = unit(0, "lines")) +
  
}
```


```{r}

Storage(Basins_Capacity, "New Melones Lake", "Stanislaus River\nNew Melones Lake", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
  png("Stn_BelowOneThird_Operating_Capacity_RCP85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r} 
Storage(Basins_Capacity, "Millerton Lake", "Upper San Joaquin River\nMillerton Lake", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
  png("USJ_BelowOneThird_Operating_Capacity_RCP85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
Storage(Basins_Capacity, "Lake McClure", "Merced River\nLake McClure", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
  png("Mer_BelowOneThird_Operating_Capacity_RCP85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
Storage(Basins_Capacity, "Don Pedro Reservoir", "Tuolumne River\nDon Pedro Reservoir", "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)")+
  png("Tuo_BelowOneThird_Operating_Capacity_RCP85_Baseline_2009prices_10GCMs_Report_March.png", units ="in", width=5, height=16, res = 300)
```

```{r}
ggplot(Basins_Capacity) +
  theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
  ggthemes::scale_color_colorblind() +
  scale_y_continuous(expand = c(0, NA),
                     limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                   expand = c(0, NA))+
  
  facet_wrap(GCM~variable, scales = "free_x", ncol = 4)+#,  strip.position = "left") +
  
  
  labs(title = "Storage Below One Third of Reservoir Operating Capacity",
       subtitle = "No Intreamflow Requirement - 2009 prices (RCP 8.5 Scenario)",
       
       #  subtitle = "CanESM2",
       x = element_blank(),
       y = "Days") +
  theme(#strip.text.x = element_blank(),
    #legend.title = element_blank(),
    #legend.position = "bottom",
    #   legend.direction = "horizontal",
    #  legend.box.margin = margin(t = -17),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    strip.placement = "outside",
    strip.background = element_blank())+
  # panel.spacing.y = unit(0, "lines")) +
  png("AllBasins_BelowOneThird_Operating_Capacity_RCP85_Baseline_2009prices_Report_March.png", units ="in", width=8, height=16, res = 300)

```


```{r}
ggplot(Basins_Capacity) +
  theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
  ggthemes::scale_color_colorblind() +
  scale_y_continuous(expand = c(0, NA),
                     limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1991", "2001", 
                              "2031", "2041", "2051"),
                   expand = c(0, NA))+
  
  facet_grid(variable~GCM, scales = "free_x") +
  
  
  labs(title = "Storage Below One Third of Reservoir Operating Capacity",
       subtitle = "Baseline - 2009 prices (RCP 8.5 Scenario)",
       
       #  subtitle = "CanESM2",
       x = element_blank(),
       y = "Days") +
  theme(strip.text.y.left = element_text(angle = 0),#strip.text.x = element_blank(),
        #legend.title = element_blank(),
        #legend.position = "bottom",
        #   legend.direction = "horizontal",
        #  legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
  # panel.spacing.y = unit(0, "lines")) +
  png("AllBasins_BelowOneThird_Operating_Capacity_FacetGrid_RCP85_Baseline_2009prices_Report_March.png", units ="in", width=18, height=6, res = 300)
```



Basins_Capacity %>%
  filter(GCM == "CanESM2") %>%
  ggplot() +
  theme_bw(base_size=12, base_family='Times New Roman') +
  geom_bar(aes(x= Year, y=Count), stat = "identity") +
  scale_color_colorblind() +
  scale_y_continuous(expand = c(0, NA),
                     limits = c(0,366), breaks = c(0, 100, 200, 300, 366)) +
  scale_x_discrete(breaks = c("1981", "1986", "1991", "1996", "2001", "2006", 
                              "2031", "2036", "2041", "2046", "2051", "2056"),
                   expand = c(0, NA))+
  
  facet_wrap(~GCM, scales = "free_x", ncol = 1, strip.position = "left") +
  
  
  labs(title = "New Melones Lake",
       subtitle = "RCP 8.5 Scenario",
       
       #  subtitle = "CanESM2",
       x = element_blank(),
       y = "Days") +
  theme(#legend.title = element_blank(),
    #legend.position = "bottom",
    #   legend.direction = "horizontal",
    #  legend.box.margin = margin(t = -17),
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5),
    strip.placement = "outside",
    strip.background = element_blank())



```{r}
ggplot(Stor_USJ2) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = MonthlyTotal, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Upper San Joaquin River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/month)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("USJ_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=10, height=5, res = 300)

```

```{r}
library(extrafont)
#annual aggreagate
ggplot(Stor_USJ3) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  # scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A","#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695")) +
  
  labs(fill = "RCP 8.5", title = "Upper San Joaquin River",
       subtitle = "Baseline (2009 prices)",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "none",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("USJ_annual_storage_10GCMs_Baseline_2009prices_RCP85_Report_March.png", units ="in", width=11.5, height=4.5, res = 300)
```

```{r}
#Facet wraps of all basins

Stor_Mer2$Basin <- "Merced River"
Stor_Mer3$Basin <- "Merced River"
Stor_Tuo2$Basin <- "Tuolumne River"
Stor_Tuo3$Basin <- "Tuolumne River"
Stor_Stn2$Basin <- "Stanislaus River"
Stor_Stn3$Basin <- "Stanislaus River"
Stor_USJ2$Basin <- "Upper San Joaquin River"
Stor_USJ3$Basin <- "Upper San Joaquin River"



all_storage_monthly <- rbind(Stor_Mer2, Stor_Tuo2, Stor_Stn2 ,Stor_USJ2)

all_storage_monthly$Basin <- factor(all_storage_monthly$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_monthly

all_storage_year <- rbind(Stor_Mer3, Stor_Tuo3, Stor_Stn3 ,Stor_USJ3)

all_storage_year$Basin <- factor(all_storage_year$Basin, levels = c("Stanislaus River", "Tuolumne River", "Merced River", "Upper San Joaquin River"))
all_storage_year

```

```{r}
all_storage_monthly$Month <- factor(all_storage_monthly$Month, levels = c("Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))
all_storage_monthly


All_Annual_Stats_Stor <- aggregate(AnnualTotal ~ variable+Basin, all_storage_year, summary)
write.csv(All_Annual_Stats_Stor, "All_Annual_Stats_Storage_Baseline_2009prices_RCP8.5_Report.csv")
```

```{r}
ggplot(all_storage_monthly) + 
  theme_bw(base_size=18, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_boxplot(aes( x = Month, y = MonthlyTotal/1000, fill = variable), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +
  
  labs(fill = "RCP 8.5",
       #title = "Upper San Joaquin River",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~Basin, scales = "free_y")+
  png("AllBasins_storage_10GCMs_RCP85_Baseline_2009prices_Report_March.png", units ="in", width=15, height=10, res = 300)

```

```{r}
#annual aggreagate
ggplot(all_storage_year) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_violin(draw_quantiles = c(.25, .5, .75), aes( x = variable, y = AnnualTotal, fill = variable)) + #plot monthly observed data in greenish blue
  #geom_line(aes(x = node, y = value)) +
  scale_y_continuous(limits = c(0, NA),
                     expand = c(0, NA),
                     labels = comma) +
  #    scale_x_discrete(limits=c("Livneh (Historical)", "HadGEM2-ES", "CanESM2", "MIROC5", "CNRM-CM5"))+
  scale_fill_manual(values = c("#5A5A5A", "#A50026", "#D73027", "#F46D43", "chocolate1", "gold1", "cadetblue2", "deepskyblue2", "dodgerblue2", "#4575B4", "#313695" )) +
  
  labs(fill = "RCP 8.5",
       #title = "Upper San Joaquin River",
       x = element_blank(), 
       y = "Total Storage (mcm/year)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.75,"line"),
        panel.spacing.y = unit(0, "lines"))+
  facet_wrap(~Basin, scales = "free_y")+
  png("AllBasins_annual_storage_10GCMs_RCP85_Baseline_2009prices_Report_March.png", units ="in", width=8, height=5, res = 300)
```

