```{r}
library(gridExtra)
library(readr)
library(dplyr)
library(ggplot2)
```

storage <- reservoir  %>%
  mutate(resource = factor(resource),
         basin = factor(basin))  %>% 
   group_by(resource) %>%
  mutate(NSE = hydroGOF::NSE(Simulated, Observed),
            RMSE = hydroGOF::rmse(Simulated, Observed),
            PBIAS = hydroGOF::pbias(Simulated, Observed)*-1)
 storage

  storage2 <- as.data.frame(storage[1,c(6:8)], row.names = F) %>%
   mutate_if(is.numeric, round, digits = 5)
storage2

storage3<- paste("NSE = ",storage2[1,1],", RMSE = ",storage2[1,2],", PBIAS = ",storage2[1,3],sep="")


```{r}
reservoir <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/results/Output_Flow_mcm.csv") %>%
  filter(basin == "upper_san_joaquin")
reservoir
resources <- "outflow"
title <- "Mean daily IFR per month (cfs)"
```

```{r}
reservoir <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/results/InstreamFlowRequirement_Flow_mcm.csv") %>%
  filter(basin == "stanislaus")
reservoir
resources <- "IFR"
title <- "Mean daily IFR per month (cfs)"
```

```{r}
reservoir <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/results/Hydropower_Energy_Mwh.csv") %>%
  filter(basin == "upper_san_joaquin")
reservoir
resources <- "Hydropower"
title <- "Monthly Generation (MWh)"
```

```{r}
reservoir <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/results/Hydropower_Flow_mcm.csv") %>%
  filter(basin == "stanislaus")
reservoir

resources <- "Hydropower Flow"
title <- "Mean daily flow per month (cfs)"
```

```{r}
reservoir <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/results/Reservoir_Storage_mcm.csv") %>%
  filter(basin == "stanislaus")


resources <- "Storage"
title <- "Mean monthly storage (TAF)"
```

```{r}
series <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19")

series2<- c("20")

for(i in series2) {
tuo <-  read_csv(paste0("C:/Users/gusta/Desktop/Original Stanislaus runoff/tot_runoff_sb",i,"_mcm.csv", sep="")) %>%
  mutate(flw = ifelse(flw < quantile(.$flw, probs = 0.99), flw*1.22, flw))

  
tuo

write_csv(tuo, paste0("C:/Users/gusta/Desktop/Corrected Stanislaus/tot_runoff_sb",i,"_mcm.csv"))
}

```

```{r}
#reservoir <- reservoir %>% filter(resource == "Cherrry Lake")
for (var in unique(reservoir$resource)) {
    dev.new()
  
storage <- reservoir  %>% filter(resource == var) %>%
  mutate(resource = factor(resource),
         basin = factor(basin))  %>% 
   group_by(resource) %>%
  mutate(NSE = hydroGOF::NSE(Simulated, Observed),
            RMSE = hydroGOF::rmse(Simulated, Observed),
            PBIAS = hydroGOF::pbias(Simulated, Observed)*-1)
 storage

  storage2 <- as.data.frame(storage[1,c(6:8)], row.names = F) %>%
   mutate_if(is.numeric, round, digits = 5)
storage2

storage3<- paste("NSE = ",storage2[1,1],", RMSE = ",storage2[1,2],", PBIAS = ",storage2[1,3],sep="")

    ggplot() + geom_line(reservoir %>% filter(resource == var), mapping = aes(x= as.Date(date, format = "%m/%d/%Y"), y=Observed, color = "Observed")) + geom_line(reservoir %>% filter(resource == var), mapping = aes(x= as.Date(date, format = "%m/%d/%Y"), y=Simulated, color = "Simulated")) + scale_y_continuous(limits = c(NA, NA), name = title) + scale_x_date(name = element_blank(), limits = as.Date(c("1980-10-01","2011-09-30")))+
  
labs(caption= storage3) + ggtitle(var)+
  theme(plot.caption=element_text(size=10, hjust=0, margin=margin(12,0,0,0)),
        legend.title = element_blank(), legend.position = c(0.7, -0.12),
        plot.title = element_text(hjust = 0.5))+
    ggsave(paste("Monthly_",resources,"_",var,".png",sep=""), units = "in", width = 8, height = 4, dpi=300) 
    dev.off()
}

```

```{r}
ggplot() + geom_line(reservoir %>% filter(resource == "Bass Lake"), mapping = aes(x= as.Date(date, format = "%m/%d/%Y"), y=Observed, color = "Observed")) + geom_line(reservoir %>% filter(resource == "Bass Lake"), mapping = aes(x= as.Date(date, format = "%m/%d/%Y"), y=Simulated, color = "Simulated")) + scale_y_continuous(limits = c(0,NA), name = "Storage (mcm/month)") + scale_x_date(name = element_blank(), limits = as.Date(c("1980-10-01","2011-09-30")))+

#scale_color_discrete(name = "Y series", labels = c("Y2", "Y1"))
#scale_color_manual(values = c(
#    'Y1' = 'darkblue',
#    'Y2' = 'red')) +
#  labs(color = 'Y series')
labs(caption= storage3) +
  theme(plot.caption=element_text(size=10, hjust=0, margin=margin(12,0,0,0)),
        legend.title = element_blank(), legend.position = c(0.7, -0.11))+   ggsave(paste("Monthly_Storage_",var,".png",sep=""), units = "in", width = 8, height = 4, dpi=300) 
  #annotation_custom(tableGrob(storage2,theme=ttheme_default(base_size = 9)), xmin = 1, ymin = -25) + coord_cartesian(clip = 'off')+ theme(plot.margin=unit(c(0,0,0.7,0),"in")) + theme(legend.title = element_blank(), legend.position = c(0.2, -0.14)) + ggsave(paste("Monthly_Storage_",var,".png",sep=""), units = "in", width = 8, height = 4, dpi=300)
```

for (var in unique(mydata$Variety)) {
    dev.new()
    print( ggplot(mydata[mydata$Variety==var,], aes(Var1, Var2)) + geom_point() )
}