---
title: "Storage"
author: "Gustavo Facincani Dourado"
date: "6/9/2020"
output: html_document
---

```{r}
library(tidyverse, quietly = TRUE)
library(readr, quietly = TRUE)
library(extrafont)
library(ggplot2, quietly = TRUE)
library(ggthemes, quietly = TRUE)
library(stringr, quietly = TRUE)
library(tidyr)
library(grid)
library(grDevices)
library(ggpubr)
library(scales)
library(reshape)
library(ggpmisc)
library(gridExtra)
library(cder)
library(lubridate)

```

```{r}
#Read storage data for Merced
SimStorage_Mer <- read_csv("C:/Users/gusta/Desktop/PhD/CERCWET/Hydropower/Merced/Reservoir_Storage_mcm.csv")[,-c(2)]
#Sim_Storage_Mer <- melt(as.data.frame(Storage_Mer), id = "Date")%>%
#  rename(c(variable = "Lake", 
#           value = "Storage")) %>%
#  filter(between(Date, as.Date("1980-10-01"), as.Date("2012-09-30")))

#SimStorage_Mer[c(1:11321), 2] <- NA

SimStorage_Mer

ObsStorage_Mer <- read.csv("C:/Users/gusta/Desktop/PhD/CERCWET/Hydropower/Merced/Observed/storage_mcm.csv")[,-c(2)]  %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y")) %>%
  filter(between(Date, as.Date("1980-10-01"), as.Date("2012-09-30"))) %>%
  dplyr::rename(#`Lake McSwain` = USGS.11270600.MCSWAIN.RES.NR.SNELLING.CA, 
                `Lake McClure` = USGS.11269500.LK.MCCLURE.A.EXCHEQUER.CA) 

ObsStorage_Mer



```

```{r}
ObsStorage_Mer2 <- melt(ObsStorage_Mer, id = "Date") %>%
  dplyr::rename("Obs_Storage(mcm)" = value)
ObsStorage_Mer2

SimStorage_Mer2 <- melt(SimStorage_Mer, id = "Date") %>%
  dplyr::rename("Sim_Storage(mcm)" = value)
SimStorage_Mer2

Mer_Storage <- cbind(SimStorage_Mer2, ObsStorage_Mer2[3])%>%
  dplyr::rename("Reservoir" = variable)

Mer_Storage<-Mer_Storage %>%
  mutate(Month = factor(format(as.Date(Date, format = "%Y/%m/%d"), "%B")))

McSwain <- Mer_Storage %>%
  filter(between(Date, as.Date("2011-10-01"), as.Date("2012-09-30")))
McSwain

```

```{r}
calc_pbias <- function(df) {
  100*(sum(df[["Sim_Storage(mcm)"]] - df[["Obs_Storage(mcm)"]])/sum((df[["Obs_Storage(mcm)"]]), na.rm =TRUE))
}

calc_rsr <- function(df) {
  sqrt( mean( (df[["Sim_Storage(mcm)"]] - df[["Obs_Storage(mcm)"]])^2, na.rm = TRUE))/sd(df[["Obs_Storage(mcm)"]])
}

calc_nse <- function(df) {
  1 - sum((df[["Obs_Storage(mcm)"]] - df[["Sim_Storage(mcm)"]])^2)/sum((df[["Obs_Storage(mcm)"]] - mean(df[["Obs_Storage(mcm)"]]))^2)
}

#Using hydroGOF
calc_pbias2 <- function(df) { require(hydroGOF)
  pbias(df[["Sim_Storage(mcm)"]], df[["Obs_Storage(mcm)"]])
}

calc_rsr2 <- function(df) { require(hydroGOF)
  rsr(df[["Sim_Storage(mcm)"]], df[["Obs_Storage(mcm)"]])
}

calc_nse2 <- function(df) { require(hydroGOF)
  NSE(df[["Sim_Storage(mcm)"]], df[["Obs_Storage(mcm)"]])
}
```

```{r}
Mer_Storage <- Mer_Storage %>%
  group_by(Month) %>%
  nest() %>%
  mutate(pbias_monthly = map(data, calc_pbias),
         rsr_monthly = map(data, calc_rsr),
         nse_monthly = map(data, calc_nse),
         pbias_monthly2 = map(data, calc_pbias2),
         rsr_monthly2 = map(data, calc_rsr2),
         nse_monthly2 = map(data, calc_nse2)) %>%
  unnest(cols = c(data, pbias_monthly, rsr_monthly, nse_monthly,
                  pbias_monthly2, rsr_monthly2, nse_monthly2))
Mer_Storage
```
```{r}
test_table.mer <- Mer_Storage %>%
  group_by(Month) %>%
  dplyr::summarize(pbias = mean(pbias_monthly),
            nse = mean(nse_monthly),
            rsr = mean(rsr_monthly))
test_table.mer

write_csv(test_table.mer, "Mer_tests_storage.csv", append=FALSE, col_names=TRUE)
```

```{r}
require(hydroGOF)

rsr(SimStorage_Mer$`Lake McClure`, ObsStorage_Mer$`Lake McClure`, na.rm = TRUE)
pbias(SimStorage_Mer$`Lake McClure`, ObsStorage_Mer$`Lake McClure`, na.rm = TRUE)
NSE(SimStorage_Mer$`Lake McClure`, ObsStorage_Mer$`Lake McClure`, na.rm = TRUE)

McClure <- model.assess(SimStorage_Mer$`Lake McClure`, ObsStorage_Mer$`Lake McClure`)

```

```{r}
SimLakeMS <- SimStorage_Mer %>%
  filter(between(Date, as.Date("2011-10-01"), as.Date("2012-09-30")))
ObsLakeMS <- ObsStorage_Mer %>%
  filter(between(Date, as.Date("2011-10-01"), as.Date("2012-09-30")))

SimLakeMS1 <- SimLakeMS$`Lake McSwain`
ObsLakeMS1 <- ObsLakeMS$`Lake McSwain`

rsr(SimLakeMS1, ObsLakeMS1, na.rm = TRUE)
pbias(SimLakeMS1, ObsLakeMS1, na.rm = TRUE)
NSE(SimLakeMS1, ObsLakeMS1, na.rm = TRUE)

McSwain <- model.assess(SimLakeMS1, ObsLakeMS1)

```


```{r}

library(facetscales)
scales_x <- list(
  `Lake McClure` = scale_x_date(limits = c(as.Date("1980-10-01"), as.Date("2012-10-01")), date_breaks = "5 years"),
  `Lake McSwain` = scale_x_date(limits = c(as.Date("2011-10-01"), as.Date("2012-10-01")), date_breaks = "1 year"))
                                
scales_y <- list(
  `Lake McClure` = scale_y_continuous(limits = c(0, 1260), breaks = seq(0, 1260, 1250)),
  `Lake McSwain` = scale_y_continuous(limits = c(0, 12), breaks = seq(0, 12, 3))
  )
```

```{r}
note_mer <- data.frame(x = c(#as.Date("2000-10-10"), 
  as.Date("2000-10-10")),
                   y = #c(3
                      200, #adding where to add text 
                   label = c(#paste(McSwain), 
                     paste(McClure)),
                   Reservoir = c(#"Lake McSwain", 
                     "Lake McClure"))
```

```{r}
McSwain %>%
  filter(Reservoir == "Lake McSwain") %>%
ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
  geom_line(aes(x = Date, y = `Sim_Storage(mcm)`), colour = "#56B4E9") +
  geom_line(aes(x = Date, y = `ObsStorage_Mer2[, 3]`), colour = "#E69F00") +
   scale_y_continuous(limits = c(0, 12),
                      expand = c(0, 0)) +
     scale_x_date(date_labels = "%b/%Y",
                  date_breaks = "3 months")+
                  #breaks = as.Date("1980-10-01") + #as.Date("1990-10-01")#,                             as.Date("2000-10-01"), as.Date("2010-10-01")),
   scale_color_identity(name = element_blank(),
                         breaks = c("#56B4E9", "#E69F00"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Lake McSwain",
    x = element_blank(), 
       y = "Storage (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))
```


```{r}
Mer_Storage %>%
  filter(Reservoir == "Lake McClure") %>%
ggplot() + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
   geom_line(aes(x = Date, y = `ObsStorage_Mer2[, 3]`, colour = "#56B4E9")) +
  geom_line(aes(x = Date, y = `Sim_Storage(mcm)`, colour = "#E69F00")) +
   scale_y_continuous(limits = c(0, NA),
                      expand = c(0, 0)) +
     scale_x_date(date_labels = "%b/%Y",
                  date_breaks = "5 years",
                  breaks = as.Date(c("1980-10-01", "1990-10-01", "2000-10-01", "2010-10-01"))) +
   scale_color_identity(name = element_blank(),
                         breaks = c("#56B4E9", "#E69F00"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River",
       subtitle = "Lake McClure",
    x = element_blank(), 
       y = "Storage (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  
    geom_text(note_mer, #adding where to add text 
              mapping = aes(x=x, y=y, label = label), size=3.2, family= "Times New Roman") +
  
#  facet_wrap(~ Reservoir, ncol=1, scales = "free")

png("mer_storage_timeseries.png", units ="in", width=8, height=2, res = 300)

```





```{r}

  ggplot(Mer_Storage) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
   geom_line(aes(x = Date, y = `Obs_Storage(mcm)`), colour = "#56B4E9") +
  geom_line(aes(x = Date, y = `Sim_Storage(mcm)`), colour = "#E69F00") +
   scale_y_continuous(limits = c(0, NA),
                      expand = c(0, 0)) +
     scale_x_date(date_labels = "%b/%Y",
                  date_breaks = "5 years",
                  breaks = as.Date("1980-10-01")) + #as.Date("1990-10-01")#,                             as.Date("2000-10-01"), as.Date("2010-10-01")),
   scale_color_identity(name = element_blank(),
                         breaks = c("#56B4E9", "#E69F00"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River",
    x = element_blank(), 
       y = "Storage (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  
    geom_text(note_mer, #adding where to add text 
              mapping = aes(x=x, y=y, label = label), size=3, family= "Times New Roman") + 
  
  facet_wrap(~ Reservoir, ncol=1, scales = "free")

```
+
#plot monthly observed data in orange
    scale_y_continuous(expand = c(0, 0))+
     scale_x_date(date_breaks = "6 months", 
                  date_labels = "%b/%Y",
              #   limits = as.Date(c('1985-01-01','2000-12-31')),
                  expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_identity(name = element_blank(),
                      labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Merced River", #title
       x = element_blank(), 
       y = "Monthly full natural Flow (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) #center the title





```{r}
#Read storage data for Tuolumne

SimStorage_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/results/baseline/tuolumne/historical/Livneh/Reservoir_Storage_mcm.csv") %>%
#Sim_Storage_Mer <- melt(as.data.frame(Storage_Mer), id = "Date")%>%
#  rename(c(variable = "Lake", 
#           value = "Storage")) %>%
  filter(between(Date, as.Date("1980-10-01"), as.Date("2012-09-30")))

SimStorage_Tuo

ObsStorage_Tuo <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/Tuolumne River/gauges/storage_mcm.csv")  %>%
  filter(between(Date, as.Date("1980-10-01"), as.Date("2012-09-30"))) %>%
  dplyr::rename("Hetch Hetchy Reservoir" = "USGS 11275500 HETCH HETCHY RES A HETCH HETCHY CA", `Lake Eleanor` = `USGS 11277500 LK ELEANOR NR HETCH HETCHY CA`, `Cherry Lake` = `USGS 11277200 CHERRY LK NR HETCH HETCHY CA`, `Don Pedro Reservoir` = `USGS 11287500 DON PEDRO RES NR LA GRANGE CA`)
#  dplyr::rename(`Lake McSwain` = USGS.11270600.MCSWAIN.RES.NR.SNELLING.CA, `Lake McClure` = USGS.11269500.LK.MCCLURE.A.EXCHEQUER.CA) 
ObsStorage_Tuo <- ObsStorage_Tuo[, c(1,3,2,5,4)]
ObsStorage_Tuo

```

```{r}
#Lake Eleanor
RSR.E <-rsr(SimStorage_Tuo$`Lake Eleanor`, ObsStorage_Tuo$`Lake Eleanor`, na.rm = TRUE)
PBIAS.E <- pbias(SimStorage_Tuo$`Lake Eleanor`, ObsStorage_Tuo$`Lake Eleanor`, na.rm = TRUE)
NSE.E <- NSE(SimStorage_Tuo$`Lake Eleanor`, ObsStorage_Tuo$`Lake Eleanor`, na.rm = TRUE)

#Eleanor <- model.assess(SimStorage_Tuo$`Lake Eleanor`, ObsStorage_Tuo$`Lake Eleanor`)
#Eleanor #My function didn't work for Eleanor, so let's use HydroGOF's

Eleanor <- print(paste0("RSR = ", sprintf("%.3f", round(RSR.E, digits=3)), "    PBIAS = ", sprintf("%.3f",round(PBIAS.E, digits=3)),"    NSE = ", sprintf("%.3f",round(NSE.E, digits=3))))  


#Hetch Hetchy
rsr(SimStorage_Tuo$`Hetch Hetchy Reservoir`, ObsStorage_Tuo$`Hetch Hetchy Reservoir`, na.rm = TRUE)
pbias(SimStorage_Tuo$`Hetch Hetchy Reservoir`, ObsStorage_Tuo$`Hetch Hetchy Reservoir`, na.rm = TRUE)
NSE(SimStorage_Tuo$`Hetch Hetchy Reservoir`, ObsStorage_Tuo$`Hetch Hetchy Reservoir`, na.rm = TRUE)

Hetchy <- model.assess(SimStorage_Tuo$`Hetch Hetchy Reservoir`, ObsStorage_Tuo$`Hetch Hetchy Reservoir`)
Hetchy

#Don Pedro

rsr(SimStorage_Tuo$`Don Pedro Reservoir`, ObsStorage_Tuo$`Don Pedro Reservoir`, na.rm = TRUE)
pbias(SimStorage_Tuo$`Don Pedro Reservoir`, ObsStorage_Tuo$`Don Pedro Reservoir`, na.rm = TRUE)
NSE(SimStorage_Tuo$`Don Pedro Reservoir`, ObsStorage_Tuo$`Don Pedro Reservoir`, na.rm = TRUE)

Pedro <- model.assess(SimStorage_Tuo$`Don Pedro Reservoir`, ObsStorage_Tuo$`Don Pedro Reservoir`)
Pedro

#Cherry Lake

rsr(SimStorage_Tuo$`Cherry Lake`, ObsStorage_Tuo$`Cherry Lake`, na.rm = TRUE)
pbias(SimStorage_Tuo$`Cherry Lake`, ObsStorage_Tuo$`Cherry Lake`, na.rm = TRUE)
NSE(SimStorage_Tuo$`Cherry Lake`, ObsStorage_Tuo$`Cherry Lake`, na.rm = TRUE)

Cherry <- model.assess(SimStorage_Tuo$`Cherry Lake`, ObsStorage_Tuo$`Cherry Lake`)
Cherry
```

```{r}
ObsStorage_Tuo2 <- melt(ObsStorage_Tuo, id = "Date") %>%
  dplyr::rename("Obs_Storage(mcm)" = value)
ObsStorage_Tuo2

SimStorage_Tuo2 <- melt(SimStorage_Tuo, id = "Date") %>%
  dplyr::rename("Sim_Storage(mcm)" = value)
SimStorage_Tuo2

Tuo_Storage <- cbind(SimStorage_Tuo2, ObsStorage_Tuo2[3])%>%
  dplyr::rename("Reservoir" = variable)

Tuo_Storage <- Tuo_Storage %>%
  mutate(Month = factor(format(as.Date(Date, format = "%Y/%m/%d"), "%B")))
Tuo_Storage

```

```{r}
Tuo_Storage <- Tuo_Storage %>%
  group_by(Reservoir, Month) %>%
  nest() %>%
  mutate(pbias_monthly = map(data, calc_pbias),
         rsr_monthly = map(data, calc_rsr),
         nse_monthly = map(data, calc_nse),
         pbias_monthly2 = map(data, calc_pbias2),
         rsr_monthly2 = map(data, calc_rsr2),
         nse_monthly2 = map(data, calc_nse2)) %>%
  unnest(cols = c(data, pbias_monthly, rsr_monthly, nse_monthly,
                  pbias_monthly2, rsr_monthly2, nse_monthly2))
Tuo_Storage

```

```{r}
test_table.tuo <- Tuo_Storage %>%
  mutate(Month = factor(month.name[Month], levels = month.name)) %>% 
   arrange(Month) %>%
  group_by(Reservoir, Month) %>%
  dplyr::summarize(pbias = mean(pbias_monthly),
                   pbias2 = mean(pbias_monthly2),
            nse = mean(nse_monthly2),
            rsr = mean(rsr_monthly2))
test_table.tuo

write_csv(test_table.tuo, "Tuo_tests_storage2.csv", append=FALSE, col_names=TRUE)
```

```{r}

Tuo_Storage <- Tuo_Storage %>%
  mutate(Month = factor(format(as.Date(Date, format = "%Y/%m/%d"), "%B"))) %>%
  group_by(Reservoir, Month) %>%
  nest() %>%
  mutate(pbias_monthly = map(data, calc_pbias),
         rsr_monthly = map(data, calc_rsr),
         nse_monthly = map(data, calc_nse)) %>%
  unnest(cols = c(data, pbias_monthly, rsr_monthly, nse_monthly))
Tuo_Storage

test_table.tuo <- Tuo_Storage %>%
  group_by(Reservoir, Month) %>%
  dplyr::summarize(pbias = mean(pbias_monthly),
            nse = mean(nse_monthly),
            rsr = mean(rsr_monthly))
test_table.tuo

```

```{r}
note_tuo <- data.frame(x = as.Date(c("2006-08-01", "2006-08-01", "2006-08-01", "2006-08-01")),
                   y = c(5, 60,300, 50), #adding where to add text 
                   label = c(paste(Eleanor), paste(Hetchy), paste(Pedro), paste(Cherry)),
                   Reservoir = c("Lake Eleanor", "Hetch Hetchy Reservoir", 
                                 "Don Pedro Reservoir", "Cherry Lake"))

```

```{r}
ggplot(Tuo_Storage) + 
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
   geom_line(aes(x = Date, y = `ObsStorage_Tuo2[, 3]`, colour = "#56B4E9")) +
  geom_line(aes(x = Date, y = `Sim_Storage(mcm)`, colour = "#E69F00")) +
   scale_y_continuous(limits = c(0, NA),
                      expand = c(0, 0)) +
     scale_x_date(expand = c(0, 0),
                  date_labels = "%b/%Y",
                 breaks = as.Date(c("1980-10-01", "1990-10-01", "2000-10-01", "2010-10-01"))) +
   scale_color_identity(name = element_blank(),
                         breaks = c("#56B4E9", "#E69F00"), #select the color
                          labels = c("Observed (CDEC)","Simulated (Livneh)"), #select the variables
                          guide = "legend")+
  labs(title = "Tuolumne River",
    x = element_blank(), 
       y = "Storage (mcm)") + #name of x axis
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  
    geom_text(note_tuo, #adding where to add text 
             mapping= aes(x=x, y=y, label = label), size=3.2, family= "Times New Roman") +
  
  facet_wrap(~ Reservoir, ncol=1, scales = "free_y") +
  
png("tuo_storage_timeseries.png", units ="in", width=8, height=5, res = 300)

```

```{r}

```

```{r}

```

```{r}

```

```{r}
#Read storage data for Upper San Joaquin

SimStorage_USJ <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/results/baseline/upper_san_joaquin/historical/Livneh/Reservoir_Storage_mcm.csv")
#Sim_Storage_Mer <- melt(as.data.frame(Storage_Mer), id = "Date")%>%
#  rename(c(variable = "Lake", 
#           value = "Storage")) %>%

SimStorage_USJ

ObsStorage_USJ <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/Upper San Joaquin River/gauges/storage_mcm.csv") %>%
  mutate(Date = as.Date(Date, format = "%Y-%m-%d")) %>%
  filter(between(Date, as.Date("1982-10-01"), as.Date("1985-06-30")))# %>%
#  dplyr::rename("Hetch Hetchy Reservoir" = "USGS 11275500 HETCH HETCHY RES A HETCH HETCHY CA", `Lake Eleanor` = `USGS 11277500 LK ELEANOR NR HETCH HETCHY CA`, `Cherry Lake` = `USGS 11277200 CHERRY LK NR HETCH HETCHY CA`, `Don Pedro Reservoir` = `USGS 11287500 DON PEDRO RES NR LA GRANGE CA`)
#  dplyr::rename(`Lake McSwain` = USGS.11270600.MCSWAIN.RES.NR.SNELLING.CA, `Lake McClure` = USGS.11269500.LK.MCCLURE.A.EXCHEQUER.CA) 
#ObsStorage_Tuo <- ObsStorage_Tuo[, c(1,3,2,5,4)]
ObsStorage_USJ
ObsStorage_USJ <- ObsStorage_USJ[, c(1, 10, 9, 8, 2, 6, 7, 4, 5, 3)]

colnames(ObsStorage_USJ) <- c("Date", "Shaver Lake", "Redinger Lake", "Millerton Lake", "Mammoth Pool Reservoir", "Lake Thomas A Edison", "Kerckhoff Lake", "Huntington Lake", "Florence Lake","Bass Lake")
ObsStorage_USJ

```

```{r}
#Shaver Lake
rsr(SimStorage_USJ$`Shaver Lake`, ObsStorage_USJ$`Shaver Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Shaver Lake`, ObsStorage_USJ$`Shaver Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Shaver Lake`, ObsStorage_USJ$`Shaver Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Shaver Lake`, ObsStorage_USJ$`Shaver Lake`)

#Redinger Lake
rsr(SimStorage_USJ$`Redinger Lake`, ObsStorage_USJ$`Redinger Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Redinger Lake`, ObsStorage_USJ$`Redinger Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Redinger Lake`, ObsStorage_USJ$`Redinger Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Redinger Lake`, ObsStorage_USJ$`Redinger Lake`)

#Millerton Lake
rsr(SimStorage_USJ$`Millerton Lake`, ObsStorage_USJ$`Millerton Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Millerton Lake`, ObsStorage_USJ$`Millerton Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Millerton Lake`, ObsStorage_USJ$`Millerton Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Millerton Lake`, ObsStorage_USJ$`Millerton Lake`)

#Mammoth Pool Reservoir
rsr(SimStorage_USJ$`Mammoth Pool Reservoir`, ObsStorage_USJ$`Mammoth Pool Reservoir`, na.rm = TRUE)
pbias(SimStorage_USJ$`Mammoth Pool Reservoir`, ObsStorage_USJ$`Mammoth Pool Reservoir`, na.rm = TRUE)
NSE(SimStorage_USJ$`Mammoth Pool Reservoir`, ObsStorage_USJ$`Mammoth Pool Reservoir`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Mammoth Pool Reservoir`, ObsStorage_USJ$`Mammoth Pool Reservoir`)
```

```{r}
#Lake Thomas A Edison
rsr(SimStorage_USJ$`Lake Thomas A Edison`, ObsStorage_USJ$`Lake Thomas A Edison`, na.rm = TRUE)
pbias(SimStorage_USJ$`Lake Thomas A Edison`, ObsStorage_USJ$`Lake Thomas A Edison`, na.rm = TRUE)
NSE(SimStorage_USJ$`Lake Thomas A Edison`, ObsStorage_USJ$`Lake Thomas A Edison`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Lake Thomas A Edison`, ObsStorage_USJ$`Lake Thomas A Edison`)

#Kerckhoff Lake
#rsr(SimStorage_USJ$`Kerckhoff Lake`, ObsStorage_USJ$`Kerckhoff Lake`, na.rm = TRUE)
#pbias(SimStorage_USJ$`Kerckhoff Lake`, ObsStorage_USJ$`Kerckhoff Lake`, na.rm = TRUE)
#NSE(SimStorage_USJ$`Kerckhoff Lake`, ObsStorage_USJ$`Kerckhoff Lake`, na.rm = TRUE)

#model.assess(SimStorage_USJ$`Kerckhoff Lake`, ObsStorage_USJ$`Kerckhoff Lake`)

#Huntington Lake
rsr(SimStorage_USJ$`Huntington Lake`, ObsStorage_USJ$`Huntington Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Huntington Lake`, ObsStorage_USJ$`Huntington Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Huntington Lake`, ObsStorage_USJ$`Huntington Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Huntington Lake`, ObsStorage_USJ$`Huntington Lake`)

#Florence Lake
rsr(SimStorage_USJ$`Florence Lake`, ObsStorage_USJ$`Florence Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Florence Lake`, ObsStorage_USJ$`Florence Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Florence Lake`, ObsStorage_USJ$`Florence Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Florence Lake`, ObsStorage_USJ$`Florence Lake`)

#Bass Lake
rsr(SimStorage_USJ$`Bass Lake`, ObsStorage_USJ$`Bass Lake`, na.rm = TRUE)
pbias(SimStorage_USJ$`Bass Lake`, ObsStorage_USJ$`Bass Lake`, na.rm = TRUE)
NSE(SimStorage_USJ$`Bass Lake`, ObsStorage_USJ$`Bass Lake`, na.rm = TRUE)

model.assess(SimStorage_USJ$`Bass Lake`, ObsStorage_USJ$`Bass Lake`)
```


```{r}
ObsStorage_USJ2 <- melt(ObsStorage_USJ, id = "Date") %>%
  dplyr::rename("Obs_Storage(mcm)" = value)
ObsStorage_USJ2

SimStorage_USJ2 <- melt(SimStorage_USJ, id = "Date") %>%
  dplyr::rename("Sim_Storage(mcm)" = value)
SimStorage_USJ2

USJ_Storage <- cbind(SimStorage_USJ2, ObsStorage_USJ2[,3])%>%
  dplyr::rename("Reservoir" = variable)

USJ_Storage
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

