---
title: "NetCDF_to_CSV"
author: "Gustavo Facincani Dourado"
date: "8/7/2020"
output: html_document
---

```{r}
library(ncdf4)
library(raster)
library(rgdal)
library(maptools)

loca_nc <- nc_open("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/baseflow.2006.v0.CA_NV.nc")
loca_globals <- ncatt_get(loca_nc, varid = 0)
names(loca_globals) # Available global attributes
names(loca_nc) # top level names of the ncdf4 object
names(loca_nc$dim) # Dimensions of the ncdf4 object
loca_nc$nvars # How many variables are available from the ncdf4 object

```

```{r}


for (i in 2006:2100){
  #read flow data in the netCDF data 
    dpath <- paste("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.",as.character(j),".v0.CA_NV.nc", sep="")
  data=brick(dpath)}
data  

extent(data)
```

```{r}
setwd("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/Shapefiles/")
Mer_shp <- shapefile("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/Shapefiles/Mer.shp")

#Check if projections of the shapefile and NetCDF files are the same

crs(Mer_shp)
crs(data) 
plot(Mer_shp)
```

```{r}
library(RNetCDF)
nc.file <- open.nc(paste0("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.2007.v0.CA_NV.nc") ) # Monthly mean absolute temperature
file.inq.nc(nc.file) 
#to = insol::JDymd(year = 1950, month = 1, day = 1)
dat <- read.nc(nc.file)
str(dat)  

lon <- var.get.nc(ncfile = nc.file, variable = 'Lon')
lat <- rev(var.get.nc(ncfile = nc.file, variable = 'Lat')) # Plotting requires incremented values
tmp <- var.get.nc(nc.file, variable = 'runoff_plus_baseflow')
```

```{r}
library(sf)
file<- nc_open("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.2007.v0.CA_NV.nc")

variable <-ncvar_get(file,"runoff_plus_baseflow")
lat <-ncvar_get(file,"Lat")
long <-ncvar_get(file,"Lon")

fillvalue<-ncatt_get(file, "runoff_plus_baseflow", "_FillValue")
variable[variable==fillvalue$value]<-NA

extract <- raster::extract
{r}
library(tidyverse)
library(ncdf4)
library(raster)
library(sf)
#library(tmap)
library(stringr)
library(tidyverse)
```

```{r}
file<- brick("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.2007.v0.CA_NV.nc")
#extent(file)

# number of layers
names(file)
nl <- nlayers(file)

# begin of loop
for (i in 1:nl){

# Extract the raster file of layers
r <- raster(file, layer = i)

# Extract relevant information from shapefile
Mer <-Mer_shp["SUBWAT"]

# Ensure command extract is from raster package
extract <- raster::extract
# Extract the mean value of cells within AMC polygon
# Alternative: look to "mask" function ?mask
masked_file<-extract(r, 
                    Mer, 
                    fun = mean,
                    na.rm=TRUE, 
                    df=F, 
                    small=T, 
                    sp=T,  
                    weights=TRUE, 
                    normalizedweights=TRUE)

# Generate variable depicting the date
# Extract the information about the time
date <- r@z[[1]]
date
date <- as.Date(date, origin = "1800-01-01")

# Compile the codes for AMC and time variable in one dataframe
df <- data.frame(date, masked_file)

# rename last variable that represents the extracted values
colnames(df)[4] <- "Total Runoff"

# save data as .csv
setwd("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/")

write.csv(df, 
         paste0("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/", date , "_amc_rainfall.csv"), 
         row.names = TRUE,
         ) # overwrites

# print
print(i)
print(date)
# end of loop
}
```
nc_close(file) 

variable.slice <- variable[, , 1] 

raster_file <- raster(t(variable.slice), xmn=min(lon), xmx=max(lon), ymn=min(lat), ymx=max(lat), crs=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0"))

```

```

```{r}
nc = nc_open("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/Shapefiles/new.nc")       #open ncdf and read variables

#to = insol::JDymd(year = 1950, month = 1, day = 1)
dat <- read.nc(nc)
str(dat)  

```

```{r}
lon = ncvar_get(nc,"Lon")              # Lon lat and time
lat = ncvar_get(nc,"Lat")
time = ncvar_get(nc, "Time")
dname = "runoff_plus_baseflow"  #variable
variabel = ncvar_get(nc,dname)
lonlat = as.matrix(expand.grid(lon,lat))
var_vektor = as.vector(variabel)
datanya = data.frame(cbind(lonlat,var_vektor))
names(datanya) = c("lon","lat",paste(dname,as.character(), sep="_"))
head(na.omit(datanya))
csvpath = "C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/"  #directory to save file
csvname = "hasil_1v2.csv" #file_output
csvfile = paste(csvpath, csvname, sep="")
write.table(na.omit(datanya),csvfile, row.names=FALSE, sep=",")
```

```{r}
writeRaster(output, "new.nc", overwrite=TRUE, format="CDF", varname="tmx", varunit="degrees celcius", longname="maximum temperature", xname="lon", yname="lat", zunit="numeric") # save output in netcdf format (nw.nc)
```

```{r}
Mer1 <- brick("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.2007.v0.CA_NV.nc") 

Mer_mask1 <- mask(Mer1, Mer_shp)

writeRaster(Mer_mask1, "new.nc", overwrite=TRUE, format="CDF")
```

```{r}
library(survival)
library(RNetCDF)
library(ncdf)
library(date)

#setwd("c:/users/mmiller21/Netcdf")

my.data <- open.nc("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/rcp45/tot_runoff.2007.v0.CA_NV.nc")

my.time <- var.get.nc(my.data, "Time")

n.latitudes  <- length(var.get.nc(my.data, "Lat"))
n.longitudes <- length(var.get.nc(my.data, "Lon"))

n.dates <- trunc(length(my.time))
n.dates

my.object <- var.get.nc(my.data, "runoff_plus_baseflow")

my.array  <- array(my.object, dim = c(n.latitudes, n.longitudes, n.dates))
my.array[,,1:5]
my.vector <- my.array[1, 2, 1:n.dates]  # first latitude, second longitude
head(my.vector)

baseDate <- att.get.nc(my.data, "NC_GLOBAL", "base_date")
bdInt    <- as.integer(baseDate[1])

year     <- date.mdy(seq(mdy.date(1, 1, bdInt), by = 1,
                     length.out = length(my.vector)))$year 

head(year)
```

```{r}
#Mer_data1 <- as.data.frame(Mer_mask1, xy=FALSE)
#Mer_data1 = Mer_data1[complete.cases(Mer_data1),]
#Mer_data1

lon = ncvar_get(Mer_mask1,"Lon")              # Lon lat and time
lat = ncvar_get(Mer_mask1,"Lat")
time = ncvar_get(Mer_mask1, "Time")
dname = "runoff_plus_baseflow"  #variable
variabel = ncvar_get(Mer_mask1,dname)
lonlat = as.matrix(expand.grid(lon,lat))
var_vektor = as.vector(variabel)
datanya = data.frame(cbind(lonlat,var_vektor))
names(datanya) = c("lon","lat",paste(dname,as.character(), sep="_"))
head(na.omit(datanya))
csvpath = "C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/ACCESS1-0/"  #directory to save file
csvname = "hasil_1v22.csv" #file_output
csvfile = paste(csvpath, csvname, sep="")
write.table(na.omit(datanya),csvfile, row.names=FALSE, sep=",")
```

```{r}
class(Mer_mask1)
```

  n<-nbands(data) #give me the number of bands in netCDF data 
  
  date.start<- paste(as.character(j),"-01-01",sep="")
  date.end<- paste(as.character(j),"-12-31",sep="")
  d<- seq(as.Date(date.start), as.Date(date.end),1)
  #convert netCDF data from mm to m
  #raster_m3<-calc(data, fun=function(x){x*0.001}) #per cell size mm to m 
  raster_m3 <- data*0.001
  i <- 1
  while (i < 39) {
    
    if (i < 10) {
      filenum <- paste("0", as.character(i), sep="")
    } else {
      filenum <- as.character(i)
    }
    # read file 1
    fpath <- paste("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/Shapefiles/", filenum, ".shp", sep="")
    print (fpath)
    SJN_shape <- readOGR(fpath)
    
    plot(SJN_shape) #check the shapefile by viewing 
    #mask netCDF with shapefile 
    SJN_mask_data<-mask(raster_m3,SJN_shape)}} #for entire historical period this takes ~4 minutes 
```

    # read file 2
    fpath2 <- paste("C:\\Users\\Aditya\\Desktop\\Work\\UC\\OA_USJR\\CatchmentROs\\VIC_Runoffs_R\\SJN_SB\\TIFF\\SJN", filenum, "_NetConR.tif", sep="")
    SJN_area=raster(fpath2)
    
    #create a raster stack replication of area with n layers
    SJN_stack <- stack(replicate(n, SJN_area)) #replicate band 1 into n bands
    
    #mutiply netcdf by SJN_stack (SJNstack has area of each cell so we are getting volume m3/day)
    runoff_vol<-SJN_mask_data*SJN_stack/86400 #Divided by 86400 to convert to m3/s; for the entire historical period this takes ~ minutes
    #s4=as.matrix(subset(runoff_vol,200))
    
    x.stats<-data.frame(x.sum=cellStats(runoff_vol,"sum",na.rm=TRUE))
    
    SB<-gsub(" ", "",
             tools::file_path_sans_ext(
               basename((fpath))))
    SJN<-substr(SB, start = 1, stop = 5)
    x.stats$Subbasin<-SJN
    
    ##ADD COLUMN of Julian Date, Month, Year, and WY 
    x.stats$dates<-d
    x.stats$month<-month(d)
    x.stats$year<-year(d)
    x.stats$day<-day(d)
    x.stats$WY <- x.stats$year + (x.stats$month %in% 10:12) #this method is called vectorization 
    
    outpath <- paste("C:\\Users\\Aditya\\Desktop\\Work\\UC\\OA_USJR\\CatchmentROs\\VIC_Runoffs_R\\Outputs\\livneh_hist\\SJN", filenum, "livneh_historic_", as.character(j),".csv", sep="")
    write.csv(x.stats, outpath)
    
    i = i+1
  }
  j = j+1
}
```