---
title: "Bias Correction USJ"
author: "Gustavo Facincani Dourado"
date: "9/17/2020"
output: html_document
---


```{r}
library(readr)
library(tidyverse)
library(hyfo)
library(lubridate)
```

```{r}
#Reading Livneh data, that is going to be used for bias correction and filtering them to have objects with the same length of the observed data, to be used as the simulated vs observed
path <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Tuolumne River/hydrology/historical/Livneh/runoff/"


Sub10_Livneh <- read_csv(paste(path,"tot_runoff_sb10_mcm.csv",sep="")) %>%
  rename(Inflow = tot_runoff_sb10)

Sub10_PreBC <- Sub10_Livneh%>%
   filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31")))


Sub22_Livneh <- read_csv(paste(path,"tot_runoff_sb22_mcm.csv",sep="")) %>%
  rename(Inflow = tot_runoff_sb22)
Sub22_PreBC <- Sub22_Livneh %>% #Granite Creek
   filter(between(Date, as.Date("1965-10-01"), as.Date("1986-09-29")))

Sub23_Livneh <- read_csv(paste(path,"tot_runoff_sb23_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb23)
Sub23_PreBC <- Sub23_Livneh%>% #San Joaquin River
    filter(between(Date, as.Date("1951-10-01"), as.Date("1991-09-29")))


Sub31_Livneh <- read_csv(paste(path,"tot_runoff_sb31_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb31) 
Sub31_PreBC <-  Sub31_Livneh %>% #Thomas Edison Lake
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31")))


Sub36_Livneh <- read_csv(paste(path,"tot_runoff_sb36_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb36)
Sub36_PreBC <- Sub36_Livneh %>% #Bear Creek
   filter(between(Date, as.Date("1975-10-01"), as.Date("1986-09-29")))

Sub37_Livneh <- read_csv(paste(path,"tot_runoff_sb37_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb37)
Sub37_PreBC <-  Sub37_Livneh %>% #SF San Joaquin River
  filter(between(Date, as.Date("2009-10-01"), as.Date("2013-12-31")))


Sub38_Livneh <- read_csv(paste(path,"tot_runoff_sb38_mcm.csv",sep=""))%>%
  rename(Inflow = tot_runoff_sb38)
Sub38_PreBC <- Sub38_Livneh %>% #Florence Lake
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29")))


```


```{r}
Reservoir_flow <- read_csv("C:/Users/gusta/Desktop/PhD/Classes/ES207/streamflow_cfs2.csv", col_types = cols(Date = col_date(), .default = col_double()))
Reservoir_flow
Reservoir_flow2 <- readxl::read_excel("C:/Users/gusta/Desktop/PhD/Classes/ES207/streamflow_cfs2_copy.xlsx")
Reservoir_flow2

Reservoir_flow$`Holm PH` <- as.numeric(Reservoir_flow2$`Holm PH`)
Reservoir_flow
```

```{r}
#Read the gauge data for the same period of the data we have for Livneh
USJpath <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Tuolumne River/"

#Subbasins 21, 31 and 38 have Florence Lake, Thomas A. Edison Lake and Mammoth Pool Reservoir respectively
Reservoir_stor <- read_csv(paste0(USJpath, "gauges/storage_mcm.csv", sep = ""), col_types = cols(Date = col_date(), .default = col_double()))#%>% #reading data column as data, others as numeric
#filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31"))) #selecting period of available gauged data
Reservoir_stor

#The other subbasins only streamflow
#Reservoir_flow <- read.csv("C:/Users/gusta/Desktop/PhD/Classes/ES207/streamflow_cfs2.csv", col_types = cols(Date = col_date(), .default = col_double()))#%>% #reading data column as data, others as numeric
#filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31"))) #selecting period of available gauged data
#Reservoir_flow

Reservoir_flow[2:21] <- (Reservoir_flow[2:21]/35.314666)*86400/1000000 #as reservoir data is in million cubic meters (mcm), let's convert cms to mcm
Reservoir_flow
```

```{r}
#Water balance of reservoirs to determine inflows
#Subbasin 38 - Florence
Cherry_outflow <- Reservoir_flow[c(1,5,6,21)] %>% #gauges 11229500 and USGS 11230000, outflow of Florence
  filter(between(Date, as.Date("1996-07-30"), as.Date("2013-12-31")))
Cherry_outflow

Sub38 <- Reservoir_stor[c(1,4)] %>% #selecting gauge with storage data
filter(between(Date, as.Date("1996-07-30"), as.Date("2013-12-31"))) %>%
   mutate(ChangeStorage = `USGS 11277200 CHERRY LK NR HETCH HETCHY CA` - lag(`USGS 11277200 CHERRY LK NR HETCH HETCHY CA`, default = first(`USGS 11277200 CHERRY LK NR HETCH HETCHY CA`)) - Cherry_outflow$`USGS 11277100 LK ELEANOR DIV TO CHERRY LAKE NR HETCH HETCHY CA`,
          #getting daily change in storage
          Outflow = rowSums(Cherry_outflow[3:4]), #sum of USGS 11229500 and USGS 11230000, which correspond to flow below the reservoir and Ward Tunnel intake, respectively 
          Inflow = (ChangeStorage + Outflow)) %>% #ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) #getting inflow, in which inflow = change in storage (storage of the day minus the storage of the previous day + outflow of the day
           select(Date, Inflow)#remove the already used column 
Sub38
```

#Subbasins 31 - Thomas Edison
Thomas_outflow <- Reservoir_flow[c(1,14)] %>%
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31")))

Sub31 <- Reservoir_stor[c(1,6)] %>% #selecting gauge with storage data
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31"))) %>%
   mutate(ChangeStorage = `USGS 11231000 LK THOMAS A. EDISON NR BIG C CA` - lag(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`, default = first(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`)), #getting daily change in storage
          Outflow = Thomas_outflow$`USGS 11231500 MONO C BL LK THOMAS A EDISON CA`, #getting outflow
          Inflow = (ChangeStorage + Outflow)) %>% 
           select(Date, Inflow)#remove the already used column 
Sub31

#Subbasin 21 - Mammoth Pool Reservoir
Mammoth_outflow <- Reservoir_flow[c(1,17,18)] %>%
   filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31")))

Sub21 <- Reservoir_stor[c(1,10)] %>% #selecting gauge below Thomas Edison
    filter(between(Date, as.Date("1980-10-01"), as.Date("2013-12-31"))) %>%
#  replace(is.na(Reservoir_flow$`USGS 11234760 SAN JOAQUIN R AB SHAKEFLAT C NR BIG CREEK CA`), 0) %>%
   mutate(ChangeStorage = `USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA` - lag(`USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA`, default = first(`USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA`)), #getting change in storage
          PH_Flow = Mammoth_outflow$`USGS 11235100 MAMMOTH POOL PP NR BIG CREEK CA`, 
          Below_Reservoir = Mammoth_outflow$`USGS 11234760 SAN JOAQUIN R AB SHAKEFLAT C NR BIG CREEK CA`,
          Sub20 = Sub20_Livneh$tot_runoff_sb20) %>% #getting outflow, summing up the flow below the reservoir, flow to the PH and I'm subtracting the contribution from Subbasin 20, as it is below the reservoir, before the gauge
          mutate(Inflow = rowSums(na.omit(.[3:5])) - Sub20) %>% #here I'm subtracting the contribution of Sub20, which is a small area below the dam, above the USGS gauge, and omitting NAs as we have 2 years of missing data in the record
           select(Date, Inflow) #remove the already used column  
Sub21
```


```{r}
#Subbasin 22
Sub22 <- Reservoir_flow[c(1,3)] %>% #Granite Creek
   filter(between(Date, as.Date("1965-10-01"), as.Date("1986-09-29"))) %>%
  rename(Inflow = 2)
Sub22

#Subbasin 36
Sub23 <- Reservoir_flow[c(1,2)]%>% #San Joaquin River
    filter(between(Date, as.Date("1951-10-01"), as.Date("1991-09-29")))%>%
  rename(Inflow = 2)
Sub23

#Subbasin 36
Sub36 <- Reservoir_flow[c(1,7)]%>% #SF San Joaquin River
   filter(between(Date, as.Date("1975-10-01"), as.Date("1986-09-29")))%>%
  rename(Inflow = 2)
Sub36

#Subbasin 37 
#If we consider these gauges, around 24% of the days will have negative values

#Sub37 <- Reservoir_flow[c(1,5,7)] %>% #SF San Joaquin, with inflow from Florence Lake
#   filter(between(Date, as.Date("1975-10-01"), as.Date("1980-09-29"))) %>%
#  mutate(Inflow = (`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230000 SF SAN JOAQUIN R NR FLORENCE LK CA`)) 
#Sub37

#Considering this slightly shorter record, we only have 4 days with negative flow
Sub37 <- Reservoir_flow[c(1,6,7)] %>% #SF San Joaquin, with inflow from Florence Lake
   filter(between(Date, as.Date("2009-10-01"), as.Date("2013-12-31"))) %>%
  mutate(Inflow = (`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230070 SF SAN JOAQUIN R AB HOOPER C NR FLORENCE LAKE CA`)) %>%
           select(Date, Inflow)#remove the already used column 
Sub37
#PortalPH <- Reservoir_flow[17] #Portal is ignored by now, as "The water delivered to Huntington Lake may also pass through Portal Powerhouse at the exit of the Ward Tunnel depending upon the amount of water being transported. Page 71 https://www.sce.com/sites/default/files/inline-files/p120bc3_initialstatement_and_exhibitsad_and_h.pdf
#PortalPH
```


#Here I tried montlhy bias correction, but daily bias correction seem to produce better results
Florence_USGS <- Florence %>% 
  group_by(year = year(Date), month = month(Date)) %>% 
  summarise(flow = sum(flow)) %>%
  ungroup %>%
  mutate(Date = as.Date(paste(year,'-', month,'-15', sep="")),
         year = NULL,
         month = NULL) %>%
  select(Date, flow)
Florence_USGS

Florence_Livneh <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/hydrology/historical/Livneh/runoff_aggregated/Florence Lake Inflow mcm.csv")
Florence_Livneh

Florence_PreBC_Livneh <- Florence_Livneh%>%
filter(between(date, as.Date("1955-01-01"), as.Date("1991-09-30")))#%>% 
#  group_by(year = year(date), month = month(date)) %>% 
#  summarise(flow = sum(flow)) %>%
#  ungroup %>%
#  mutate(Date = as.Date(paste(year,'-', month,'-15', sep="")),
#         year = NULL,
#         month = NULL) %>%
#  select(Date, flow)
Florence_PreBC_Livneh




#Bias Correction, testing the monthly BC

bc_df <- list()
fin_df <- list()

for (i in (1:12)){

  obs <- filter(Florence_USGS,month(Florence_USGS$Date)== i)
  hind <- filter(Florence_PreBC_Livneh,month(Florence_PreBC_Livneh$Date)== i)

  bF <- getBiasFactor(as.data.frame(hind),as.data.frame(obs),method = "scaling", scaleType = "multi",preci = FALSE, prThreshold = 0, extrapolate = "no")
  bF
  print(paste(i," bias factor is ", bF@biasFactor, sep = ""))
    new_df <- filter(Florence_Livneh,month(as.Date(Florence_Livneh$date, format = "%Y-%m-%d")) ==i)
    bc_df <- applyBiasFactor(new_df,bF)
    if (i==1){
      fin_df <- bc_df
    }
    else {
      fin_df <- bind_rows(fin_df,bc_df)
     
    }
  }

#write_csv(fin_df, "Florence_inflow_BC_monthly.csv")


```{r}
#Bias Correction with daily data

  path <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/USJR/SubCatchment_RO_BC"
BiasCorrection <- function(Observed, Simulated, ToBeCorrected, Subbasin){

  
bc_df <- list()
fin_df <- list()

for (i in (1:366)){

  obs <- filter(Observed,yday(Observed$Date)== i)
  hind <- filter(Simulated,yday(Simulated$Date)== i)

  bF <- getBiasFactor(as.data.frame(hind),as.data.frame(obs),method = "scaling", scaleType = "multi",preci = FALSE, prThreshold = 0, extrapolate = "no")
  bF
  print(paste(i," bias factor is ", bF@biasFactor, sep = ""))
    new_df <- filter(ToBeCorrected,yday(as.Date(ToBeCorrected$Date, format = "%Y-%m-%d")) ==i)
    bc_df <- applyBiasFactor(new_df,bF)
    if (i==1){
      fin_df <- bc_df
    }
    else {
      fin_df <- bind_rows(fin_df,bc_df)
     
    }
  }
fin_df2 <-  arrange(fin_df, Date) #bias corrected Florence Lake inflow
head(fin_df2)
write_csv(fin_df2, paste(path,"/tot_runoff_sb",Subbasin,"_mcm.csv", sep=""))

}
```

```{r}
BiasCorrection(Sub21, Sub21_PreBC, Sub21_Livneh, "21")
BiasCorrection(Sub22, Sub22_PreBC, Sub22_Livneh, "22")
BiasCorrection(Sub23, Sub23_PreBC, Sub23_Livneh, "23")
BiasCorrection(Sub31, Sub31_PreBC, Sub31_Livneh, "31")
BiasCorrection(Sub36, Sub36_PreBC, Sub36_Livneh, "36")
BiasCorrection(Sub37, Sub37_PreBC, Sub37_Livneh, "37")
BiasCorrection(Sub38, Sub38_PreBC, Sub38_Livneh, "38")
```


```{r}
Make_Figures <- function(Observed, Simulated, Subbasin, StartDate, EndDate){

#Observed <- Sub22 
#Simulated<-  Sub22_PreBC
#Subbasin <- "sb22"
#StartDate <- "1965-10-01"
#EndDate <- "1986-09-29"

Pre_BC2 <- Simulated %>% #getting the data pre-bias correction
  mutate(Data = "Pre-Bias Correction (Livneh)") 
Pre_BC2

BC_daily <- read_csv(paste(path_BC,"/Daily_BC/","tot_runoff_",Subbasin,"_mcm.csv", sep="")) %>% #Getting the Bias Corrected data we generated
  mutate(Data = "Post-Bias Correction (Livneh)") %>%
  rename(Inflow = 2) %>%
   filter(between(Date, as.Date(StartDate), as.Date(EndDate)))

BC_daily

Reference <- Observed %>% #getting the observed data from USGS
    mutate(Data = "USGS Reference (Observed)")
Reference

Final <- rbind(Pre_BC2, BC_daily, Reference)
Final
Final$Data <- factor(Final$Data, levels = c("Pre-Bias Correction (Livneh)", "USGS Reference (Observed)","Post-Bias Correction (Livneh)"))

##Line Curve
Final2 <- Final %>%
  mutate(Yearmon = zoo::as.yearmon(Date)) %>%
  group_by(Yearmon, Data) %>%
  summarise(Inflow = sum(Inflow)) %>%
  ungroup() %>%
  mutate(Date = as.Date(Yearmon))

ggplot(Final2,aes(x=Date, y=Inflow, color=Data))+ geom_line()+  scale_x_date(date_labels = "%b-%Y", date_minor_breaks = '6 month')+
ggsave(filename=paste(path,"/",Subbasin,"_line.png",sep=""), units="in",width=6.5,height=3)#,res=360)

##FDC Curve
data.nm <- unique(Final$Data)
Final$FDC <- NA
for (i in (1:length(data.nm))){
  vls <- Final$Inflow[Final$Data==data.nm[i]]
  Fn <- ecdf(vls)
  Final$FDC[Final$Data==data.nm[i]] <- 1-Fn(vls) # exceedance probabilities
}

ggplot(Final, aes(x=FDC, y=Inflow, color=Data)) + geom_line() + geom_point(shape=21, size=0.05, alpha=0.25) + 
        ylab(expression("Q ("*m^3/s*")")) + xlab("Exceedance probability") +
  ggsave(filename=paste(path,"/",Subbasin,"_fdc.png",sep=""), units="in",width=6.5,height=3.5)#,res=360)

## Box&whisker
ggplot(Final, aes(x=Data, y=Inflow)) + geom_boxplot() +
 #       scale_y_log10(limits=c(3e-1,3e3)) +
        ylab(expression("Q ("*m^3/s*")")) + xlab("Data")  +
  ggsave(filename=paste(path,"/",Subbasin,"_box.png",sep=""), units="in",width=6.5,height=4)#,res=360)


## Q-Q plot
ggplot(Final, aes(sample=Inflow, color=Data)) + stat_qq(shape=21, size=0.75)+
  png(filename=paste(path,"/",Subbasin,"_qq.png",sep=""), units="in",width=6.5,height=3,res=360)
}
```

```{r}
Make_Figures(Sub21, Sub21_PreBC, "sb21", "1980-10-01", "2013-12-31")
Make_Figures(Sub22, Sub22_PreBC, "sb22", "1965-10-01" ,"1986-09-29") 
Make_Figures(Sub23, Sub23_PreBC, "sb23", "1951-10-01", "1991-09-29")
Make_Figures(Sub31, Sub31_PreBC, "sb31", "1954-10-12", "2013-12-31")
Make_Figures(Sub36, Sub36_PreBC, "sb36", "1975-10-01", "1986-09-29")
Make_Figures(Sub37, Sub37_PreBC, "sb37", "2009-10-01", "2013-12-31")
Make_Figures(Sub38, Sub38_PreBC, "sb38", "1950-01-01", "1980-09-29")
```