
```{r}
library(readr)
library(tidyverse)
USJpath <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Tuolumne River/gauges/"

#Subbasins 31 and 38
Reservoir_flow <- read_csv(paste0(USJpath, "streamflow_cfs.csv", sep = ""))
Reservoir_flow[2:23] <- Reservoir_flow[2:23]*2446.58/1000000 #converting to mcm/day
Reservoir_flow

Reservoir_stor <- read_csv(paste0(USJpath, "storage_mcm.csv", sep = ""))
Reservoir_stor
```

```{r}
ph1 <- read.csv("C:/Users/gusta/Desktop/PhD/CERCWET/GCMs/SJ_PH1.csv") %>%
  mutate(Date = as.Date(ï..Date, format = "%m/%d/%Y"),
         `USGS.11238600.SAN.JOAQUIN.R.AB.STEVENSON.C.NR.BIG.CREEK.CA` = as.double(`USGS.11238600.SAN.JOAQUIN.R.AB.STEVENSON.C.NR.BIG.CREEK.CA`),
         Month = format(Date, format = "%m"),
         Year= format(Date, format = "%Y")) %>%
  group_by(Year, Month) %>%
  summarize(USGS = mean(`USGS.11238600.SAN.JOAQUIN.R.AB.STEVENSON.C.NR.BIG.CREEK.CA`))
ph1

write_csv(ph1, "ph1.csv")
```


```{r}
siteNo <- c("11292500", "11293710", "11294000", "11292000")
pCode <- "00060"
start.date <- "1950-01-01"
end.date <- "2013-12-31"

USGS <- dataRetrieval::readNWISdv(siteNumbers = siteNo,
                     parameterCd = pCode,
                     startDate = start.date,
                     endDate = end.date)
USGS
```

```{r}
siteInfo <- attr(USGS, "siteInfo")
siteInfo

```

```{r}
library(dplyr)
common_column_names <- intersect(names(USGS), names(siteInfo))
#2. Use this character vector as your by parameters in the merge function.

USGS2 <- merge(USGS, siteInfo, by="site_no", all.dataframe_1=TRUE) %>%
  dplyr::select(Date, site_no, agency_cd.x, station_nm, X_00060_00003) %>%
  mutate(ID = paste(agency_cd.x, site_no, station_nm, sep = " "),
         station_nm = NULL,
         site_no = NULL,
         agency_cd.x = NULL) %>%
  rename(flow = X_00060_00003)
USGS2

```

```{r}
USGS3 <- tidyr::spread(USGS2, ID, flow, fill = "") 
USGS3

USGS4 <- USGS3 %>%
  mutate(`USGS_11292500 ` = ((as.double(`USGS 11292500 CLARK FORK STANISLAUS R NR DARDANELLE CA`)/35.3146667)*86400)/1000000,
         `USGS_11293710` = ((as.double(`USGS 11292500 CLARK FORK STANISLAUS R NR DARDANELLE CA`)/35.3146667)*86400)/1000000,
         `USGS_11294000` = ((as.double(`USGS 11294000 HIGHLAND C BL SPICER MEADOWS RES CA`)/35.3146667)*86400)/1000000,
          `USGS_11292000` = ((as.double(`USGS 11292000 MF STANISLAUS R AT KENNEDY MDWS NR DARDANELLE CA`)/35.3146667)*86400)/1000000,
        
`USGS 11292500 CLARK FORK STANISLAUS R NR DARDANELLE CA` = NULL,
`USGS 11294000 HIGHLAND C BL SPICER MEADOWS RES CA` = NULL,
`USGS 11293710 NF STANISLAUS DIV TU OL BL HOBART C NR NSMD CA` = NULL,
`USGS 11292000 MF STANISLAUS R AT KENNEDY MDWS NR DARDANELLE CA` = NULL
)



USGS4

```

```{r}
readr::write_csv(USGS4, "streamflow_mcm_Stn.csv", na = "")
```


library(dataRetrieval)
siteNo2 <- c("11234700", "11243400", "11236000", "11229600", "11231000", "11246650", "11250100", "11241950", "11239500")
pCode <- "00054" #code for reservoir storage
start.date <- "1949-10-01"
end.date <- "2019-09-30"


res_info <- whatNWISdata(sites= siteNo2, parameterCd = pCode)
res_info
USGS2 <- readNWISdv(siteNumbers = "11234700",
                     parameterCd = res_info$parm_cd[1],
                     startDate = start.date,
                     endDate = end.date)
USGS2



```{r}
Redinger <- read.table("C:/Users/gusta/Downloads/USGS 11241950 REDINGER LK NR AUBERRY CA.txt")[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"REDINGER LK NR AUBERRY CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)
```

```{r}

Shaver <- read.table("C:/Users/gusta/Downloads/USGS 11239500 SHAVER LK NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"SHAVER LK NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)
Shaver
```

```{r}
Kerchoff <- read.table("C:/Users/gusta/Downloads/USGS 11246650 KERCKHOFF RES NR AUBERRY CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"KERCKHOFF RES NR AUBERRY CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Millerton <- read.table("C:/Users/gusta/Downloads/USGS 11250100 MILLERTON LK A FRIANT CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"MILLERTON LK A FRIANT CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Thomas <- read.table("C:/Users/gusta/Downloads/USGS 11231000 LK THOMAS A. EDISON NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"LK THOMAS A. EDISON NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Huntington <- read.table("C:/Users/gusta/Downloads/USGS 11236000 HUNTINGTON LK NR BIG CREEK CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"HUNTINGTON LK NR BIG CREEK CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Florence <- read.table("C:/Users/gusta/Downloads/USGS 11229600 FLORENCE LK NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"FLORENCE LK NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Bass <- read.table("C:/Users/gusta/Downloads/USGS 11243400 BASS LK NR BASS LAKE CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"BASS LK NR BASS LAKE CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Mammoth <- read.table("C:/Users/gusta/Downloads/USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"MAMMOTH POOL RE NR BIG CREEK CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

#gauges <- cbind(Redinger, Shaver, Kerchoff,Millerton, Thomas, Huntington, Florence, Bass, Mammoth)
gauges <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Redinger, Shaver, Kerchoff,Millerton, Thomas, Huntington, Florence, Bass, Mammoth))
gauges
```

```{r}
readr::write_csv(gauges, "storage_mcm.csv", na = "")
```