
```{r}
library(readr)
library(tidyverse)
USJpath <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Tuolumne River/gauges/"

#Subbasins 31 and 38
Reservoir_flow <- read_csv(paste0(USJpath, "streamflow_cfs.csv", sep = ""))
Reservoir_flow[2:23] <- Reservoir_flow[2:23]*2446.58/1000000 #converting to mcm/day
Reservoir_flow

Reservoir_stor <- read_csv(paste0(USJpath, "storage_mcm.csv", sep = ""))
Reservoir_stor
```

```{r}
colname <- colnames(Reservoir_flow)
USGS_gauges <- stringr::str_sub(colname, 5, 13)[-1]
USGS_gauges

colname2 <- colnames(Reservoir_stor)
USGS_gauges2 <- stringr::str_sub(colname2, 5, 13)[-1]
USGS_gauges2
```

```{r}
library(dataRetrieval)

siteNo <- "11251000"
pCode <- "00060"
start.date <- "1999-10-01"
end.date <- "2019-09-30"

USGS <- readNWISdv(siteNumbers = siteNo,
                     parameterCd = pCode,
                     startDate = start.date,
                     endDate = end.date)
head(USGS)
```




```{r}
siteNo <- c("11276500", "11276600", "11276900", "11277100","11277300", "11278000", "11278200", "11278300", "11278400", "11281000", "11282000", "11283250", "11283350", "11283500", "11284400", "11284700", "11289000", "11289500", "11289650")
pCode <- "00060"
start.date <- "1949-10-01"
end.date <- "2019-09-30"

USGS <- readNWISdv(siteNumbers = siteNo,
                     parameterCd = pCode,
                     startDate = start.date,
                     endDate = end.date)
```

```{r}
siteInfo <- attr(USGS, "siteInfo")
siteInfo

```

```{r}
library(dplyr)
common_column_names <- intersect(names(USGS), names(siteInfo))
#2. Use this character vector as your by parameters in the merge function.

USGS2 <- merge(USGS, siteInfo, by="site_no", all.dataframe_1=TRUE) %>%
  select(Date, site_no, agency_cd.x, station_nm, X_00060_00003) %>%
  mutate(ID = paste(agency_cd.x, site_no, station_nm, sep = " "),
         station_nm = NULL,
         site_no = NULL,
         agency_cd.x = NULL) %>%
  rename(flow = X_00060_00003)
USGS2

```

```{r}
USGS3 <- tidyr::spread(USGS2, ID, flow, fill = "")
USGS3


```

```{r}
readr::write_csv(USGS3, "streamflow_cfs2.csv", na = "")
```


library(dataRetrieval)
siteNo2 <- c("11234700", "11243400", "11236000", "11229600", "11231000", "11246650", "11250100", "11241950", "11239500")
pCode <- "00054" #code for reservoir storage
start.date <- "1949-10-01"
end.date <- "2019-09-30"


res_info <- whatNWISdata(sites= siteNo2, parameterCd = pCode)
res_info
USGS2 <- readNWISdv(siteNumbers = "11234700",
                     parameterCd = res_info$parm_cd[1],
                     startDate = start.date,
                     endDate = end.date)
USGS2



```{r}
Redinger <- read.table("C:/Users/gusta/Downloads/USGS 11241950 REDINGER LK NR AUBERRY CA.txt")[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"REDINGER LK NR AUBERRY CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)
```

```{r}

Shaver <- read.table("C:/Users/gusta/Downloads/USGS 11239500 SHAVER LK NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"SHAVER LK NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)
Shaver
```

```{r}
Kerchoff <- read.table("C:/Users/gusta/Downloads/USGS 11246650 KERCKHOFF RES NR AUBERRY CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"KERCKHOFF RES NR AUBERRY CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Millerton <- read.table("C:/Users/gusta/Downloads/USGS 11250100 MILLERTON LK A FRIANT CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"MILLERTON LK A FRIANT CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Thomas <- read.table("C:/Users/gusta/Downloads/USGS 11231000 LK THOMAS A. EDISON NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"LK THOMAS A. EDISON NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Huntington <- read.table("C:/Users/gusta/Downloads/USGS 11236000 HUNTINGTON LK NR BIG CREEK CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"HUNTINGTON LK NR BIG CREEK CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Florence <- read.table("C:/Users/gusta/Downloads/USGS 11229600 FLORENCE LK NR BIG C CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"FLORENCE LK NR BIG C CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Bass <- read.table("C:/Users/gusta/Downloads/USGS 11243400 BASS LK NR BASS LAKE CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"BASS LK NR BASS LAKE CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

Mammoth <- read.table("C:/Users/gusta/Downloads/USGS 11234700 MAMMOTH POOL RE NR BIG CREEK CA.txt", fill = TRUE)[-c(1:2),-5] %>%
  rename(Date = V3) %>%
  mutate(USGS = paste(V1, V2,"MAMMOTH POOL RE NR BIG CREEK CA",sep = " "),
         V1 = NULL,
         V2 = NULL,
         V4 = as.integer(as.character(V4))/810.71318210885,
         Date = as.Date(Date)) %>%
tidyr::spread(., USGS, V4, fill = 0)

#gauges <- cbind(Redinger, Shaver, Kerchoff,Millerton, Thomas, Huntington, Florence, Bass, Mammoth)
gauges <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Redinger, Shaver, Kerchoff,Millerton, Thomas, Huntington, Florence, Bass, Mammoth))
gauges
```

```{r}
readr::write_csv(gauges, "storage_mcm.csv", na = "")
```