---
title: "Bias Correction USJ"
author: "Gustavo Facincani Dourado"
date: "9/17/2020"
output: html_document
---

The Big Creek system is composed of subbasins 31-38, which discharge into Mammoth Pool Reservoir, together with subbasins 22 (ungauged) and 23 (gauged). Subbasins 32-35 have a very poor record of USGS gauge data. So, here we're collecting data as of an uncontrolled system, according to the data available, to bias correct the Livneh data for this regions, which does not represent this part of the system well.

```{r}
library(readr)
library(tidyverse)
library(dataRetrieval)
```

```{r}
#Read the data for the same period of the data we have for Livneh
USJpath <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/gauges/"

#Subbasins 21, 31 and 38 have reservoirs
Reservoir_flow <- read_csv(paste0(USJpath, "streamflow_cfs.csv", sep = ""), col_types = cols(Date = col_date(), .default = col_double()))%>%
filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31")))

Reservoir_flow[2:49] <- (Reservoir_flow[2:49]/35.314666)*86400/1000000 #converting to mcm
Reservoir_flow

#The other subbasins only streamflow
Reservoir_stor <- read_csv(paste0(USJpath, "storage_mcm.csv", sep = ""), col_types = cols(Date = col_date(), .default = col_double()))%>%
filter(between(Date, as.Date("1950-01-01"), as.Date("2013-12-31")))
Reservoir_stor
```

```{r}
#Water balance of reservoir to determine inflows
#Subbasin 38 - Florence Lake
Florence_lake <- Reservoir_flow[c(1,3,4)] %>% #gauges 11229500 and USGS 11230000, outflow of Florence
  filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29")))

Sub38 <- Reservoir_stor[c(1,8)] %>%
filter(between(Date, as.Date("1950-01-01"), as.Date("1980-09-29"))) %>%
   mutate(ChangeStorage = `USGS 11229600 FLORENCE LK NR BIG C CA` - lag(`USGS 11229600 FLORENCE LK NR BIG C CA`, default = first(`USGS 11229600 FLORENCE LK NR BIG C CA`)), #getting change in storage
          Outflow = rowSums(Florence_lake[2:3], na.rm=T), #sum of USGS gauges 11229500 and USGS 11230000 
          Inflow_Florence = (ChangeStorage + Outflow))#ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) #getting inflow, in which inflow = change in storage (storage of the day minus the storage of the previous day + outflow of the day)
Sub38

#Subbasins 31 - Lake Thomas Edison
Sub31 <- Reservoir_stor[c(1,6)] %>%
  filter(between(Date, as.Date("1954-10-12"), as.Date("2013-12-31"))) %>%
   mutate(ChangeStorage = `USGS 11231000 LK THOMAS A. EDISON NR BIG C CA` - lag(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`, default = first(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`)), #getting change in storage
          Outflow = Reservoir_flow$`USGS 11231500 MONO C BL LK THOMAS A EDISON CA`, #getting outflow
          Inflow_Thomas = (ChangeStorage + Outflow))#ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) #getting inflow
Sub31

#Subbasin 21 - Mammoth Pool Reservoir
Sub31 <- Reservoir_stor[c(1,6)] %>%
   mutate(ChangeStorage = `USGS 11231000 LK THOMAS A. EDISON NR BIG C CA` - lag(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`, default = first(`USGS 11231000 LK THOMAS A. EDISON NR BIG C CA`)), #getting change in storage
          Outflow = Reservoir_flow$`USGS 11231500 MONO C BL LK THOMAS A EDISON CA`, #getting outflow
          Inflow_Thomas = #ifelse((ChangeStorage + Outflow) < 0, 0, (ChangeStorage + Outflow))) #getting inflow
Sub31
```

```{r}
library(lubridate)
Florence <- Sub38[c(1,5)] %>%
  rename(flow = Inflow_Florence) 
Florence

#readr::write_csv(Florence, "Florence_inflow_mcm_withnegative.csv")
```

```{r}
Florence_USGS <- Florence %>% 
  group_by(year = year(Date), month = month(Date)) %>% 
  summarise(flow = sum(flow)) %>%
  ungroup %>%
  mutate(Date = as.Date(paste(year,'-', month,'-15', sep="")),
         year = NULL,
         month = NULL) %>%
  select(Date, flow)
Florence_USGS

Florence_Livneh <- read_csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/hydrology/historical/Livneh/runoff_aggregated/Florence Lake Inflow mcm.csv")
Florence_Livneh

Florence_PreBC_Livneh <- Florence_Livneh%>%
filter(between(date, as.Date("1950-01-01"), as.Date("1980-09-30")))#%>% 
#  group_by(year = year(date), month = month(date)) %>% 
#  summarise(flow = sum(flow)) %>%
#  ungroup %>%
#  mutate(Date = as.Date(paste(year,'-', month,'-15', sep="")),
#         year = NULL,
#         month = NULL) %>%
#  select(Date, flow)
Florence_PreBC_Livneh


```

```{r}
library(hyfo)
#Bias Correction
#new_df <- list()
bc_df <- list()
fin_df <- list()

for (i in (1:12)){

  obs <- filter(Florence,month(Florence$Date)== i)
  hind <- filter(Florence_PreBC_Livneh,month(Florence_PreBC_Livneh$date)== i)

  bF <- getBiasFactor(as.data.frame(hind),as.data.frame(obs),method = "scaling", scaleType = "multi",preci = FALSE, prThreshold = 0, extrapolate = "no")
  bF
  print(paste(i," bias factor is ", bF@biasFactor, sep = ""))
    new_df <- filter(Florence_Livneh,month(as.Date(Florence_Livneh$date, format = "%Y-%m-%d")) ==i)
    bc_df <- applyBiasFactor(new_df,bF)
    if (i==1){
      fin_df <- bc_df
    }
    else {
      fin_df <- bind_rows(fin_df,bc_df)
     
    }
  }
Florence_monthly <-  arrange(fin_df, date) #bias corrected Florence Lake inflow
head(Florence_monthly)

write_csv(Florence_monthly, "Florence_inflow_BC_monthly.csv")
```


```{r}
library(hyfo)
#Bias Correction
#new_df <- list()
bc_df <- list()
fin_df <- list()

for (i in (1:366)){

  obs <- filter(Florence,yday(Florence$Date)== i)
  hind <- filter(Florence_PreBC_Livneh,yday(Florence_PreBC_Livneh$date)== i)

  bF <- getBiasFactor(as.data.frame(hind),as.data.frame(obs),method = "scaling", scaleType = "multi",preci = FALSE, prThreshold = 0, extrapolate = "no")
  bF
  print(paste(i," bias factor is ", bF@biasFactor, sep = ""))
    new_df <- filter(Florence_Livneh,yday(as.Date(Florence_Livneh$date, format = "%Y-%m-%d")) ==i)
    bc_df <- applyBiasFactor(new_df,bF)
    if (i==1){
      fin_df <- bc_df
    }
    else {
      fin_df <- bind_rows(fin_df,bc_df)
     
    }
  }
Florence_daily <-  arrange(fin_df, date) #bias corrected Florence Lake inflow
head(Florence_daily)

write_csv(Florence_daily, "Florence_inflow_BC_daily_withnegative.csv")

```

```{r}
Florence_LivnehPreBC <- Florence_PreBC_Livneh %>%
  mutate(Data = "Pre Bias Correction") 
Florence_LivnehPreBC

BC_daily <- Florence_inflow %>%
  mutate(Data = "BC Corrected - Daily") %>%
filter(between(date, as.Date("1955-01-01"), as.Date("1991-09-30")))
BC_daily

Florence_Reference <- Florence %>%
    mutate(Data = "USGS Reference")%>%
  rename(date = Date)
Florence_Reference

Final <- rbind(Florence_LivnehPreBC, BC_daily, Florence_Reference)
Final
```

```{r}
##Line Curve
line <- ggplot(Final,aes(x=date, y=flow, color=Data))+ geom_line()+  scale_x_date()
line#limits = as.Date(c('2006-01-01','2099-12-31')))
#line + png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/", mdlname,"/",mdlname,"_line.png",sep=""), units="in",width=6.5,height=3,res=360)

##CFD Curve
data.nm <- unique(Final$Data)
Final$FDC <- NA
for (i in (1:length(data.nm))){
  vls <- Final$flow[Final$Data==data.nm[i]]
  Fn <- ecdf(vls)
  Final$FDC[Final$Data==data.nm[i]] <- 1-Fn(vls) # exceedance probabilities
}

ggplot(Final, aes(x=FDC, y=flow, color=Data)) + geom_line() + geom_point(shape=21, size=0.05, alpha=0.25) + #[rvic.hist.all.m$Model=="CCSM4_rcp85",]
       # scale_y_log10(limits=c(3e-1,3e3)) +
#        facet_wrap(~Data, ncol=2) +
        ylab(expression("Q ("*m^3/s*")")) + xlab("Exceedance probability") #+
#  png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_fdc.png",sep=""), type="cairo", units="in",width=6.5,height=3.5,res=360)

## Box&whisker
ggplot(Final, aes(x=Data, y=flow)) + geom_boxplot() +
 #       scale_y_log10(limits=c(3e-1,3e3)) +
        ylab(expression("Q ("*m^3/s*")")) + xlab("Data") # +
#png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_box.png",sep=""), type="cairo", units="in",width=6.5,height=4,res=360)

## Q-Q plot
ggplot(Final, aes(sample=flow, color=Data)) + stat_qq(shape=21, size=0.75) #+
        #+ facet_wrap(~Data, ncol=2)
#png(filename=paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/bias correction/TUOR/Catchment_RO_BC/",mdlname,"/",mdlname,"_qq.png",sep=""), type="cairo", units="in",width=6.5,height=3,res=360)

```



```{r}
#Subbasins using Livneh data, as they don't have USGS gauges
#path <- "C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/data/Upper San Joaquin River/hydrology/historical/Livneh/runoff/"

#Sub20 <- read_csv(paste(path,"tot_runoff_sb20_mcm.csv",sep=""))
#Sub22 <- read_csv(paste(path,"tot_runoff_sb22_mcm.csv",sep=""))

#Sub32 <- read_csv(paste(path,"tot_runoff_sb32_mcm.csv",sep=""))
#Sub33 <- read_csv(paste(path,"tot_runoff_sb33_mcm.csv",sep=""))
#Sub34 <- read_csv(paste(path,"tot_runoff_sb34_mcm.csv",sep=""))
#Sub35 <- read_csv(paste(path,"tot_runoff_sb35_mcm.csv",sep=""))

#Subbasin 22
Sub22 <- Reservoir_flow[c(1,7)]
Sub22

#Subbasin 36
Sub36 <- Reservoir_flow[c(1,7)]
Sub36

#Subbasin 37
Sub37 <- Reservoir_flow[c(1,c(4,6))] %>%
  mutate(Inflow = (`USGS 11230215 SF SAN JOAQUIN R BL HOOPER C NR FLORENCE LAKE CA` - `USGS 11230070 SF SAN JOAQUIN R AB HOOPER C NR FLORENCE LAKE CA`))#Subbasin 36 feeds into 37, so let's not double count it
Sub37

#PortalPH <- Reservoir_flow[17]
#PortalPH
```