
```{r}
library(readr)
library(dplyr)
library(lfstat)
library(tidyverse)
```


filenames <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-02-03/", recursive=TRUE)

# Find all .csv files
#files <- dir("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-12-14/merced/sequences/S0001_Y08_D2W1_N01/", recursive=TRUE, full.names=TRUE, pattern="//.csv$")
#filenames
# Apply the function to all files.
#result <- sapply(files, processFile)




MER_Hydro <- filenames %>%
  grep("D2W1", ., value = TRUE) %>%
  grep("merced", ., value = TRUE) %>%
  grep("Hydropower_Energy", ., value = TRUE)
MER_Hydro
  

```{r}

All <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-02-07/", recursive=TRUE) %>%
 # grep("D2W1", ., value = TRUE) %>%
  #grep("merced", ., value = TRUE) %>%
  grep(#"Hydropower_Energy"
    "Hydropower_Energy_MWh", ., value = TRUE)

head(All)

#names_mer <- substr(Mer_D2W1,18,57)
#names_mer
```

```{r}
filelist <- lapply(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-02-07/",All,sep=""), read.csv)

#if necessary, assign names to data.frames
names(filelist) <- paste(All)

#note the invisible function keeps lapply from spitting out the data.frames to the console
```


```{r}
filelist2<- invisible(lapply(names(filelist), function(x) assign(x,filelist[[x]][-c(1,2),]%>% 
                                                                   mutate(Sequence = substr(str_split(names(filelist[x]), "/")[[1]][3], 1,5), 
                                                                          Scenario = substr(str_split(names(filelist[x]), "/")[[1]][3], 11,14),
                                                                          Number = substr(str_split(names(filelist[x]), "/")[[1]][3], 16,20),
                                                                          Basin = str_split(names(filelist[x]),"/")[[1]][1]),envir=.GlobalEnv))) 
head(filelist2)
#D2_W1 <- read_csv(print("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-12-14/",MER_Hydro, sep=""))
#D2_W1
```


for (x in 1:800) {
names(filelist2[[x]])
}

```{r}
D2W1_Mer <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "merced"))%>%
  do.call("rbind", .) %>%
  select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:4)]))
D2W1_Mer

D2W1_Tuo <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "tuolumne"))%>%
  do.call("rbind", .) %>%
  select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:5)]))
D2W1_Tuo

D2W1_Stn <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "stanislaus"))%>%
  do.call("rbind", .) %>%
  select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:11)]))
D2W1_Stn

D2W1_USJ <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "upper_san_joaquin"))%>%
  do.call("rbind", .) %>%
  select(., -contains("PH.1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:15)]))
D2W1_USJ
```

ggplot(D2W1_Mer, aes(x = node, y = Total, color = Scenario)) + geom_line()



#ggplot(D2W1_Mer, x = node, y = Total) + geom_line()

#write.csv(D2W1_Mer, "Whiplash_Mer.csv")
write.csv(D2W1_Tuo, "Whiplash_Tuo.csv")
write.csv(D2W1_Stn, "Whiplash_Stn.csv")
write.csv(D2W1_USJ, "Whiplash_USJ_storage.csv")



#D2W1_Mer %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_Tuo %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_Stn %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_USJ %>% group_by(Scenario) %>% summarize(Total = mean(Total))


diff_Mer <- D2W1_Mer %>% mutate(`Relative Difference` = (Total - 990.2191077)/990.2191077*100, `Absolute Difference` = Total - 990.2191077) #%>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_Tuo <- D2W1_Tuo %>% mutate(`Relative Difference` = (Total - 6223.447953)/6223.447953*100, `Absolute Difference` = Total - 6223.447953) #%>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_Stn <- D2W1_Stn %>% mutate(`Relative Difference` = (Total - 4681.885331)/4681.885331*100, `Absolute Difference` = Total - 4681.885331)# %>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_USJ <- D2W1_USJ %>% mutate(`Relative Difference` = (Total - 12070.95512)/12070.95512*100, `Absolute Difference` = Total - 12070.95512)# %>% group_by(Scenario) %>% summarize(Total = mean(Total))

head(diff_Mer)


```{r}
#hydropower
Total_Mer <- D2W1_Mer %>% select(node, Total, Basin, Scenario, Sequence, Number) %>% mutate(`Relative Difference` = (Total - 990.2191077)/990.2191077*100, `Absolute Difference` = Total - 990.2191077) 
Total_Tuo <- D2W1_Tuo %>% select(node, Total, Basin, Scenario, Sequence, Number) %>% mutate(`Relative Difference` = (Total - 6223.447953)/6223.447953*100, `Absolute Difference` = Total - 6223.447953) 
Total_Stn <- D2W1_Stn %>% select(node, Total, Basin, Scenario, Sequence, Number) %>% mutate(`Relative Difference` = (Total - 4681.885331)/4681.885331*100, `Absolute Difference` = Total - 4681.885331) 
Total_USJ <- D2W1_USJ %>% select(node, Total, Basin, Scenario, Sequence, Number) %>% mutate(`Relative Difference` = (Total - 12070.95512)/12070.95512*100, `Absolute Difference` = Total - 12070.95512) 

Total_Gen <- rbind(Total_Mer, Total_Tuo, Total_Stn, Total_USJ) %>%
  mutate(Month = as.Date(node, format = "%B/%Y"),#as.Date(cut(node,  breaks = "month")),
         Year = as.Date(water_year(node, origin = "usgs"), "%Y"),
         #Year = as.Date(cut(node, breaks = "year")),
         Scenario = as.factor(Scenario)) %>%
#    Month = as.factor(format(as.Date(node, format = "%B/%Y"), "%b/%Y")))%>%
 #        Year = water_year(node, origin = "usgs")) %>%
  group_by(Basin, Month, Year, Sequence, Number, Scenario) %>%
   dplyr::summarize(MonthlyTotal = sum(Total),
                    `Absolute Difference` = sum(`Absolute Difference`),
                    `Relative Difference` = mean(`Relative Difference`))# %>%
#  mutate(YearType = ifelse(.$Scenario == "D2W1" & .$Year == "2003-02-08", "Wet", "Dry"))
Total_Gen

Total_Gen$YearType <- ifelse(Total_Gen$Scenario == "D2W1" & Total_Gen$Year == "2003-02-08", "Wet", 
ifelse(Total_Gen$Year == "2003-02-08" & Total_Gen$Scenario == "D2W2", "Wet", 
       ifelse(Total_Gen$Year == "2004-02-08" & Total_Gen$Scenario == "D2W2", "Wet",
       ifelse(Total_Gen$Scenario == "D3W1" & Total_Gen$Year == "2004-02-08", "Wet",
ifelse(Total_Gen$Year == "2004-02-08" & Total_Gen$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen$Year == "2005-02-08" & Total_Gen$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen$Scenario == "D4W1" & Total_Gen$Year == "2005-02-08", "Wet", 
ifelse(Total_Gen$Year == "2005-02-08" & Total_Gen$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen$Year == "2006-02-08" & Total_Gen$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen$Scenario == "D5W1" & Total_Gen$Year == "2006-02-08", "Wet",
ifelse(Total_Gen$Year == "2006-02-08" & Total_Gen$Scenario == "D5W2", "Wet",
       ifelse(Total_Gen$Year == "2007-02-08" & Total_Gen$Scenario == "D5W2", "Wet","Dry"))))))))))))

Total_Gen_Year <- Total_Gen %>%
group_by(Basin, Year, Scenario, YearType) %>%
dplyr::summarize(`Annual Total` = sum(MonthlyTotal),
`Absolute Difference` = sum(`Absolute Difference`),
`Relative Difference` = mean(`Relative Difference`),
Change = ifelse(`Absolute Difference` < 0, "Negative", "Positive")) %>%
mutate(Basin = replace(Basin, Basin == 'merced', 'Merced')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'Stanislaus')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'Tuolumne')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'Upper San Joaquin'))
Total_Gen_Year

Total_Gen_Year$YearType <- ifelse(Total_Gen_Year$Scenario == "D2W1" & Total_Gen_Year$Year == "2003-02-08", "Wet", 
ifelse(Total_Gen_Year$Year == "2003-02-08" & Total_Gen_Year$Scenario == "D2W2", "Wet", 
       ifelse(Total_Gen_Year$Year == "2004-02-08" & Total_Gen_Year$Scenario == "D2W2", "Wet",
       ifelse(Total_Gen_Year$Scenario == "D3W1" & Total_Gen_Year$Year == "2004-02-08", "Wet",
ifelse(Total_Gen_Year$Year == "2004-02-08" & Total_Gen_Year$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen_Year$Year == "2005-02-08" & Total_Gen_Year$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen_Year$Scenario == "D4W1" & Total_Gen_Year$Year == "2005-02-08", "Wet", 
ifelse(Total_Gen_Year$Year == "2005-02-08" & Total_Gen_Year$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen_Year$Year == "2006-02-08" & Total_Gen_Year$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen_Year$Scenario == "D5W1" & Total_Gen_Year$Year == "2006-02-08", "Wet",
ifelse(Total_Gen_Year$Year == "2006-02-08" & Total_Gen_Year$Scenario == "D5W2", "Wet",
       ifelse(Total_Gen_Year$Year == "2007-02-08" & Total_Gen_Year$Scenario == "D5W2", "Wet","Dry"))))))))))))

Total_Gen_Year2 <- Total_Gen %>%
  group_by(Basin, Year, Number, Scenario) %>%
   dplyr::summarize(`Annual Total` = sum(MonthlyTotal),
                    `Absolute Difference` = sum(`Absolute Difference`),
                    `Relative Difference` = mean(`Relative Difference`),
                    Change = ifelse(`Absolute Difference` < 0, "Negative", "Positive")) %>%
  mutate(Basin = replace(Basin, Basin == 'merced', 'Merced')) %>%
    mutate(Basin = replace(Basin, Basin == 'stanislaus', 'Stanislaus')) %>%
  mutate(Basin = replace(Basin, Basin == 'tuolumne', 'Tuolumne')) %>%
  mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'Upper San Joaquin'))

Total_Gen_Year2

Total_Gen_Year2$YearType <- ifelse(Total_Gen_Year2$Scenario == "D2W1" & Total_Gen_Year2$Year == "2003-02-08", "Wet", 
ifelse(Total_Gen_Year2$Year == "2003-02-08" & Total_Gen_Year2$Scenario == "D2W2", "Wet", 
       ifelse(Total_Gen_Year2$Year == "2004-02-08" & Total_Gen_Year2$Scenario == "D2W2", "Wet",
       ifelse(Total_Gen_Year2$Scenario == "D3W1" & Total_Gen_Year2$Year == "2004-02-08", "Wet",
ifelse(Total_Gen_Year2$Year == "2004-02-08" & Total_Gen_Year2$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen_Year2$Year == "2005-02-08" & Total_Gen_Year2$Scenario == "D3W2", "Wet", 
       ifelse(Total_Gen_Year2$Scenario == "D4W1" & Total_Gen_Year2$Year == "2005-02-08", "Wet", 
ifelse(Total_Gen_Year2$Year == "2005-02-08" & Total_Gen_Year2$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen_Year2$Year == "2006-02-08" & Total_Gen_Year2$Scenario == "D4W2", "Wet", 
       ifelse(Total_Gen_Year2$Scenario == "D5W1" & Total_Gen_Year2$Year == "2006-02-08", "Wet",
ifelse(Total_Gen_Year2$Year == "2006-02-08" & Total_Gen_Year2$Scenario == "D5W2", "Wet",
       ifelse(Total_Gen_Year2$Year == "2007-02-08" & Total_Gen_Year2$Scenario == "D5W2", "Wet","Dry"))))))))))))


#replace(Total_Gen_Year$Basin == "merced", "Merced")
#Total_Gen_Year$Basin == "stanislaus" <- "Stanislaus"
#Total_Gen_Year$Basin == "tuolumne" <- "Tuolumne"
#Total_Gen_Year$Basin == "upper_san_joaquin" <- "Upper San Joaquin"

Total_Gen_Year$Basin <- factor(Total_Gen_Year$Basin, levels = c("Stanislaus", "Tuolumne", "Merced", "Upper San Joaquin"))
Total_Gen_Year2$Basin <- factor(Total_Gen_Year2$Basin, levels = c("Stanislaus", "Tuolumne", "Merced", "Upper San Joaquin"))

```

```{r}

 ggplot(Total_Gen)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_line(aes(x=as.Date(Month), y = MonthlyTotal/1000, color = Number))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(expand = c(0, 0))+
   scale_x_date(date_labels = "%b/%Y")+
  #scale_x_date(date_labels = "%b/%Y",
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_grid(Scenario~Basin, scales = "free")+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation.png", units ="in", width=16, height=10, res = 300)

```

```{r}

 ggplot(Total_Gen_Year2)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_rect(aes(color = NULL, fill = YearType, xmin = as.numeric(format(Year, "%Y"))-0.5, xmax = as.numeric(format(Year, "%Y"))+0.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  geom_line(aes(x=as.numeric(format(Year, "%Y")), y = `Annual Total`/1000, color=Number))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
    scale_fill_manual(values = c("white", "lightblue"))+

#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(limits = c(0, NA), expand = c(0, 0))+
  # scale_x_date(date_labels = "%b/%Y")+
  scale_x_continuous(expand = c(0, 0))+
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_grid(Basin~Scenario, scales = "free")+
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        axis.text.x = element_text(angle = -45, vjust=-0.4),
        plot.title = element_text(hjust = 0.5)) + #center the title
 # guides(colour = guide_legend(nrow = 1))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Annual2.png", units ="in", width=18, height=10, res = 300)

```

```{r}

 ggplot(Total_Gen_Year2, aes(x=as.numeric(format(Year, "%Y")), color=Number))+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_rect(aes(color = NULL, fill = YearType, xmin = as.numeric(format(Year, "%Y"))-0.5, xmax = as.numeric(format(Year, "%Y"))+0.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  geom_line(aes(y = cumsum(`Annual Total`)/1000000))+
    geom_line(aes(y = (cumsum(`Annual Total`)/1000000)+(cumsum(`Absolute Difference`)/1000000)), linetype = "twodash")+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
    
  scale_fill_manual(values = c("white", "lightblue"))+

#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(expand = c(0, 0)) +
  # scale_x_date(date_labels = "%b/%Y")+
  scale_x_continuous(expand = c(0, 0), limits = c(2001,NA))+
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (TWh)") + #name of x axis
  facet_grid(Basin~Scenario, scales = "free")+
  theme(legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        axis.text.x = element_text(angle = -45, vjust=-0.4),
        plot.title = element_text(hjust = 0.5)) + #center the title
 # guides(colour = guide_legend(nrow = 1))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Annual_Difference5.png", units ="in", width=18, height=10, res = 300)

```



 ggplot(Total_Gen)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_violin(aes(x=Year, y = MonthlyTotal/1000, fill=Scenario), draw_quantiles = c(.25, .5, .75))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(expand = c(0, 0))+
   scale_x_discrete()+
  #scale_x_date(date_labels = "%b/%Y",
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_wrap(Scenario~Basin, scales = "free_x", ncol=4)+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Violin.png", units ="in", width=16, height=10, res = 300)




```{r}

 ggplot(Total_Gen_Year)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
 geom_rect(aes(fill = `YearType`, xmin = as.Date(as.numeric(Year)-182), xmax = as.Date(as.numeric(Year)+182), ymin = -Inf, ymax = Inf), alpha = 0.5)+

  geom_col(aes(x=Year, y = `Relative Difference`, fill = Change), position = "identity")+# fill=Scenario))+#, draw_quantiles = c(.25, .5, .75))+
  theme_bw(base_size=12, base_family='Times New Roman') +
  #  scale_fill_manual(values = c("red", "blue"), guide = FALSE)+
#change font to Times New Roman, 12pt, Bold
#plot monthly observed data in orange
    scale_fill_manual(values = c("white", "red", "blue", "lightblue"))+

    scale_y_continuous(expand = c(0, 0))+
   scale_x_continuous(expand = c(0, 0))+
  #scale_x_date(date_labels = "%b/%Y",
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Relative Difference in Hydropower Generation (%)") + #name of x axis
  facet_grid(Basin~Scenario, scales = "free_x")+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Ba3r.png", units ="in", width=16, height=10, res = 300)

```


