
```{r}
library(readr)
library(dplyr)
library(lfstat)
library(tidyverse)
```


```{r}
#Historical deliveries
Mer_Hist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/merced/historical/Livneh/Output_Flow_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Mer_Hist_Deliveries
Tuo_Hist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/tuolumne/historical/Livneh/Output_Flow_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Tuo_Hist_Deliveries
Stn_Hist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/stanislaus/historical/Livneh/Output_Flow_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Stn_Hist_Deliveries
USJ_Hist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/upper_san_joaquin/historical/Livneh/Output_Flow_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
USJ_Hist_Deliveries
Mer_ExpHist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/merced/historical/Livneh/Output_Demand_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Mer_ExpHist_Deliveries
Tuo_ExpHist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/tuolumne/historical/Livneh/Output_Demand_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Tuo_ExpHist_Deliveries
Stn_ExpHist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/stanislaus/historical/Livneh/Output_Demand_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
Stn_ExpHist_Deliveries
USJ_ExpHist_Deliveries <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/upper_san_joaquin/historical/Livneh/Output_Demand_mcm.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))
USJ_ExpHist_Deliveries
  
```

```{r}
#y = expected demand, x = flow delivery
Mer_Irrig <- Mer_Hist_Deliveries%>% 
  inner_join(Mer_ExpHist_Deliveries, by = 'node') %>% 
  mutate(WaterYear = lfstat::water_year(node, origin = "usgs"),
         UnmetAg = ifelse(((MID.Northside.y - MID.Northside.x) + (MID.Main.y - MID.Main.x)) < 0.001, 0, ((MID.Northside.y - MID.Northside.x) + (MID.Main.y - MID.Main.x))),
         Failure = ifelse(UnmetAg > 0, 1, 0),
         NonFailure = ifelse(UnmetAg == 0, 0, 1),
         `Volumetric Reliability` = (MID.Northside.x + MID.Main.x)/(MID.Northside.y + MID.Main.y)*100) %>%
  group_by(WaterYear) %>%
  summarize(`Volumetric Reliability` = mean(`Volumetric Reliability`),
            `Volumetric Reliability` = (1-sum(NonFailure)/365)*100,
            `Failed Year` = ifelse(`Volumetric Reliability` < 100, 1, 0)) %>% 
  mutate(`Annual Reliability` = (1-sum(`Failed Year`)/length(unique(.$WaterYear)))*100)
Mer_Irrig

Tuo_Irrig <- Tuo_Hist_Deliveries%>% 
  inner_join(Tuo_ExpHist_Deliveries, by = 'node') %>% 
  mutate(WaterYear = lfstat::water_year(node, origin = "usgs"),
         UnmetAg = ifelse(((Turlock.Irrigation.District.y - Turlock.Irrigation.District.x) + (Modesto.Irrigation.District.y - Modesto.Irrigation.District.x)) < 0.001, 0, ((Turlock.Irrigation.District.y - Turlock.Irrigation.District.x) + (Modesto.Irrigation.District.y - Modesto.Irrigation.District.x))),
         SFPUC.y = ifelse(SFPUC.y > 1.1, 1.1, SFPUC.y),
         UnmetUrban = ifelse((SFPUC.y - SFPUC.x) < 0.001, 0, (SFPUC.y - SFPUC.x)),
         Failure = ifelse(UnmetAg > 0, 1, 0),
         NonFailure = ifelse(UnmetAg == 0, 0, 1),
         UrbanFailure = ifelse(UnmetUrban > 0, 1, 0),
         UrbanNonFailure = ifelse(UnmetUrban == 0, 0, 1),
         `Volumetric Reliability` = (Modesto.Irrigation.District.x + Turlock.Irrigation.District.x) / (Modesto.Irrigation.District.y + Turlock.Irrigation.District.y)*100,
         `Urban Volumetric Reliability` = (SFPUC.x/SFPUC.y)*100) %>%
  group_by(WaterYear) %>%
  summarize(`Volumetric Reliability` = mean(`Volumetric Reliability`),
            `Volumetric Reliability` = (1-sum(NonFailure)/365)*100,
            `Failed Year` = ifelse(`Volumetric Reliability` < 100, 1, 0),
            `Urban Volumetric Reliability` = mean(`Urban Volumetric Reliability`),
            `Urban Volumetric Reliability` = (1-sum(UrbanNonFailure)/365)*100,
            `Urban Failed Year` = ifelse(`Urban Volumetric Reliability` < 100, 1, 0)) %>% 
  mutate(`Annual Reliability` = (1-sum(`Failed Year`)/length(unique(.$WaterYear)))*100,
         `Urban Annual Reliability` = (1-sum(`Urban Failed Year`)/length(unique(.$WaterYear)))*100)
Tuo_Irrig

Stn_Irrig <- Stn_Hist_Deliveries%>% 
  inner_join(Stn_ExpHist_Deliveries, by = 'node') %>% 
  mutate(WaterYear = lfstat::water_year(node, origin = "usgs"),
         UnmetAg = ifelse(((South.San.Joaquin.Irrigation.District.y - South.San.Joaquin.Irrigation.District.x) + (Oakdale.Irrigation.District.y - Oakdale.Irrigation.District.x)) < 0.001, 0, ((South.San.Joaquin.Irrigation.District.y - South.San.Joaquin.Irrigation.District.x) + (Oakdale.Irrigation.District.y - Oakdale.Irrigation.District.x))),
         Failure = ifelse(UnmetAg > 0, 1, 0),
         NonFailure = ifelse(UnmetAg == 0, 0, 1),
         `Volumetric Reliability` = (Oakdale.Irrigation.District.x + South.San.Joaquin.Irrigation.District.x)/(Oakdale.Irrigation.District.y + South.San.Joaquin.Irrigation.District.y)*100,
      #   Days = ifelse(`Volumetric Reliability` != "NaN", 1,0)
      )%>% tidyr::drop_na() %>%
  group_by(WaterYear) %>%
  summarize(`Volumetric Reliability` = mean(`Volumetric Reliability`),
            `Volumetric Reliability` = (1-sum(NonFailure)/245)*100, #Stanislaus just has ag deliveries 245 days/year
            `Failed Year` = ifelse(`Volumetric Reliability` < 100, 1, 0)) %>% 
  mutate(`Annual Reliability` = (1-sum(`Failed Year`)/length(unique(.$WaterYear)))*100)
Stn_Irrig

USJ_Irrig <- USJ_Hist_Deliveries%>% 
  inner_join(USJ_ExpHist_Deliveries, by = 'node') %>% 
  mutate(WaterYear = lfstat::water_year(node, origin = "usgs"),
         CVP.Friant.Kern.Canal.y =ifelse(CVP.Friant.Kern.Canal.y > 10.57710973, 10.57710973, CVP.Friant.Kern.Canal.y),
         CVP.Madera.Canal.y = ifelse(CVP.Madera.Canal.y > 3.132, 3.132, CVP.Madera.Canal.y),
         UnmetAg = ifelse(((CVP.Friant.Kern.Canal.y - CVP.Friant.Kern.Canal.x) + (CVP.Madera.Canal.y - CVP.Madera.Canal.x)) < 0.001, 0, ((CVP.Friant.Kern.Canal.y - CVP.Friant.Kern.Canal.x) + (CVP.Madera.Canal.y - CVP.Madera.Canal.x))),
         Failure = ifelse(UnmetAg > 0, 1, 0),
         NonFailure = ifelse(UnmetAg == 0, 0, 1),
         `Volumetric Reliability` = (CVP.Friant.Kern.Canal.x + CVP.Madera.Canal.x)/(CVP.Friant.Kern.Canal.y + CVP.Madera.Canal.y)*100) %>%
  group_by(WaterYear) %>%
  summarize(`Volumetric Reliability` = ifelse(mean(`Volumetric Reliability`) > 100, 100, mean(`Volumetric Reliability`)),
            `Volumetric Reliability` = (1-sum(NonFailure)/365)*100,
            `Failed Year` = ifelse(`Volumetric Reliability` < 100, 1, 0)) %>% 
  mutate(`Annual Reliability` = (1-sum(`Failed Year`)/length(unique(.$WaterYear)))*100)
USJ_Irrig

 # dplyr::select(node, `MID Northside`, `MID Main`)
```

```{r}

All_demands <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/", recursive=TRUE) %>%
 # grep("D2W1D2", ., value = TRUE) %>%
  #grep("merced", ., value = TRUE) %>%
  grep(#"Hydropower_Energy"
    "Output_Demand_mcm.csv", ., value = TRUE)

head(All_demands)

All_deliveries <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/", recursive=TRUE) %>%
 # grep("D2W1D2", ., value = TRUE) %>%
  #grep("merced", ., value = TRUE) %>%
  grep(#"Hydropower_Energy"
    "Output_Flow_mcm.csv", ., value = TRUE)

head(All_deliveries)
#names_mer <- substr(Mer_D2W1,18,57)
#names_mer
```

```{r}
filelist_deliveries <- lapply(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/",All_deliveries,sep=""), read.csv)

#if necessary, assign names to data.frames
names(filelist_deliveries) <- paste(All_deliveries)


filelist_demands <- lapply(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/",All_demands,sep=""), read.csv)

#if necessary, assign names to data.frames
names(filelist_demands) <- paste(All_demands)
#note the invisible function keeps lapply from spitting out the data.frames to the console
```
  
```{r}
filelist_deliveries2<- invisible(lapply(names(filelist_deliveries), function(x) assign(x,filelist_deliveries[[x]][-c(1,2),]%>% 
                                                                   mutate(Sequence = substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 1,5), 
                                                                          Scenario = paste(substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 11,14), substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 11,12), sep=""), 
                                                                          Scenario2 =substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 11,12),
                                                                          Scenario3 =substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 13,14),
                                                                          Number = substr(str_split(names(filelist_deliveries[x]), "/")[[1]][3], 16,20),
                                                                          Basin = str_split(names(filelist_deliveries[x]),"/")[[1]][1]),envir=.GlobalEnv))) 
head(filelist_deliveries2)

filelist_demands2<- invisible(lapply(names(filelist_demands), function(x) assign(x,filelist_demands[[x]][-c(1,2),]%>% 
                                                                   mutate(Sequence = substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 1,5), 
                                                                          Scenario = paste(substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 11,14), substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 11,12), sep=""), 
                                                                          Scenario2 =substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 11,12),
                                                                          Scenario3 =substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 13,14),
                                                                          Number = substr(str_split(names(filelist_demands[x]), "/")[[1]][3], 16,20),
                                                                          Basin = str_split(names(filelist_demands[x]),"/")[[1]][1]),envir=.GlobalEnv))) 
head(filelist_demands2)
#D2_W1 <- read_csv(print("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-12-14/",MER_Hydro, sep=""))
#D2_W1
```

```{r}
Demand_Mer <- filelist_demands2 %>%
  lapply(., function(x) filter(x, Basin == "merced"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Demand_Mer

Demand_Tuo <- filelist_demands2 %>%
 # purrr::discard(~ nrow(.x) == 0) %>%
  lapply(., function(x) filter(x, Basin == "tuolumne"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  mutate(SFPUC = ifelse(SFPUC > 1.1, 1.1, SFPUC)) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Demand_Tuo

Demand_Stn <- filelist_demands2 %>%
  lapply(., function(x) filter(x, Basin == "stanislaus"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Demand_Stn

Demand_USJ <- filelist_demands2 %>%
  lapply(., function(x) filter(x, Basin == "upper_san_joaquin"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  mutate(CVP.Friant.Kern.Canal = ifelse(CVP.Friant.Kern.Canal > 10.57710973, 10.57710973, CVP.Friant.Kern.Canal),
         CVP.Madera.Canal = ifelse(CVP.Madera.Canal > 3.132, 3.132, CVP.Madera.Canal)) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Demand_USJ


Delivery_Mer <- filelist_deliveries2 %>%
  lapply(., function(x) filter(x, Basin == "merced"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Delivery_Mer

Delivery_Tuo <- filelist_deliveries2 %>%
  lapply(., function(x) filter(x, Basin == "tuolumne"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Delivery_Tuo

Delivery_Stn <- filelist_deliveries2 %>%
  lapply(., function(x) filter(x, Basin == "stanislaus"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Delivery_Stn

Delivery_USJ <- filelist_deliveries2 %>%
  lapply(., function(x) filter(x, Basin == "upper_san_joaquin"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  reshape2::melt(., by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"))
Delivery_USJ
```

```{r}
Demand <- rbind(Demand_Mer, Demand_Tuo, Demand_Stn, Demand_USJ) %>%
  rename(Demand = value)
Demand

Delivery <- rbind(Delivery_Mer, Delivery_Tuo, Delivery_Stn, Delivery_USJ) %>%
  rename(Delivery = value)
Delivery

```


```{r}

Irrigation <- Delivery %>% inner_join(., Demand, by = c("node", "Sequence", "Scenario", "Scenario2", "Scenario3","Number", "Basin", "variable")) %>%
  mutate(Type = ifelse(variable == "SFPUC", "Urban", "Agricultural")) %>%
  group_by(node, Sequence, Scenario, Scenario2, Scenario3, Number, Basin, Type) %>%
  summarize(Delivery = sum(Delivery),
            Demand = sum(Demand))
Irrigation
  
Irrigation2 <- Irrigation %>%  mutate(WaterYear = lfstat::water_year(node, origin = "usgs"),
         UnmetAg = ifelse(Demand - Delivery  < 0.001, 0, Demand - Delivery),
         Failure = ifelse(UnmetAg > 0, 1, 0),
         NonFailure = ifelse(UnmetAg == 0, 0, 1),
         `Volumetric Reliability` = (Delivery/Demand)*100)
Irrigation2
```
```{r}
Irrigation2$YearType <- ifelse(Irrigation2$Scenario == "D2W1D2" & Irrigation2$WaterYear == "2003", "Wet", 
ifelse(Irrigation2$WaterYear == "2003" & Irrigation2$Scenario == "D2W2D2", "Wet", 
       ifelse(Irrigation2$WaterYear == "2004" & Irrigation2$Scenario == "D2W2D2", "Wet",
       ifelse(Irrigation2$Scenario == "D3W1D3" & Irrigation2$WaterYear == "2004", "Wet",
ifelse(Irrigation2$WaterYear == "2004" & Irrigation2$Scenario == "D3W2D3", "Wet", 
       ifelse(Irrigation2$WaterYear == "2005" & Irrigation2$Scenario == "D3W2D3", "Wet", 
       ifelse(Irrigation2$Scenario == "D4W1D4" & Irrigation2$WaterYear == "2005", "Wet", 
ifelse(Irrigation2$WaterYear == "2005" & Irrigation2$Scenario == "D4W2D4", "Wet", 
       ifelse(Irrigation2$WaterYear == "2006" & Irrigation2$Scenario == "D4W2D4", "Wet", 
       ifelse(Irrigation2$Scenario == "D5W1D5" & Irrigation2$WaterYear == "2006", "Wet",
ifelse(Irrigation2$WaterYear == "2006" & Irrigation2$Scenario == "D5W2D5", "Wet",
       ifelse(Irrigation2$WaterYear == "2007" & Irrigation2$Scenario == "D5W2D5", "Wet","Dry"))))))))))))

Irrigation3 <- Irrigation2 %>% 
  filter(Type == "Agricultural")  %>%
  tidyr::drop_na() %>% group_by(Basin, WaterYear, Sequence, Scenario, Scenario2, Scenario3, Number, YearType) %>%
  summarize(`Volumetric Reliability` = ifelse(mean(`Volumetric Reliability`) > 100, 100, mean(`Volumetric Reliability`)),
         `Time Reliability` = ifelse(Basin=="stanislaus", (1-sum(NonFailure)/245)*100, (1-sum(NonFailure)/365)*100),
         `Total Failure (days)` = sum(Failure))#/n())*100,
         #`Length of unsatisfactory performance (days)` = (100 - `Time Reliability`)/sum(Failure),
         #`Count of breaks` = ifelse(`Time Reliability`== 100 & lead(`Time Reliability`) < 100, 1, 0))
         #Resilience = `Length of unsatisfactory performance (days)`/ (100 - `Time Reliability`))
  

Irrigation3
```
Irrigation3 %>% mutate(Count = ifelse(`Time Reliability` < 100 & lag(`Time Reliability`) == 100, 1, 0)) #%>% n_distinct()-1


Irrigation3 <- Irrigation2 %>% tidyr::drop_na() %>% group_by(Basin,Sequence,Number, Scenario, WaterYear, Type) %>%
  summarize(`Volumetric Reliability` = ifelse(mean(`Volumetric Reliability`) > 100, 100, mean(`Volumetric Reliability`)),
            `Time Reliability` = ifelse(Basin=="stanislaus", (1-sum(NonFailure)/245)*100, (1-sum(NonFailure)/365)*100),
            #`Failed Year` = ifelse(`Volumetric Reliability` < 100, 1, 0),
            Resilience = (1 - `Time Reliability`)/)
           
Irrigation3

```{r}
Irrigation_3 <- Irrigation2 %>% 
  filter(Type == "Agricultural") %>% ungroup() %>%
    group_by(Basin, Number, Sequence, Scenario, Scenario2, Scenario3)%>%

  mutate(`Total consecutive failures` = ave(Failure,cumsum(Failure==0),FUN=cumsum)) %>%# accumulate(Failure, ~ifelse(.y == 0, .y, .x + .y))) #%>%
   filter(!`Total consecutive failures` == 0) %>%
 # ungroup() %>%
  mutate(Total = lead(`Total consecutive failures`) - `Total consecutive failures`,
         Total = ifelse(is.na(Total), -1, Total)) %>% #in case the last day (NA due to lead()) is an NA, make it negative to not be filtered out in Irrigation_)%>%
    filter(!`Total` > 0) # %>% distinct(Sequence,Number, Delivery, `Total consecutive failures`, Demand, .keep_all = TRUE)

Irrigation_3

Irrigation_3 <- Irrigation_3 %>% mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ'))%>%
  group_by(Basin, Scenario) %>%
    mutate(`Longest Failure` = max(`Total consecutive failures`))
Irrigation_3

Irrigation_3$Basin <- factor(Irrigation_3$Basin, levels = c("STN", "TUO", "MER", "USJ"))
```

```{r}
saco <- Irrigation2 %>% 
  filter(Type == "Agricultural") %>% ungroup()%>%
  group_by(Basin, Number, Sequence, Scenario, Scenario2, Scenario3)%>%
  mutate(`Total consecutive failures` = ave(Failure,cumsum(Failure==0),FUN=cumsum)) %>%# accumulate(Failure, ~ifelse(.y == 0, .y, .x + .y))) #%>%
 #  filter(!`Total consecutive failures` == 0) %>%
 # ungroup() %>%
  mutate(Total = lead(`Total consecutive failures`) - `Total consecutive failures`) %>%
   # filter(`Total` == 0) %>%
  filter(Basin == "stanislaus" & Scenario == "D5W1D5" & Sequence == "S0175") 
saco[c(1:36),]
```


```{r}

Irrigation_4 <- Irrigation_3 %>%
  mutate(Total = 1) %>%
  group_by(Basin, Number, Sequence, Scenario, Scenario2, Scenario3) %>%
    summarize(`Longest Failure` = max(`Total consecutive failures`),
              `Shortest Failure` = min(`Total consecutive failures`),
      `Total Failure (A)` = sum(`Total consecutive failures`),
              `Total Switching (B)` = sum(`Total`),
              Resilience = `Total Switching (B)`/`Total Failure (A)`,
      `Recovery rate` = `Total Failure (A)`/`Total Switching (B)`)

Irrigation_4
```

```{r}

Irrigation_fixed <- merge (Irrigation_4, resilience[c(1:6)] , all.x=T, all.y=T) %>%
  mutate(`Total Switching (B)` = ifelse(is.na(`Total Switching (B)`), 0, as.numeric(`Total Switching (B)`)),
      #   `Total consecutive failures` = ifelse(`Total consecutive failures` == "NA", 0, `Total consecutive failures`),
         Resilience = ifelse(is.na(Resilience), 1, as.numeric(Resilience)))
         
  
Irrigation_fixed

```

```{r}
ggplot(Irrigation_fixed) +         
  geom_bar(mapping= aes(y = factor(Scenario), x= as.numeric(Resilience)*100, fill=factor(Number)), position = position_dodge2(preserve = "single"), stat="identity") + 

    facet_grid(~Basin, scales = "free")+
  scale_fill_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  scale_y_discrete(drop = FALSE, expand = c(0, 0), limits = rev) +
      scale_x_continuous(expand = c(0, 0), limits = c(0, 100)) +
  #scale_y_log10(limits = c(0.01, 1), breaks = c(0.01, 0.1, 0.2, 0.4, 0.6, 1.0))+    
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
  
   theme_bw(base_size=12)+
  
  ylab(element_blank())+
  xlab("Resilience (%)")+
        theme(legend.title = element_blank(),
    legend.position = "none",
       # legend.direction = "horizontal",
    axis.text.x = element_text(angle = -90),
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_IRrig_Recovery_Resiliency422.png", units ="in", width=12, height=6, res = 300)
```

```{r}
ggplot(Irrigation_fixed) +         
 # geom_bar(mapping= aes(y = factor(Scenario), x= as.numeric(Resilience)*100, fill=factor(Number)), position = position_dodge2(preserve = "single"), stat="identity") + 

  geom_violin(mapping= aes(y = as.numeric(Resilience)*100, x= Scenario, fill = Scenario), draw_quantiles = c(.25, .5, .75)) +
  
    facet_grid(rows = vars(Basin), scales = "free", switch = "y")+
  scale_fill_manual(values = wes_palette("Zissou1", 8, type = "continuous"))+
  
      scale_y_continuous(expand = c(0, 0), limits = c(0, 101)) +
  scale_x_discrete(position = "top") +
  #scale_y_log10(limits = c(0.01, 1), breaks = c(0.01, 0.1, 0.2, 0.4, 0.6, 1.0))+    
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 100)) +
  
   theme_bw(base_size=14)+
  
  ylab(element_blank())+
  xlab("Resilience (%)")+
        theme(legend.title = element_blank(),
    legend.position = "none",
       # legend.direction = "horizontal",
   # axis.text.x = element_text(angle = -90),
    axis.text.x = element_text(angle = 25, vjust = 1, hjust=0.25),
        strip.placement = "outside",
        strip.background = element_blank(),
       plot.margin = margin(0, 0.5,0, 0, "cm"))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Irrig_Recovery_Resiliency522.png", units ="in", width=5, height=11, res = 300)
```

```{r}
#Silence lines in Irrigation_3

ggplot() +

        geom_bar(Irrigation_4, mapping= aes(y = Scenario, x=`Total Switching (B)`, fill=Number), stat="identity",  position = position_dodge2(preserve = "single")) + 

   #geom_violin(mapping= aes(x = `Total consecutive failures`, y = Scenario, fill = Scenario), draw_quantiles = c(.25, .5, .75)) +
    facet_grid(~Basin, scales = "free")+
  scale_fill_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  
      scale_x_continuous(expand = c(0, 0), limits = c(0, 40)) +
  #scale_y_log10(limits = c(0.01, 1), breaks = c(0.01, 0.1, 0.2, 0.4, 0.6, 1.0))+    
  scale_y_discrete(expand = c(0, 0), limits = rev) +
 # scale_fill_manual(values = wes_palette("Zissou1", 33, type = "continuous"))+
   theme_bw(base_size=12)+
  
  xlab("Recovery rate (days)")+
  ylab(element_blank())+
        theme(legend.title = element_blank(),
    legend.position = "none",
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Irrig_Recovery_Resiliency_1212.png", units ="in", width=12, height=6, res = 300)
```

```{r}
ggplot(Irrigation_3) +

 #       geom_bar(Eflow_4, mapping= aes(y = Scenario, x=`Total Switching (B)`, fill=Number), stat="identity", position = "dodge", color="black") + 

   geom_violin(mapping= aes(y = `Total consecutive failures`, x = Scenario, fill = Scenario), draw_quantiles = c(.25, .5, .75)) +
    facet_grid(rows = vars(Basin), scales = "fixed", switch = "y")+
  scale_fill_manual(values = wes_palette("Zissou1", 8, type = "continuous"))+
  geom_text(aes(y = 130, x = Scenario, label= `Longest Failure`), position=position_dodge(width=0.9), vjust=-0.25, angle = 90)+

      scale_y_continuous(expand = c(0, 0), limits = c(0, 160)) +
  #scale_y_log10(limits = c(0.01, 1), breaks = c(0.01, 0.1, 0.2, 0.4, 0.6, 1.0))+    
  scale_x_discrete(position = "top", expand = c(0, 0)) +
 # scale_fill_manual(values = wes_palette("Zissou1", 33, type = "continuous"))+
   theme_bw(base_size=14)+
  
  xlab("Recovery rate (days)")+
  ylab(element_blank())+
        theme(legend.title = element_blank(),
    legend.position = "none",
    axis.text.x = element_text(angle = 25, vjust = 1, hjust=0.25),
        strip.placement = "outside",
        strip.background = element_blank(),
        plot.margin = margin(0, 0.5,0, 0, "cm"))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Irrig_recovery_Resiliency_1_po.png", units ="in", width=5, height=11, res = 300)
```

```{r}
ggplot(Irrigation_fixed) +

        geom_bar(Irrigation_fixed, mapping= aes(y = factor(Scenario), x=`Total Switching (B)`, fill=factor(Number)), position = position_dodge2(preserve = "single"), stat="identity") + 

 #  geom_violin(mapping= aes(x = `Total consecutive failures`, y = Scenario, fill = Scenario), draw_quantiles = c(.25, .5, .75)) +
    facet_grid(~Basin, scales = "free")+
  scale_fill_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
      scale_x_continuous(expand = c(0, 0), limits = c(0, 40)) +
  #scale_y_log10(limits = c(0.01, 1), breaks = c(0.01, 0.1, 0.2, 0.4, 0.6, 1.0))+    
  scale_y_discrete(drop = FALSE, expand = c(0, 0), limits = rev) +
 # scale_fill_manual(values = wes_palette("Zissou1", 33, type = "continuous"))+
   theme_bw(base_size=12)+
  
  xlab("Occurrence of failures (n)")+
  ylab(element_blank())+
        theme(legend.title = element_blank(),
    legend.position = "none",
    axis.text.x = element_text(angle = -90),
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank())+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Irrig_Recovery_Resiliency32.png", units ="in", width=12, height=6, res = 300)
```



```{r}
Irrigation4 <- Irrigation3 %>%
  mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ')) %>%
  group_by(Basin, WaterYear, Sequence, Scenario, Scenario2, Scenario3, Number, YearType) %>%
  dplyr::summarize(`Volumetric Reliability` = mean(`Volumetric Reliability`),
                   `Time Reliability` = mean(`Time Reliability`))
Irrigation4

Irrigation4$Basin <- factor(Irrigation4$Basin, levels = c("STN", "TUO", "MER", "USJ"))
```
```{r}
Irrigation5 <- Irrigation4 %>% 
  group_by(Basin, WaterYear, Scenario, Scenario2, Scenario3, YearType) %>%
  dplyr::summarize(`Volumetric Reliability` = mean(`Volumetric Reliability`),
                   `Time Reliability` = mean(`Time Reliability`))
Irrigation5
```

```{r}

 ggplot(Irrigation4)+# aes(Month, Total)) + 
  geom_rect(aes(color = NULL, fill = YearType, xmin = (as.numeric(WaterYear))-0.5, xmax = (as.numeric(WaterYear))+0.5, ymin = -Inf, ymax = Inf), alpha =0.025)+
    geom_line(aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`, color=Number), alpha = 0.65)+
  theme_bw(base_size=12)+ #, base_family='Volumetrics New Roman') + 
  scale_fill_manual(values = c("white", "lightblue"))+

  scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  
    scale_y_continuous(expand = c(0, 0), limits = c(0,102)) +
  scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+

  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="line", fun.y=mean, linetype = "dashed")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Volumetric Reliability (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +#center the title
png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Vol_Ag_July.png", units ="in", width=12, height=7, res = 300)
```

```{r}

 ggplot(Irrigation4)+# aes(Month, Total)) + 
  geom_rect(aes(color = NULL, fill = YearType, xmin = (as.numeric(WaterYear))-0.5, xmax = (as.numeric(WaterYear))+0.5, ymin = -Inf, ymax = Inf), alpha =0.025)+
    geom_line(aes(x=as.numeric(WaterYear), y = `Time Reliability`, color=Number), alpha = 0.65)+
  theme_bw(base_size=12)+ #, base_family='Volumetrics New Roman') + 
  scale_fill_manual(values = c("white", "lightblue"))+

  scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  
    scale_y_continuous(expand = c(0, 0), limits = c(0,102)) +
  scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Time Reliability`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+

  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Time Reliability`), geom="line", fun.y=mean, linetype = "dashed")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Time Reliability (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +#center the title
png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Time_Ag_Jul2.png", units ="in", width=12, height=7, res = 300)
```

```{r}

 ggplot(Irrigation4%>% filter(Scenario == "D5W1D5" | Scenario == "D5W2D5"))+# aes(Month, Total)) + 
  geom_rect(aes(color = NULL, fill = YearType, xmin = (as.numeric(WaterYear))-0.5, xmax = (as.numeric(WaterYear))+0.5, ymin = -Inf, ymax = Inf), alpha =0.025)+
    geom_line(aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`, color=Number), alpha = 0.65)+
  theme_bw(base_size=12)+ #, base_family='Volumetrics New Roman') + 
  scale_fill_manual(values = c("white", "lightblue"))+

  scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  
    scale_y_continuous(expand = c(0, 0), limits = c(0,102)) +
  scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+

  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="line", fun.y=mean, linetype = "dashed")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Volumetric Reliability (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +#center the title
png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Vol2_Ag_July.png", units ="in", width=7, height=5, res = 300)
```

```{r}

 ggplot(Irrigation4 %>% filter(Scenario == "D5W1D5" | Scenario == "D5W2D5"))+# aes(Month, Total)) + 
  geom_rect(aes(color = NULL, fill = YearType, xmin = (as.numeric(WaterYear))-0.5, xmax = (as.numeric(WaterYear))+0.5, ymin = -Inf, ymax = Inf), alpha =0.025)+
    geom_line(aes(x=as.numeric(WaterYear), y = `Time Reliability`, color=Number), alpha = 0.65)+
  theme_bw(base_size=12)+ #, base_family='Volumetrics New Roman') + 
  scale_fill_manual(values = c("white", "lightblue"))+

  scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  
    scale_y_continuous(expand = c(0, 0), limits = c(0,102)) +
  scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Time Reliability`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+

  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Time Reliability`), geom="line", fun.y=mean, linetype = "dashed")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Time Reliability (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +#center the title
png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Time2_Ag_Jul2.png", units ="in", width=7, height=5, res = 300)
```


```{r}

 ggplot(Irrigation4 %>% filter(Type == "Urban"))+# aes(Month, Total)) + 
  geom_rect(aes(color = NULL, fill = YearType, xmin = (as.numeric(WaterYear))-0.5, xmax = (as.numeric(WaterYear))+0.5, ymin = -Inf, ymax = Inf), alpha =0.025)+
    geom_line(aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`, color=Number), alpha = 0.65)+
  theme_bw(base_size=12)+ #, base_family='Volumetrics New Roman') + 
  scale_fill_manual(values = c("white", "lightblue"))+

    scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(-0.035, -0.035), limits = c(1,NA), breaks = c(1,3,5,7,9,11))+
  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+

  stat_summary(mapping = aes(x=as.numeric(WaterYear), y = `Volumetric Reliability`), geom="line", fun.y=mean, linetype = "dashed")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Volumetric Reliability (%)") + #name of x axis
  facet_grid(~Scenario, scales = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) +#center the title
png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Ag_May2023.png", units ="in", width=16, height=4, res = 300)
```


```{r}
Irrigation4 <- Irrigation3 %>%
#  mutate(Length = lenght(unique(WaterYear))
    group_by(Basin,Type, Sequence, Scenario) %>%
  summarise(`Annual Reliability` = (1-sum((`Failed Year`))/length(WaterYear))*100) %>%
  group_by(Basin,Type, Scenario) %>%
  summarize(`Mean Annual Reliability` = mean(`Annual Reliability`),
         `Min Annual Reliability`= min(`Annual Reliability`),
         `Max Annual Reliability`= max(`Annual Reliability`))
Irrigation4

write_csv(Irrigation4, "C:/Users/gusta/University of California Merced/WhiplashTotal_Deliveries_AnnualReliability_March2023.csv")

```

```{r}
Irrigation5 <- Irrigation3 %>% group_by(Basin, Scenario, WaterYear) %>%
  summarize(`Mean Volumetric Reliability` = ifelse(mean(`Volumetric Reliability`) > 100, 100, mean(`Volumetric Reliability`)),
            `Min Volumetric Reliability` = ifelse(min(`Volumetric Reliability`) > 100, 100, min(`Volumetric Reliability`)),
            `Max Volumetric Reliability` = ifelse(max(`Volumetric Reliability`) > 100, 100, max(`Volumetric Reliability`)),
            `Mean Volumetric Reliability` = mean(`Volumetric Reliability`),
            `Min Volumetric Reliability` = min(`Volumetric Reliability`), #ifelse(Basin=="stanislaus", (1-max(NonFailure)/245)*100, (1-max(NonFailure)/365)*100),
            `Max Volumetric Reliability` = max(`Volumetric Reliability`)) %>%#ifelse(Basin=="stanislaus", (1-min(NonFailure)/245)*100, (1-min(NonFailure)/365)*100),)
  group_by(Basin, Scenario) %>%
  summarize(`Mean Volumetric Reliability` = mean(`Mean Volumetric Reliability`),
            `Min Volumetric Reliability` = mean(`Min Volumetric Reliability`),
            `Max Volumetric Reliability` = mean(`Max Volumetric Reliability`),
            `Mean Volumetric Reliability` = mean(`Mean Volumetric Reliability`),
            `Min Volumetric Reliability` = mean(`Min Volumetric Reliability`), #ifelse(Basin=="stanislaus", (1-max(NonFailure)/245)*100, (1-max(NonFailure)/365)*100),
            `Max Volumetric Reliability` = mean(`Max Volumetric Reliability`))
Irrigation5
```



Irrigation3 %>%group_by(Basin, Type, Scenario, Sequence)   %>% count(WaterYear)


```{r}
#write_csv(Irrigation3 %>% filter(Basin == "upper_san_joaquin"), "C:/Users/gusta/University of California Merced/WhiplashTotal_Deliveries_Stats_USJ.csv")
write_csv(Irrigation5, "C:/Users/gusta/University of California Merced/WhiplashTotal_Deliveries_Stats_March2023_2.csv")
```

