
```{r}
library(readr)
library(dplyr)
library(lfstat)
library(tidyverse)
```


filenames <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-02-03/", recursive=TRUE)

# Find all .csv files
#files <- dir("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-12-14/merced/sequences/S0001_Y08_D2W1_N01/", recursive=TRUE, full.names=TRUE, pattern="//.csv$")
#filenames
# Apply the function to all files.
#result <- sapply(files, processFile)




MER_Hydro <- filenames %>%
  grep("D2W1D2", ., value = TRUE) %>%
  grep("merced", ., value = TRUE) %>%
  grep("Hydropower_Energy", ., value = TRUE)
MER_Hydro

```{r}
Mer_Tot_Hydro <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/merced/historical/Livneh/Hydropower_Energy_MWh.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))  %>%
  mutate(Total = rowSums(.[c(2:4)])) %>%  dplyr::select(1,5)
Mer_Tot_Hydro

Tuo_Tot_Hydro <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/tuolumne/historical/Livneh/Hydropower_Energy_MWh.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))  %>%
  mutate(Total = rowSums(.[c(2:5)])) %>%  dplyr::select(1,6)
Tuo_Tot_Hydro

Stn_Tot_Hydro <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/stanislaus/historical/Livneh/Hydropower_Energy_MWh.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".1"))  %>%
  mutate(Total = rowSums(.[c(2:12)])) %>%  dplyr::select(1,13)
Stn_Tot_Hydro

USJ_Tot_Hydro <- read.csv("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Energy Prices - 2023-02-07/upper_san_joaquin/historical/Livneh/Hydropower_Energy_MWh.csv")[-c(1,2),] %>%
  dplyr::select(., -contains(".PH.1"))  %>%
  mutate(Total = rowSums(.[c(2:17)])) %>%  dplyr::select(1,18)
USJ_Tot_Hydro
```
```{r}
tothydro <- rbind(Mer_Tot_Hydro %>% mutate(Basin = "MER"), 
                    Tuo_Tot_Hydro  %>% mutate(Basin = "TUO"), 
                    Stn_Tot_Hydro  %>% mutate(Basin = "STN"), 
                    USJ_Tot_Hydro  %>% mutate(Basin = "USJ")) %>%
  mutate(Month = format(as.Date(node), "%b"),
          Year = as.numeric(lfstat::water_year(node, origin = "usgs"))) %>%
  group_by(Basin, Year, Month) %>%
  summarize(Generation = mean(Total)) %>%
  mutate(Sequence = "whatever",
         Scenario = "whatever",
         Scenario2 = "whatever",
         Scenario3 = "whatever",
         YearType = "Historical (Livneh)")
tothydro



```

```{r}
mer <-mean(Mer_Tot_Hydro$Total)
tuo <- mean(Tuo_Tot_Hydro$Total)
stn <- mean(Stn_Tot_Hydro$Total)
usj <- mean(USJ_Tot_Hydro$Total) 

mer2 <-lapply(Mer_Tot_Hydro[-c(1)], mean, na.rm = T)
tuo2 <- lapply(Tuo_Tot_Hydro[-c(1)], mean, na.rm = T)
stn2 <- lapply(Stn_Tot_Hydro[-c(1)], mean, na.rm = T)
usj2 <- lapply(USJ_Tot_Hydro[-c(1)], mean, na.rm = T) 

```

```{r}

All <- list.files("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/", recursive=TRUE) %>%
 # grep("D2W1D2", ., value = TRUE) %>%
  #grep("merced", ., value = TRUE) %>%
  grep(#"Hydropower_Energy"
    "Hydropower_Energy_MWh", ., value = TRUE)

head(All)

#names_mer <- substr(Mer_D2W1D2,18,57)
#names_mer
```

```{r}
filelist <- lapply(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2023-03-13/",All,sep=""), read.csv)

#if necessary, assign names to data.frames
names(filelist) <- paste(All)

#note the invisible function keeps lapply from spitting out the data.frames to the console
```


```{r}
filelist2<- invisible(lapply(names(filelist), function(x) assign(x,filelist[[x]][-c(1,2),]%>% 
                                                                   mutate(Sequence = substr(str_split(names(filelist[x]), "/")[[1]][3], 1,5), 
                                                                          Scenario = paste(substr(str_split(names(filelist[x]), "/")[[1]][3], 11,14), substr(str_split(names(filelist[x]), "/")[[1]][3], 11,12), sep=""),
                                                                          Scenario2 = substr(str_split(names(filelist[x]), "/")[[1]][3], 11,12),
                                                                          Scenario3 = substr(str_split(names(filelist[x]), "/")[[1]][3], 13,14),
                                                                          Number = substr(str_split(names(filelist[x]), "/")[[1]][3], 16,20),
                                                                          Basin = str_split(names(filelist[x]),"/")[[1]][1]),envir=.GlobalEnv))) 
head(filelist2)
#D2_W1 <- read_csv(print("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/pywr_models/results/Whiplash - 2022-12-14/",MER_Hydro, sep=""))
#D2_W1
```


for (x in 1:800) {
names(filelist2[[x]])
}

```{r}
D2W1_Mer <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "merced"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:4)]))
D2W1_Mer

D2W1_Tuo <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "tuolumne"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:5)]))
D2W1_Tuo

D2W1_Stn <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "stanislaus"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains(".1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:12)]))
D2W1_Stn

D2W1_USJ <- filelist2 %>%
  lapply(., function(x) filter(x, Basin == "upper_san_joaquin"))%>%
  do.call("rbind", .) %>%
  dplyr::select(., -contains("PH.1")) %>%
  mutate(node = as.Date(node, "%Y-%m-%d"),
         Total = rowSums(.[c(2:17)]))
D2W1_USJ
```

ggplot(D2W1_Mer, aes(x = node, y = Total, color = Scenario)) + geom_line()



#ggplot(D2W1_Mer, x = node, y = Total) + geom_line()

#write.csv(D2W1_Mer, "Whiplash_Mer.csv")
write.csv(D2W1_Tuo, "Whiplash_Tuo.csv")
write.csv(D2W1_Stn, "Whiplash_Stn.csv")
write.csv(D2W1_USJ, "Whiplash_USJ_storage.csv")



#D2W1_Mer %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_Tuo %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_Stn %>% group_by(Scenario) %>% summarize(Total = mean(Total))
#D2W1_USJ %>% group_by(Scenario) %>% summarize(Total = mean(Total))


diff_Mer <- D2W1_Mer %>% mutate(`Relative Difference` = (Total - 990.2191077)/990.2191077*100, `Absolute Difference` = Total - 990.2191077) #%>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_Tuo <- D2W1_Tuo %>% mutate(`Relative Difference` = (Total - 6223.447953)/6223.447953*100, `Absolute Difference` = Total - 6223.447953) #%>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_Stn <- D2W1_Stn %>% mutate(`Relative Difference` = (Total - 4681.885331)/4681.885331*100, `Absolute Difference` = Total - 4681.885331)# %>% group_by(Scenario) %>% summarize(Total = mean(Total))
diff_USJ <- D2W1_USJ %>% mutate(`Relative Difference` = (Total - 12070.95512)/12070.95512*100, `Absolute Difference` = Total - 12070.95512)# %>% group_by(Scenario) %>% summarize(Total = mean(Total))

head(diff_Mer)


```{r}
#hydropower
Total_Mer <- D2W1_Mer %>% dplyr::select(node, Total, Basin, Scenario, Scenario2, Scenario3, Sequence, Number) %>% mutate(`Relative Difference` = (Total - mer)/mer*100, `Absolute Difference` = Total - mer) 
Total_Tuo <- D2W1_Tuo %>% dplyr::select(node, Total, Basin, Scenario, Scenario2, Scenario3, Sequence, Number) %>% mutate(`Relative Difference` = (Total - tuo)/tuo*100, `Absolute Difference` = Total - tuo) 
Total_Stn <- D2W1_Stn %>% dplyr::select(node, Total, Basin, Scenario, Scenario2, Scenario3, Sequence, Number) %>% mutate(`Relative Difference` = (Total - stn)/stn*100, `Absolute Difference` = Total - stn) 
Total_USJ <- D2W1_USJ %>% dplyr::select(node, Total, Basin, Scenario, Scenario2, Scenario3, Sequence, Number) %>% mutate(`Relative Difference` = (Total - usj)/usj*100, `Absolute Difference` = Total - usj) 

Total_Gen <- rbind(Total_Mer, Total_Tuo, Total_Stn, Total_USJ) %>%
  mutate(Month = as.Date(node, format = "%B/%Y"),#as.Date(cut(node,  breaks = "month")),
         Year = as.numeric(lfstat::water_year(node, origin = "usgs")),
         #Year = as.Date(cut(node, breaks = "year")),
         Scenario = as.factor(Scenario)) %>%
#    Month = as.factor(format(as.Date(node, format = "%B/%Y"), "%b/%Y")))%>%
 #        Year = water_year(node, origin = "usgs")) %>%
  group_by(Basin, Month, Year, Sequence, Number, Scenario, Scenario2, Scenario3) %>%
   dplyr::summarize(MonthlyTotal = sum(Total),
                    `Absolute Difference` = sum(`Absolute Difference`),
                    `Relative Difference` = mean(`Relative Difference`))# %>%
#  mutate(YearType = ifelse(.$Scenario == "D2W1D2" & .$Year == "2003", "Wet", "Dry"))
Total_Gen

Total_Gen$YearType <- ifelse(Total_Gen$Scenario == "D2W1D2" & Total_Gen$Year == "3", "Wet", 
ifelse(Total_Gen$Year == "3" & Total_Gen$Scenario == "D2W2D2", "Wet", 
       ifelse(Total_Gen$Year == "4" & Total_Gen$Scenario == "D2W2D2", "Wet",
       ifelse(Total_Gen$Scenario == "D3W1D3" & Total_Gen$Year == "4", "Wet",
ifelse(Total_Gen$Year == "4" & Total_Gen$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen$Year == "5" & Total_Gen$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen$Scenario == "D4W1D4" & Total_Gen$Year == "5", "Wet", 
ifelse(Total_Gen$Year == "5" & Total_Gen$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen$Year == "6" & Total_Gen$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen$Scenario == "D5W1D5" & Total_Gen$Year == "6", "Wet",
ifelse(Total_Gen$Year == "6" & Total_Gen$Scenario == "D5W2D5", "Wet",
       ifelse(Total_Gen$Year == "7" & Total_Gen$Scenario == "D5W2D5", "Wet","Dry"))))))))))))

Total_Gen_Year <- Total_Gen %>%
group_by(Basin, Year, Scenario, Scenario2, Scenario3, YearType) %>%
dplyr::summarize(`Annual Total` = sum(MonthlyTotal),
`Absolute Difference` = sum(`Absolute Difference`),
`Relative Difference` = mean(`Relative Difference`),
Change = ifelse(`Absolute Difference` < 0, "Negative", "Positive")) %>%
mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ'))
Total_Gen_Year

#Damn dates in "Year" column keep changing, check before running

Total_Gen_Year$YearType <- ifelse(Total_Gen_Year$Scenario == "D2W1D2" & Total_Gen_Year$Year == "2003", "Wet", 
ifelse(Total_Gen_Year$Year == "2003" & Total_Gen_Year$Scenario == "D2W2D2", "Wet", 
       ifelse(Total_Gen_Year$Year == "2004" & Total_Gen_Year$Scenario == "D2W2D2", "Wet",
       ifelse(Total_Gen_Year$Scenario == "D3W1D3" & Total_Gen_Year$Year == "2004", "Wet",
ifelse(Total_Gen_Year$Year == "2004" & Total_Gen_Year$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen_Year$Year == "2005" & Total_Gen_Year$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen_Year$Scenario == "D4W1D4" & Total_Gen_Year$Year == "2005", "Wet", 
ifelse(Total_Gen_Year$Year == "2005" & Total_Gen_Year$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen_Year$Year == "2006" & Total_Gen_Year$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen_Year$Scenario == "D5W1D5" & Total_Gen_Year$Year == "2006", "Wet",
ifelse(Total_Gen_Year$Year == "2006" & Total_Gen_Year$Scenario == "D5W2D5", "Wet",
       ifelse(Total_Gen_Year$Year == "2007" & Total_Gen_Year$Scenario == "D5W2D5", "Wet","Dry"))))))))))))

Total_Gen_Year2 <- Total_Gen %>%
  group_by(Basin, Year, Number, Scenario, Scenario2, Scenario3) %>%
   dplyr::summarize(`Annual Total` = sum(MonthlyTotal),
                    `Absolute Difference` = sum(`Absolute Difference`),
                    `Relative Difference` = mean(`Relative Difference`),
                    Change = ifelse(`Absolute Difference` < 0, "Negative", "Positive")) %>%
  mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
    mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
  mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
  mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ'))

Total_Gen_Year2

Total_Gen_Year2$YearType <- ifelse(Total_Gen_Year2$Scenario == "D2W1D2" & Total_Gen_Year2$Year == 3, "Wet", 
ifelse(Total_Gen_Year2$Year == 3 & Total_Gen_Year2$Scenario == "D2W2D2", "Wet", 
       ifelse(Total_Gen_Year2$Year == 4 & Total_Gen_Year2$Scenario == "D2W2D2", "Wet",
       ifelse(Total_Gen_Year2$Scenario == "D3W1D3" & Total_Gen_Year2$Year == 4, "Wet",
ifelse(Total_Gen_Year2$Year == 4 & Total_Gen_Year2$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen_Year2$Year == 5 & Total_Gen_Year2$Scenario == "D3W2D3", "Wet", 
       ifelse(Total_Gen_Year2$Scenario == "D4W1D4" & Total_Gen_Year2$Year == 5, "Wet", 
ifelse(Total_Gen_Year2$Year == 5 & Total_Gen_Year2$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen_Year2$Year == 6 & Total_Gen_Year2$Scenario == "D4W2D4", "Wet", 
       ifelse(Total_Gen_Year2$Scenario == "D5W1D5" & Total_Gen_Year2$Year == 6, "Wet",
ifelse(Total_Gen_Year2$Year == 6 & Total_Gen_Year2$Scenario == "D5W2D5", "Wet",
       ifelse(Total_Gen_Year2$Year == 7 & Total_Gen_Year2$Scenario == "D5W2D5", "Wet","Dry"))))))))))))


#replace(Total_Gen_Year$Basin == "merced", "Merced")
#Total_Gen_Year$Basin == "stanislaus" <- "Stanislaus"
#Total_Gen_Year$Basin == "tuolumne" <- "Tuolumne"
#Total_Gen_Year$Basin == "upper_san_joaquin" <- "Upper San Joaquin"

#storage <- rbind(tothydro, storage)

Total_Gen_Year$Basin <- factor(Total_Gen_Year$Basin, levels = c("STN", "TUO", "MER", "USJ"))
Total_Gen_Year2$Basin <- factor(Total_Gen_Year2$Basin, levels = c("STN", "TUO", "MER", "USJ"))

```

```{r}
Total_Gen_Year3 <- Total_Gen_Year2 %>%
  group_by(Basin, Year, Scenario, Scenario2, Scenario3) %>%
  mutate(`Mean Annual Total` = mean(`Annual Total`))
  
Total_Gen_Year3
```


 ggplot(Total_Gen)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_line(aes(x=as.Date(Month), y = MonthlyTotal/1000, color = Number))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(expand = c(0, 0))+
   scale_x_date(date_labels = "%b/%Y")+
  #scale_x_date(date_labels = "%b/%Y",
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_grid(Scenario~Basin, scales = "free")+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_March2023.png", units ="in", width=16, height=10, res = 300)


```{r}

 ggplot(Total_Gen_Year3, aes(x=as.numeric(Year), y = `Annual Total`/1000))+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_rect(aes(color = NULL, fill = YearType, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf), alpha = 0.020)+
  geom_line(aes(x=as.numeric(Year), y = `Annual Total`/1000, color=Number), alpha = 0.45)+
    stat_summary(geom="ribbon", fun.data=mean_cl_normal, width=0.1, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+
  stat_summary(geom="line", fun.y=mean, linetype="dashed")+
  #stat_summary(geom="point", fun.y=mean, color="red")+

 #   geom_line(aes(x=as.numeric(format(Year, "%Y"))-2000, y = as.numeric(`Mean Annual Total`/1000)), color = "black")+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
    scale_fill_manual(values = c("white", "lightblue"))+

#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(limits = c(0, NA), expand = c(0, 0))+
  # scale_x_date(date_labels = "%b/%Y")+
  scale_x_continuous(expand = c(0, 0), breaks = c(1,3,5,7,9,11))+
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free")+
  theme(legend.position = "none",
        strip.background = element_blank(),
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        axis.text.x = element_text(angle = -45, vjust=-0.4),
        plot.title = element_text(hjust = 0.5)) + #center the title
 # guides(colour = guide_legend(nrow = 1))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Annual_May.png", units ="in", width=12, height=7, res = 300)

```



 ggplot(Total_Gen_Year3)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
 # geom_rect(aes(color = NULL, fill = YearType, xmin = as.numeric(format(Year, "%Y"))-2000.5, xmax = as.numeric(format(Year, "%Y"))-1999.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  geom_boxplot(aes(x=as.factor(as.numeric(format(Year, "%Y"))-2000), y = `Annual Total`/1000))+
 #   geom_line(aes(x=as.numeric(format(Year, "%Y"))-2000, y = as.numeric(`Mean Annual Total`/1000)), color = "black")+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
    scale_fill_manual(values = c("white", "lightblue"))+

#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(limits = c(0, NA), expand = c(0, 0))+
  # scale_x_date(date_labels = "%b/%Y")+
  #scale_x_continuous(expand = c(0, 0), breaks = c(1,3,5,7,9,11))+
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
 # scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_grid(Basin~Scenario, Scenario2, Scenario3, scales = "free")+
  theme(legend.position = "none",
        strip.background = element_blank(),
        #legend.direction = "horizontal",
        #legend.box.margin = margin(t = -19),
        axis.text.x = element_text(angle = -45, vjust=-0.4),
        plot.title = element_text(hjust = 0.5)) + #center the title
 # guides(colour = guide_legend(nrow = 1))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Annual_March_2023_3.png", units ="in", width=18, height=10, res = 300)

```{r}
Total_Gen_Year_2 <- Total_Gen_Year2 %>%
  mutate(TotalYears = as.numeric(substr(Scenario, 2, 2))*2 + as.numeric(substr(Scenario, 4, 4)))
Total_Gen_Year_2
```


```{r}

 ggplot(Total_Gen_Year_2, aes(x=as.numeric(Year), color=Number))+# 
  
  geom_rect(aes(color = NULL, fill = YearType, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  geom_line(aes(y = (cumsum(`Annual Total`)/1000000)))+
    geom_line(aes(y = ((cumsum(`Annual Total`)/1000000)+(cumsum(`Absolute Difference`)/1000000))), linetype = "twodash")+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New 
    scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
  scale_fill_manual(values = c("white", "lightblue"))+

    scale_y_continuous(expand = c(0, 0)) +
  # scale_x_date(date_labels = "%b/%Y")+
  scale_x_continuous(expand = c(1, NA), breaks = c(1,3,5,7,9,11))+ #limits = c(2001,NA))+

  labs(title = element_blank(),
    x = "Whiplash Year (n)", 
       y = "Cummulative Hydropower Generation (TWh/Year)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
 # guides(colour = guide_legend(nrow = 1))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Annual_Difference_May3.png", units ="in", width=18, height=10, res = 300)

```



 ggplot(Total_Gen)+# aes(Month, Total)) + 
 # stat_summary(fun.y = sum, # adds up all observations for the week
  #  geom = "line") 
  geom_violin(aes(x=Year, y = MonthlyTotal/1000, fill=Scenario), draw_quantiles = c(.25, .5, .75))+
  theme_bw(base_size=12, base_family='Times New Roman') + #change font to Times New Roman, 12pt, Bold
# stat_summary(aes(x = Month, y = `New Exchequer PH`, colour = "#000000"), alpha = 0.9, fun = sum, geom = "line")+ #plot monthly observed data in greenish blue
 #stat_summary(aes(x = Month, y = `McSwain PH`, colour = "#56B4E9"), linetype = "dashed", alpha = 0.7, fun = sum, geom = "line")+
#plot monthly observed data in orange
#stat_summary(aes(x = Month, y = `Merced Falls PH`, colour = "#F0E442"), linetype = "dotdash", alpha = 0.7, fun = sum, geom = "line")+
    scale_y_continuous(expand = c(0, 0))+
   scale_x_discrete()+
  #scale_x_date(date_labels = "%b/%Y",
        #          breaks = c(as.Date("1980-10-01"), as.Date("1990-10-01"), as.Date("2000-10-01"), as.Date("2010-10-01")),
     #             expand = c(0, 0)) + #scale x axis by each 6 years and label it by month and year
  scale_color_manual(values=c("#313695", "#4575B4", "dodgerblue2",  "deepskyblue2", "cadetblue2", "gold1", "chocolate1", "#D73027","#A50026"))+#name = element_blank(),
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Hydropower Generation (GWh)") + #name of x axis
  facet_wrap(Scenario~Basin, scales = "free_x", ncol=4)+
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -19),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Violin.png", units ="in", width=16, height=10, res = 300)

```{r}
Total_Gen3 <- Total_Gen %>%
group_by(Basin, Year, Scenario, Scenario2, Scenario3, Number, YearType) %>%
dplyr::summarize(`Annual Total` = sum(MonthlyTotal),
`Absolute Difference` = sum(`Absolute Difference`),
`Relative Difference` = mean(`Relative Difference`),
Change = ifelse(`Absolute Difference` < 0, "Negative", "Positive")) %>%
mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ'))


Total_Gen3

Total_Gen3$Basin <- factor(Total_Gen3$Basin, levels = c("STN", "TUO", "MER", "USJ"))

```

```{r}

ggplot(Total_Gen3)+
  
 geom_rect(aes(color = NULL, fill = `YearType`, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  
  geom_line(aes(x = as.numeric(Year), y = `Relative Difference`, color = Number), alpha = 0.7) +
  
  geom_hline(yintercept=0, linetype="dashed", color = "red")+
  scale_color_manual(values = wes_palette("Zissou1", 25, type = "continuous"))+
      scale_fill_manual(values = c("white", "lightblue"))+

    theme_bw(base_size=12) +
    stat_summary(mapping = aes(x=as.numeric(Year), y = `Relative Difference`), geom="ribbon", fun.data=mean_cl_normal, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.8)+
  
  stat_summary(mapping = aes(x=as.numeric(Year), y = `Relative Difference`), geom="line", fun.y=mean, linetype = "dashed")+

  
    scale_y_continuous(expand = c(0, 0), breaks = c(-80, -40,0,40,80,120))+
   scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  #scale_x_date(date_labels = "%b/%Y",
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Relative Difference in Hydropower Generation (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free_x", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Line_May3.png", units ="in", width=12, height=7, res = 300)

```


```{r}

```

```{r}


Total_Gen2 <- Total_Gen[-c(5, 10,11)] %>%
  mutate(Generation = MonthlyTotal,
         Month = format(as.Date(Month), "%b")) %>%
mutate(Basin = replace(Basin, Basin == 'merced', 'MER')) %>%
mutate(Basin = replace(Basin, Basin == 'stanislaus', 'STN')) %>%
mutate(Basin = replace(Basin, Basin == 'tuolumne', 'TUO')) %>%
mutate(Basin = replace(Basin, Basin == 'upper_san_joaquin', 'USJ'))


Total_Gen2$YearType <- ifelse(Total_Gen2$Scenario == "D2W1D2" & Total_Gen2$Year == 3, "1st Wet Year", 
ifelse(Total_Gen2$Year == 3 & Total_Gen2$Scenario == "D2W2D2", "1st Wet Year", 
       ifelse(Total_Gen2$Year == 4 & Total_Gen2$Scenario == "D2W2D2", "2nd Wet Year",
       ifelse(Total_Gen2$Scenario == "D3W1D3" & Total_Gen2$Year == 4, "1st Wet Year",
ifelse(Total_Gen2$Year == 4 & Total_Gen2$Scenario == "D3W2D3", "1st Wet Year", 
       ifelse(Total_Gen2$Year == 5 & Total_Gen2$Scenario == "D3W2D3", "2nd Wet Year", 
       ifelse(Total_Gen2$Scenario == "D4W1D4" & Total_Gen2$Year == 5, "1st Wet Year", 
ifelse(Total_Gen2$Year == 5 & Total_Gen2$Scenario == "D4W2D4", "1st Wet Year", 
       ifelse(Total_Gen2$Year == 6 & Total_Gen2$Scenario == "D4W2D4", "2nd Wet Year", 
       ifelse(Total_Gen2$Scenario == "D5W1D5" & Total_Gen2$Year == 6, "1st Wet Year",
ifelse(Total_Gen2$Year == 6 & Total_Gen2$Scenario == "D5W2D5", "1st Wet Year",
       ifelse(Total_Gen2$Year == 7 & Total_Gen2$Scenario == "D5W2D5", "2nd Wet Year",
              
              ifelse(Total_Gen2$Scenario == "D2W1D2" & Total_Gen2$Year > 3, "2nd Drought", 
ifelse(Total_Gen2$Year > 3 & Total_Gen2$Scenario == "D2W2D2", "2nd Drought", 
       ifelse(Total_Gen2$Year > 4 & Total_Gen2$Scenario > "D2W2D2", "2nd Drought",
       ifelse(Total_Gen2$Scenario == "D3W1D3" & Total_Gen2$Year > 4, "2nd Drought",
ifelse(Total_Gen2$Year > 4 & Total_Gen2$Scenario == "D3W2D3", "2nd Drought", 
       ifelse(Total_Gen2$Year > 5 & Total_Gen2$Scenario == "D3W2D3", "2nd Drought", 
       ifelse(Total_Gen2$Scenario == "D4W1D4" & Total_Gen2$Year > 5, "2nd Drought", 
ifelse(Total_Gen2$Year > 5 & Total_Gen2$Scenario == "D4W2D4", "2nd Drought", 
       ifelse(Total_Gen2$Year > 6 & Total_Gen2$Scenario == "D4W2D4", "2nd Drought", 
       ifelse(Total_Gen2$Scenario == "D5W1D5" & Total_Gen2$Year > 6, "2nd Drought",
ifelse(Total_Gen2$Year > 6 & Total_Gen2$Scenario == "D5W2D5", "2nd Drought",
       ifelse(Total_Gen2$Year > 7 & Total_Gen2$Scenario == "D5W2D5", "2nd Drought",
              "1st Drought"))))))))))))))))))))))))


Total_Gen2 <- rbind(Total_Gen2, tothydro)
Total_Gen2

Total_Gen2$Basin <- factor(Total_Gen2$Basin, levels = c("STN", "TUO", "MER", "USJ"))

Total_Gen2$YearType <- factor(Total_Gen2$YearType, levels = c("Historical (Livneh)", "1st Drought", "2nd Drought", "1st Wet Year", "2nd Wet Year"))
```

```{r}
ggplot(Total_Gen2) + 
  theme_bw(base_size=12) + #change font to Times New Roman, 12pt, Bold
    geom_boxplot(aes( x = Month, y = Generation/1000, fill = YearType), outlier.alpha = 0.3) + #plot monthly observed data in greenish blue
  scale_fill_manual(values = c("darkgray","#F46D43","orange","cadetblue2", "dodgerblue2"))+
   #geom_line(aes(x = node, y = value)) +
    scale_y_continuous(labels = scales::comma, limits = c(0, NA),
                      expand = c(0, NA)) +
  scale_x_discrete(limits=c("Oct","Nov","Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")) +
  
    facet_wrap(~Basin, scales = "free_y", nrow = 2)+

  labs(x = element_blank(),
       y = "Hydropower Generation (GWh/month)") + #name of x axis
  theme(legend.title = element_blank(),
    legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box.margin = margin(t = -17),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        strip.placement = "outside",
        strip.background = element_blank(),
        panel.spacing.y = unit(0, "lines"))+
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Hydropower_Boxplots.png", units ="in", width=12, height=8, res = 300)

```


```{r}
write_csv(Total_Gen3, "Hydropower_whiplash_May2023.csv")

write_csv(Total_Gen2, "Hydropower_Whiplash_Avg_May2023.csv")
```


```{r}
Storage_Year_Mean <- Storage_Year %>% group_by(Basin, WaterYear, Scenario, Scenario2, Scenario3) %>%
  dplyr::summarize(`Relative Difference` = mean(`Relative Difference`),
                   Change = ifelse(`Relative Difference` < 0, "Negative", "Positive"),
`Annual Total` = mean(`Annual Total`),
YearType = YearType)
Storage_Year_Mean
```


```{r}

 ggplot(Total_Gen2)+
  
 geom_rect(aes(color = NULL, fill = `YearType`, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf), alpha = 0.5)+
  
  geom_bar(aes(x = as.numeric(Year), y = `Relative Difference`, fill = Change), 
           stat="identity", position="identity") + #plot monthly observed data in greenish blue
  
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  
      scale_fill_manual(values = c("white", "#DD8D29", "#46ACC8", "lightblue"))+

     #   geom_line(aes(color=Number, x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), alpha = 0.45)+
  
    #stat_summary( mapping =aes(x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), geom="ribbon", fun.data=mean_cl_normal, width=0.1, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+
  
  #stat_summary( mapping =aes(x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), geom="line", fun.y=mean, linetype = "dashed")+

    theme_bw(base_size=12, base_family='Times New Roman') +
  
    scale_y_continuous(expand = c(0, 0), breaks = c(-100,-80, -60, -40,-20,0,20,40,60,80,100,120))+
   scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  #scale_x_date(date_labels = "%b/%Y",
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Relative Difference in Hydropower Generation (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free_x", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Ba3r_May2.png", units ="in", width=12, height=7, res = 300)

```

```{r}
Generation_Year_Mean <- Total_Gen_Year2 %>% group_by(Basin, Year, Scenario, Scenario2, Scenario3) %>%
  dplyr::summarize(`Relative Difference` = mean(`Relative Difference`),
                   Change = ifelse(`Relative Difference` < 0, "Negative", "Positive"),
`Annual Total` = mean(`Annual Total`),
YearType = YearType)
Generation_Year_Mean
```

```{r}

 ggplot(Generation_Year_Mean%>% filter(Scenario == "D5W1D5" | Scenario == "D5W2D5"))+
  
 geom_rect(aes(color = NULL, fill = `YearType`, xmin = as.numeric(Year)-0.5, xmax = as.numeric(Year)+0.5, ymin = -Inf, ymax = Inf), alpha = 0.025)+
  
  geom_bar(aes(x = as.numeric(Year), y = `Relative Difference`, fill = Change), 
           stat="identity", position="identity") + #plot monthly observed data in greenish blue
  
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  
      scale_fill_manual(values = c("white", "#DD8D29", "#46ACC8", "lightblue"))+

    theme_bw(base_size=12, base_family='Times New Roman') +
  
    scale_y_continuous(expand = c(0, 0), breaks = c(-60,-40, -20,0,20,40,60,80, 120))+
   scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  #scale_x_date(date_labels = "%b/%Y",
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Relative Difference in Hydropower Generation (%)") + #name of x axis
  facet_grid(Basin~Scenario3+Scenario2, scales = "free_x", space = "free")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Ba3r_May22.png", units ="in", width=7, height=5, res = 300)

```

```{r}

 ggplot(Total_Gen2)+
  
 geom_rect(aes(color = NULL, fill = `YearType`, xmin = as.numeric(format(Year, "%Y"))-2000.5, xmax = as.numeric(format(Year, "%Y"))-1999.5, ymin = -Inf, ymax = Inf), alpha = 0.5)+
  
  geom_bar(aes(x = as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`, fill = Change), 
           stat="identity", position="identity") + #plot monthly observed data in greenish blue
  
  geom_hline(yintercept=0, linetype="dashed", color = "black")+
  
      scale_fill_manual(values = c("white", "red", "blue", "lightblue"))+

     #   geom_line(aes(color=Number, x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), alpha = 0.45)+
  
    #stat_summary( mapping =aes(x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), geom="ribbon", fun.data=mean_cl_normal, width=0.1, fun.args=list(conf.int=0.95), fill="darkgray", alpha = 0.65)+
  
  #stat_summary( mapping =aes(x=as.numeric(format(Year, "%Y"))-2000, y = `Relative Difference`), geom="line", fun.y=mean, linetype = "dashed")+

    theme_bw(base_size=12, base_family='Times New Roman') +
  
    scale_y_continuous(expand = c(0, 0), breaks = c(-100,-80, -60, -40,-20,0,20,40,60,80,100,120))+
   scale_x_continuous(expand = c(-0.035, -0.035), breaks = c(1,3,5,7,9,11))+
  #scale_x_date(date_labels = "%b/%Y",
                     #    breaks = c("#000000", "#56B4E9", "#F0E442"), #dplyr::select the color
                      #    labels = c("New Exchequer PH","McSwain PH", "Merced Falls PH"), #dplyr::select the variables
                        #  guide = "legend")+
  labs(title = element_blank(),
    x = element_blank(), 
       y = "Relative Difference in Hydropower Generation (%)") + #name of x axis
  facet_grid(Basin~Scenario, Scenario2, Scenario3, scales = "free_x")+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = -45),
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5)) + #center the title
  png("C:/Users/gusta/Desktop/PhD/Classes/ES207/Sequences_Generation_Line_May.png", units ="in", width=16, height=10, res = 300)

```
