```{r}
library(dismo)
library(sdmpredictors)
library(raster)
library(dplyr)
library(rgdal)
```


myraster=raster("C:/Users/gusta/Downloads/hydgrp_int.tif")
projection(myraster)

ca <- readOGR("C:/Users/gusta/Documents/CA_State_TIGER2016.shp") %>% #ca boundary.shp")%>%
  spTransform(CRS(projection(myraster)))



myraster2 <- crop(myraster, ca) 
myraster2 <- mask(myraster2, ca)  
plot(myraster2)




hydro_poly <- rasterToPolygons(myraster2)
#Range of variables is here: hydro_poly@data$hydgrp_int




```{r}
ca_crops <- readOGR("C:/Users/gusta/Documents/i15_Crop_Mapping_2021_Provisional.shp")%>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ca_crops

ca_crops2 <- readOGR("C:/Users/gusta/Documents/i15_Crop_Mapping_2020.shp")%>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ca_crops2
```

ca_crops3 <- readOGR("C:/Users/gusta/Documents/i15_Crop_Mapping_2019.shp")%>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ca_crops3

ca_crops4 <- readOGR("C:/Users/gusta/Documents/i15_Crop_Mapping_2018.shp")%>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ca_crops4

ca_crops5 <- readOGR("C:/Users/gusta/Documents/i15_Crop_Mapping_2016.shp")%>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ca_crops5

```{r}
wine_grapes <- subset(ca_crops, CROPTYP2 == "V")

plot(wine_grapes)

wine_grapes2 <- subset(ca_crops2, CROPTYP2 == "V")

plot(wine_grapes2)
```

wine_grapes3 <- subset(ca_crops3, CROPTYP2 == "V2")

plot(wine_grapes3)

wine_grapes3 <- subset(ca_crops4, CROPTYP2 == "V2")

plot(wine_grapes3)

wine_grapes3 <- subset(ca_crops5, CROPTYP2 == "V2")

plot(wine_grapes3)


```{r}
vinifera <- gbif("Vitis", "vinifera", download = T, geo = T, sp = F)
vinifera

class(vinifera)

is.na(vinifera$lon)

head(vinifera)
```

```{r}
vinhas <- vinifera %>% filter(country == "United States") 
vinhas


WA <- sf::st_read("C:/Users/gusta/Downloads/WA.gdb")
CA <- sf::st_read("C:/Users/gusta/Downloads/CA.gdb")
OR <- sf::st_read("C:/Users/gusta/Downloads/OR.gdb")



pacific <- readOGR("C:/Users/gusta/Documents/PacificCoast.shp")

AVAs <- readOGR("C:/Users/gusta/Documents/All_AVAs.shp")

w <- which(is.na(vinhas$lon))
sp <- vinhas[-w,]
sp$species <- 1
sp <- sp[,c('lon', 'lat', 'species')]
coordinates(sp) <- ~lon + lat

class(sp)
projection(sp) <- projection(AVAs)

vine <- crop(sp, AVAs, inverse = F) 

plot(vine)

writeOGR(vine, ".", "AVAs_vines", 
          driver = "ESRI Shapefile") #also you were missing the driver argument

#x <- SpatialPointsDataFrame(samplepoints, data.frame(row.names=row.names(samplepoints),
#                                          ID=1:length(samplepoints)))
#class(x)

#writeOGR(x, ".", "Sample_US", 
#          driver = "ESRI Shapefile") #also you were missing the driver argument
```

```{r}
bio <- raster::getData('worldclim', var = 'bio', res = 2.5)#,  lon=-129, lat=37)
bio

alt <- raster::getData('alt', country='USA', res = 0.5)#,  lon=-119, lat=37)
alt

alt2 <- alt$`C:/Users/gusta/Desktop/PhD/Classes/ES207/USA1_msk_alt.grd`

SlopeAspect <- raster::terrain(alt2, opt=c('slope', 'aspect'), unit='degrees')

terrain <- addLayer(SlopeAspect,alt2)
#BIO1 = Annual Mean Temperature
#BIO2 = Mean Diurnal Range (Mean of monthly (max temp - min temp))
#BIO3 = Isothermality (BIO2/BIO7) (×100)
#BIO4 = Temperature Seasonality (standard deviation ×100)
#BIO5 = Max Temperature of Warmest Month
#BIO6 = Min Temperature of Coldest Month
#IO7 = Temperature Annual Range (BIO5-BIO6)
#BIO8 = Mean Temperature of Wettest Quarter
#BIO9 = Mean Temperature of Driest Quarter
#BIO10 = Mean Temperature of Warmest Quarter
#BIO11 = Mean Temperature of Coldest Quarter
#BIO12 = Annual Precipitation
#BIO13 = Precipitation of Wettest Month
#BIO14 = Precipitation of Driest Month
#BIO15 = Precipitation Seasonality (Coefficient of Variation)
#BIO16 = Precipitation of Wettest Quarter
#BIO17 = Precipitation of Driest Quarter
#BIO18 = Precipitation of Warmest Quarter
#BIO19 = Precipitation of Coldest Quarter
```

```{r}
library(usdm)

#variance inflation factor (VIF) to test multi-collinearity
v1 <- vifstep(bio)

v2 <- vifcor(bio, th = 0.7) #th = Pearson’s correlation coefficient (r) threshold

v1
v2
```

```{r}

biom <- exclude(bio, v1) #removing collinear variables 
biom

plot(biom[[1]])
points(vine, cex = 0.5, pch = 16)

```
```{r}
#read in soil data from Davis

#first import all files in a single folder as a list 
rastlist <- list.files(path = "C:/Users/gusta/University of California Merced/Winegrapes/SoilData", pattern='.tif$', all.files=TRUE, full.names=TRUE)
rastlist
#library(raster)

# Open your reference Raster

#Reference_Raster <- raster("C:/Users/gusta/University of California Merced/Winegrapes/SoilData/ph.tif")


allrasters <- stack(rastlist)

```
```{r}
allrasters2 <- allrasters

allrasters2 <- raster::projectRaster(allrasters2, 
                                       crs=crs(biom))

d2 <- sdm::sdmData(species~., vine, predictors = allrasters2, bg = list(n=1000))
d2

m3 <- sdm(species~., d2, methods = 'rf', replication = c('boot'), n = 100)
#), replication = c('boot'), n = 2)
m3

d3 <- sdm::sdmData(species~., vine, predictors = terrain, bg = list(n=1000))
d3

m4 <- sdm(species~., d3, methods = 'rf', replication = c('boot'), n = 100)
#), replication = c('boot'), n = 2)
m4

```


```{r}
library(sdm)

samplepoints <- sp::spsample(AVAs,n=1000,"random", iter=10)



#d2 <- sdm::sdmData(species~., AVAs, predictors = biom, bg = list(n=1000))


d <- sdm::sdmData(species~., vine, predictors = biom, bg = list(n=1000))
d


m2 <- sdm(species~., d, methods = c('fda','bioclim', 'bioclim.dismo', 'brt', 'CART', 'domainDismo', 'mahal.dismo', 'mars', 'rbf', 'rf', 'svm', 'glm','glmnet','maxlike','rpart','glmpoly', 'gam', 'maxent'), replication = c('boot'), n = 100)
#), replication = c('boot'), n = 2)
m2
sdm::gui(m2)
```


```{r}
p <- sdm:: predict(m, biom, 'predictions.img',overwrite=TRUE)

en <- ensemble(m, biom, setting = list(method= 'weighted', stat = "TSS", opt = 2))
writeRaster(en, filename="ensemble.tif", format="GTiff", overwrite=TRUE) 

```

```{r}
biof <- raster::getData('CMIP5', var = "bio", res = 10, rcp = 85, year = 50, model = c("MC"))#"AC", "CC", "CN", "GF", "HG", "HE", "MC"))
biof

v3 <- vifstep(biof)
v3

biomf <- exclude(biof, v3)
biomf


soil_filtered <- vifstep(allrasters2)
soil_filtered

names(biomf)
names(biomf)

names(biomf) <- names(biomf)

pf <- raster::predict(m, biomf)

writeRaster(pf[[3]], filename="predictionsf.tif", format="GTiff", overwrite=TRUE) 


#enf <- calc(pf, mean) #unweighted average

enf <- ensemble(m, biomf, setting = list(method= 'weighted', stat = "TSS", opt = 2))
writeRaster(enf, filename="ensemblef.tif", format="GTiff", overwrite=TRUE) 


```
```{r}
library(mapview)
library(proj4)


plot(stack(en,enf))
mapview::mapView(stack(en,enf))
```


```{r}
#probability of occurrence to show extinction or colonization (based on absence/presence)
ev <- getEvaluation(m, stat = c('AUC', 'TSS', 'threshold'), opt = 2)
mean <- mean(ev$threshol)

pa <- raster(en)
pa[] <- ifelse(en[] >= mean, 1, 0)

plot(pa)

paf <- raster(enf)
paf[] <- ifelse(enf[] >= mean, 1, 0)

plot(paf)

pac <- paf - pa 
cl <- colorRampPalette(c('chocolate2', 'gray90','springgreen3'))
plot(pac, col = cl(3))
```


```{r}
#response curve
#The output of rcurve shows species response to different values of environmental conditions, so they can show the range suitable for species.

rcurve(m)



```