
library(data.table)
library(purrr)
library(dplyr)
library(lubridate)
library(tidyverse)



number <- c("sb01", "sb02", "sb03", "sb04" ,"sb05", "sb06")#, "sb07", "sb08", "sb09", "sb10" ,"sb11", "sb12", "sb13", "sb14", "sb15", "sb16" ,"sb17", "sb18", "sb19", "sb20", "sb21", "sb22" ,"sb23", "sb24", "sb25")#, "sb26", "sb27", "sb28" ,"sb29", "sb30", "sb31", "sb32", "sb33", "sb34" ,"sb35", "sb36", "sb37", "sb38")
rcp <- "rcp85"
GCMs <- c("CMCC-CMS", "ACCESS1-0", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "CESM1-BGC")
basin <- "Stanislaus River"
basin2 <- "STNR"
for(GCM in GCMs){
for (i in number) {
csv <- read_csv(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/bias correction/",basin2,"/Catchment_RO_BC/",GCM,"_",rcp,"/tot_runoff_",i,".csv", sep = ""))
csv


#Shp_file <- raster::shapefile("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/common/hydrology/Shapefiles/Mer.shp")

#Shp_file$SUBWAT <- gsub("^.{0,4}", "sb", Shp_file$SUBWAT) #switch names in the attribute table of the shp file
#Shp_file$AREA <- area(Shp_file)

csv$flow <- (csv$flow*86400)/1000000
csv

csv_path <- paste0("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/",basin,"/hydrology/gcms/",GCM,"_",rcp,"/runoff")
#if the directory doesn't exist, make it!
if (!dir.exists(csv_path)){
  dir.create(file.path(csv_path), recursive = TRUE)
}
  
write.csv(csv,file= paste(csv_path,"/","tot_runoff_", i,"_mcm.csv", sep = ""), row.names=F)}
}



```{r}


rcp <- "rcp85"
GCM <- "ACCESS1-0"
basin <- "Upper San Joaquin River"
#GCMs<- c("CMCC-CMS", "ACCESS1-0", "GFDL-CM3", "CCSM4", "HadGEM2-CC", "CESM1-BGC")
#for(GCM in GCMs){


#McClure_path <- paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/",basin,"/hydrology/gcms/",GCM,"_",rcp,"/runoff/")

temp <- list.files(paste("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/",basin,"/hydrology/gcms/",GCM,"_",rcp,"/runoff/", sep =""), "\\.csv$", full.names = TRUE)
temp

myfiles <- lapply(temp, read_csv)

myfiles
```

```{r}
temp %>%
  map(., fread, select = 'flow') %>%
      bind_cols %>%
  mutate(Total = rowSums(.))

total_flow <- temp %>%
  map(., fread, select = 'flow') %>%
      bind_cols %>%
  mutate(Total = rowSums(.),
         Date = as.Date(myfiles[[1]]$Date, format = "%Y-%m-%d")) %>%
  dplyr::select(Date, Total) %>%
  rename(flow = Total)
total_flow


```

```{r}
total_monthly <- total_flow %>%
   mutate(month = month(Date),
          year = year(Date)) %>%
  dplyr::select(month, year, flow) %>%
  group_by(year, month) %>%
  summarise(flow = sum(flow)) 


total_monthly$Date <- ymd(paste(total_monthly$year,'-',total_monthly$month,"-01", sep = ""))
total_monthly$year <- NULL
total_monthly$month <- NULL
total_monthly

total_WY <- total_flow %>%
  mutate(WY = lfstat::water_year(.$Date),
         Date = NULL) %>%
   dplyr::select(WY, flow) %>%
  group_by(WY) %>%
  summarise(flow = sum(flow))
total_WY
```           

```{r}
#Lakename <- "Lake McClure Inflow mcm.csv"
Lakename2 <- "full_natural_flow_daily_mcm.csv"
Lakename3 <- "full_natural_flow_monthly_mcm.csv"
Lakename4 <- "full_natural_flow_annual_mcm.csv"

#csv_path2 <- paste0("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/",basin,"/hydrology/gcms/",GCM,"_",rcp,"/runoff_aggregated/")
#if the directory doesn't exist, make it!
#if (!dir.exists(csv_path2)){
#  dir.create(file.path(csv_path2), recursive = TRUE)
#}
  
#write.csv(total_flow,file= paste(csv_path2,"/",Lakename,".csv", sep = ""), row.names=F)

csv_path3 <- paste0("C:/Users/gusta/Box/VICE Lab/RESEARCH/PROJECTS/CERC-WET/Task7_San_Joaquin_Model/Pywr models/data/",basin,"/hydrology/gcms/",GCM,"_",rcp,"/preprocessed/")
#if the directory doesn't exist, make it!
if (!dir.exists(csv_path3)){
  dir.create(file.path(csv_path3), recursive = TRUE)
}
  
write.csv(total_flow,file= paste(csv_path3,"/",Lakename2,".csv", sep = ""), row.names=F)
write.csv(total_monthly,file= paste(csv_path3,"/",Lakename3,".csv", sep = ""), row.names=F)
write.csv(total_WY,file= paste(csv_path3,"/",Lakename4,".csv", sep = ""), row.names=F)
```